### 2021-03-23 Article.Rmd
Creation of the Rmd file

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Corresponding author at : General Practice Department - Primary Care and Health Research Unit, MD - PhD student,  University of Liège, Liège, Belgium <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, research assistant, University of Liège, Liège, Belgium <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, lecturer, University of Liège, Liège, Belgium <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^ General Practice Department - Primary Care and Health Research Unit, Postdoctoral Researcher,  University of Liège, Liège, Belgium <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
output: 
  bookdown::word_document2:
    reference_docx: "article_template.docx"
bibliography: library.bib
csl: bmj.csl

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### 2021-03-23 Article.Rmd
Updating references.bib and uploading PRISMA.png

@@
     reference_docx: "article_template.docx"
-bibliography: library.bib
 csl: bmj.csl
-
+bibliography: references.bib
 ---
@@
 ```
+
+# Results
+
+## Literature search
+
+![](Files/images/PRISMA.png)

### 2021-03-23 Article.Rmd
Bookdown

--- 2021-03-23 Article.Rmd
@@
     reference_docx: "article_template.docx"
-bibliography: library.bib
 csl: bmj.csl
-
+bibliography: references.bib
+link-citations: true
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+library(bookdown)
 ```
+
+# Results
+
+## Literature search
+
+You can find the complete flowchart in Figure \@ref(fig:PRISMA)
+
+```{r PRISMA, fig.cap = "PRISMA flowchart of the included search strategy"}
+knitr::include_graphics("Files/images/PRISMA.png")
+
+```
+
+## How are studies concerning Syndemic Theory applied to MSM conducted?
+
+### General characteristics of included studies
+
+### Subpopulations studied
+
+### Syndemic conditions and their measurement
+
+### Outcomes and their measurement
+
+### Interventions
+
+## How is the concept of interaction explored in syndemic research applied to MSM?
+
+### Statistics used to show an interaction
+
+### Proposed mechanisms of interaction
+
+## What were the key findings of these studies?
+
+# Discussion
+
+# Conclusion

### 2021-03-24 Article.Rmd
Literature search and preparation of data for general characteristics

@@
 
-You can find the complete flowchart in Figure \@ref(fig:PRISMA)
+The electronic search identified 769 citations and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
+After duplicates removal, 277 unique references were left to be screened for inclusion.
+
+Among these references, 109 were excluded after reading the title and abstract.
+The two main reasons for exclusion at this stage were that MSM were not the main population of the study (n=46) or that syndemic was not the main focus of the paper (n=34).
+29 additional studies were excluded because the type of publication did not meet our inclusion criteria.
+
+The full texts of the 168 remaining references were obtained and read, which lead to the exclusion of 59 citations.
+During the previous step, we decided to include papers in which the sample was not entirely comprised of MSM.
+After reading the full paper, we opted to exclude the studies if the MSM data was aggregated with data from another population (n=9), most commonly transgender women.
+The rationale for this decision was to keep the focus clearly on MSM.
+
+The PRISMA flowchart generated by DistillerSR can be found in Figure \@ref(fig:PRISMA)
 
@@
 ### General characteristics of included studies
+
+```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+source("./scripts/read_overview.R", local = knitr::knit_global())
+source("./scripts/create_year_data.R", local = knitr::knit_global())
+source("./scripts/create_design_data.R", local = knitr::knit_global())
+source("./scripts/create_location_data.R", local = knitr::knit_global())
+
+```
 
@@
 # Conclusion
+
+# References
+
+::: {#refs}
+:::

### 2021-03-24 Scripts/create_design_data.R

@@ -1,0 +1,6 @@
+library(tidyverse)
+design_data <- overview_of_studies %>%
+  select(design) %>%
+  group_by(design) %>%
+  summarise(Studies = n()) %>% 
+  ungroup()

### 2021-03-24 Scripts/create_location_data.R

@@ -1,0 +1,6 @@
+library(tidyverse)
+location_data <- overview_of_studies %>%
+  select(location) %>%
+  group_by(location) %>%
+  summarise(Studies = n()) %>% 
+  ungroup()

### 2021-03-24 Scripts/create_year_data.R

@@ -1,0 +1,7 @@
+library(tidyverse)
+year_data <- overview_of_studies %>%
+  select(year) %>%
+  group_by(year) %>%
+  summarise(Studies = n()) %>% 
+  ungroup() %>%
+  mutate(Cumulative = cumsum(Studies))

### 2021-03-24 Scripts/read_overview.R

@@ -1,0 +1,3 @@
+library(readr)
+overview_of_studies <- read_csv("Data/overview_of_studies.csv", 
+                                col_types = cols(X6 = col_skip()))

### 2021-03-29 Article.Rmd
Literature search
Updating scripts and Article.Rmd for better readability

@@
 
+knitr::knit_exit()
+
 ```
@@
 ```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+#Load required packages :
+library(tidyverse)
+library(readr)
+
+#Load the data from the .csv files
 source("./scripts/read_overview.R", local = knitr::knit_global())
+
+#Source the scripts used to manipulate the data from the .csv files
 source("./scripts/create_year_data.R", local = knitr::knit_global())

### 2021-03-29 Scripts/create_design_data.R

@@ -1,4 +1,3 @@
-library(tidyverse)
 design_data <- overview_of_studies %>%
   select(design) %>%
   group_by(design) %>%

### 2021-03-29 Scripts/create_location_data.R

@@ -1,4 +1,3 @@
-library(tidyverse)
 location_data <- overview_of_studies %>%
   select(location) %>%
   group_by(location) %>%

### 2021-03-29 Scripts/create_year_data.R

@@ -1,4 +1,3 @@
-library(tidyverse)
 year_data <- overview_of_studies %>%
   select(year) %>%
   group_by(year) %>%

### 2021-03-29 Scripts/read_overview.R

@@ -1,3 +1,2 @@
-library(readr)
 overview_of_studies <- read_csv("Data/overview_of_studies.csv", 
                                 col_types = cols(X6 = col_skip()))

### 2021-04-14 Article.Rmd
Data manipulation and vizualisation of year, design and location of studies

@@
 
-knitr::knit_exit()
-
 ```
@@
 library(readr)
+library(scales)
+library(ggplot2)
+library(ggpubr)
 
@@
 #Source the scripts used to manipulate the data from the .csv files
-source("./scripts/create_year_data.R", local = knitr::knit_global())
+source("./scripts/create_year_design.R", local = knitr::knit_global())
 source("./scripts/create_design_data.R", local = knitr::knit_global())
 source("./scripts/create_location_data.R", local = knitr::knit_global())
+source("./scripts/create_sample.R", local = knitr::knit_global())
+
+#Create the plot 
+source("./scripts/create_plot_year.R", local = knitr::knit_global())
 
 ```
+
+The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in \@ref(fig:PlotYear).
+
+```{r PlotYear, fig.cap = "Plot of the cumulative number of studies published yearly, grouped by continent (A) and design (B)"}
+
+knitr::include_graphics("./Output/Plots/Plot_Year.png")
+
+```
+
+Out of the 104 quantitative and qualitative studies included, most were conducted in North America (N = `r North_America_studies`), with a large predominance of studies in the United States of America (N= `r max(year_country$cumulative_location[year_country$location == "USA"])`).
+The majority of the remaining studies were then located in Asia (N = `r Asia_studies`) or in Europe (N = `r Europe_studies`).
+South America and Africa were the least represented continents, with only `r South_America_studies` and `r Africa_studies` studies respectively.
 

### 2021-04-14 Scripts/create_location_data.R

@@ -1,5 +1,37 @@
-location_data <- overview_of_studies %>%
-  select(location) %>%
+year_country <- overview_of_studies %>%
+  select(year, location) %>%
+  group_by(year, location) %>%
+  summarise(studies_location = n()) %>% 
+  ungroup() %>%
+  drop_na() %>%
   group_by(location) %>%
-  summarise(Studies = n()) %>% 
-  ungroup()
+  mutate(cumulative_location = cumsum(studies_location))
+
+year_continent <- overview_of_studies %>%
+  select(year, location) %>%
+  drop_na()
+year_continent$continent <- ifelse(grepl(c("USA|Canada"), year_continent$location), "North America", 
+ifelse(grepl(c("China|India|Malaysia|Taiwan|Thailand|Vietnam"), year_continent$location), "Asia", 
+ifelse(grepl(c("Belgium|England|Netherlands|Portugal|Sweden"), year_continent$location), "Europe",
+ifelse(grepl(c("Latin America|Mexico"), year_continent$location), "South America", 
+ifelse(grepl(c("Nigeria|South Africa"), year_continent$location), "Africa", "International"
+       ))))) 
+year_continent <- year_continent%>%
+  group_by(year, continent) %>%
+  summarise(studies_continent = n()) %>%
+  ungroup() %>%
+  group_by(continent) %>%
+  mutate(cumulative_continent = cumsum(studies_continent))
+
+
+
+
+North_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "North America"])
+
+Asia_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Asia"])
+
+Europe_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Europe"])
+
+South_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "South America"])
+
+Africa_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Africa"])

### 2021-04-14 Scripts/create_plot_year.R

@@ -1,0 +1,55 @@
+plot_year_design <- year_design %>%
+  ggplot() +
+  scale_fill_brewer(palette="Set2")+
+  geom_line(aes(x=year, y = cumulative, color = design), size = 1, alpha = .5) +
+  geom_point(aes(x=year, y = cumulative, color = design), size = 1) +
+  scale_x_continuous(name = "Year of publication", 
+                     breaks = seq(2003, 2021, by = 2), 
+                     minor_breaks = c(2003:2021)) +
+  scale_y_continuous(name ="Cumulative number of studies", 
+                     breaks = seq(0, 75, by = 10), 
+                     minor_breaks = seq(0, 75, by = 5)) +
+  ggtitle("B. Studies, by design and year of publication") +
+  theme(
+    axis.text.x = element_text(size=8),
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.title.x = element_text(size = 9, face = "italic"),
+    axis.title.y = element_text(size = 9, face = "italic")
+  )
+
+plot_year_continent <- year_continent %>%
+  ggplot() +
+  scale_fill_brewer(palette="Set2")+
+  geom_line(aes(x=year, y = cumulative_continent, color = continent), size = 1, alpha = .5) +
+  geom_point(aes(x=year, y = cumulative_continent, color = continent), size = 1) +
+  scale_x_continuous(name = "Year of publication", 
+                     breaks = seq(2003, 2021, by = 2), 
+                     minor_breaks = c(2003:2021)) +
+  scale_y_continuous(name ="Cumulative number of studies", 
+                     breaks = seq(0, 75, by = 10), 
+                     minor_breaks = seq(0, 75, by = 5)) +
+  ggtitle("A. Studies, by continent and year of publication") +
+  theme(
+    axis.text.x = element_text(size=8),
+    plot.title = element_text(size = 10, face = "bold"),
+    axis.title.x = element_text(size = 9, face = "italic"),
+    axis.title.y = element_text(size = 9, face = "italic")
+  )
+
+
+plot_year <- ggarrange(plot_year_continent, plot_year_design,
+                       ncol = 1, 
+                       nrow = 2,
+                       common.legend = F, 
+                       legend = "bottom")
+
+ggsave(
+  "./Output/Plots/Plot_Year.png",
+  plot = plot_year,
+  width = 140,
+  height = 178,
+  unit = "mm",
+  dpi = 300,
+  scale = 1,
+  limitsize = F
+)

### 2021-04-14 Scripts/create_sample.R

@@ -1,0 +1,12 @@
+summary_qualitative <- read_csv("Data/summary_qualitative.csv", 
+                                col_types = cols(X23 = col_skip()))
+summary_quantitative <- read_csv("Data/summary_quantitative.csv")
+
+sample_qualitative <- summary_qualitative %>%
+  select(sample_size, age) 
+
+sample_quantitative <- summary_quantitative %>%
+  select(sample_size, age)
+  
+sample <- rbind(sample_qualitative,
+                     sample_quantitative)

### 2021-04-14 Scripts/create_year_data.R

@@ -1,6 +1,0 @@
-year_data <- overview_of_studies %>%
-  select(year) %>%
-  group_by(year) %>%
-  summarise(Studies = n()) %>% 
-  ungroup() %>%
-  mutate(Cumulative = cumsum(Studies))

### 2021-04-14 Scripts/create_year_design.R

@@ -1,0 +1,23 @@
+year_design <- overview_of_studies %>%
+  select(year, design) 
+year_design$design <- ifelse(grepl(c("Case series|Cross-sectional"), year_design$design), "Cross-sectional", 
+                           ifelse(grepl(c("Intact group design|Pretest-posttest nonequivalent groups design|Randomized controlled trials"), year_design$design), "Interventional",
+                                  ifelse(grepl(c("Meta-analysis|Systematic review"), year_design$design), "Systematic reviews, meta-analyses",
+                                         ifelse(grepl("Mixed", year_design$design), "Mixed",
+                                                ifelse(grepl(c("Longitudinal|Population-based cohort study"), year_design$design), "Longitudinal", 
+                                                       ifelse(grepl("Qualitative", year_design$design), "Qualitative", "Other"
+                                                       ))))))
+year_design <- year_design %>%
+  group_by(year, design) %>%
+  summarise(Studies = n()) %>% 
+  ungroup() %>%
+  group_by(design) %>%
+  mutate(cumulative = cumsum(Studies))
+
+# This data frame corresponds to the numbers and cumulative 
+# numbers of studies by type, in order to create the plot used in the paper. 
+# To improve readability of the plot , we decided to merge some of the design, 
+# using a mix of  ifelse function and grepl function. Case series was merged with 
+# cross-sectional  because we only had one case-series in our review (Tan et al. 2016)
+# and because this study also had a cross-sectional part. 
+

### 2021-04-14 Scripts/create_plot_year.R
Minor correction on plot legend

@@ -10,11 +10,13 @@ plot_year_design <- year_design %>%
                      breaks = seq(0, 75, by = 10), 
                      minor_breaks = seq(0, 75, by = 5)) +
   ggtitle("B. Studies, by design and year of publication") +
+  labs (color = "Study design") +
   theme(
     axis.text.x = element_text(size=8),
     plot.title = element_text(size = 10, face = "bold"),
     axis.title.x = element_text(size = 9, face = "italic"),
-    axis.title.y = element_text(size = 9, face = "italic")
+    axis.title.y = element_text(size = 9, face = "italic"),
+    legend.title = element_text(size = 7, face = "bold")
   )
 
 plot_year_continent <- year_continent %>%
@@ -29,11 +31,13 @@ plot_year_continent <- year_continent %>%
                      breaks = seq(0, 75, by = 10), 
                      minor_breaks = seq(0, 75, by = 5)) +
   ggtitle("A. Studies, by continent and year of publication") +
+  labs (color = "Continent") +
   theme(
     axis.text.x = element_text(size=8),
     plot.title = element_text(size = 10, face = "bold"),
     axis.title.x = element_text(size = 9, face = "italic"),
-    axis.title.y = element_text(size = 9, face = "italic")
+    axis.title.y = element_text(size = 9, face = "italic"),
+    legend.title = element_text(size = 7, face = "bold")
   )
 
 

### 2021-04-14 Article.Rmd
Writing the part "2.1 - General characteristics"

@@
 The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in \@ref(fig:PlotYear).
+Apart from the quantitative increase in the number of studies, there's also a qualitative increase in the diversity of the studies, both in the type of design used and the countries where the studies are conducted.
 
@@
 
-Out of the 104 quantitative and qualitative studies included, most were conducted in North America (N = `r North_America_studies`), with a large predominance of studies in the United States of America (N= `r max(year_country$cumulative_location[year_country$location == "USA"])`).
+However, despite this growing diversity, the vast majority of studies are conducted in North America (N = `r North_America_studies`), with a large predominance of studies in the United States of America (N= `r max(year_country$cumulative_location[year_country$location == "USA"])`).
 The majority of the remaining studies were then located in Asia (N = `r Asia_studies`) or in Europe (N = `r Europe_studies`).
 South America and Africa were the least represented continents, with only `r South_America_studies` and `r Africa_studies` studies respectively.
+
+In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r N_cross_sec`).
+The number of longitudinal studies steadily grew since 2014 but only represents `r percent(N_long/109)` of the papers to this day.
+Qualitative studies are also under-represented, with only `r N_qual` papers.
+Of note, we only identified 1 mixed design @buttram2015 ; this study employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part.
+The first systematic reviews and meta-analyses were published recently, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])` while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.
+
+Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported ranged from `r min(sample$age, na.rm = T)` to `r max(sample$age, na.rm = T)`.
 

### 2021-04-14 Scripts/create_year_design.R

@@ -21,3 +21,8 @@ year_design <- year_design %>%
 # cross-sectional  because we only had one case-series in our review (Tan et al. 2016)
 # and because this study also had a cross-sectional part. 
 
+N_cross_sec <- max(year_design$cumulative[year_design$design == "Cross-sectional"])
+N_long <- max(year_design$cumulative[year_design$design == "Longitudinal"])
+N_qual <- max(year_design$cumulative[year_design$design == "Qualitative"])
+N_int <- max(year_design$cumulative[year_design$design == "Interventional"])
+N_SR <- max(year_design$cumulative[year_design$design == "Systematic reviews, meta-analyses"])

### 2021-05-09 Scripts/create_location_data.R
Data corrections

@@ -26,12 +26,13 @@ year_continent <- year_continent%>%
 
 
 
-North_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "North America"])
+.North_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "North America"])
+.USA_studies <- max(year_country$cumulative_location[year_country$location == "USA"])
 
-Asia_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Asia"])
+.Asia_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Asia"])
 
-Europe_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Europe"])
+.Europe_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Europe"])
 
-South_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "South America"])
+.South_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "South America"])
 
-Africa_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Africa"])
+.Africa_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Africa"])

### 2021-05-09 Scripts/create_population_plot.R
Subpopulation and minor corrections

@@ -1,0 +1,137 @@
+
+.age_pop_plot <- ggplot(data = population, aes(x = fct_infreq(age))) +
+  geom_bar(fill = c("#FE9666", "#A66999", "#FD625E", "#F2C80F")) +
+  geom_text(stat='count', 
+            aes(label=..count..), 
+            vjust =-0.1,
+            colour = c("#FE9666", "#A66999", "#FD625E", "#F2C80F"),
+            fontface = "bold",
+            cex = 3) + 
+  xlab("Age group") +
+  ylab("Number of studies") +
+  labs(title = "Age groups of study participants")+
+  font("title", size = 8, face = "bold") +
+  font("xlab", size = 7) +
+  font("ylab", size = 7) +
+  font("xy.text", size = 6) +
+  scale_y_continuous(expand = expansion(mult = 0.1), 
+                     breaks = c(0,25,50,75,100))
+
+.race_pop_plot <- ggplot(data = population, aes(x = fct_infreq(race_ethnicity))) +
+  geom_bar(fill = c("#FE9666", "#A66999", "#FD625E", "#F2C80F")) +
+  geom_text(stat='count', 
+            aes(label=..count..), 
+            vjust =-0.1,
+            colour = c("#FE9666", "#A66999", "#FD625E", "#F2C80F"),
+            fontface = "bold",
+            cex = 3) + 
+  xlab("Race/ethnicity") +
+  ylab("Number of studies") +
+  labs(title = "Races/ethnicities of study participants")+
+  font("title", size = 8, face = "bold") +
+  font("xlab", size = 7) +
+  font("ylab", size = 7) +
+  font("xy.text", size = 6) +
+  scale_y_continuous(expand = expansion(mult = 0.1), 
+                     breaks = c(0,25,50,75,100))
+
+.sero_pop_plot <- ggplot(data = population, aes(x = fct_infreq(serologic_status))) +
+  geom_bar(fill = c("#FE9666", "#A66999")) +
+  geom_text(stat='count', 
+            aes(label=..count..), 
+            vjust =-0.1,
+            colour = c("#FE9666", "#A66999"),
+            fontface = "bold",
+            cex = 3) + 
+  xlab("Serologic status") +
+  ylab("Number of studies") +
+  labs(title = "Serologic status of study participants")+
+  font("title", size = 8, face = "bold") +
+  font("xlab", size = 7) +
+  font("ylab", size = 7) +
+  font("xy.text", size = 6) +
[…]

### 2021-05-09 Scripts/create_year_design.R

@@ -21,8 +21,8 @@ year_design <- year_design %>%
 # cross-sectional  because we only had one case-series in our review (Tan et al. 2016)
 # and because this study also had a cross-sectional part. 
 
-N_cross_sec <- max(year_design$cumulative[year_design$design == "Cross-sectional"])
-N_long <- max(year_design$cumulative[year_design$design == "Longitudinal"])
-N_qual <- max(year_design$cumulative[year_design$design == "Qualitative"])
-N_int <- max(year_design$cumulative[year_design$design == "Interventional"])
-N_SR <- max(year_design$cumulative[year_design$design == "Systematic reviews, meta-analyses"])
+.N_cross_sec <- max(year_design$cumulative[year_design$design == "Cross-sectional"])
+.N_long <- max(year_design$cumulative[year_design$design == "Longitudinal"])
+.N_qual <- max(year_design$cumulative[year_design$design == "Qualitative"])
+.N_int <- max(year_design$cumulative[year_design$design == "Interventional"])
+.N_SR <- max(year_design$cumulative[year_design$design == "Systematic reviews, meta-analyses"])

### 2021-05-09 Scripts/read_data.R

@@ -1,0 +1,10 @@
+overview_of_studies <- read_csv("Data/overview_of_studies.csv", 
+                                col_types = cols(X6 = col_skip()))
+
+summary_qualitative <- read_csv("Data/summary_qualitative.csv", 
+                                col_types = cols(X23 = col_skip()))
+summary_quantitative <- read_csv("Data/summary_quantitative.csv",
+                                 col_types = cols(X299 = col_skip()))
+
+summary_reviews <- read_csv("Data/summary_reviews.csv", 
+                           col_types = cols(X12 = col_skip()))

### 2021-05-09 Scripts/read_overview.R

@@ -1,2 +1,0 @@
-overview_of_studies <- read_csv("Data/overview_of_studies.csv", 
-                                col_types = cols(X6 = col_skip()))

### 2021-05-09 Article.Rmd
Subpopulation and minor corrections

@@
 library(ggpubr)
+library(sunburstR)
+library(d3r)
 
 #Load the data from the .csv files
-source("./scripts/read_overview.R", local = knitr::knit_global())
+source("./scripts/read_data.R", local = knitr::knit_global())
 
@@
 source("./scripts/create_year_design.R", local = knitr::knit_global())
-source("./scripts/create_design_data.R", local = knitr::knit_global())
 source("./scripts/create_location_data.R", local = knitr::knit_global())
@@
 
-The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in \@ref(fig:PlotYear).
+The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in Figure \@ref(fig:PlotYear).
 Apart from the quantitative increase in the number of studies, there's also a qualitative increase in the diversity of the studies, both in the type of design used and the countries where the studies are conducted.
@@
 
-However, despite this growing diversity, the vast majority of studies are conducted in North America (N = `r North_America_studies`), with a large predominance of studies in the United States of America (N= `r max(year_country$cumulative_location[year_country$location == "USA"])`).
-The majority of the remaining studies were then located in Asia (N = `r Asia_studies`) or in Europe (N = `r Europe_studies`).
-South America and Africa were the least represented continents, with only `r South_America_studies` and `r Africa_studies` studies respectively.
+However, despite this growing diversity, the vast majority of studies are conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the United States of America (N= `r .USA_studies`).
+The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`).
+South America and Africa were the least represented continents, with only `r .South_America_studies` and `r .Africa_studies` studies respectively.
 
-In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r N_cross_sec`).
-The number of longitudinal studies steadily grew since 2014 but only represents `r percent(N_long/109)` of the papers to this day.
-Qualitative studies are also under-represented, with only `r N_qual` papers.
+In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r .N_cross_sec`).
+The number of longitudinal studies steadily grew since 2014 but only represents `r percent(.N_long/109)` of the papers to this day.
+Qualitative studies are also under-represented, with only `r .N_qual` papers.
 Of note, we only identified 1 mixed design @buttram2015 ; this study employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part.
@@
 ### Subpopulations studied
+
+```{r Subpopulation_data_prep, message=FALSE, warning=FALSE, include=FALSE}
+library(cowplot)
+source("./scripts/create_population_data.R", local = knitr::knit_global())
+source("./scripts/create_population_plot.R", local = knitr::knit_global())
+
+```
+
+A bit less than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focus on a subpopulation of MSM.
+In this review, we identified 6 kind of MSM subpopulations studied in syndemic literature : (a) young MSM and older MSM ; (b) MSM from a racial/ethnic minority ; (c) MSM living with HIV ; (d) MSM engaged in sex work ; (e) Men who have Sex with Men and Women (MSMW) ; and (f) transgender MSM.
+
+Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r sum(population$age == "Older men")` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r sum(population$age == "Adolescent")` study focuses on adolescents[@Perry].
+Of note, the two studies on older MSM are both entirely composed of a sample of older MSM living with HIV.
+
+Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.
+Among these studies, `r .N_YBMSM` studies are composed of young BMSM[@Maiorana; @Reed2016] and `r .N_MSM_SW` study focuses on Black MSM engaged in sex work[@chandler2020].
+\
+Only (N= `r sum(population$race_ethnicity == "Latino")`) studies focus on Latino MSM (LMSM) and `r .N_LMSMW` of these studies focus on Latino MSMW[@Munoz-Laboy2018].
+Furthermore, `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].
+
+Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV.
+Apart from the aforementioned studies on older MSM living with HIV, `r sum(population$serologic_status == "HIV-positive" & population$age == "Young adult")` studies focus on young MSM living with HIV[@Lyons2013; @Bruce2011] .
+Notably, we identified no studies conducted on racial minority MSM living with HIV.
+
+Finally, the least represented subpopulation of MSM in this review are MSMW (N = `r sum(population$sex_behav == "MSMW")`), MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
+Strikingly, transgender MSM, in addition to being the focus of only one study[@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.
+
+Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.
+
+In order to have the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also measured took into account studies who did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulation.
+\
+`r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].
+
+```{r PlotPop, fig.cap = "Number of studies focusing on a MSM subpopulation, by kind of subpopulation"}
+
+knitr::include_graphics("./Output/Plots/Plot_population.png")
+```
 

### 2021-05-09 Scripts/create_design_data.R

@@ -1,5 +1,0 @@
-design_data <- overview_of_studies %>%
-  select(design) %>%
-  group_by(design) %>%
-  summarise(Studies = n()) %>% 
-  ungroup()

### 2021-05-09 Scripts/create_population_data.R

@@ -1,0 +1,39 @@
+.population_qualitative <- summary_qualitative %>%
+  select(subpopulation, authors, year)
+
+.population_quantitative <- summary_quantitative %>%
+  select(subpopulation, authors, year)
+
+population <- bind_rows(.population_quantitative, .population_qualitative) %>%
+  mutate (ref = paste(authors, year)) %>%
+  select(-authors, -year)
+
+population$age <- ifelse(grepl("AMSM", population$subpopulation), "Adolescent",
+                         
+                         ifelse(grepl("YMSM|HIV+YMSM|YBMSM", population$subpopulation), "Young adult", 
+                                ifelse(grepl("HIVOMSM", population$subpopulation), "Older men", "Various age"
+                                )))
+
+population$race_ethnicity <- ifelse(grepl("BMSM", population$subpopulation), "Black",
+                                    ifelse(grepl("LMSM", population$subpopulation), "Latino",
+                                           ifelse(grepl("LB_MSM", population$subpopulation), "Latino & Black", "Various race/ethnicity"
+                                           )))
+population$serologic_status <- ifelse(grepl("HIV", population$subpopulation), "HIV-positive", "Mostly HIV-negative")
+population$sex_work <- ifelse(grepl("SW", population$subpopulation), "Sex workers", "Mostly no sex-work engagement")
+population$sex_behav <- ifelse(grepl("MSMW", population$subpopulation), "MSMW", "Mostly MSM")
+population$gender_identity <- ifelse(grepl("TMSM", population$subpopulation), "Transgender", "Cisgender")
+
+disaggregated <- summary_quantitative %>%
+  select(disaggregated_logical, disaggregated, authors, year) %>%
+  mutate(ref = paste(authors, year)) %>%
+  select(-authors, year)
+
+.N_YBMSM <- sum(population$race_ethnicity == "Black" & population$age == "Young adult")
+.N_MSM_SW <- sum(population$race_ethnicity == "Black" & population$sex_work == "Sex workers")
+.N_LMSMW <- sum(population$race_ethnicity == "Latino" & population$sex_behav == "MSMW")
+
+.N_disaggregated <- sum(disaggregated$disaggregated_logical == "Yes", na.rm = TRUE)
[…]

### 2021-05-09 Scripts/create_sample.R

@@ -1,7 +1,3 @@
-summary_qualitative <- read_csv("Data/summary_qualitative.csv", 
-                                col_types = cols(X23 = col_skip()))
-summary_quantitative <- read_csv("Data/summary_quantitative.csv")
-
 sample_qualitative <- summary_qualitative %>%
   select(sample_size, age) 
 

### 2021-05-18 Article.Rmd
Corrections

@@
 
-The electronic search identified 769 citations and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
-After duplicates removal, 277 unique references were left to be screened for inclusion.
+The electronic search identified 769 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
+After duplicates removal, 277 records were left to be screened for inclusion.
 
-Among these references, 109 were excluded after reading the title and abstract.
-The two main reasons for exclusion at this stage were that MSM were not the main population of the study (n=46) or that syndemic was not the main focus of the paper (n=34).
-29 additional studies were excluded because the type of publication did not meet our inclusion criteria.
+After screening the title and abstract, 109 records were excluded.
+The two main reasons for exclusion at this stage were that MSM were not the main study population (n=46) and that syndemic was not the main focus of the paper (n=34).
+29 studies were excluded because the type of publication did not meet our inclusion criteria.
 
-The full texts of the 168 remaining references were obtained and read, which lead to the exclusion of 59 citations.
-During the previous step, we decided to include papers in which the sample was not entirely comprised of MSM.
-After reading the full paper, we opted to exclude the studies if the MSM data was aggregated with data from another population (n=9), most commonly transgender women.
+The full texts of the 168 remaining references were obtained and read; 59 were excluded after this phase.
+During the previous step, we had decided to tentatively include papers in which the sample was not entirely comprised of MSM.
+After reviewing the full paper, we decided to exclude studies if the MSM data was aggregated with data from another population (n=9), most commonly transgender women.
 The rationale for this decision was to keep the focus clearly on MSM.
@@
 
-The publication date of the studies range from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published yearly from 2013 onward as illustrated in Figure \@ref(fig:PlotYear).
-Apart from the quantitative increase in the number of studies, there's also a qualitative increase in the diversity of the studies, both in the type of design used and the countries where the studies are conducted.
+The publication date of the studies ranges from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published annually from 2013 onward as illustrated in Figure \@ref(fig:PlotYear).
+There is also an increase in the diversity of the studies, both in the type of design used and the continents where the studies were conducted.
 
@@
 
-However, despite this growing diversity, the vast majority of studies are conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the United States of America (N= `r .USA_studies`).
+However, despite the emerging diversity, the vast majority of studies are conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the United States of America (N= `r .USA_studies`).
 The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`).
@@
 In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r .N_cross_sec`).
-The number of longitudinal studies steadily grew since 2014 but only represents `r percent(.N_long/109)` of the papers to this day.
-Qualitative studies are also under-represented, with only `r .N_qual` papers.
+The number of longitudinal studies grew steadily since 2014 and represents `r .N_long/109` papers to this day.
+Qualitative studies are under-represented, with only `r .N_qual` papers.
 Of note, we only identified 1 mixed design @buttram2015 ; this study employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part.
-The first systematic reviews and meta-analyses were published recently, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])` while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.
+The first systematic reviews and meta-analyses were published, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])`, while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.
 
-Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported ranged from `r min(sample$age, na.rm = T)` to `r max(sample$age, na.rm = T)`.
+Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported ranged from `r min(sample$age, na.rm = T)` to `r round(max(sample$age, na.rm = T), digits = 0)`.
 
@@
 
-A bit less than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focus on a subpopulation of MSM.
+Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focus on a subpopulation of MSM.
 In this review, we identified 6 kind of MSM subpopulations studied in syndemic literature : (a) young MSM and older MSM ; (b) MSM from a racial/ethnic minority ; (c) MSM living with HIV ; (d) MSM engaged in sex work ; (e) Men who have Sex with Men and Women (MSMW) ; and (f) transgender MSM.
@@
 Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.
-Among these studies, `r .N_YBMSM` studies are composed of young BMSM[@Maiorana; @Reed2016] and `r .N_MSM_SW` study focuses on Black MSM engaged in sex work[@chandler2020].
-\
-Only (N= `r sum(population$race_ethnicity == "Latino")`) studies focus on Latino MSM (LMSM) and `r .N_LMSMW` of these studies focus on Latino MSMW[@Munoz-Laboy2018].
+Among these studies, `r .N_YBMSM` studies are composed of young BMSM[@Maiorana; @Reed2016] and `r .N_MSM_SW` study focuses on Black MSM engaged in sex work[@chandler2020].\
+`r sum(population$race_ethnicity == "Latino")` studies focus on Latino MSM (LMSM) and `r .N_LMSMW` of these studies focus on Latino MSMW[@Munoz-Laboy2018].
 Furthermore, `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].
@@
 
-In order to have the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also measured took into account studies who did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulation.
-\
+In order to have the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies who did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulation.\
 `r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].

### 2021-05-18 Scripts/create_population_data.R
Corrections

@@ -11,16 +11,16 @@ population <- bind_rows(.population_quantitative, .population_qualitative) %>%
 population$age <- ifelse(grepl("AMSM", population$subpopulation), "Adolescent",
                          
                          ifelse(grepl("YMSM|HIV+YMSM|YBMSM", population$subpopulation), "Young adult", 
-                                ifelse(grepl("HIVOMSM", population$subpopulation), "Older men", "Various age"
+                                ifelse(grepl("HIVOMSM", population$subpopulation), "Older men", "No specific age group"
                                 )))
 
 population$race_ethnicity <- ifelse(grepl("BMSM", population$subpopulation), "Black",
                                     ifelse(grepl("LMSM", population$subpopulation), "Latino",
-                                           ifelse(grepl("LB_MSM", population$subpopulation), "Latino & Black", "Various race/ethnicity"
+                                           ifelse(grepl("LB_MSM", population$subpopulation), "Latino & Black", "No specific race/ethnicity"
                                            )))
-population$serologic_status <- ifelse(grepl("HIV", population$subpopulation), "HIV-positive", "Mostly HIV-negative")
-population$sex_work <- ifelse(grepl("SW", population$subpopulation), "Sex workers", "Mostly no sex-work engagement")
-population$sex_behav <- ifelse(grepl("MSMW", population$subpopulation), "MSMW", "Mostly MSM")
+population$serologic_status <- ifelse(grepl("HIV", population$subpopulation), "HIV-positive", "Majority HIV-negative")
+population$sex_work <- ifelse(grepl("SW", population$subpopulation), "Sex workers", "Majority no sex-work engagement")
+population$sex_behav <- ifelse(grepl("MSMW", population$subpopulation), "MSMW", "Majority MSM")
 population$gender_identity <- ifelse(grepl("TMSM", population$subpopulation), "Transgender", "Cisgender")
 
 disaggregated <- summary_quantitative %>%

### 2021-06-29 Scripts/supplementary_tables_CSA.R
Supplementary tables

@@ -1,0 +1,59 @@
+source("./scripts/supplementary_tables_general.R")
+
+.CSA_measurement <- measurement %>%
+  select(c(1, 61:63)) %>%
+  filter(!is.na(CSA_type)) %>%
+  add_count(CSA_type, name = "type_n") %>%
+  add_count(CSA_scale_criteria, name = "criteria_n") %>%
+  relocate("type_n", .after = "CSA_type") %>%
+  relocate("criteria_n", .after = "CSA_scale_criteria") %>%
+  relocate("reference", .after = "CSA_cutoff") %>%
+  arrange(desc(type_n), desc(criteria_n), desc(CSA_scale_criteria), desc(CSA_cutoff))
+
+.pal_type_CSA <- col_numeric(
+  palette = c("transparent", "#9DE0AD"),
+  domain = c(0, max(.CSA_measurement$type_n)+1)) 
+
+.pal_scale_CSA <- col_numeric(
+  palette = c("transparent", "#9DE0AD"),
+  domain = c(0, max(.CSA_measurement$criteria_n)+1)) 
+
+.CSA_ft <- flextable(.CSA_measurement, cwidth = c(0.8, 0.8, 1.7, 1, 1, 2))
+
+.CSA_ft <- bg(.CSA_ft, bg = "#45ADA8", part = "header")
+.CSA_ft <- bg(.CSA_ft, bg = .pal_type_CSA, j = 2, part = "body")
+.CSA_ft <- bg(.CSA_ft, bg = .pal_scale_CSA, j = 4, part = "body")
+.CSA_ft <- .CSA_ft %>%
+  bold(part = "header") %>%
+  bold(j = 6, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(CSA_type = "Use of a scale or a criteria", 
+                    type_n = "Number of studies", 
+                    CSA_scale_criteria = "Scale or criteria used",
+                    scale_n = "Number of studies",
+                    criteria_n = "Number of studies",
+                    CSA_cutoff = "Cutoff used",
+                    reference = "References") %>%
+  footnote(i = 1, j = 3, part = "header", 
+           value = as_paragraph("Finkelhor definition : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (Finkelhor 1994)")) %>%
+  merge_v(j = c(1:3, 5), part = "body") %>%
+  merge_at(j = 4, i = 1:6, part = "body") %>%
[…]

### 2021-06-29 Scripts/supplementary_tables_IPV.R

@@ -2,7 +2,7 @@ source("./scripts/supplementary_tables_general.R")
 
 
 .IPV_measurement <- measurement %>%
-  select(c(1, 25:35)) %>%
+  select(c(1, 24:34)) %>%
   filter(!is.na(IPV_type)) %>%
   add_count(IPV_type, name = "type_n") %>%
   unite(col = IPV_scale_criteria, 3:11, sep = ", ", na.rm = T) %>%
@@ -14,11 +14,11 @@ source("./scripts/supplementary_tables_general.R")
 
 
 .IPV_prevalence <- list()
-for (i in 26:30) {
-  .IPV_prevalence$sum[[i-25]] <- sum(!is.na(measurement[i]))
-  .IPV_prevalence$perc[[i-25]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$IPV_type))))
-  names(.IPV_prevalence[["sum"]])[[i-25]] <- names(measurement[i])
-  names(.IPV_prevalence[["perc"]])[[i-25]] <- names(measurement[i])
+for (i in 25:29) {
+  .IPV_prevalence$sum[[i-24]] <- sum(!is.na(measurement[i]))
+  .IPV_prevalence$perc[[i-24]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$IPV_type))))
+  names(.IPV_prevalence[["sum"]])[[i-24]] <- names(measurement[i])
+  names(.IPV_prevalence[["perc"]])[[i-24]] <- names(measurement[i])
 }
 .IPV_prevalence$footer <- c(paste0("Physical intimate partner violence: ", 
                                   .IPV_prevalence[["sum"]][["physical IPV"]],
@@ -56,12 +56,12 @@ for (i in 26:30) {
   domain = c(0, max(.IPV_measurement$criteria_n)+1)) 
 
 
-IPV_ft <- flextable(.IPV_measurement, cwidth = c(1, 1, 2, 1, 1, 2))
+.IPV_ft <- flextable(.IPV_measurement, cwidth = c(0.8, 0.8, 1.7, 1, 1, 2))
 
-IPV_ft <- bg(IPV_ft, bg = "#45ADA8", part = "header")
-IPV_ft <- bg(IPV_ft, bg = .pal_type_IPV, j = 2, part = "body")
-IPV_ft <- bg(IPV_ft, bg = .pal_scale_IPV, j = 4, part = "body")
-IPV_ft <- IPV_ft %>%
[…]

### 2021-06-29 Scripts/supplementary_tables_anxiety.R

@@ -1,0 +1,53 @@
+source("./scripts/supplementary_tables_general.R")
+
+.anxiety_measurement <- measurement %>%
+  filter(!is.na(anxiety_type)) %>%
+  select(c(1, 42:45, 47:56)) %>%
+  unite(col = disorder, 2:5, sep = ", ", na.rm = T) %>%
+  unite(col = criteria, 3:11, sep = ", ", na.rm = T) %>%
+  add_count(disorder, name = "disorder_n") %>%
+  add_count(criteria, name = "criteria_n") %>%
+  relocate("reference", .after = "anxiety_cutoff_period") %>%
+  relocate("disorder_n", .after = "disorder") %>%
+  relocate("criteria_n", .after = "criteria") %>%
+  arrange(desc(disorder_n), desc(criteria_n))
+
+
+.pal_type_anxiety <- col_numeric(
+  palette = c("transparent", "#9DE0AD"),
+  domain = c(0, max(.anxiety_measurement$disorder_n)+1)) 
+
+.pal_scale_anxiety <- col_numeric(
+  palette = c("transparent", "#9DE0AD"),
+  domain = c(0, max(.anxiety_measurement$criteria_n)+1)) 
+
+.anxiety_ft <- flextable(.anxiety_measurement, cwidth = c(1.3, 0.8, 1.6, 0.8, 0.8, 2))
+.anxiety_ft <- bg(.anxiety_ft, bg = "#45ADA8", part = "header")
+.anxiety_ft <- bg(.anxiety_ft, bg = .pal_type_anxiety, j = 2, part = "body")
+.anxiety_ft <- bg(.anxiety_ft, bg = .pal_scale_anxiety, j = 4, part = "body")
+.anxiety_ft <- .anxiety_ft %>%
+  bold(part = "header") %>%
+  bold(j = 6, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(disorder = "Type of anxiety disorder screened, if specified", 
+                    disorder_n = "Number of studies", 
+                    criteria = "Criteria or scale used",
+                    criteria_n = "Number of studies",
+                    anxiety_cutoff_period = "Reference period or cutoff used",
+                    reference = "References") %>%
+  merge_v(j = c(1:3, 5), part = "body") %>%
+  merge_at(j = 4, i = 1:2, part = "body") %>%
+  merge_at(j = 4, i = 6:9, part = "body") %>%
[…]

### 2021-06-29 Scripts/supplementary_tables_binge.R

@@ -1,0 +1,48 @@
+source("./scripts/supplementary_tables_general.R")
+
+.binge_measurement <- measurement %>%
+  select(c(1, 35:36)) %>%
+  filter(!is.na(binge_episodes)) %>%
+  add_count(binge_episodes, name = "episodes_n") %>%
+  relocate("episodes_n", .after = "binge_episodes") %>%
+  relocate("reference", .after = "binge_period") %>%
+  arrange(desc(episodes_n), desc(binge_period))
+
+.pal_type_binge <- col_numeric(
+  palette = c("transparent", "#9DE0AD"),
+  domain = c(0, max(.binge_measurement$episodes_n)+1)) 
+
+.binge_ft <- flextable(.binge_measurement, cwidth = c(3, 0.8, 1.5, 2))
+
+.binge_ft <- bg(.binge_ft, bg = "#45ADA8", part = "header")
+.binge_ft <- bg(.binge_ft, bg = .pal_type_binge, j = 2, part = "body")
+.binge_ft <- .binge_ft %>%
+  bold(part = "header") %>%
+  bold(j = 4, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(binge_episodes = "Number of episodes to qualify as binge drinking", 
+                    episodes_n = "Number of studies", 
+                    binge_period = "Reference period",
+                    reference = "References") %>%
+  merge_v(j = 1, part = "body") %>%
+  merge_at(j = 2, i = 1:12, part = "body") %>%
+  merge_at(j = 2, i = 13:16, part = "body") %>%
+  merge_at(j = 2, i = 17:18, part = "body") %>%
+  merge_at(j = 2, i = 19:20, part = "body") %>%
+  merge_at(j = 3, i = 1:4, part = "body") %>%
+  merge_at(j = 3, i = 5:9, part = "body") %>%
+  merge_at(j = 3, i = 10:11, part = "body") %>%
+  merge_at(j = 3, i = 13:14, part = "body") %>%
+  merge_at(j = 3, i = 15:16, part = "body") %>%
+  merge_at(j = 3, i = 17:18, part = "body") %>%
+  merge_at(j = 3, i = 19:20, part = "body") %>%
+  hline(j = c(1, 3:4), border = .borders, part = "body") %>%
+  align(align = "center", j=1:4, part = "body") %>%
+  vline(j = 3, border = .borders, part = "body") %>%
[…]

### 2021-06-29 Scripts/supplementary_tables_depression.R

@@ -5,7 +5,7 @@ source("./scripts/supplementary_tables_general.R")
   filter (!is.na(depression_scale)) %>%
   add_count(depression_scale, name = "type_n") %>%
   add_count(depression_scale_criteria, name = "scale_n") %>%
-  arrange(desc(depression_scale), desc(scale_n), depression_cutoff, depression_scale_criteria ) %>%
+  arrange(desc(depression_scale), desc(scale_n), depression_scale_criteria, depression_cutoff,  ) %>%
   relocate("type_n", .after = "depression_scale") %>%
   relocate("scale_n", .after = "depression_scale_criteria") %>%
   relocate("reference", .after = "depression_cutoff")
@@ -19,12 +19,12 @@ source("./scripts/supplementary_tables_general.R")
   palette = c("transparent", "#9DE0AD"),
   domain = c(0, max(.depression_measurement$scale_n)+1)) 
 
-depression_ft <- flextable(.depression_measurement, cwidth = c(1, 1, 2, 1, 1, 2))
+.depression_ft <- flextable(.depression_measurement, cwidth = c(0.7, 0.8, 1.8, 1, 1, 2))
 
-depression_ft <- bg(depression_ft, bg = "#45ADA8", part = "header")
-depression_ft <- bg(depression_ft, bg = .pal_type_dep, j = 2, part = "body")
-depression_ft <- bg(depression_ft, bg = .pal_scale_dep, j = 4, part = "body")
-depression_ft <- depression_ft %>%
+.depression_ft <- bg(.depression_ft, bg = "#45ADA8", part = "header")
+.depression_ft <- bg(.depression_ft, bg = .pal_type_dep, j = 2, part = "body")
+.depression_ft <- bg(.depression_ft, bg = .pal_scale_dep, j = 4, part = "body")
+.depression_ft <- .depression_ft %>%
   bold(part = "header") %>%
   bold(j = 6, part = "body") %>%
   color(color = "white", part = "header") %>%
@@ -41,10 +41,12 @@ depression_ft <- depression_ft %>%
   merge_at(j = 4, i = 43:47, part = "body") %>%
   merge_at(j = 4, i = 48:51, part = "body") %>%
   merge_at(j = 4, i = 52:54, part = "body") %>%
-  merge_at(j = 4, i = 57:58, part = "body") %>%
-  merge_at(j = 4, i = 66:68, part = "body") %>%
[…]

### 2021-06-29 Scripts/supplementary_tables_general.R

@@ -12,3 +12,13 @@ measurement <- measurement %>%
 .outer.border <- fp_border(color = "#45ADA8", style = "solid", width = 2.5)
 
 
+.supp_autonum <- run_autonum(
+  seq_id = "table",
+  pre_label = "Table S",
+  post_label = ": ",
+  bkm = NULL,
+  bkm_all = FALSE,
+  prop = NULL
+)
+
+

### 2021-06-29 Scripts/supplementary_tables_polysubstance.R

@@ -1,0 +1,42 @@
+source("./scripts/supplementary_tables_general.R")
+
+.polysubstance_measurement <- measurement %>%
+  select(c(1, 64:66)) %>%
+  filter(!is.na(polysubstance_number)) %>%
+  add_count(polysubstance_number, name = "number_n") %>%
+  relocate("number_n", .after = "polysubstance_number") %>%
+  relocate("reference", .after = "polysubstance_period") %>%
+  arrange(desc(number_n), desc(polysubstance_marijuana), desc(polysubstance_period))
+
+.pal_type_pol <- col_numeric(
+  palette = c("transparent", "#9DE0AD"),
+  domain = c(0, max(.polysubstance_measurement$number_n)+1)) 
+
+.polysubstance_ft <- flextable(.polysubstance_measurement, cwidth = c(2.5, 0.8, 1, 1, 2))
+
+.polysubstance_ft <- bg(.polysubstance_ft, bg = "#45ADA8", part = "header")
+.polysubstance_ft <- bg(.polysubstance_ft, bg = .pal_type_pol, j = 2, part = "body")
+.polysubstance_ft <- .polysubstance_ft %>%
+  bold(part = "header") %>%
+  bold(j = 5, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(polysubstance_number = "Number of substances to qualify as polysubstance use", 
+                    number_n = "Number of studies", 
+                    polysubstance_marijuana = "Inclusion of marijuana in the substances count",
+                    polysubstance_period = "Reference period",
+                    reference = "References") %>%
+  merge_v(j = c(1:2, 4), part = "body") %>%
+  merge_at(j = 3, i = 1:4, part = "body") %>%
+  merge_at(j = 3, i = 5:16, part = "body") %>%
+  merge_at(j = 3, i = 17:18, part = "body") %>%
+  merge_at(j = 3, i = 19:25, part = "body") %>%
+  hline(j = c(1, 3:5), border = .borders, part = "body") %>%
+  align(align = "center", j=1:5, part = "body") %>%
+  vline(j = 3:4, border = .borders, part = "body") %>%
+  align(align = "right", j = 5, part = "body") %>%
+  hline_bottom(border = .outer.border, part = "body") %>%
+  border_outer(border = .outer.border, part = "header") %>%
+  fix_border_issues(part = "all")
+.polysubstance_ft <- set_caption(.polysubstance_ft, 
[…]

### 2021-06-29 Scripts/supplementary_tables_substance.R

@@ -1,0 +1,97 @@
+source("./scripts/supplementary_tables_general.R")
+
+.substance_measurement <- measurement %>%
+  select(c(1, 5:14)) %>%
+  filter(!is.na(substance_use_period)) %>%
+  unite(col = substances, 2:10, sep = ", ", na.rm = T) %>%
+  add_count(substances, name = "studies_n") %>%
+  relocate("reference", .after = "substance_use_period") %>%
+  relocate("studies_n", .after = "substances") %>%
+  arrange(desc(studies_n), desc(substances), desc(substance_use_period))
+
+.substances_prev <- list()
+for (i in 5:12) {
+  .substances_prev$sum[[i-4]] <- sum(!is.na(measurement[i]))  
+  .substances_prev$perc[[i-4]] <- percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$substance_use_period)))) 
+  names(.substances_prev[["sum"]])[[i-4]] <- names(measurement[i])
+  names(.substances_prev[["perc"]])[[i-4]] <- names(measurement[i])
+}
+.substances_prev$footer <- c(paste0("Stimulants : cocaine/crack, amphetamine (", 
+                                              .substances_prev[["sum"]][["stimulants"]],
+                                              " studies ; ",
+                                              .substances_prev[["perc"]][["stimulants"]],
+                                              ")"),
+                                       paste0("Ecstasy (", 
+                                              .substances_prev[["sum"]][["ecstasy"]],
+                                              " studies ; ",
+                                              .substances_prev[["perc"]][["ecstasy"]],
+                                              ")"),
+                                       paste0("Hallucinogens : ketamine, psilocybine, phencyclidine (", 
+                                              .substances_prev[["sum"]][["hallucinogens"]],
+                                              " studies ; ",
+                                              .substances_prev[["perc"]][["hallucinogens"]],
+                                              ")"),
+                                       paste0("Marijuana (", 
+                                              .substances_prev[["sum"]][["marijuana"]],
+                                              " studies ; ",
+                                              .substances_prev[["perc"]][["marijuana"]],
+                                              ")"),
+                                       paste0("Depressants : GHB/GBL, benzodiazebines (", 
+                                              .substances_prev[["sum"]][["depressants"]],
+                                              " studies ; ",
[…]

### 2021-06-29 Scripts/supplementary_tables_violence.R

@@ -1,0 +1,80 @@
+source("./scripts/supplementary_tables_general.R")
+
+.violence_measurement <- measurement %>%
+  select(c(1, 18:23)) %>%
+  filter(!is.na(violence_period)) %>%
+  unite(col = violence_criteria, 2:6, sep = ", ", na.rm = T) %>%
+  add_count(violence_criteria, name = "criteria_n") %>%
+  relocate("criteria_n", .after = "violence_criteria") %>%
+  relocate("reference", .after = "violence_period") %>%
+  arrange(desc(criteria_n), desc(violence_criteria), desc(violence_period))
+
+
+.violence_prevalence <- list()
+for (i in 18:22) {
+  .violence_prevalence$sum[[i-17]] <- sum(!is.na(measurement[i]))
+  .violence_prevalence$perc[[i-17]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$IPV_type))))
+  names(.violence_prevalence[["sum"]])[[i-17]] <- names(measurement[i])
+  names(.violence_prevalence[["perc"]])[[i-17]] <- names(measurement[i])
+}
+.violence_prevalence$footer <- c(paste0("Physical violence: ", 
+                                   .violence_prevalence[["sum"]][["physical"]],
+                                   " studies ; ", 
+                                   .violence_prevalence[["perc"]][["physical"]],
+                                   " of studies with violence as a syndemic condition"),
+                            paste0("Psychological violence: ",
+                                   .violence_prevalence[["sum"]][["psychological"]],
+                                   " studies ; ",
+                                   .violence_prevalence[["perc"]][["psychological"]],
+                                   " of studies with violence as a syndemic condition"),
+                            paste0("Sexual violence: ",
+                                   .violence_prevalence[["sum"]][["sexual"]],
+                                   " studies ; ",
+                                   .violence_prevalence[["perc"]][["sexual"]],
+                                   " of studies with violence as a syndemic condition"),
+                            paste0("Physical harassment by the Police: ",
+                                   .violence_prevalence[["sum"]][["physical harassment by police"]],
+                                   " studies ; ",
+                                   .violence_prevalence[["perc"]][["physical harassment by police"]],
+                                   " of studies with violence as a syndemic condition"),
[…]

### 2021-06-29 Article.Rmd
Syndemic conditions and their measurement (WIP)

@@
 output: 
-  bookdown::word_document2:
+  officedown::rdocx_document:
     reference_docx: "article_template.docx"
@@
 library(bookdown)
+library(officedown)
+```
+
+```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+#Load required packages :
+library(tidyverse)
+library(readr)
+library(scales)
+library(ggplot2)
+library(ggpubr)
+library(sunburstR)
+library(d3r)
+
+#Load the data from the .csv files
+source("./scripts/read_data.R", local = knitr::knit_global())
+
 ```
@@
 
-```{r PRISMA, fig.cap = "PRISMA flowchart of the included search strategy"}
+```{r fig.cap= "PRISMA flowchart of the search strategy", fig.height=7.5, fig.id="PRISMA", fig.width=7, fig.align='center'}
 knitr::include_graphics("Files/images/PRISMA.png")
@@
 ```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-#Load required packages :
-library(tidyverse)
-library(readr)
-library(scales)
-library(ggplot2)
-library(ggpubr)
-library(sunburstR)
-library(d3r)
-
-#Load the data from the .csv files
-source("./scripts/read_data.R", local = knitr::knit_global())
 
@@
 
-```{r PlotYear, fig.cap = "Plot of the cumulative number of studies published yearly, grouped by continent (A) and design (B)"}
+```{r fig.cap="Plot of the cumulative number of studies published yearly", fig.height=7, fig.id="PlotYear", fig.width=5.5, fig.align='center'}
 
@@
 
-```{r PlotPop, fig.cap = "Number of studies focusing on a MSM subpopulation, by kind of subpopulation"}
+```{r fig.cap="Number of studies focusing on a MSM subpopulation", fig.height=7, fig.id="PlotPop", fig.width=5.5, fig.align='center'}
 
@@
 ### Syndemic conditions and their measurement
+
+```{r Syndemic network script, include=FALSE}
+
+source("./scripts/create_syndemic_network.R", local = knitr::knit_global())
+
+```
+
+We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "CSA"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), childhood abuse ( (N = `r nodes$studies[nodes$label == "childhood"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`) and frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`).
+
+We chose to distinguish alcohol use disorder, binge drinking and alcohol use instead of merging them in a broad "alcohol-related syndemic condition".
+Some authors also considered heavy drinking [@Martinez2016a; @martinez2020] or "heavy alcohol use"[@Mimiaga2015b] but we chose to aggregate these conditions under "binge drinking" for clarity.
+Similarly, we distinguished substance use, substance use disorder, intravenous drug use, polysubstance use, marijuana use, tobacco use and chemsex since they differ in potential harm and context of use.
+
+```{r include=FALSE}
+.Stall_conditions <- summary_quantitative %>%
+  filter(!is.na(CSA) | (!is.na(depression) | (!is.na(polysubstance) | (!is.na(IPV)))))
+
+```
+
+Despite the important number of syndemic conditions studied in the literature, the impact of the seminal study by Stall et al.[@Stall2003] is striking as the conditions in this paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
+Furthermore, `r percent(nrow(.Stall_conditions)/nrow(summary_quantitative))` of the quantitative studies included in our review consider at least one of the four conditions studied by Stall and colleagues as part of a syndemic.
+
+Expliquer la répartition entre social/structural/mental et donner une idée de la fréquence de chaque
+
+Pointer vers le graphique et le commenter (quels sont les noeuds les plus centraux, les principales connexions, etc.)
 
@@
 
+\newpage
+
 # References
@@
 :::
+
+\newpage
+
+# Supplementary Materials
+
+```{r message=FALSE, warning=FALSE, include=FALSE}
+
+#Load the scripts to generate the tables 
+source("./scripts/supplementary_tables_CSA.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_depression.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_IPV.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_substance.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_polysubstance.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_binge.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_violence.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_anxiety.R", local = knitr::knit_global())
+
+```
+
+```{r, tab.id = "Depression", tab.cap = "Test", echo=FALSE}
+
+.depression_ft
+
+```
+
+\newpage
+
+```{r tab.id = "CSAMeasurement", echo=FALSE, message=FALSE, warning=FALSE}
+
+.CSA_ft
+
+```
+
+\newpage
+
+```{r tab.id = "IPVMeasurement", echo=FALSE, message=FALSE, warning=FALSE}
+
+.IPV_ft
+```
+
+\newpage
+
+```{r substance_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.substance_ft
+```
+
+\newpage
+
+```{r polysubstance_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.polysubstance_ft
+```
+
+\newpage
+
+```{r binge_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.binge_ft
+```
+
+\newpage
+
+```{r violence_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.violence_ft
+```
+
+\newpage
+
+```{r anxiety_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.anxiety_ft
+
+```

### 2021-07-06 Article.Rmd
Part 2.3 : syndemic conditions and their measurement

--- 2021-05-18 Article.Rmd
@@
 output: 
-  bookdown::word_document2:
+  officedown::rdocx_document:
     reference_docx: "article_template.docx"
+    page_margins:
+      bottom: 0.4
+      top: 0.4
+      right: 0.4
+      left: 0.4
+      header: 0.4
+      footer: 0.4
+      gutter: 0
+    plots:
+      style: Normal
+      align: center
+      caption:
+        style: Image Caption
+        pre: 'Figure '
+        sep: ': '
 csl: bmj.csl
@@
 library(bookdown)
+library(officedown)
+```
+
+```{r packages_data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
+
+#Load required packages :
+library(tidyverse)
+library(readr)
+library(scales)
+library(ggplot2)
+library(ggpubr)
+library(sunburstR)
+library(d3r)
+
+#Load the data from the .csv files
+source("./scripts/read_data.R", local = knitr::knit_global())
+
 ```
@@
 
-```{r PRISMA, fig.cap = "PRISMA flowchart of the included search strategy"}
+```{r PRISMA, fig.cap= "PRISMA flowchart of the search strategy", fig.height=7.5, fig.id="PRISMA", fig.width=7, fig.align='center'}
 knitr::include_graphics("Files/images/PRISMA.png")
@@
 
-```{r General_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
-#Load required packages :
-library(tidyverse)
-library(readr)
-library(scales)
-library(ggplot2)
-library(ggpubr)
-library(sunburstR)
-library(d3r)
-
-#Load the data from the .csv files
-source("./scripts/read_data.R", local = knitr::knit_global())
+```{r general_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
 
@@
 
-```{r PlotYear, fig.cap = "Plot of the cumulative number of studies published yearly, grouped by continent (A) and design (B)"}
+```{r plot_year, fig.cap="Plot of the cumulative number of studies published yearly", fig.height=7, fig.id="PlotYear", fig.width=5.5, fig.align='center'}
 
@@
 
-```{r PlotPop, fig.cap = "Number of studies focusing on a MSM subpopulation, by kind of subpopulation"}
+```{r plot_population, fig.cap="Number of studies focusing on a MSM subpopulation", fig.height=7, fig.id="PlotPop", fig.width=5.5, fig.align='center'}
 
@@
 ### Syndemic conditions and their measurement
+
+```{r syndemic_network_script, include=FALSE}
+
+source("./scripts/create_syndemic_network.R", local = knitr::knit_global())
+
+```
+
+We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "CSA"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`) and frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`).
+
+We chose to distinguish alcohol use disorder, binge drinking and alcohol use instead of merging them in a broad "alcohol-related syndemic condition".
+Some authors also considered "heavy drinking" [@Martinez2016a; @martinez2020] or "heavy alcohol use"[@Mimiaga2015b] but we chose to aggregate these conditions under "binge drinking" for clarity.
+Similarly, we distinguished substance use, substance use disorder, intravenous drug use, polysubstance use, marijuana use, tobacco use and chemsex since they differ in potential harm and context of use.
+
+```{r Stall_conditions, include=FALSE}
+.Stall_conditions <- summary_quantitative %>%
+  filter(!is.na(CSA) | (!is.na(depression) | (!is.na(polysubstance) | (!is.na(IPV)))))
+
+```
+
+Despite the important number of syndemic conditions studied in the literature, the impact of the seminal study by Stall et al.[@Stall2003] is striking as the conditions in this paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
+Furthermore, `r percent(nrow(.Stall_conditions)/nrow(summary_quantitative))` of the quantitative studies included in our review consider at least one of the four conditions studied by Stall and colleagues as part of a syndemic.
+
+In order to better understand the connections between the syndemic conditions in the studies we elaborated a network plot (Figure \@ref(fig:SyndemicNetwork)).
+Nodes represent the syndemic conditions studied in the literature and edges are drawn between two nodes when two conditions are studied in the same research paper.
+Furthermore, edges between nodes are thicker as the two conditions are frequently studied together.
+
+In this graph, we divided each conditions into 4 categories : mental health (e.g.
+depression, anxiety, PTSD), social conditions (e.g.
+substance use, loneliness), structural conditions (e.g.
+unemployment, healthcare access) and physical health (e.g.
+STI, HIV) .
+When viewing this graph, it is readily apparent that structural syndemic conditions and physical health-related syndemic conditions are way less central than social syndemic conditions and mental health-related syndemic conditions.
+
+Regarding the edges of the network, we identified `r nrow(edges)` pairs of syndemic conditions.
+However, nearly half of these pairs of conditions (N = `r nrow(.edges_1)`) appear in only one research paper.
+On the other hand , the most studied pairs of syndemic conditions were depression and IPV (N = `r edges$weight[edges$from == 1 & edges$to == 4]`), depression and substance use (N = (N = `r edges$weight[edges$from == 1 & edges$to == 2]`), depression and CSA (N = `r edges$weight[edges$from == 1 & edges$to == 10]`), depression and polysubstance use (N = `r edges$weight[edges$from == 1 & edges$to == 11]`) and IPV and CSA (N = `r edges$weight[edges$from == 4 & edges$to == 10]`).
+
+We also computed centrality indices for this network, namely degree centrality, the sum of weight in the network, closeness centrality, the inverse of the total length of the paths from a node to all other nodes, and betweennness, the number of shortest path passing through a node[@opsahl2010].\
+Because the weight of the nodes in this network corresponds to the number of studies in which the syndemic conditions appear, degree centrality of each node does is nearly perfectly correlated to the number of studies in which the syndemic condition was studied (`r paste0("r(", .cor_degree$parameter,")", " = ", round(.cor_degree$estimate, digits = 2), ", ", pvalue(.cor_degree$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE))`).\
+Closeness centrality and betweenness centrality are also strongly correlated to the number of studies `r paste0("(r(", .cor_closeness$parameter,")", " = ", round(.cor_closeness$estimate, digits = 2), ", ", pvalue(.cor_closeness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " and r(", .cor_betweenness$parameter,")", " = ", round(.cor_betweenness$estimate, digits = 2), ", ", pvalue(.cor_betweenness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " respectively)")`.
+Interestingly, the betweenness centrality of unstable housing is notably high given the low number of studies taking this syndemic condition into account (N = `r nodes$studies[nodes$label == "unstable_housing"]`).
+Betweenness centrality can be seen as the extent of brokerage a node can exert on a network [@zweig2016].
+Moreover, the three structural syndemic conditions "unstable housing", "incarceration" and "poverty" are mostly connected between each others.
+In other words, in syndemic literature, unstable housing acts as a bridge, notably between the two aforementioned structural syndemic conditions and the rest of the syndemic conditions.
+Indeed, unstable housing as been studied alongside `r nrow(.edges_UH)` other syndemic conditions : depression, substance use, IPV, binge drinking, sexual compulsivity, IDU, CSA, polysubstance use, incarceration, poverty, unemployment, discrimination, poor healthcare access, alcohol use and violence.
+
+```{r syndemic_network_plot, fig.cap="Network of the syndemic conditions studied in quantitative research.
+The centrality of the nodes gives an indication on the importance of the condition in the literature, the most studied conditions being the most central.
+Moreover, each node is circled by a pie chart of their frequency in the review.
+The thickness of the edges linking two nodes depends on the number of studies in which the two conditions were studied together.", fig.id="SyndemicNetwork", fig.width=7.45, fig.height=5.32, fig.align='center'}
+
+knitr::include_graphics("./Output/Plots/syndemic_network.png")
+```
+
+```{r measurement_data, message=FALSE, warning=FALSE, include=FALSE}
+
+#Load the scripts to generate the tables 
+source("./scripts/supplementary_tables_CSA.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_depression.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_IPV.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_substance.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_polysubstance.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_binge.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_violence.R", local = knitr::knit_global())
+source("./scripts/supplementary_tables_anxiety.R", local = knitr::knit_global())
+```
+
+The other part of our research question was to examine the way the syndemic conditions were studied in the literature.
+For the most often studied syndemic conditions, we found an important variability in their measurement.
+Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies.
+For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions represented in less than 10% of our studies sample.
+
+For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria were used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.\
+66 studies used scales while 10 studies used criteria to assess the presence of depression or depressive symptoms among the participants.
+The most used scales were the full Center for Epidemiologic Studies-Depression scale [CESD] (N = 24) and the 10-items version of this scale [CESD-10] (N=10), the 9-items version of the Patient Health Questionnaire [PHQ-9] (N=8) and the Beck Depression Inventory [BDI-II] (N = 5).\
+Cutoff for these scales varied the most for the CESD (range : 16 to 27) and the PHQ-9 (range : 5 to 15).\
+When a scale was not used, the most frequent criteria to assess the presence of depression was the participant being on medication for depression in the past 12 months (N = 4).\
+Table S1 summarizes every scales, criteria and cutoff used in the measurement of depression as well as the references of the studies.
+
+For IPV, 5 types of intimate partner violence were identified : physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), gay-related violence (e.g.
+threats of revealing the partner's sexual orientation ; N = `r .IPV_prevalence$sum[["gay-related IPV"]]`) and HIV-related violence (e.g.
+threats of disclosing the partner's serologic status ; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`).
+Reference period varied from past month to lifetime.\
+Furthermore, 7 studies used a scale to assess the presence of IPV : the HITS scale (N = 3) the Revised Conflict Tactics Scale [CTS2] (N= 3) and a scale developed by the authors of the study, assessing physical and psychological violence[@Yu2013].\
+Table S2 summarizes every combination of IPV, reference periods, scales and cutoff used as well as the references of the studies.
+
+For substance use, we looked at the class of substances explicitly screened by the authors and the reference period used.
+The most frequently screened class of substance was stimulants (i.e.
+cocaine/crack, amphetamines ; N = `r .substances_prev$sum[["stimulants"]]`), followed by depressants (i.e.
+GHB/GBL, benzodiazepines without prescriptions ; (N = `r .substances_prev$sum[["depressants"]]`), opioids (i.e.
+opioids misuse and ecstasy ; N = `r .substances_prev$sum[["opioids"]]`), marijuana (N = `r .substances_prev$sum[["marijuana"]]`), ecstasy /MDMA (N = `r .substances_prev$sum[["ecstasy"]]`), hallucinogens (i.e.
+ketamine, psilocybine, phencyclidine ; N = `r .substances_prev$sum[["hallucinogens"]]`), inhalants (nitrous oxyde, Popper ; N = `r .substances_prev$sum[["inhalants"]]`) and new psychoactive substances (i.e.
+synthetic cannabinoids, cathinones ; N = `r .substances_prev$sum[["NPS"]]`).\
+Reference period ranged from past month to lifetime.\
+Table S3 summarizes every class of substances screened and reference period as well as the references of the studies.
+
+For CSA, we identified `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Definition"]))` different definitions and `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Scale"]))` scales among the `r nodes$studies[nodes$label == "CSA"]` studies.
+The various definitions differed on the age at which the sexual intercourse occurred to be qualified as childhood sexual abuse, the age gap between the victim and the perpetrator and the need for the sexual intercourse to be unwanted.
+The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (N = 7).\
+Table S4 summarizes every definition and scales as well as the references of the studies.
+
+For polysubstance use, 17 studies considered there were polysubstance when 3 or more class of substance use were used while 9 studies defined polysubstance use as more than one class of substance use.
+Moreover, 4 studies excluded marijuana from the class of substances screened and 1 study excluded stimulants, because stimulants were already screened in another syndemic condition.\
+Table S5 summarizes every definition of polysubstance use and the references of the studies.
+
+For binge drinking, we identified `r length(unique(.binge_measurement$binge_episodes))` different thresholds for binge drinking, differing on the number and frequency of binge drinking episodes.
+The threshold ranged from one episode in the past 12 months to more than one episode per week, every week in the past 12 months.\
+Table S6 summarizes every definition and reference period used as well as the references of the studies.
+
+Measurement of sexual compulsivity was surprisingly standardized, compared to the rest of the most frequently studied syndemic conditions.
+Nearly every study used the Kalichman's Sexual Compulsivity Scale, with cutoff ranging from 20 to 26, except for two studies using the Compulsive Sexual Behavior Inventory[@Herrick2013; @Dyer2012] and one study using a scale devised by the authors[@Wang2017].
+
+For AUD, we identified 4 different definitions.
+`r sum(str_count(measurement$AUD_scale, pattern = "AUDIT-10"), na.rm = T)` studies used the full Alcohol Use Disorder Identification Test (AUDIT-10) [@tomori2018; @Morrison2018a; @semple2017; @Biello2014; @tan2016; @achterbergh2021; @shuper2020; @scheer2021], `r sum(str_count(measurement$AUD_scale, pattern = "AUDIT-C"), na.rm = T)` studies used the 3-items version of this screening test (AUDIT-C) [@Chakrapania; @Perry; @Ogunbajo2019; @sullivan2020], `r sum(str_count(measurement$AUD_scale, pattern = "CAGE"), na.rm = T)` studies used the CAGE questionnaire [@Zhang2019; @Biello2016; @oleary2014; @Mimiaga2015; @Safren2018] and one study used clinical diagnosis based on the DSM-IV criteria[@Mustanski2017].
+
+Regarding suicide, `r sum(is.na(measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered only suicidal thoughts[@lee2020; @Mustanski2017; @Biello2016; @Mimiaga2015; @Halkitis2015; @scheer2021] , `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered both suicidal thoughts and suicide attempts[@McDaid2019a; @ferlatte2018; @Ferlatte2018a; @Guadamuz2014; @Halkitis2013] and `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & is.na(measurement$suicidal_thoughts))` studies considered only suicide attempts[@ocleirigh2018; @Branstrom2018; @Pantalone2018] .
+Furthermore, one study used the Positive and Negative Suicide Ideation scale (PANSI)[@oginni2019] and one study used the Suicide Behaviors Questionnaire-Revised (SBQ-R)[@ng2020].
+
+A number of behaviors have been used to define sexual risk behaviors as a syndemic condition.
+The most widely used of these criteria is condomless anal sex (N = `r sum(!is.na(measurement$CAS))`)[@chandler2020; @Wu2018; @semple2017; @beymer2016; @Li2016; @Halkitis2015; @Mustanski2014; @eaton2013; @Halkitis2013a; @Storholm2011; @blondeel2021], followed by the number of partners (N = `r sum(!is.na(measurement$number_partners))`)[@chandler2020; @Wu2018; @semple2017; @beymer2016; @Li2016; @Mustanski2014; @blondeel2021] .
+The condomless anal sex criteria has been refined in three studies, two of them taking into account the type of partner (regular versus casual)[@Friedman2015; @friedman2016] and one, the serologic status of both partners[@Ferlatte2015].\
+Other criteria such as condomless oral sex[@Halkitis2015; @Halkitis2013a; @Storholm2011] , condomless vaginal sex[@eaton2013], STI diagnosis[@chandler2020], engagement in sex work[@chandler2020] and sexual intercourse with a HIV positive partner[@chandler2020] have been used.
+Finally, one study used the Kalichman's Sexual Sensation Seeking Scale to assess the propensity of participants to engage in novel or risky sexual stimulation [@Wim2014a].
+
+For violence `r .violence_prevalence$sum[["sexual"]]` studies looked at sexual violence, `r .violence_prevalence$sum[["physical"]]`, at physical violence and `r .violence_prevalence$sum[["psychological"]]` at psychological violence.
+One Indian study also took into account sexual and physical harassment by the police[@Chakrapani2017].\
+Table S7 summarizes every combination of violence studied, the reference period as well as the reference of the studies.
+
+Several types of anxiety disorder were studied : generalized anxiety disorder (N = `r sum(!is.na(measurement$"generalized anxiety disorder"))`), social phobia (N = `r sum(!is.na(measurement$"social phobia"))`) and panic disorder (N = `r sum(!is.na(measurement$"panic disorder"))`).
+The type of anxiety disorder screened was not specified in `r sum(!is.na(measurement$"not specified"))` studies.\
+`r length(unique(.anxiety_measurement$criteria))` different criteria were used to assess the presence of an anxiety disorder among the `r nodes$studies[nodes$label == "anxiety"]` studies considering anxiety as a syndemic condition.
+The most frequent criteria was a score equal or greater than 10 on the 7-items version of the Generalized Anxiety Disorder screening test (GAD-7 ; N = `r sum(!is.na(measurement$"GAD-7"))`).\
+Table S8 summarizes every combination of anxiety disorder studied, the criteria or scale used and the cutoff or reference period, as appropriate, as well as the references of the studies.
+
+SUD was screened through a clinical diagnosis based on the DSM-IV[@Batchelder2019; @carrico2018; @buttram2015; @Kurtz2012], mention of substance abuse in the electronic medical record[@Byg2016] or the participant thinking he should reduce his substance use[@Ferlatte2014].
+Several screening test were also used : the Drug Use Disorder Identification Test (DUDIT)[@Morrison2018a; @tan2016; @achterbergh2021], the Texas Christian University Drug Screen (TCUDS)[@Zhang2019; @OLeary2014b], the Mini International Neuropsychiatric Interview (MINI)[@Safren2018] and the 10-items Drug Abuse Screening Test (DAST-10)[@chuang2018].
+
+Outside of binge drinking and alcohol use disorder, which represents two distinct syndemic conditions, we aggregated three aspects of alcohol use studied in syndemic literature to form a generic "alcohol use" syndemic condition : alcohol consumption[@Halkitis2015; @Yu2013; @oginni2019; @Halkitis2013], alcohol use until intoxication[@Halkitis2012; @Guadamuz2014; @Storholm2011] and early alcohol use[@Hirshfield2015].
+
+Finally, for discrimination, there were as many criteria as there were research papers studying this condition.
+Most of the studies only considered discrimination based on sexual orientation, except for two studies examining racist discrimination[@turpin2020; @dyer2020], one study examining HIV-based discrimination[@chuang2018] and one study who did not distinguish discrimination based on sexuality, race/ethnicity or any other factor[@Martinez2016a].
 
@@
 :::
+
+\newpage
+
+# Supplementary Materials
+
+```{r, tab.id = "Depression", tab.cap = "Test", echo=FALSE}
+
+.depression_ft
+
+```
+
+\newpage
+
+```{r tab.id = "IPVMeasurement", echo=FALSE, message=FALSE, warning=FALSE}
+
+.IPV_ft
+```
+
+\newpage
+
+```{r substance_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.substance_ft
+```
+
+\newpage
+
+```{r tab.id = "CSAMeasurement", echo=FALSE, message=FALSE, warning=FALSE}
+
+.CSA_ft
+
+```
+
+\newpage
+
+```{r polysubstance_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.polysubstance_ft
+```
+
+\newpage
+
+```{r binge_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.binge_ft
+```
+
+\newpage
+
+```{r violence_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.violence_ft
+```
+
+\newpage
+
+```{r anxiety_measurement, echo=FALSE, message=FALSE, warning=FALSE}
+
+.anxiety_ft
+
+```

### 2021-07-06 Scripts/create_syndemic_network.R

@@ -177,3 +177,18 @@ syndemic_network <- qgraph(edges,
                            filename = "./Output/Plots/syndemic_network",
                            filetype = "png")
 
+.syndemic_centrality <- centrality(syndemic_network)
+nodes$degree <- .syndemic_centrality$OutDegree
+nodes$closeness <- .syndemic_centrality$Closeness
+nodes$betweenness <- .syndemic_centrality$Betweenness
+.cor_degree <- cor.test(nodes$studies, nodes$degree)
+.cor_closeness <- cor.test(nodes$studies, nodes$closeness)
+.cor_betweenness <- cor.test(nodes$studies, nodes$betweenness)
+
+.edges_UH <- edges %>%
+  filter(edges$from == "16" | edges$to == "16")
+
+.edges_1 <- edges %>%
+  filter(edges$weight <= 1)
+
+

### 2021-07-06 Scripts/create_population_plot.R
Correction of package conflict

@@ -1,3 +1,5 @@
+detach("package:flextable", unload=TRUE)
+
 
 .age_pop_plot <- ggplot(data = population, aes(x = fct_infreq(age))) +
   geom_bar(fill = c("#FE9666", "#A66999", "#FD625E", "#F2C80F")) +
@@ -9,7 +11,7 @@
             cex = 3) + 
   xlab("Age group") +
   ylab("Number of studies") +
-  labs(title = "Age groups of study participants")+
+  labs(title = "Age groups of study participants") +
   font("title", size = 8, face = "bold") +
   font("xlab", size = 7) +
   font("ylab", size = 7) +

### 2021-08-09 _bookdown_files/04-results.Rmd
Bookdown conversion

---
bibliography: references.bib
---

```{r include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

```

```{r packages_data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

#Load required packages :
library(tidyverse)
library(readr)
library(scales)
library(ggplot2)
library(ggpubr)
library(sunburstR)
library(d3r)

#Load the data from the .csv files
source("./scripts/read_data.R", local = knitr::knit_global())

```

# Results

This part of the paper answers to the three main research questions of our protocol : "How are studies concerning Syndemic Theory applied to MSM conducted ?" ; "How is the concept of interaction explored in syndemic research applied to MSM ?" and "What were the key findings of these studies ?". \@ref(tab:RefTabQuant), \@ref(tab:RefTabQual) and \@ref(tab:RefTabRev) in our supplementary material, summarize every reference identified and the variables extracted to answer our research questions for quantitative studies, qualitative studies and reviews, respectively.

## Literature search

The electronic search identified 769 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 . After removing duplicates, 277 records were screened for inclusion.

After screening the title and abstract, 109 records were excluded. The two main reasons for exclusion at this stage were that MSM were not the main study population (n=46) and that syndemic was not the main focus of the paper (n=34). 29 studies were excluded because the type of publication did not meet our inclusion criteria.

The full texts of the 168 remaining references were obtained and read; 59 were excluded after this phase. During the previous step, we had decided to tentatively include papers in which the sample was not entirely comprised of MSM. After reviewing the full paper, we decided to exclude studies if the MSM data was aggregated with data from another population (n=9), most commonly transgender women. The rationale for this decision was to keep the focus clearly on MSM.

The PRISMA flowchart generated by DistillerSR can be found in Figure \@ref(fig:PRISMA)

```{r PRISMA, fig.cap= "PRISMA flowchart of the search strategy", fig.height=7.5, fig.id="PRISMA", fig.width=7, fig.align='center'}
knitr::include_graphics("Files/images/PRISMA.png")

```

## How are studies concerning Syndemic Theory applied to MSM conducted?

### General characteristics of included studies

```{r general_characteristics_data_preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

#Source the scripts used to manipulate the data from the .csv files
source("./scripts/create_year_design.R", local = knitr::knit_global())
source("./scripts/create_location_data.R", local = knitr::knit_global())
source("./scripts/create_sample.R", local = knitr::knit_global())

#Create the plot 
source("./scripts/create_plot_year.R", local = knitr::knit_global())

```

The publication date of the studies ranges from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published annually from 2013 onward as illustrated in Figure \@ref(fig:PlotYear). There is also an increase in the diversity of the studies, both in the study design used and the continents where the studies were conducted.

```{r plot_year, fig.cap="Plot of the cumulative number of studies published yearly", fig.height=7, fig.id="PlotYear", fig.width=5.5, fig.align='center'}

knitr::include_graphics("./Output/Plots/Plot_Year.png")

```

However, despite the increasing diversity, the vast majority of the studies were conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the United States of America (N= `r .USA_studies`). The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`). South America and Africa were the least represented continents, with only `r .South_America_studies` and `r .Africa_studies` studies respectively.

In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r .N_cross_sec`). The number of longitudinal studies grew steadily since 2014 and represents `r percent(.N_long/nrow(overview_of_studies))` of the papers. The duration of longitudinal studies ranged from `r min(summary_quantitative$study_duration[summary_quantitative$design == "Longitudinal"], na.rm = T)` to `r max(summary_quantitative$study_duration[summary_quantitative$design == "Longitudinal"], na.rm = T)` months.

Compared to quantitative studies, qualitative studies are under-represented, with only `r .N_qual` papers. In terms of analysis method, the most common was thematic (content) analysis (N= `r sum(!is.na(summary_qualitative$thematic_content)) + sum(!is.na(summary_qualitative$thematic))`). The rest of the studies consisted in framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and life-story interviews (N = `r sum(!is.na(summary_qualitative$life_story))`).

We only identified 2 mixed methods design were identified[@buttram2015; @Halkitis2012]; Buttram et al. employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part while Halkitis et al used a cross-sectional quantitative survey and in-depth discovery interviews.

The first systematic reviews and meta-analyses were published, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])`, while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.

Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported ranged from `r min(sample$age, na.rm = T)` to `r round(max(sample$age, na.rm = T), digits = 0)` years.

### Subpopulations studied

```{r Subpopulation_data_prep, message=FALSE, warning=FALSE, include=FALSE}
source("./scripts/create_population_data.R", local = knitr::knit_global())
source("./scripts/create_population_plot.R", local = knitr::knit_global())

```

Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM. In this review, we identified 6 types of MSM subpopulations studied in syndemic literature : (a) young MSM and older MSM ; (b) MSM from a racial/ethnic minority ; (c) MSM living with HIV ; (d) MSM engaged in sex work ; (e) Men who have Sex with Men and Women (MSMW) ; and (f) transgender MSM.

Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r sum(population$age == "Older men")` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r sum(population$age == "Adolescent")` study focuses on adolescents[@Perry]. Of note, the two studies on older MSM are both entirely composed of a sample of older MSM living with HIV.

Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample. Among these studies, `r .N_YBMSM` studies are composed of young BMSM[@Maiorana; @Reed2016] and `r .N_MSM_SW` study focuses on Black MSM engaged in sex work[@chandler2020].\
`r sum(population$race_ethnicity == "Latino")` studies focus on Latino MSM (LMSM) and `r .N_LMSMW` of these studies focus on Latino MSMW[@Munoz-Laboy2018]. Furthermore, `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].

Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV. Apart from the aforementioned studies on older MSM living with HIV, `r sum(population$serologic_status == "HIV-positive" & population$age == "Young adult")` studies focus on young MSM living with HIV[@Lyons2013; @Bruce2011] . Notably, we identified no studies conducted on racial minority MSM living with HIV.

Finally, the least represented subpopulation of MSM in this review are MSMW (N = `r sum(population$sex_behav == "MSMW")`), MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`). Strikingly, transgender MSM, in addition to being the focus of only one study[@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.

Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.

In order to have the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulation.\
`r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].

```{r plot_population, fig.cap="Number of studies focusing on a MSM subpopulation", fig.height=7, fig.id="PlotPop", fig.width=5.5, fig.align='center'}

knitr::include_graphics("./Output/Plots/Plot_population.png")
```

### Syndemic conditions and their measurement

#### Number and type of syndemic conditions identified

```{r syndemic_network_script, include=FALSE}

source("./scripts/create_syndemic_network.R", local = knitr::knit_global())

```

We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "CSA"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`) and frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`).

We chose to distinguish alcohol use disorder, binge drinking and alcohol use instead of merging them in a broad "alcohol-related syndemic condition". Some authors also considered "heavy drinking" [@Martinez2016a; @martinez2020] or "heavy alcohol use"[@Mimiaga2015b] but we chose to aggregate these conditions under "binge drinking" for clarity. Similarly, we distinguish between substance use, substance use disorder, intravenous drug use, polysubstance use, marijuana use, tobacco use and chemsex since they differ in potential harm and the context of use.

```{r Stall_conditions, include=FALSE}
.Stall_conditions <- summary_quantitative %>%
  filter(!is.na(CSA) | (!is.na(depression) | (!is.na(polysubstance) | (!is.na(IPV)))))

```

Despite the important number of syndemic conditions studied in the literature, the impact of the seminal study by Stall et al.[@Stall2003] is striking as the conditions in this paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field. Furthermore, `r percent(nrow(.Stall_conditions)/nrow(summary_quantitative))` of the quantitative studies included in our review consider at least one of the four conditions studied by Stall and colleagues as part of a syndemic.

#### Network analysis of the syndemic conditions

In order to better understand the connections between the syndemic conditions in the studies we elaborated a network plot (Figure \@ref(fig:SyndemicNetwork)). Nodes represent the syndemic conditions studied in the literature and edges are drawn between two nodes when two conditions are studied in the same research paper. Furthermore, edges between nodes are thicker as the two conditions are frequently studied together. Furthermore, circles around the nodes represent pie chart of their frequency in syndemic literature. For example, depression, the most studied condition, appears in `r percent((nodes$studies[nodes$label == "depression"])/nrow(summary_quantitative))` of our sample. As such, the node is circled by a chart representing this proportion. Moreover, as a force-directed graph, the location of the nodes gives an indication regarding their importance. As such, depression occupies a more central position than ADHD which was only studied once.

In this graph, we divided each conditions into 4 categories : mental health (e.g. depression, anxiety, PTSD), social conditions (e.g. substance use, loneliness), structural conditions (e.g. unemployment, healthcare access) and physical health (e.g. STI, HIV) . When viewing this graph, it is readily apparent that structural syndemic conditions and physical health-related syndemic conditions are much less central than social syndemic conditions and mental health-related syndemic conditions.

Regarding the edges of the network, we identified `r nrow(edges)` pairs of syndemic conditions. However, nearly half of these pairs of conditions (N = `r nrow(.edges_1)`) appear in only one research paper. On the other hand , the most studied pairs of syndemic conditions were depression and IPV (N = `r edges$weight[edges$from == 1 & edges$to == 4]`), depression and substance use (N = (N = `r edges$weight[edges$from == 1 & edges$to == 2]`), depression and CSA (N = `r edges$weight[edges$from == 1 & edges$to == 10]`), depression and polysubstance use (N = `r edges$weight[edges$from == 1 & edges$to == 11]`) and IPV and CSA (N = `r edges$weight[edges$from == 4 & edges$to == 10]`).

We also computed centrality indices for this network, namely degree centrality, the sum of weight in the network, closeness centrality, the inverse of the total length of the paths from a node to all other nodes, and betweenness, the number of shortest path passing through a node[@opsahl2010].\
Because the weight of the nodes in this network corresponds to the number of studies in which the syndemic conditions appear, degree centrality of each node does is nearly perfectly correlated to the number of studies in which the syndemic condition was studied (`r paste0("r(", .cor_degree$parameter,")", " = ", round(.cor_degree$estimate, digits = 2), ", ", pvalue(.cor_degree$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE))`).\
Closeness centrality and betweenness centrality are also strongly correlated to the number of studies `r paste0("(r(", .cor_closeness$parameter,")", " = ", round(.cor_closeness$estimate, digits = 2), ", ", pvalue(.cor_closeness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " and r(", .cor_betweenness$parameter,")", " = ", round(.cor_betweenness$estimate, digits = 2), ", ", pvalue(.cor_betweenness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " respectively)")`. Interestingly, the betweenness centrality of unstable housing is notably high given the low number of studies taking this syndemic condition into account (N = `r nodes$studies[nodes$label == "unstable_housing"]`). Betweenness centrality can be seen as the extent of brokerage a node can exert on a network [@zweig2016]. Moreover, the three structural syndemic conditions "unstable housing", "incarceration" and "poverty" are grouped together, indicating that they are frequently studied together. In other words, in syndemic literature, unstable housing acts as a bridge, notably between the two aforementioned structural syndemic conditions and the rest of the syndemic conditions. Indeed, unstable housing has been studied alongside `r nrow(.edges_UH)` other syndemic conditions : depression, substance use, IPV, binge drinking, sexual compulsivity, IDU, CSA, polysubstance use, incarceration, poverty, unemployment, discrimination, poor healthcare access, alcohol use and violence.

```{r syndemic_network_plot, fig.cap="Network of the syndemic conditions studied in quantitative research. As a force-directed network, the most studied and interconnected conditions are the most central. Moreover, each node is circled by a pie chart of their frequency in the review. The thickness of the edges linking two nodes depends on the number of studies in which the two conditions were studied together.", fig.id="SyndemicNetwork", fig.width=7.45, fig.height=5.32, fig.align='center'}

knitr::include_graphics("./Output/Plots/syndemic_network.png")
```

#### Measurement of the syndemic conditions

```{r measurement_data, message=FALSE, warning=FALSE, include=FALSE}

source("./scripts/supplementary_tables/depression.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/IPV.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/substance.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/CSA.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/polysubstance.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/binge.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/violence.R", local = knitr::knit_global())
source("./scripts/supplementary_tables/anxiety.R", local = knitr::knit_global())

```

The next part of our research question was to examine the way the syndemic conditions were studied in the literature. For the most often studied syndemic conditions, we found a high degree of variability in their measurement. Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies. For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our studies sample.

For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria were used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.\
66 studies used scales while 10 studies used criteria to assess the presence of depression or depressive symptoms among the participants. The most frequently used scales were the full Center for Epidemiologic Studies-Depression scale [CESD] (N = 24) and the 10-items version of this scale [CESD-10] (N=10), the 9-items version of the Patient Health Questionnaire [PHQ-9] (N=8) and the Beck Depression Inventory [BDI-II] (N = 5).\
Cutoff for these scales varied the most for the CESD (range : 16 to 27) and the PHQ-9 (range : 5 to 15).\
When a scale was not used, the most frequent criteria to assess the presence of depression was the participant being on medication for depression in the past 12 months (N = 4).\
See \@ref(tab:DepressionTab) for more details.

For IPV, 5 types of intimate partner violence were identified : physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), gay-related violence (e.g. threats to reveal the partner's sexual orientation ; N = `r .IPV_prevalence$sum[["gay-related IPV"]]`) and HIV-related violence (e.g. threats to disclose the partner's serologic status ; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`). Reference period varied from past month to lifetime.\
Furthermore, 7 studies used a scale to assess the presence of IPV : the HITS scale (N = 3) the Revised Conflict Tactics Scale [CTS2] (N= 3) and a scale developed by the authors of the study, assessing physical and psychological violence[@Yu2013].\
See \@ref(tab:IPVTab) for more details.

For substance use, we looked at the class of substances explicitly screened by the authors and the reference period used. The most frequently screened class of substance was stimulants (i.e. cocaine/crack, amphetamines ; N = `r .substances_prev$sum[["stimulants"]]`), followed by depressants (i.e. GHB/GBL, benzodiazepines without prescriptions ; (N = `r .substances_prev$sum[["depressants"]]`), opioids (i.e. opioids misuse and ecstasy ; N = `r .substances_prev$sum[["opioids"]]`), marijuana (N = `r .substances_prev$sum[["marijuana"]]`), ecstasy /MDMA (N = `r .substances_prev$sum[["ecstasy"]]`), hallucinogens (i.e. ketamine, psilocybine, phencyclidine ; N = `r .substances_prev$sum[["hallucinogens"]]`), inhalants (nitrous oxyde, Popper ; N = `r .substances_prev$sum[["inhalants"]]`) and new psychoactive substances (i.e. synthetic cannabinoids, cathinones ; N = `r .substances_prev$sum[["NPS"]]`).\
Reference period ranged from the past month to over the lifetime.\
See \@ref(tab:SubstanceTab) for more details.

For CSA, we identified `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Definition"]))` different definitions and `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Scale"]))` scales among the `r nodes$studies[nodes$label == "CSA"]` studies. The various definitions differed on the age at which the sexual intercourse occurred to be qualified as childhood sexual abuse, the age gap between the victim and the perpetrator and whether the sexual intercourse was unwanted. The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (N = 7).\
See \@ref(tab:CSATab) for more details.

For polysubstance use, 17 studies considered there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used. Furthermore, 4 studies excluded marijuana from the class of substances screened and 1 study excluded stimulants, because stimulants were already screened in another syndemic condition.\
See \@ref(tab:PolysubstanceTab) for more details.

For binge drinking, we identified `r length(unique(.binge_measurement$binge_episodes))` different thresholds for binge drinking, differing on the number and frequency of binge drinking episodes. The threshold ranged from one episode in the past 12 months to more than one episode per week, every week in the past 12 months.\
See \@ref(tab:BingeTab) for more details.

Measurement of sexual compulsivity was relatively standardized, compared to the rest of the syndemic conditions. Nearly every study used the Kalichman's Sexual Compulsivity Scale, with cutoff ranging from 20 to 26, except for two studies using the Compulsive Sexual Behavior Inventory[@Herrick2013; @Dyer2012] and one study using a scale devised by the authors @Wang2017.

For AUD, we identified 4 different definitions. `r sum(str_count(measurement$AUD_scale, pattern = "AUDIT-10"), na.rm = T)` studies used the full Alcohol Use Disorder Identification Test (AUDIT-10), `r sum(str_count(measurement$AUD_scale, pattern = "AUDIT-C"), na.rm = T)` studies used the 3-items version of this screening test (AUDIT-C), `r sum(str_count(measurement$AUD_scale, pattern = "CAGE"), na.rm = T)` studies used the CAGE questionnaire and one study used clinical diagnosis based on the DSM-IV criteria.

Regarding suicide, `r sum(is.na(measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered only suicidal thoughts , `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered both suicidal thoughts and suicide attempts and `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & is.na(measurement$suicidal_thoughts))` studies considered only suicide attempts. Furthermore, one study used the Positive and Negative Suicide Ideation scale (PANSI) and one study used the Suicide Behaviors Questionnaire-Revised (SBQ-R).

A number of behaviors have been used to define sexual risk behaviors as a syndemic condition. The most widely used of these criteria is condomless anal sex (N = `r sum(!is.na(measurement$CAS))`), followed by the number of partners (N = `r sum(!is.na(measurement$number_partners))`). The condomless anal sex criteria has been refined in three studies, two of them taking into account the type of partner (regular versus casual) and one, the serologic status of both partners.\
Other criteria such as condomless oral sex, condomless vaginal sex, STI diagnosis, engagement in sex work and sexual intercourse with a HIV positive partner have been used. Finally, one study used the Kalichman's Sexual Sensation Seeking Scale to assess the propensity of participants to engage in novel or risky sexual stimulation.

For violence `r .violence_prevalence$sum[["sexual"]]` studies looked at sexual violence, `r .violence_prevalence$sum[["physical"]]`, at physical violence and `r .violence_prevalence$sum[["psychological"]]` at psychological violence. One Indian study also took into account sexual and physical harassment by the police.\
See \@ref(tab:ViolenceTab) for more details.

Several types of anxiety disorder were studied : generalized anxiety disorder (N = `r sum(!is.na(measurement$"generalized anxiety disorder"))`), social phobia (N = `r sum(!is.na(measurement$"social phobia"))`) and panic disorder (N = `r sum(!is.na(measurement$"panic disorder"))`). The type of anxiety disorder screened was not specified in `r sum(!is.na(measurement$"not specified"))` studies.\
`r length(unique(.anxiety_measurement$criteria))` different criteria were used to assess the presence of an anxiety disorder among the `r nodes$studies[nodes$label == "anxiety"]` studies considering anxiety as a syndemic condition. The most frequent criteria was a score equal or greater than 10 on the 7-items version of the Generalized Anxiety Disorder screening test (GAD-7 ; N = `r sum(!is.na(measurement$"GAD-7"))`).\
See \@ref(tab:AnxietyTab) for more details.

SUD was screened through a clinical diagnosis based on the DSM-IV, mention of substance abuse in the electronic medical record or the participant thinking he should reduce his substance use. Several screening test were also used : the Drug Use Disorder Identification Test (DUDIT), the Texas Christian University Drug Screen (TCUDS), the Mini International Neuropsychiatric Interview (MINI) and the 10-items Drug Abuse Screening Test (DAST-10).

Outside of binge drinking and alcohol use disorder, which represents two distinct syndemic conditions, we aggregated three aspects of alcohol use studied in syndemic literature to form a generic "alcohol use" syndemic condition : alcohol consumption, alcohol use until intoxication and early alcohol use.

Finally, for discrimination, there were as many criteria as there were research papers studying this condition. Most of the studies only considered discrimination based on sexual orientation, except for two studies examining racist discrimination, one study examining HIV-based discrimination and one study which did not distinguish between discrimination based on sexuality, race/ethnicity or any other factor.

### Outcomes and their measurement

```{r outcomes_data, include=FALSE}

source("./scripts/create_outcomes_data.R", local = knitr::knit_global())

```

We identified `r ncol(.outcomes) - 1` different outcomes in our sample of quantitative studies. Sexual risk behaviors was the most frequent outcome as it appeared in `r sum(!is.na(.outcomes$outcome_sexual_risk))` research papers. The second most studied outcome was HIV diagnosis (N = `r sum(!is.na(.outcomes$outcome_HIV))`), followed by STI diagnosis (N = `r sum(!is.na(.outcomes$outcome_STI))`), adherence to antiretroviral therapy (N = `r sum(!is.na(.outcomes$outcome_adherence))`), pre-exposure prophylaxis (PrEP) use (N = `r sum(!is.na(.outcomes$outcome_PrEP))`), healthcare use (N = `r sum(!is.na(.outcomes$outcome_healthcare))`) and the syndemic conditions themselves (N = `r sum(!is.na(.outcomes$outcome_syndemic))`). Less often, researchers also used viral load (N = `r sum(!is.na(.outcomes$outcome_VL))`), suicidality (N = `r sum(!is.na(.outcomes$outcome_suicide))`) or engaging in exchange sex (N = `r sum(!is.na(.outcomes$outcome_exchange_sex))`) as outcomes.

Every other outcome were only studied once : HIV screening[@Chandler2019b], physical activity[@Zhang2019], hypothalamic-pituitary-adrenal (HPA) axis dysregulation[@carrico2018], sexual violence[@semple2017], glycemic control[@Byg2016], engagement in HIV care[@Biello2016], engagement in chemsex[@friedman2014], having sexual intercourse with both men and women[@eaton2013] , help-seeking behaviors[@achterbergh2021] and substance use[@turpin2020].

There was a high degree of variability in the definition of what constitutes a sexual risk behaviors though the most frequently used proxy was, by far, condomless anal sex. Indeed, condomless anal sex was one of the criteria in `r .CAS_number` studies out of the `r sum(!is.na(.outcomes$outcome_sexual_risk))` with sexual risk behaviors as an outcome. While `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CAS))` studies considered all form of condomless anal sex as a risk behavior, the other tried to refine the criteria. The most frequent of such refinement was to consider only serodiscordant condomless anal sex as a risk behavior (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_serodiscodant_CAS))`). Other options were to only consider condomless anal sex with casual partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_casual_CAS))`), condomless anal sex without PrEP or with a detectable viral load, if HIV-positive (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_CAS)) + sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))`), receptive condomless anal sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_receptive_CAS))`) or condomless anal sex at first sexual intercourse with the current male partner (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_current_CAS))`).

Used in conjunction with condomless anal sex, other proxies for sexual risk were number of partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_number_partners))`), substance use during sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_substance_sex))`), condomless vaginal sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CVS))`), condomless oral sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_COS))`), sexual intercourse with female partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_female_sex))`) , engaging in group sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_non_disclosure))`) and non-disclosure of HIV serostatus before first sexual intercourse with current main partner (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_non_disclosure))`).

When HIV was used as an outcome, it was self-reported in nearly half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-report was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`).

### Interventions

We identified only `r .N_int` interventional studies guided by syndemic theory [@Chakrapani; @achterbergh2021]. Chakrapani et al. used a pre-test/post-test non-equivalent group design and the intervention consisted in motivational-interviews. The goal of this intervention was to reduce condomless anal intercourse by enhancing condom self-efficacy and addressing co-occurring syndemic conditions.

Achterbergh et al. conducted a randomized controlled trial and the intervention consisted in tailored feedback and help-seeking advice on mental health screening. The primary endpoint was to increase help-seeking behaviors ; the secondary endpoints were reducing sexual risk behaviors and STI incidence.

Intervention in both studies lasted for 12 months.

In Chakrapani et al. the intervention was successful in reducing the psychosocial conditions investigated (depression, alcohol use and internalised homophobia) and improving condom use. Furthermore, synergy, as measured by interaction on the additive and multiplicative scales, was present for depression and alcohol use as well as for depression and internalised homophobia on inconsistent condom use. Finally, mediation analysis revealed that the improvement in consistent condom use was due to an improvement in condom self-efficacy caused by a reduction in alcohol use and internalised homophobia.

On the other hand, the RCT of Achterbergh et al. failed to affect the primary endpoint and the two secondary endpoints.

### Summary of reviews

We found `r sum(summary_reviews$design == "Systematic review")` systematic reviews [@lewis2017; @woodward2017; @Lassiter2016] and 2 meta-analysis [@Rooney2018a; @Pantalone2020] in our review.

Woodward et al. tried to identify a set of resilience resources among MSM burdened with minority stress and psychosocial condition in order to improve HIV prevention. They included `r summary_reviews$studies_included[summary_reviews$authors== "Woodward et al."]` in their reviews and identified 31 resilience resources, with social support and incomes as the two most frequently cited. Of note, most of these resources were associated with a lower HIV risk.

Lassiter et al. wanted to propose a framework to include religion and spirituality into HIV research with MSM. They found that religion and spirituality had mixed effect on syndemic conditions but could be more beneficial for MSM of color than for white MSM. Of note, they only included `r summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."]` as these two factors were very sparse in syndemic literature.

Lewis et al. sought to examine the HIV prevalence and associated risk behaviors among migrant and ethnic minority MSM in North America and Europe. They found high rates of HIV prevalence and associated risk factors and proposed that transnational migration could be part of a syndemic.

In their meta-analysis, Rooney et al. tried to determine the syndemic conditions associated with sexual compulsivity among MSM and to compute the mean effect size as well as if this effect varied as a function of the type of syndemic conditions. They included `r summary_reviews$studies_included[summary_reviews$authors== "Rooney et al."]` papers and found that sexual compulsivity was significantly associated with 7 syndemic conditions (anxiety, depression, CSA, alcohol use, substance use, IPV and sexual risk behaviors). The two strongest associations were with depression and anxiety.

Finally, Pantalone et al. sought to have a better understanding of the state of interventions co-targeting interconnected syndemic conditions and HIV-related health behaviors of MSM. They included `r summary_reviews$studies_included[summary_reviews$authors== "Pantalone et al."]` studies and found a small significant positive effect of combined behavioral interventions to improve mental health, substance use, alcohol use and sexual risk behaviors, with significant heterogeneity. Interestingly, a greater number of sessions (at least 9) and individual rather than group interventions showed greater efficacy.

## How is the concept of interaction explored in syndemic research applied to MSM?

### Statistics used to show an interaction

```{r statistics_data, include=FALSE}

source("./scripts/create_statistics_data.R", local = knitr::knit_global())
```

It should be stated that, when we speak of interaction between syndemic conditions we don't necessarily mean "synergy", though synergy is indeed one of the interaction we consider. As such, we consider that a statistic method such as mediation analysis to show interaction between variables as it sheds light on the mechanism by which syndemic conditions may influence an outcome or on how syndemic conditions may influence each others.

Our review revealed a great degree of variability in statistic analysis too. The most frequently used statistic method was to conduct regression analysis using a summation score of the syndemic conditions (N = `r sum(!is.na(.statistics_data$score))`). Among studies employing this method, `r nrow(.score_data)` did not use any other method to determine the degree of interaction between syndemic conditions and the outcome.

In comparison, only `r .N_additivity` studies tried to evaluate departure from additivity on the additive and/or multiplicative scales, as recommended by Tsai [@tsai2015] to show synergy between syndemic conditions.

Furthermore, some studies sought to get a better understanding on the mechanism of interaction between the syndemic conditions and the outcome by using mediation analysis (N = `r sum(!is.na(.statistics_data$mediation))`), moderation analysis (N = `r sum(!is.na(.statistics_data$moderation))`), Structural Equation Modeling (N = `r sum(!is.na(.statistics_data$SEM))`) or path analysis (N = `r sum(!is.na(.statistics_data$path))`).

Moreover, `r .N_latent` studies used latent variables modeling such as Exploratory/Confirmatory Factor Analysis, Latent Profile Analysis, Latent Class Analysis or Latent Transition Analysis.

Using a different approach, `r sum(!is.na(.statistics_data$network))` studies conducted by Lee and colleagues [@lee2020; @Lee] used network analysis, in which syndemic is conceptualized as a network and the syndemic conditions as interconnected nodes reinforcing each others.

Finally, other statistic analysis used to assess interaction were observed/expected ratio (N = `r sum(!is.na(.statistics_data$O_E))`), cluster analysis (N = `r sum(!is.na(.statistics_data$cluster))`) and point-biserial correlation matrix (N= `r sum(!is.na(.statistics_data$biserial))`).

### Proposed mechanisms of interaction

In our sample of quantitative studies, we found only one study offering a mechanism of biological interaction @carrico2018 and one study offering a mechanism of bio-social interaction [@Klein2011].

Carrico et al. showed that the combined effects of HIV infection and methamphetamine use were detrimental for the functioning of the Hypothalamic-Pituitary-Adrenal axis which is thought to play an important part in the reinforcing effect of stimulants.

Klein proposed that attitudes towards condom was one of the key factor contributing to condomless sex and, subsequently, HIV infection. In their study, attitudes toward condoms was predicted by low self-esteem, as condom use represents a self-protecting mechanism, as well as by sexual preferences, substance use, race and education. Furthermore, childhood emotional neglect had a negative influence on self esteem thus indirectly contributing to sexual risk taking.

Qualitative studies proposed mechanism of bio-social interaction more often than quantitative studies as we identified `r sum(!is.na(summary_qualitative$bio_social_interaction))` papers with such hypothesis of interaction. On the other hand, we did not found any qualitative paper exploring biological interaction.

Stigma and structural inequalities were pointed out as the root causes of syndemic conditions and HIV risk behaviors. Maionara et al. showed that economic dependency and fear of violence may maintain YBMSM in dysfunctional relationships plagued by IPV and substance abuse which increase their odds of incarceration and HIV infection [@Maiorana]. Furthermore, methamphetamine is used as a coping strategy against this structural violence and HIV diagnosis while representing a potential factor in acquiring or transmitting HIV to others, notably during sex parties. This finding of substance use as a coping mechanism was supported by the study of Pollard et al. who found that maladaptive coping strategies to minority stress and the performative resistant space of the gay scene contributed to chemsex use [@Pollard2018a]. For Black MSM, other sources of structural violence such as racial neighborhood segregation contributed, alongside poverty, unemployment, violence, unstable housing, incarceration and poor healthcare access to expectations surrounding masculinity which may conflict with the sexual orientation of BMSM, leading to internalised homophobia [@Quinn]. Internalised homophobia, in turn, may lead to poor mental health as well as to substance abuse and sexual risk taking as coping mechanisms. Moreover, the use of PrEP, perceived as a "gay pill" may negatively impact the use of PrEP in this community. Lyons et al. also showed that the marginalization of YMSM withing their school, communities of origin and families resulted in a lack of gay-specific HIV prevention education, role-model and productive goal-related activities [@Lyons2013]. The HIV-positive MSM youth in this study linked these factors to their HIV acquisition. Finally, [@Chakrapani2019a] showed the role of family support and communities of MSM to serve as resilience resource to counteract the negative effects of stigma and syndemic conditions.

## What were the key findings of these studies?

In nearly all of the quantitative studies, the syndemic conditions chosen by the authors were found to be associated to the outcomes of interest.

However, some interesting discrepancies in the findings were found. On the topic of synergy, results were conflicting between studies. Chakrapani and colleagues found support to the three models of interacting epidemics (synergistically interactig epidemics, serially causal epidemics and mutually causal epidemics) with the strongest support for the model of synergistically interacting epidemics [@Chakrapani2019]. These findings were supported by other studies who found synergy when using significant product terms in the additive and/or multiplicative scales [@Chakrapani; @chandler2020; @Chandler2019; @tomori2018]. However, other studies found no synergy between the syndemic conditions using the same statistical approach [@Batchelder2019; @shuper2020; @Ferlatte2018a].

Conflicting results were also found for MSMW. Brandstrom and Pachankis found no clustering of syndemic conditions for MSMW [@Branstrom2018] while Mustanski et al. found a stronger clustering of syndemic conditions in YMSMW compared to YMSM[@Mustanski2014]. Furthermore, Dyer et al. found more STI in the Black MSM compared to the Black MSMW [@dyer2020] and Ferlatte found more syndemic conditions in the MSM compared to the MSM [@ferlatte2018], mainly driven by party drug use and treatment for depression or anxiety. Finally, in a sample of Latino MSMW, having two syndemic conditions predicted receptive condomless anal sex and STI diagnosis but not insertive nor vaginal condomless sex [@Munoz-Laboy2018].

While condomless anal sex is often used as a proxy for the risk of acquiring HIV or another STI, the findings of some studies tend to show some limitation of this proxy. For example, Moeller et al. found an association between syndemic conditions and condomless anal sex but not with HIV diagnosis [@moeller]. A similar pattern was found in a longitudinal study that found an association between syndemic conditions and sexual risk behaviors but not with HIV or STI incidence [@Mustanski2017]. On the other hand, some authors found an association between syndemic conditions and HIV but not with condom use [@chuang2018].

Alcohol misuse was inconsistently linked to risk taking. Card et al found no association between the AUDIT score and sexual risk behaviors [@Card2018] while another study using latent class analysis found that the class with alcohol misuse had a lower level of risk behaviors [@scheer2021]. Nonetheless, alcohol misuse was found to be associated with PrEP nonadherence [@shuper2020].

In a longitudinal study [@Mustanski2017] Black MSM were found to have the highest HIV incidence while having a lower burden of syndemic condition than White MSM, raising the question of the need to focus on syndemic conditions specific to Black MSM.

Finally, social was shown to moderate the effect of syndemic conditions on viral load, providing a significant protective effect [@friedman2016]. Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic condition on substance use showed that Black MSM with more social support had higher odds of staying in the low-risk class or transitioning from the high risk class to the low-risk class [@turpin2020]. However, Chakrapani et al. found no moderation of social support on the relationship between syndemic conditions and risk taking [@Chakrapani2017].

### 2021-08-09 _bookdown_files/08-appendix.Rmd
Bookdown conversion

<!---BLOCK_LANDSCAPE_START--->

# Supplementary Materials

### A. Reference tables

```{r reference_table_quantitative, tab.id = "RefTabQuant", echo=FALSE, message=FALSE, warning=FALSE}

source("./scripts/supplementary_tables/reference_quantitative.R", local = knitr::knit_global())
.reference_quantitative_ft
```

\newpage

```{r reference_table_qualitative, tab.id = "RefTabQual", echo=FALSE, message=FALSE, warning=FALSE}

source("./scripts/supplementary_tables/reference_qualitative.R", local = knitr::knit_global())
.reference_qualitative_ft
```

\newpage

```{r reference_table_reviews, tab.id = "RefTabRev", echo=FALSE, message=FALSE, warning=FALSE}

source("./scripts/supplementary_tables/reference_reviews.R", local = knitr::knit_global())
.reference_reviews_ft
```

<!---BLOCK_LANDSCAPE_STOP--->

#### List of references included in the review

Achterbergh, R.C.A., van Rooijen, M.S.,
van den Brink, W., Boyd, A., e Vries, H.J.C., 2021. Enhancing help-seeking
behaviour among men who have sex with men at risk for sexually transmitted
infections: the syn.bas.in randomised controlled trial. Sex Transm Infect 97,
11--17. <https://doi.org/10.1136/sextrans-2020-054438>

Adam, B.D., Hart, T.A., Mohr, J., Coleman,
T., Vernon, J., 2018. Resilience pathways, childhood escape routes, and mentors
reported by gay and bisexual men affected by syndemic conditions. Sexualities
22, 642. <https://doi.org/10.1177/1363460718758663>

Adam, B.D., Hart, T.A., Mohr, J., Coleman,
T., Vernon, J., 2017. HIV-related syndemic pathways and risk subjectivities
among gay and bisexual men: a qualitative investigation. Cult Health Sex 19,
1254--1267. <https://doi.org/10.1080/13691058.2017.1309461>

Batchelder, A.W., Choi, K., Dale, S.K.,
Pierre-Louis, C., Sweek, E.W., Ironson, G., Safren, S.A., O'Cleirigh, C., 2019.
Effects of syndemic psychiatric diagnoses on health indicators in men who have
sex with men. Health Psychology 38, 509--517. <https://doi.org/10.1037/hea0000724>

Beymer, M.R., Weiss, R.E., Halkitis, P.N.,
Kapadia, F., Ompad, D.C., Bourque, L., Bolan, R.K., 2016. Disparities Within
the Disparity-Determining HIV Risk Factors Among Latino Gay and Bisexual Men
Attending a Community-Based Clinic in Los Angeles, CA. J Acquir Immune Defic
Syndr 73, 237--244. <https://doi.org/10.1097/QAI.0000000000001072>

Biello, K.B., Colby, D., Closson, E.,
Mimiaga, M.J., 2014. The syndemic condition of psychosocial problems and HIV
risk among male sex workers in Ho Chi Minh City, Vietnam. AIDS Behav 18, 1264--1271.
<https://doi.org/10.1007/s10461-013-0632-8>

Biello, K.B., Oldenburg, C.E., Safren,
S.A., Rosenberger, J.G., Novak, D.S., Mayer, K.H., Mimiaga, M.J., 2016.
Multiple syndemic psychosocial factors are associated with reduced engagement
in HIV care among a multinational, online sample of HIV-infected MSM in Latin
America. AIDS Care 28 Suppl 1, 84--91.
<https://doi.org/10.1080/09540121.2016.1146205>

Blashill, A.J., Brady, J.P., Rooney, B.M.,
Rodriguez-Diaz, C.E., Horvath, K.J., Blumenthal, J., Morris, S., Moore, D.J.,
Safren, S.A., 2020. Syndemics and the PrEP Cascade: Results from a Sample of
Young Latino Men Who Have Sex with Men. Arch Sex Behav 49, 125--135.
<https://doi.org/10.1007/s10508-019-01470-7>

Blondeel, K., Dias, S., Furegato, M.,
Seuc, A., Gama, A., Fuertes, R., Mendao, L., Temmerman, M., Toskin, I., 2021.
Sexual behaviour patterns and STI risk: results of a cluster analysis among men
who have sex with men in Portugal. BMJ Open 11, e033290.
<https://doi.org/10.1136/bmjopen-2019-033290>

Bränström, R., Pachankis, J.E., 2018.
Validating the Syndemic Threat Surrounding Sexual Minority Men's Health in a
Population-Based Study With National Registry Linkage and a Heterosexual
Comparison. J. Acquir. Immune Defic. Syndr. 78, 376--382.
<https://doi.org/10.1097/QAI.0000000000001697>

Bruce, D., Harper, G.W., Interventions,
A.M.T.N. for H., 2011. Operating without a safety net: gay male adolescents and
emerging adults' experiences of marginalization and migration, and implications
for theory of syndemic production of health disparities. Health Educ Behav 38,
367--378. <https://doi.org/10.1177/1090198110375911>

Buttram, M.E., Kurtz, S.P., 2015. A mixed
methods study of health and social disparities among substance-using African
American/Black men who have sex with men. J Racial Ethn Health Disparities 2, 1--10.
<https://doi.org/10.1007/s40615-014-0042-2>

Byg, B., Bazzi, A.R., Funk, D., James, B.,
Potter, J., 2016. The Utility of a Syndemic Framework in Understanding Chronic
Disease Management Among HIV-Infected and Type 2 Diabetic Men Who Have Sex with
Men. J. Community Health 41, 1204--1211.
<https://doi.org/10.1007/s10900-016-0202-x>

Card, K.G., Lachowsky, N.J., Armstrong,
H.L., Cui, Z., Wang, L., Sereda, P., Jollimore, J., Patterson, T.L., Corneil,
T., Hogg, R.S., Roth, E.A., Moore, D.M., 2018. The additive effects of
depressive symptoms and polysubstance use on HIV risk among gay, bisexual, and
other men who have sex with men. Addict. Behav 82, 158--165.
<https://doi.org/10.1016/j.addbeh.2018.03.005>

Carrico, A.W., Rodriguez, V.J., Jones,
D.L., Kumar, M., 2018. Short circuit: Disaggregation of adrenocorticotropic
hormone and cortisol levels in HIV-positive, methamphetamine-using men who have
sex with men. Human psychopharmacology 33. <https://doi.org/10.1002/hup.2645>

Cassels, S., Meltzer, D., Loustalot, C.,
Ragsdale, A., Shoptaw, S., Gorbach, P.M., 2020. Geographic Mobility, Place
Attachment, and the Changing Geography of Sex among African American and Latinx
MSM Who Use Substances in Los Angeles. J Urban Health 97, 609--622.
<https://doi.org/10.1007/s11524-020-00481-3>

Chakrapani, V., Kaur, M., Newman, P.A.,
Mittal, S., Kumar, R., 2019a. Syndemics and HIV-related sexual risk among men
who have sex with men in India: influences of stigma and resilience. Cult
Health Sex 21, 416--431. <https://doi.org/10.1080/13691058.2018.1486458>

Chakrapani, V., Kaur, M., Tsai, A.C.,
Newman, P.A., Kumar, R., 2020. The impact of a syndemic theory-based
intervention on HIV transmission risk behaviour among men who have sex with men
in India: Findings from a pretest-posttest non-equivalent comparison group
trial. Soc Sci Med. <https://doi.org/10.1016/j.socscimed.2020.112817>

Chakrapani, V., Lakshmi, P.V.M., Tsai,
A.C., Vijin, P.P., Kumar, P., Srinivas, V., 2019b. The syndemic of violence
victimisation, drug use, frequent alcohol use, and HIV transmission risk
behaviour among men who have sex with men: Cross-sectional, population-based
study in India. SSM Popul Health 7, 100348.
<https://doi.org/10.1016/j.ssmph.2018.100348>

Chakrapani, V., Newman, P.A., Shunmugam,
M., Logie, C.H., Samuel, M., 2017. Syndemics of depression, alcohol use, and
victimisation, and their association with HIV-related sexual risk among men who
have sex with men and transgender women in India. Glob. Public Health 12, 250--265.
<https://doi.org/10.1080/17441692.2015.1091024>

Chandler, Cristian J., Bukowski, L.A.,
Matthews, D.D., Hawk, M.E., Markovic, N., Egan, J.E., Stall, R.D., 2020a.
Examining the Impact of a Psychosocial Syndemic on Past Six-Month HIV Screening
Behavior of Black Men who have Sex with Men in the United States: Results from
the POWER Study. AIDS Behav 28, 428--436.
<https://doi.org/10.1007/s10461-019-02458-z>

Chandler, Cristian J., Bukowski, L.A.,
Matthews, D.D., Hawk, M.E., Markovic, N., Stall, R.D., Egan, J.E., 2020b.
Understanding the impact of a syndemic on the use of pre-exposure prophylaxis
in a community-based sample of behaviorally PrEP-eligible BMSM in the United
States. AIDS Care 32, 551--556. <https://doi.org/10.1080/09540121.2019.1659921>

Chandler, Cristian J, Meunier, E., Eaton,
L.A., Andrade, E., Bukowski, L.A., Matthews, D.D., Raymond, H.F., Stall, R.D.,
Friedman, M.R., 2020. Syndemic health disparities and sexually transmitted
infection burden among black men who have sex with men engaged in sex work in
the u.S. Arch Sex Behav. <https://doi.org/10.1007/s10508-020-01828-2>

Chuang, D.-M., Newman, P.A., Li, A.T.-W.,
2018. Syndemic factors and HIV infection among men who have sex with men in
Taiwan. J HIV AIDS Soc Serv 17, 337--352. <https://doi.org/10.1080/15381501.2018.1454866>

Dyer, T.P., Shoptaw, S., Guadamuz, T.E.,
Plankey, M., Kao, U., Ostrow, D., Chmiel, J.S., Herrick, A., Stall, R., 2012.
Application of syndemic theory to black men who have sex with men in the
Multicenter AIDS Cohort Study. J Urban Health 89, 697--708.
<https://doi.org/10.1007/s11524-012-9674-x>

Dyer, T.V., Turpin, R.E., Stall, R., Khan,
M.R., Nelson, L.E., Brewer, R., Friedman, M.R., Mimiaga, M.J., Cook, R.L., O'Cleirigh,
C., Mayer, K.H., 2020. Latent Profile Analysis of a Syndemic of Vulnerability
Factors on Incident Sexually Transmitted Infection in a Cohort of Black Men Who
Have Sex With Men Only and Black Men Who Have Sex With Men and Women in the HIV
Prevention Trials Network 061 Study. Sex Transm Dis 47, 571--579.
<https://doi.org/10.1097/OLQ.0000000000001208>

Eaton, L.A., Pitpitan, E.V., Kalichman,
S.C., Sikkema, K.J., Skinner, D., Watt, M.H., Pieterse, D., 2013. Men who
report recent male and female sex partners in Cape Town, South Africa: an
understudied and underserved population. Arch Sex Behav 42, 1299--1308.
<https://doi.org/10.1007/s10508-013-0077-1>

Ferlatte, O., Dulai, J., Hottes, T.S.,
Trussler, T., Marchand, R., 2015. Suicide related ideation and behavior among
Canadian gay and bisexual men: a syndemic analysis. BMC public health 15, 597.
<https://doi.org/10.1186/s12889-015-1961-5>

Ferlatte, O., Hottes, T.S., Trussler, T.,
Marchand, R., 2014. Evidence of a syndemic among young Canadian gay and
bisexual men: uncovering the associations between anti-gay experiences,
psychosocial issues, and HIV risk. AIDS Behav 18, 1256--1263. <https://doi.org/10.1007/s10461-013-0639-1>

Ferlatte, O., Salway, T., Samji, H., Dove,
N., Gesink, D., Gilbert, M., Oliffe, J.L., Grennan, T., Wong, J., 2018a. An
Application of Syndemic Theory to Identify Drivers of the Syphilis Epidemic
among Gay, Bisexual, and Other Men Who Have Sex with Men. Sexually Transmitted
Diseases 45, 163--168. <https://doi.org/10.1097/OLQ.0000000000000713>

Ferlatte, O., Salway, T., Trussler, T.,
Oliffe, J.L., Gilbert, M., 2018b. Combining intersectionality and syndemic
theory to advance understandings of health inequities among Canadian gay,
bisexual and other men who have sex with men. Crit Public Health 28, 509--521.
<https://doi.org/10.1080/09581596.2017.1380298>

Friedman, M.R., Coulter, R.W.S.,
Silvestre, A.J., Stall, R., Teplin, L., Shoptaw, S., Surkan, P.J., Plankey,
M.W., 2016. Someone to count on: social support as an effect modifier of viral
load suppression in a prospective cohort study. AIDS Care 29, 469--480.
<https://doi.org/10.1080/09540121.2016.1211614>

Friedman, M.R., Kurtz, S.P., Buttram,
M.E., Wei, C., Silvestre, A.J., Stall, R., 2014. HIV risk among substance-using
men who have sex with men and women (MSMW): findings from South Florida. AIDS
Behav 111--19. <https://doi.org/10.1007/s10461-013-0495-z>

Friedman, M.R., Stall, R., Silvestre,
A.J., Wei, C., Shoptaw, S., Herrick, A., Surkan, P.J., Teplin, L., Plankey,
M.W., 2015. Effects of syndemics on HIV viral load and medication adherence in
the multicentre AIDS cohort study. AIDS 29, 1087--1096.
<https://doi.org/10.1097/QAD.0000000000000657>

Guadamuz, T.E., McCarthy, K., Wimonsate,
W., Thienkrua, W., Varangrat, A., Chaikummao, S., Sangiamkittikul, A., Stall,
R.D., van Griensven, F., 2014. Psychosocial Health Conditions and HIV
Prevalence and Incidence in a Cohort of Men Who have Sex with Men in Bangkok,
Thailand: Evidence of a Syndemic Effect. AIDS Behav 18, 2089--2096.
<https://doi.org/10.1007/s10461-014-0826-8>

Halkitis, P.N., Kapadia, F., Bub, K.L.,
Barton, S., Moreira, A.D., Stults, C.B., 2015. A Longitudinal Investigation of
Syndemic Conditions Among Young Gay, Bisexual, and Other MSM: The P18 Cohort
Study. AIDS Behav 19, 970--980. <https://doi.org/10.1007/s10461-014-0892-y>

Halkitis, P.N., Kupprat, S.A., Hampton,
M.B., Perez-Figueroa, R., Kingdon, M., Eddy, J.A., Ompad, D.C., 2012. Evidence
for a Syndemic in Aging HIV-positive Gay, Bisexual, and Other MSM: Implications
for a Holistic Approach to Prevention and Healthcare. Ann Anthropol Pract 36,
365--386. <https://doi.org/10.1111/napa.12009>

Halkitis, P.N., Moeller, R.W., Siconolfi,
D.E., Storholm, E.D., Solomon, T.M., Bub, K.L., 2013. Measurement model
exploring a syndemic in emerging adult gay and bisexual men. AIDS Behav 17, 662--673.
<https://doi.org/10.1007/s10461-012-0273-3>

Harkness, A., Bainter, S.A., O'Cleirigh,
C., Albright, C., Mayer, K.H., Safren, S.A., 2019. Longitudinal Effects of
Syndemics on HIV-Positive Sexual Minority Men's Sexual Health Behaviors. Arch
Sex Behav 48, 1159--1170. <https://doi.org/10.1007/s10508-018-1329-x>

Harkness, A., Bainter, S.A., O'Cleirigh,
C., Mendez, N.A., Mayer, K.H., Safren, S.A., 2018. Longitudinal Effects of
Syndemics on ART Non-adherence Among Sexual Minority Men. AIDS Behav 22, 2564--2574.
<https://doi.org/10.1007/s10461-018-2180-8>

Hart, T.A., Noor, S.W., Adam, B.D.,
Vernon, J.R.G., Brennan, D.J., Gardner, S., Husbands, W., Myers, T., 2017.
Number of Psychosocial Strengths Predicts Reduced HIV Sexual Risk Behaviors
Above and Beyond Syndemic Problems Among Gay and Bisexual Men. AIDS Behav 21,
3035--3046. <https://doi.org/10.1007/s10461-016-1669-2>

Herrick, A., Stall, R., Egan, J.,
Schrager, S., Kipke, M., 2014. Pathways towards risk: syndemic conditions
mediate the effect of adversity on HIV risk behaviors among young men who have
sex with men (YMSM). J Urban Health 91, 969--982.
<https://doi.org/10.1007/s11524-014-9896-1>

Herrick, A.L., Lim, S.H., Plankey, M.W.,
Chmiel, J.S., Guadamuz, T.E., Kao, U., Shoptaw, S., Carrico, A., Ostrow, D.,
Stall, R., 2013. Adversity and syndemic production among men participating in
the multicenter AIDS cohort study: a life-course approach. Am J Public Health
103, 79--85. <https://doi.org/10.2105/AJPH.2012.300810>

Hirshfield, S., Schrimshaw, E.W., Stall,
R.D., Margolis, A.D., Downing  Jr, M.J.,
Chiasson, M.A., 2015. Drug Use, Sexual Risk, and Syndemic Production Among Men
Who Have Sex With Men Who Engage in Group Sexual Encounters. Am J Public Health
105, 1849--1858. <https://doi.org/10.2105/AJPH.2014.302346>

Jiang, H., Li, J., Tan, Z., Chen, X.,
Cheng, W., Gong, X., Yang, Y., 2020. Syndemic Factors and HIV Risk Among Men
Who Have Sex with Men in Guangzhou, China: Evidence from Synergy and Moderated
Analyses. Arch Sex Behav 49, 311--320.
<https://doi.org/10.1007/s10508-019-01488-x>

Jie, W., Ciyong, L., Xueqing, D., Hui, W.,
Lingyao, H., 2012. A syndemic of psychosocial problems places the MSM (men who
have sex with men) population at greater risk of HIV infection. PLoS ONE 7,
e32312. <https://doi.org/10.1371/journal.pone.0032312>

Klein, H., 2011. Using a syndemics theory
approach to study HIV risk taking in a population of men who use the internet
to find partners for unprotected sex. Am J Men's Health 5, 466--476.
<https://doi.org/10.1177/1557988311398472>

Kurtz, S.P., Buttram, M.E., Surratt, H.L.,
Stall, R.D., 2012. Resilience, syndemic factors, and serosorting behaviors
among HIV-positive and HIV-negative substance-using MSM. AIDS Educ Prev 24, 193--205.
<https://doi.org/10.1521/aeap.2012.24.3.193>

Lassiter, J.M., Parsons, J.T., 2016.
Religion and Spirituality's Influences on HIV Syndemics Among MSM: A Systematic
Review and Conceptual Model. AIDS Behav 20, 461--472.
<https://doi.org/10.1007/s10461-015-1173-0>

Lee, J S, Bainter, S.A., Carrico, A.W.,
Glynn, T.R., Rogers, B.G., Albright, C., O'Cleirigh, C., Mayer, K.H., Safren,
S.A., 2020. Connecting the dots: a comparison of network analysis and
exploratory factor analysis to examine psychosocial syndemic indicators among
HIV-negative sexual minority men. J Behav Med.
<https://doi.org/10.1007/s10865-020-00148-z>

Lee, Jasper S., Safren, S.A., Bainter,
S.A., Rodríguez-Díaz, C.E., Horvath, K.J., Blashill, A.J., 2020. Examining a
Syndemics Network Among Young Latino Men Who Have Sex with Men. Int J Behav Med
27, 39--51. <https://doi.org/10.1007/s12529-019-09831-1>

Lewis, N.M., Wilson, K., 2017. HIV risk
behaviours among immigrant and ethnic minority gay and bisexual men in North
America and Europe: A systematic review. Soc Sci Med 179, 115--128.
<https://doi.org/10.1016/j.socscimed.2017.02.033>

Li, R., Cai, Y., Wang, Y., Sun, Z., Zhu,
C., Tian, Y., Jiang, X., Gan, F., 2016. Psychosocial syndemic associated with
increased suicidal ideation among men who have sex with men in Shanghai, China.
Health Psychol 35, 148--156. <https://doi.org/10.1037/hea0000265>

Lyons, T., Johnson, A.K., Garofalo, R.,
2013. "What Could Have Been Different": A Qualitative Study of Syndemic Theory
and HIV Prevention among Young Men Who Have Sex with Men. J HIV AIDS Soc Serv
12, 368--383. <https://doi.org/10.1080/15381501.2013.816211>

Maiorana, A., Kegeles, S.M., Brown, S.,
Williams, R., Arnold, E.A., 2020. Substance use, intimate partner violence,
history of incarceration and vulnerability to HIV among young Black men who
have sex with men in a Southern US city. Cult Health Sex.
<https://doi.org/10.1080/13691058.2019.1688395>

Martinez, O., Arreola, S., Wu, E., Muñoz-Laboy,
M., Levine, E.C., Rutledge, S.E., Hausmann-Stabile, C., Icard, L., Rhodes,
S.D., Carballo-Diéguez, A., Rodríguez-Díaz, C.E., Fernandez, M.I., Sandfort,
T., 2016. Syndemic factors associated with adult sexual HIV risk behaviors in a
sample of Latino men who have sex with men in New York City. Drug Alcohol
Depend 166, 258--262. <https://doi.org/10.1016/j.drugalcdep.2016.06.033>

Martinez, O., Brady, K.A., Levine, E.,
Page, K.R., Zea, M.C., Yamanis, T.J., Grieb, S., Shinefeld, J., Ortiz, K.,
Davis, W.W., Mattera, B., Martinez-Donate, A., Chavez-Baray, S., Moya, E.M.,
2020. Using Syndemics Theory to Examine HIV Sexual Risk Among Latinx Men Who
Have Sex with Men in Philadelphia, PA: Findings from the National HIV
Behavioral Surveillance. EHQUIDAD 13, 217--236.
<https://doi.org/10.15257/ehquidad.2020.0009>

McDaid, L.M., Flowers, P., Ferlatte, O.,
McAloney-Kocaman, K., Gilbert, M., Frankis, J., 2019. Informing theoretical
development of salutogenic, asset-based health improvement to reduce syndemics
among gay, bisexual and other men who have sex with men: Empirical evidence
from secondary analysis of multi-national, online cross-sectional surveys. SSM
Popul Health 10, 100519. <https://doi.org/10.1016/j.ssmph.2019.100519>

Mimiaga, Matthew J, Biello, K.B.,
Robertson, A.M., Oldenburg, C.E., Rosenberger, J.G., O'Cleirigh, C., Novak,
D.S., Mayer, K.H., Safren, S.A., 2015. High prevalence of multiple syndemic
conditions associated with sexual risk behavior and HIV infection among a large
sample of Spanish- and Portuguese-speaking men who have sex with men in Latin
America. Archives of Sexual Behavior 44, 1869--1878.
<https://doi.org/10.1007/s10508-015-0488-2>

Mimiaga, Matthew J., OʼCleirigh, C.,
Biello, K.B., Robertson, A.M., Safren, S.A., Coates, T.J., Koblin, B.A.,
Chesney, M.A., Donnell, D.J., Stall, R.D., Mayer, K.H., 2015. The Effect of
Psychosocial Syndemic Production on 4-Year HIV Incidence and Risk Behavior in a
Large Cohort of Sexually Active Men Who Have Sex With Men. J Acquir Immune
Defic Syndr 68, 329--336. <https://doi.org/10.1097/QAI.0000000000000475>

Moeller, R.W., Halkitis, P.N., Surrence,
K., n.d. The interplay of syndemic production and serosorting in drug-using gay
and bisexual men. J. Gay Lesbian Soc. Serv 23, 89--106.
<https://doi.org/10.1080/10538720.2010.538007>

Morrison, S.A., Yoong, D., Hart, T.A.,
MacPherson, P., Bogoch, I., Sivarajah, V., Gough, K., Naccarato, M., Tan,
D.H.S., 2018. High prevalence of syndemic health problems in patients seeking
post-exposure prophylaxis for sexual exposures to HIV. PLoS ONE 13, e0197998.
<https://doi.org/10.1371/journal.pone.0197998>

Muñoz-Laboy, M., Martinez, O., Levine,
E.C., Mattera, B.T., Isabel Fernandez, M., 2018. Syndemic Conditions
Reinforcing Disparities in HIV and Other STIs in an Urban Sample of
Behaviorally Bisexual Latino Men. J Immigr Minor Health 20, 497--501.
<https://doi.org/10.1007/s10903-017-0568-6>

Mustanski, B., Andrews, R., Herrick, A.,
Stall, R., Schnarrs, P.W., 2014. A Syndemic of Psychosocial Health Disparities
and Associations With Risk for Attempting Suicide Among Young Sexual Minority
Men. Am J Public Health 104, 287--294. <https://doi.org/10.2105/AJPH.2013.301744>

Mustanski, B., Garofalo, R., Herrick, A.,
Donenberg, G., 2007. Psychosocial health problems increase risk for HIV among
urban young men who have sex with men: preliminary evidence of a syndemic in
need of attention. Ann Behav Med 34, 37--45. <https://doi.org/10.1007/bf02879919>

Mustanski, B., Phillips, G., Ryan, D.T.,
Swann, G., Kuhns, L., Garofalo, R., 2017. Prospective Effects of a Syndemic on
HIV and STI Incidence and Risk Behaviors in a Cohort of Young Men Who Have Sex
with Men. AIDS Behav 21, 845--857. <https://doi.org/10.1007/s10461-016-1607-3>

Ng, R.X., Guadamuz, T.E., Akbar, M.,
Kamarulzaman, A., Lim, S.H., 2020. Association of co-occurring psychosocial
health conditions and HIV infection among MSM in Malaysia: Implication of a
syndemic effect. Int. J. STD AIDS 31, 568--578.
<https://doi.org/10.1177/0956462420913444>

Nostlinger, C., Reyniers, T., Smekens, T.,
Apers, H., Laga, M., Wouters, K., Vuylsteke, B., 2020. Drug use, depression and
sexual risk behaviour: a syndemic among early pre-exposure prophylaxis (PrEP)
adopters in Belgium?. AIDS Care 32, 57--64.
<https://doi.org/10.1080/09540121.2020.1739218>

O'Cleirigh, C., Pantalone, D.W.,
Batchelder, A.W., Hatzenbuehler, M.L., Marquez, S.M., Grasso, C., Safren, S.A.,
Mayer, K.H., 2018. Co-occurring psychosocial problems predict HIV status and
increased health care costs and utilization among sexual minority men. J Behav
Med 41, 450--457. <https://doi.org/10.1007/s10865-018-9913-z>

Oginni, O.A., Mapayi, B.M., Afolabi, O.T.,
Ebuenyi, I.D., Akinsulore, A., Mosaku, K.S., 2019. Association between risky
sexual behavior and a psychosocial syndemic among nigerian men who have sex
with men. J Gay Lesbian Ment Health, Journal of Gay & Lesbian Psychotherapy
23, 168--185. <https://doi.org/10.1080/19359705.2018.1552640>

Ogunbajo, A., Oke, T., Jin, H., Rashidi,
W., Iwuagwu, S., Harper, G.W., Biello, K.B., Mimiaga, M.J., 2019. A syndemic of
psychosocial health problems is associated with increased HIV sexual risk among
Nigerian gay, bisexual, and other men who have sex with men (GBMSM). AIDS Care
32, 337--342. <https://doi.org/10.1080/09540121.2019.1678722>

O'Leary, A., Jemmott  3rd, J.B., Stevens, R., Rutledge, S.E.,
Icard, L.D., 2014. Optimism and education buffer the effects of syndemic
conditions on HIV status among African American men who have sex with men. AIDS
Behav 18, 2080--2088. <https://doi.org/10.1007/s10461-014-0708-0>

Pantalone, D.W., Nelson, K.M., Batchelder,
A.W., Chiu, C., Gunn, H.A., Horvath, K.J., 2020. A Systematic Review and
Meta-Analysis of Combination Behavioral Interventions Co-Targeting Psychosocial
Syndemics and HIV-Related Health Behaviors for Sexual Minority Men. J Sex Res
57, 681--708. <https://doi.org/10.1080/00224499.2020.1728514>

Pantalone, D.W., Valentine, S.E.,
Woodward, E.N., O'Cleirigh, C., 2018. Syndemic Indicators Predict Poor
Medication Adherence and Increased Health Care Utilization for Urban
HIV-Positive Men Who Have Sex with Men. J Gay Lesbian Ment Health 22, 71--87.
<https://doi.org/10.1080/19359705.2017.1389794>

Parsons, J.T., Grov, C., Golub, S.A.,
2012. Sexual compulsivity, co-occurring psychosocial health problems, and HIV
risk among gay and bisexual men: further evidence of a syndemic. Am J Public Health
102, 156--162. <https://doi.org/10.2105/AJPH.2011.300284>

Parsons, J.T., Millar, B.M., Moody, R.L.,
Starks, T.J., Rendina, H.J., Grov, C., 2017. Syndemic conditions and HIV
transmission risk behavior among HIV-negative gay and bisexual men in a U.S. national
sample. Health Psychol 36, 695--703. <https://doi.org/10.1037/hea0000509>

Parsons, J.T., Rendina, H.J., Moody, R.L.,
Ventuneac, A., Grov, C., 2015. Syndemic production and sexual
compulsivity/hypersexuality in highly sexually active gay and bisexual men:
further evidence for a three group conceptualization. Arch Sex Behav 44, 1903--1913.
<https://doi.org/10.1007/s10508-015-0574-5>

Perry, N.S., Nelson, K.M., Carey, M.P.,
2019. Diversity of Psychosocial Syndemic Indicators and Associations with
Sexual Behavior with Male and Female Partners Among Early Adolescent Sexual
Minority Males. LGBT Health 6, 386--392. <https://doi.org/10.1089/lgbt.2019.0113>

Pitpitan, E.V., Smith, L.R., Goodman-Meza,
D., Torres, K., Semple, S.J., Strathdee, S.A., Patterson, T.L., 2016. "Outness"
as a Moderator of the Association Between Syndemic Conditions and HIV
Risk-Taking Behavior Among Men Who Have Sex with Men in Tijuana, Mexico. AIDS
Behav 20, 431--438. <https://doi.org/10.1007/s10461-015-1172-1>

Pollard, A., Nadarzynski, T., Llewellyn,
C., 2018. Syndemics of stigma, minority-stress, maladaptive coping, risk
environments and littoral spaces among men who have sex with men using chemsex.
Cult Health Sex 20, 411--427. <https://doi.org/10.1080/13691058.2017.1350751>

Quinn, B., Gorbach, P.M., Okafor, C.N.,
Heinzerling, K.G., Shoptaw, S., 2020. Investigating possible syndemic
relationships between structural and drug use factors, sexual HIV transmission
and viral load among men of colour who have sex with men in Los Angeles County.
Drug Alcohol Rev. 39, 116--127. <https://doi.org/10.1111/dar.13026>

Quinn, K.G., 2019. Applying an
intersectional framework to understand syndemic conditions among young Black
gay, bisexual, and other men who have sex with men. Soc Sci Med.
<https://doi.org/10.1016/j.socscimed.2019.112779>

Reed, S.J., Miller, R.L., 2016. Thriving
and Adapting: Resilience, Sense of Community, and Syndemics among Young Black
Gay and Bisexual Men. Am J Community Psychol 57, 129--143.
<https://doi.org/10.1002/ajcp.12028>

Reisner, S.L., White Hughto, J.M., Pardee,
D., Sevelius, J., 2016. Syndemics and gender affirmation: HIV sexual risk in
female-to-male trans masculine adults reporting sexual contact with cisgender
males. Int J STD AIDS 27, 955--966. <https://doi.org/10.1177/0956462415602418>

Rooney, B.M., Tulloch, T.G., Blashill,
A.J., 2018. Psychosocial Syndemic Correlates of Sexual Compulsivity Among Men
Who Have Sex with Men: A Meta-Analysis. Arch Sex Behav 47, 75--93.
<https://doi.org/10.1007/s10508-017-1032-3>

Safren, S.A., Blashill, A.J., Lee, J.S., O'Cleirigh,
C., Tomassili, J., Biello, K.B., Mimiaga, M.J., Mayer, K.H., 2018. Condom-use
self-efficacy as a mediator between syndemics and condomless sex in men who
have sex with men (MSM). Health Psychol 37, 820--827.
<https://doi.org/10.1037/hea0000617>

Santos, G.-M., Do, T., Beck, J., Makofane,
K., Arreola, S., Pyun, T., Hebert, P., Wilson, P.A., Ayala, G., 2014. Syndemic
conditions associated with increased HIV risk in a global sample of men who
have sex with men. Sex Transm Infect 90, 250--253. <https://doi.org/10.1136/sextrans-2013-051318>

Scheer, J.R., Clark, K.A., Maiolatesi,
A.J., Pachankis, J.E., 2021. Syndemic profiles and sexual minority men's
hiv-risk behavior: A latent class analysis. Arch Sex Behav.
<https://doi.org/10.1007/s10508-020-01850-4>

Semple, S.J., Stockman, J.K.,
Goodman-Meza, D., Pitpitan, E.V., Strathdee, S.A., Chavarin, C.V., Rangel, G.,
Torres, K., Patterson, T.L., 2017. Correlates of Sexual Violence Among Men Who
Have Sex With Men in Tijuana, Mexico. Arch Sex Behav 46, 1011--1023.
<https://doi.org/10.1007/s10508-016-0747-x>

Shuper, P.A., Joharchi, N., Bogoch, I.I.,
Loutfy, M., Crouzat, F., El-Helou, P., Knox, D.C., Woodward, K., Rehm, J.,
2020. Alcohol consumption, substance use, and depression in relation to HIV
Pre-Exposure Prophylaxis (PrEP) nonadherence among gay, bisexual, and other
men-who-have-sex-with-men. BMC Public Health 20, 1782.
<https://doi.org/10.1186/s12889-020-09883-z>

Stall, R., Mills, T.C., Williamson, J.,
Hart, T., Greenwood, G., Paul, J., Pollack, L., Binson, D., Osmond, D.,
Catania, J.A., 2003. Association of Co-Occurring Psychosocial Health Problems
and Increased Vulnerability to HIV/AIDS among Urban Men Who Have Sex with Men.
Am J Public Health 93, 939--942. <https://doi.org/10.2105/AJPH.93.6.939>

Starks, T.J., Millar, B.M., Eggleston, J.J.,
Parsons, J.T., 2014. Syndemic factors associated with HIV risk for gay and
bisexual men: comparing latent class and latent factor modeling. AIDS Behav 18,
2075--2079. <https://doi.org/10.1007/s10461-014-0841-9>

Starks, T.J., Tuck, A.N., Millar, B.M.,
Parsons, J.T., 2016. Linking Syndemic Stress and Behavioral Indicators of Main
Partner HIV Transmission Risk in Gay Male Couples. AIDS Behav 20, 439--448.
<https://doi.org/10.1007/s10461-015-1248-y>

Storholm, E.D., Halkitis, P.N., Siconolfi,
D.E., Moeller, R.W., 2011. Cigarette smoking as part of a syndemic among young
men who have sex with men ages 13-29 in New York City. J Urban Health 88, 663--676.
<https://doi.org/10.1007/s11524-011-9563-8>

Sullivan, M.C., Eaton, L.A., 2020.
Intersecting barriers to prep awareness and uptake in black men who have sex
with men in atlanta, ga: A syndemic perspective. Int J Behav Med.
<https://doi.org/10.1007/s12529-020-09925-1>

Tan, D.H.S., Leon-Carlyle, M., Mills, R.,
Moses, E., Carvalhal, A., 2016. Self-administered screening for syndemic mental
health problems should be routinely implemented among MSM PrEP users. J Gay
Lesbian Ment Health, Journal of Gay & Lesbian Mental Health 20, 13--20.
<https://doi.org/10.1080/19359705.2015.1105765>

Tomori, C., McFall, A.M., Solomon, S.S.,
Srikrishnan, A.K., Anand, S., Balakrishnan, P., Mehta, S.H., Celentano, D.D.,
2018. Is there synergy in syndemics? Psychosocial conditions and sexual risk
among men who have sex with men in India. Soc Sci Med 206, 110--116.
<https://doi.org/10.1016/j.socscimed.2018.03.032>

Tulloch, T.G., Rotondi, N.K., Ing, S.,
Myers, T., Calzavara, L.M., Loutfy, M.R., Hart, T.A., 2015. Retrospective
reports of developmental stressors, syndemics, and their association with
sexual risk outcomes among gay men. Arch Sex Behav 44, 1879--1889.
<https://doi.org/10.1007/s10508-015-0479-3>

Turpin, R.E., Dyer, T.V., Dangerfield,
D.T. 2nd, Liu, H., Mayer, K.H., 2020a. Syndemic latent transition analysis in
the HPTN 061 cohort: Prospective interactions between trauma, mental health,
social support, and substance use. Drug Alcohol Depend 214.
<https://doi.org/10.1016/j.drugalcdep.2020.108106>

Turpin, R.E., Salerno, J.P., Rosario,
A.D., Boekeloo, B., 2020b. Victimization, Substance Use, Depression, and Sexual
Risk in Adolescent Males Who Have Sex with Males: A Syndemic Latent Profile
Analysis. Arch Sex Behav. <https://doi.org/10.1007/s10508-020-01685-z>

Van den Berghe, W., Nöstlinger, C., Laga,
M., 2014. Syndemic and other risk factors for unprotected anal intercourse
among an online sample of belgian HIV negative men who have sex with men. AIDS
Behav 18, 50--58. <https://doi.org/10.1007/s10461-013-0516-y>

Walters, S.M., Braksmajer, A., Coston, B.,
Yoon, I., Grov, C., Downing, M.J., Teran, R., Hirshfield, S., 2020. A Syndemic
Model of Exchange Sex Among HIV-Positive Men Who Have Sex With Men. Arch Sex
Behav 49, 1965--1978. <https://doi.org/10.1007/s10508-020-01628-8>

Wang, Ying, Wang, Z., Jia, M., Liang, A.,
Yuan, D., Sun, Z., Gan, F., Wang, Yichen, Cai, Y., Zhang, Z., 2017. Association
between a syndemic of psychosocial problems and unprotected anal intercourse
among men who have sex with men in Shanghai, China. BMC Infect Dis 17, 46.
<https://doi.org/10.1186/s12879-016-2132-8>

Wang, Z., Zhao, X., Zhang, Z., Luo, M.,
Shen, Q., Dong, Y., Wang, Y., Cai, Y., 2018. Co-Occurring Psychosocial Problems
and Multiple Sexual Partners among Men Who Have Sex with Men in Shanghai,
China: A Syndemic Approach. J Sex Res 55, 892--901.
<https://doi.org/10.1080/00224499.2017.1399333>

Woodward, E.N., Banks, R.J., Marks, A.K.,
Pantalone, D.W., 2017. Identifying Resilience Resources for HIV Prevention
Among Sexual Minority Men: A Systematic Review. AIDS Behav 2860--2873.
<https://doi.org/10.1007/s10461-016-1608-2>

Wu, E., 2018. Childhood sexual abuse among
Black men who have sex with men: A cornerstone of a syndemic? PLoS ONE 13,
e0206746--e0206746. <https://doi.org/10.1371/journal.pone.0206746>

Yu, F., Nehl, E.J., Zheng, T., He, N.,
Berg, C.J., Lemieux, A.F., Lin, L., Tran, A., Sullivan, P.S., Wong, F.Y., 2013.
A syndemic including cigarette smoking and sexual risk behaviors among a sample
of MSM in Shanghai, China. Drug Alcohol Depend 132, 265--270.
<https://doi.org/10.1016/j.drugalcdep.2013.02.016>

Zepf, R., Greene, M., Hessol, N.A.,
Johnson, M.O., Santos, G.M., John, M.D., Dawson-Rose, C., 2020. Syndemic
conditions and medication adherence in older men living with HIV who have sex
with men. AIDS Care 32, 1610--1616.
<https://doi.org/10.1080/09540121.2020.1772954>

Zhang, J., O'Leary, A., Jemmott  3rd, J.B., Icard, L.D., Rutledge, S.E., 2019.
Syndemic conditions predict lower levels of physical activity among African
American men who have sex with men: A prospective survey study. PLOS One 14,
e0213439--e0213439. <https://doi.org/10.1371/journal.pone.0213439>

\newpage

### B. Measurement tables

```{r depression_table, tab.id = "DepressionTab", echo=FALSE}

source("./scripts/supplementary_tables/depression.R", local = knitr::knit_global())
.depression_ft

```

\newpage

```{r IPV_table, tab.id = "IPVTab", echo=FALSE, message=FALSE, warning=FALSE}

.IPV_ft
```

\newpage

```{r substance_table, tab.id = "SubstanceTab", echo=FALSE, message=FALSE, warning=FALSE}

.substance_ft
```

\newpage

```{r CSA_table, tab.id = "CSATab", echo=FALSE, message=FALSE, warning=FALSE}

.CSA_ft

```

\newpage

```{r polysubstance_measurement, tab.id = "PolysubstanceTab", echo=FALSE, message=FALSE, warning=FALSE}

.polysubstance_ft
```

\newpage

```{r binge_measurement, tab.id = "BingeTab", echo=FALSE, message=FALSE, warning=FALSE}

.binge_ft
```

\newpage

```{r violence_measurement, tab.id = "ViolenceTab", echo=FALSE, message=FALSE, warning=FALSE}

.violence_ft
```

\newpage

```{r anxiety_measurement, tab.id = "AnxietyTab", echo=FALSE, message=FALSE, warning=FALSE}

.anxiety_ft

```

### 2021-08-09 _bookdown_files/index.Rmd
Bookdown conversion

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Corresponding author at : General Practice Department - Primary Care and Health Research Unit, MD - PhD student,  University of Liège, Liège, Belgium <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, research assistant, University of Liège, Liège, Belgium <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, lecturer, University of Liège, Liège, Belgium <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^ General Practice Department - Primary Care and Health Research Unit, Postdoctoral Researcher,  University of Liège, Liège, Belgium <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"

link-citations: true
csl: ["./_bookdown_files/social-science-and-medicine.csl"]
bibliography: ["./_bookdown_files/references.bib"]
rmd_files: ("index.Rmd", "01-abstract.Rmd", "02-introduction.Rmd", "03-methodology.Rmd", "04-results.Rmd", "05-discussion.Rmd", "06-conclusion.Rmd", "07-references.Rmd", "08-appendix.Rmd")
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(bookdown)
library(officedown)
library(officer)
```

### 2021-08-09 Scripts/create_outcomes_data.R
Scripts rearrangement

@@ -1,0 +1,19 @@
+.outcomes <- summary_quantitative %>%
+  select(1:3, 182:201) %>%
+  unite("reference", 1:3, sep =" ", na.rm = T)
+
+.outcomes_measurement <- summary_quantitative %>%
+  select(1:3, 202:251) %>%
+  unite("reference", 1:3, sep =" ", na.rm = T)
+
+.outcomes_sex_risk_measurement <- .outcomes_measurement %>%
+  select(1, 5:21)
+
+
+.CAS_number <- sum(!is.na(.outcomes_sex_risk_measurement$outcome_CAS)) + 
+  sum(!is.na(.outcomes_sex_risk_measurement$outcome_serodiscodant_CAS)) +
+  sum(!is.na(.outcomes_sex_risk_measurement$outcome_receptive_CAS)) + 
+  sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS)) +
+  sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_CAS)) +
+  sum(!is.na(.outcomes_sex_risk_measurement$outcome_casual_CAS)) +
+  sum(!is.na(.outcomes_sex_risk_measurement$outcome_current_CAS))

### 2021-08-09 Scripts/create_population_plot.R

@@ -1,5 +1,4 @@
-detach("package:flextable", unload=TRUE)
-
+library(cowplot)
 
 .age_pop_plot <- ggplot(data = population, aes(x = fct_infreq(age))) +
   geom_bar(fill = c("#FE9666", "#A66999", "#FD625E", "#F2C80F")) +
@@ -12,10 +11,13 @@ detach("package:flextable", unload=TRUE)
   xlab("Age group") +
   ylab("Number of studies") +
   labs(title = "Age groups of study participants") +
-  font("title", size = 8, face = "bold") +
-  font("xlab", size = 7) +
-  font("ylab", size = 7) +
-  font("xy.text", size = 6) +
+  theme(
+    axis.text.x = element_text(size=6),
+    axis.text.y = element_text(size = 6),
+    plot.title = element_text(size = 8, face = "bold"),
+    axis.title.x = element_text(size = 7),
+    axis.title.y = element_text(size = 7)
+    ) +
   scale_y_continuous(expand = expansion(mult = 0.1), 
                      breaks = c(0,25,50,75,100))
 
@@ -30,10 +32,13 @@ detach("package:flextable", unload=TRUE)
   xlab("Race/ethnicity") +
   ylab("Number of studies") +
   labs(title = "Races/ethnicities of study participants")+
-  font("title", size = 8, face = "bold") +
-  font("xlab", size = 7) +
-  font("ylab", size = 7) +
-  font("xy.text", size = 6) +
+  theme(
+    axis.text.x = element_text(size=6),
+    axis.text.y = element_text(size = 6),
+    plot.title = element_text(size = 8, face = "bold"),
+    axis.title.x = element_text(size = 7),
+    axis.title.y = element_text(size = 7)
+  ) +
   scale_y_continuous(expand = expansion(mult = 0.1), 
                      breaks = c(0,25,50,75,100))
 
@@ -48,10 +53,13 @@ detach("package:flextable", unload=TRUE)
   xlab("Serologic status") +
   ylab("Number of studies") +
   labs(title = "Serologic status of study participants")+
-  font("title", size = 8, face = "bold") +
-  font("xlab", size = 7) +
-  font("ylab", size = 7) +
-  font("xy.text", size = 6) +
+  theme(
+    axis.text.x = element_text(size=6),
+    axis.text.y = element_text(size = 6),
+    plot.title = element_text(size = 8, face = "bold"),
+    axis.title.x = element_text(size = 7),
[…]

### 2021-08-09 Scripts/create_statistics_data.R

@@ -1,0 +1,16 @@
+.statistics_data <- summary_quantitative %>%
+  select(1:3, 259:274, 276:278) %>%
+  unite(col = "author_year", c(authors, year), sep = " ") %>%
+  unite(col = "reference", c(author_year, letter), sep = "", na.rm = TRUE) 
+
+.N_latent <- sum(!is.na(.statistics_data$LCA_LPA)) +
+  sum(!is.na(.statistics_data$EFA)) +
+  sum(!is.na(.statistics_data$CFA)) + 
+  sum(!is.na(.statistics_data$LTA))
+
+.N_additivity <- sum(!is.na(.statistics_data$RERI)) +
+  sum(!is.na(.statistics_data$product_term))
+
+.score_data <- .statistics_data %>%
+  unite(col = "statistics", 2:20, sep = ", ", na.rm = TRUE) %>%
+  filter(statistics == "score")

### 2021-08-09 Scripts/create_syndemic_table.R

@@ -1,0 +1,24 @@
+source("./scripts/supplementary_tables/general.R")
+
+.synd.cond.table <- nodes %>%
+  select(label_full, studies, category) %>%
+  relocate("label_full", .before = "category") %>%
+  relocate("studies", .after = "category") %>%
+  arrange(desc(studies))
+
+.synd.cond.ft <- flextable(.synd.cond.table, cwidth = c(2.2, 1.2, 0.8))
+.synd.cond.ft <- bg(.synd.cond.ft, bg = "#45ADA8", part = "header")
+.synd.cond.ft <- .synd.cond.ft %>%
+  bold(part = "header") %>%
+  bold(j = 3, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(label_full = "Name of the syndemic condition",
+                    category = "Category",
+                    studies = "Number of studies") %>%
+  hline(j = 1:3, border = .borders, part = "body") %>%
+  align(align = "center", j=2:3, part = "body") %>%
+  hline_bottom(border = .outer.border, part = "body") %>%
+  border_outer(border = .outer.border, part = "header") 
+  
+
+  

### 2021-08-09 Scripts/create_year_design.R

@@ -1,7 +1,7 @@
 year_design <- overview_of_studies %>%
   select(year, design) 
-year_design$design <- ifelse(grepl(c("Case series|Cross-sectional"), year_design$design), "Cross-sectional", 
-                           ifelse(grepl(c("Intact group design|Pretest-posttest nonequivalent groups design|Randomized controlled trials"), year_design$design), "Interventional",
+year_design$design <- ifelse(grepl(c("Intact group design|Case series|Cross-sectional"), year_design$design), "Cross-sectional", 
+                           ifelse(grepl(c("Pretest-posttest nonequivalent groups design|Randomized controlled trials"), year_design$design), "Interventional",
                                   ifelse(grepl(c("Meta-analysis|Systematic review"), year_design$design), "Systematic reviews, meta-analyses",
                                          ifelse(grepl("Mixed", year_design$design), "Mixed",
                                                 ifelse(grepl(c("Longitudinal|Population-based cohort study"), year_design$design), "Longitudinal", 

### 2021-08-09 Scripts/read_data.R

@@ -1,10 +1,6 @@
-overview_of_studies <- read_csv("Data/overview_of_studies.csv", 
-                                col_types = cols(X6 = col_skip()))
+overview_of_studies <- read_csv("Data/overview_of_studies.csv")
 
-summary_qualitative <- read_csv("Data/summary_qualitative.csv", 
-                                col_types = cols(X23 = col_skip()))
-summary_quantitative <- read_csv("Data/summary_quantitative.csv",
-                                 col_types = cols(X299 = col_skip()))
+summary_qualitative <- read_csv("Data/summary_qualitative.csv")
+summary_quantitative <- read_csv("Data/summary_quantitative.csv")
 
-summary_reviews <- read_csv("Data/summary_reviews.csv", 
-                           col_types = cols(X12 = col_skip()))
+summary_reviews <- read_csv("Data/summary_reviews.csv")

### 2021-08-09 Scripts/supplementary_tables/CSA.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .CSA_measurement <- measurement %>%
   select(c(1, 61:63)) %>%

### 2021-08-09 Scripts/supplementary_tables/IPV.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 
 .IPV_measurement <- measurement %>%

### 2021-08-09 Scripts/supplementary_tables/anxiety.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .anxiety_measurement <- measurement %>%
   filter(!is.na(anxiety_type)) %>%

### 2021-08-09 Scripts/supplementary_tables/binge.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .binge_measurement <- measurement %>%
   select(c(1, 35:36)) %>%

### 2021-08-09 Scripts/supplementary_tables/depression.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .depression_measurement <- measurement %>%
   select(1:4) %>%

### 2021-08-09 Scripts/supplementary_tables/polysubstance.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .polysubstance_measurement <- measurement %>%
   select(c(1, 64:66)) %>%

### 2021-08-09 Scripts/supplementary_tables/reference_qualitative.R

@@ -1,0 +1,50 @@
+# Reference table for qualitative data
+reference_table_qualitative <- summary_qualitative %>%
+  select(1:3, 6:12, 14, 17:18) 
+
+# Human readable data for subpopulation 
+reference_table_qualitative[reference_table_qualitative == "BMSM"] <- "Black MSM"
+reference_table_qualitative[reference_table_qualitative == "YBMSM"] <- "Young Black MSM"
+reference_table_qualitative[reference_table_qualitative == "HIV+YMSM"] <- "Young MSM living with HIV"
+reference_table_qualitative[reference_table_qualitative == "LB_MSM"] <- "Latino & Black MSM"
+
+# Human readable data for method
+reference_table_qualitative[reference_table_qualitative == "thematic_content"] <- "thematic content analysis"
+reference_table_qualitative[reference_table_qualitative == "thematic"] <- "thematic analysis"
+reference_table_qualitative[reference_table_qualitative == "life_story"] <- "life story interview"
+reference_table_qualitative[reference_table_qualitative == "cross_case"] <- "cross case analysis"
+reference_table_qualitative[reference_table_qualitative == "framework"] <- "framework analysis"
+reference_table_qualitative[reference_table_qualitative == "grounded"] <- "grounded theory"
+reference_table_qualitative[reference_table_qualitative == "analytic_induction"] <- "analytic induction"
+
+
+reference_table_qualitative <- reference_table_qualitative %>%
+  unite(col = "reference", c(authors, year), sep = " ") %>% 
+  unite(col = "method", 3:9, sep = ", ", na.rm = TRUE) %>%
+  arrange(reference)
+
+.reference_qualitative_ft <- flextable(reference_table_qualitative, cwidth = c(1.9, 1, 1.5, 0.8, 2, 3.5)) 
+.reference_qualitative_ft <-  bg(.reference_qualitative_ft, bg = "#45ADA8", part = "header")
+.reference_qualitative_ft <- .reference_qualitative_ft %>%
+  bold(part = "header") %>%
+  bold(j = 1, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(reference = "References",
+                    location = "Location",
+                    method = "Analysis method", 
+                    subpopulation = "Subpopulation",
+                    bio_social_interaction = "Bio-social interaction",
+                    additional_framework = "Additional framework",
+                    findings = "Key findings") %>%
+  hline(j = 1:6, border = .borders, part = "body") %>%
[…]

### 2021-08-09 Scripts/supplementary_tables/reference_quantitative.R

@@ -1,0 +1,142 @@
+reference_table_quantitative <- summary_quantitative %>%
+  select(1:6, 8, 10, 11:56, 182:201, 252:254, 259:278, 285) 
+
+# Human readable data for subpopulation
+reference_table_quantitative[reference_table_quantitative == "AMSM"] <- "Adolescent MSM"
+reference_table_quantitative[reference_table_quantitative == "BMSM"] <- "Black MSM"
+reference_table_quantitative[reference_table_quantitative == "BMSM-SW"] <- "Black MSM engaged in sex work"
+reference_table_quantitative[reference_table_quantitative == "HIVMSM"] <- "MSM living with HIV"
+reference_table_quantitative[reference_table_quantitative == "HIVOMSM"] <- "Older MSM living with HIV"
+reference_table_quantitative[reference_table_quantitative == "LMSM"] <- "Latino MSM"
+reference_table_quantitative[reference_table_quantitative == "LMSMW"] <- "Latino Men who have Sex with Men and Women"
+reference_table_quantitative[reference_table_quantitative == "MSM-SW"] <- "MSM engaged in sex work"
+reference_table_quantitative[reference_table_quantitative == "MSM_CSA"] <- "MSM with a history of childhood sexual abuse"
+reference_table_quantitative[reference_table_quantitative == "MSMW"] <- "Men who have Sex with Men and Women"
+reference_table_quantitative[reference_table_quantitative == "TMSM"] <- "Transgender MSM"
+reference_table_quantitative[reference_table_quantitative == "YMSM"] <- "Young MSM"
+reference_table_quantitative[reference_table_quantitative == "BMSMW_dis"] <- "disagregated data for Black Men who have Sex with Men and Women"
+reference_table_quantitative[reference_table_quantitative == "HIVMSM_dis"] <- "disagregated data for MSM living with HIV"
+reference_table_quantitative[reference_table_quantitative == "LBMSM"] <- "disagregated data for Black & Latino MSM"
+reference_table_quantitative[reference_table_quantitative == "MSMW_dis"] <- "disagregated data for Men who have Sex with Men and Women"
+
+#Human readable data for syndemic conditions
+reference_table_quantitative[reference_table_quantitative == "substance_use"] <- "substance use"
+reference_table_quantitative[reference_table_quantitative == "binge"] <- "binge drinking"
+reference_table_quantitative[reference_table_quantitative == "suicide"] <- "suicidality"
[…]

### 2021-08-09 Scripts/supplementary_tables/reference_reviews.R

@@ -1,0 +1,30 @@
+source("./scripts/supplementary_tables/general.R")
+
+reference_table_reviews <- summary_reviews %>%
+  select(1:5, 10) %>%
+  unite(col = "reference", c(authors, year), sep = " ") %>%
+  arrange(reference)
+
+.reference_reviews_ft <- flextable(reference_table_reviews, cwidth = c(1.9, 1, 3.5, 0.8, 3.5)) 
+.reference_reviews_ft <-  bg(.reference_reviews_ft, bg = "#45ADA8", part = "header")
+.reference_reviews_ft <- .reference_reviews_ft %>%
+  bold(part = "header") %>%
+  bold(j = 1, part = "body") %>%
+  color(color = "white", part = "header") %>%
+  set_header_labels(reference = "References",
+                    design = "Design", 
+                    purpose = "Purpose of the review",
+                    studies_included = "Number of included studies",
+                    findings = "Key findings") %>%
+  hline(j = 1:5, border = .borders, part = "body") %>%
+  align(align = "center", j= 4, part = "body") %>%
+  align(align = "center", j= 1:5, part = "header") %>%
+  vline(j = 1:4, border = .borders, part = "body") %>%
+  hline_bottom(border = .outer.border, part = "body") %>%
+  border_outer(border = .outer.border, part = "header") %>%
+  fontsize(size = 9, part = "body")
+
+.reference_reviews_ft <- set_caption(.reference_reviews_ft, 
+                             "Reference table of the included reviews",
+                             autonum = .supp_autonum)
+

### 2021-08-09 Scripts/supplementary_tables/substance.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .substance_measurement <- measurement %>%
   select(c(1, 5:14)) %>%

### 2021-08-09 Scripts/supplementary_tables/violence.R

@@ -1,4 +1,4 @@
-source("./scripts/supplementary_tables_general.R")
+source("./scripts/supplementary_tables/general.R")
 
 .violence_measurement <- measurement %>%
   select(c(1, 18:23)) %>%

### 2021-10-05 _bookdown_files/04-results.Rmd
Working on the discussion

@@
 
-This part of the paper answers to the three main research questions of our protocol : "How are studies concerning Syndemic Theory applied to MSM conducted ?" ; "How is the concept of interaction explored in syndemic research applied to MSM ?" and "What were the key findings of these studies ?".
+This section summarizes the findings relevant to our aforementioned research questions.
 \@ref(tab:RefTabQuant), \@ref(tab:RefTabQual) and \@ref(tab:RefTabRev) in our supplementary material, summarize every reference identified and the variables extracted to answer our research questions for quantitative studies, qualitative studies and reviews, respectively.
@@
 After screening the title and abstract, 109 records were excluded.
-The two main reasons for exclusion at this stage were that MSM were not the main study population (n=46) and that syndemic was not the main focus of the paper (n=34).
+The two main reasons for exclusion at this stage were that MSM was not the main study population (n=46) and that syndemic was not the main focus of the paper (n=34).
 29 studies were excluded because the type of publication did not meet our inclusion criteria.
@@
 The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`).
-South America and Africa were the least represented continents, with only `r .South_America_studies` and `r .Africa_studies` studies respectively.
+South America (N = `r .South_America_studies`) and Africa (N = `r .Africa_studies`)were the least represented continents.
 
 In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r .N_cross_sec`).
-The number of longitudinal studies grew steadily since 2014 and represents `r percent(.N_long/nrow(overview_of_studies))` of the papers.
+The number of longitudinal studies has grown steadily since 2014 and represents `r percent(.N_long/nrow(overview_of_studies))` of the papers.
 The duration of longitudinal studies ranged from `r min(summary_quantitative$study_duration[summary_quantitative$design == "Longitudinal"], na.rm = T)` to `r max(summary_quantitative$study_duration[summary_quantitative$design == "Longitudinal"], na.rm = T)` months.
@@
 In terms of analysis method, the most common was thematic (content) analysis (N= `r sum(!is.na(summary_qualitative$thematic_content)) + sum(!is.na(summary_qualitative$thematic))`).
-The rest of the studies consisted in framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and life-story interviews (N = `r sum(!is.na(summary_qualitative$life_story))`).
+The rest of the studies consisted in framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and constant comparative analysis (N = `r sum(!is.na(summary_qualitative$comparative))`).
 
-We only identified 2 mixed methods design were identified[@buttram2015; @Halkitis2012]; Buttram et al.
-employed a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part while Halkitis et al used a cross-sectional quantitative survey and in-depth discovery interviews.
+We only identified 2 papers employing mixed methods design [@buttram2015; @Halkitis2012]; Buttram et al.
+used a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part while Halkitis et al used a cross-sectional quantitative survey and in-depth discovery interviews.
 
@@
 
-Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported ranged from `r min(sample$age, na.rm = T)` to `r round(max(sample$age, na.rm = T), digits = 0)` years.
+Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported, ranged from `r min(sample$age, na.rm = T)` to `r round(max(sample$age, na.rm = T), digits = 0)` years.
 
@@
 
-Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM.
-In this review, we identified 6 types of MSM subpopulations studied in syndemic literature : (a) young MSM and older MSM ; (b) MSM from a racial/ethnic minority ; (c) MSM living with HIV ; (d) MSM engaged in sex work ; (e) Men who have Sex with Men and Women (MSMW) ; and (f) transgender MSM.
+Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.
 
@@
 Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV.
-Apart from the aforementioned studies on older MSM living with HIV, `r sum(population$serologic_status == "HIV-positive" & population$age == "Young adult")` studies focus on young MSM living with HIV[@Lyons2013; @Bruce2011] .
-Notably, we identified no studies conducted on racial minority MSM living with HIV.
+Apart from the studies mentioned above on older MSM living with HIV, `r sum(population$serologic_status == "HIV-positive" & population$age == "Young adult")` studies focus on young MSM living with HIV[@Lyons2013; @Bruce2011] .
+Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.
 
 Finally, the least represented subpopulation of MSM in this review are MSMW (N = `r sum(population$sex_behav == "MSMW")`), MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
-Strikingly, transgender MSM, in addition to being the focus of only one study[@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.
+Strikingly, transgender MSM, in addition to being the focus of only one study [@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.
 
@@
 
-In order to have the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulation.\
+In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulations.\
 `r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].
@@
 
-We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "CSA"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`) and frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`).
+We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "CSA"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
 
-We chose to distinguish alcohol use disorder, binge drinking and alcohol use instead of merging them in a broad "alcohol-related syndemic condition".
+We chose to distinguish between alcohol use disorder, binge drinking and alcohol use instead of merging them into a broad "alcohol-related syndemic condition".
 Some authors also considered "heavy drinking" [@Martinez2016a; @martinez2020] or "heavy alcohol use"[@Mimiaga2015b] but we chose to aggregate these conditions under "binge drinking" for clarity.
-Similarly, we distinguish between substance use, substance use disorder, intravenous drug use, polysubstance use, marijuana use, tobacco use and chemsex since they differ in potential harm and the context of use.
+Similarly, we distinguish between substance use, substance use disorder, intravenous drug use, polysubstance use, marijuana use, tobacco use and chemsex since they differ in terms of potential harm and the context of use.
 
@@
 
-Despite the important number of syndemic conditions studied in the literature, the impact of the seminal study by Stall et al.[@Stall2003] is striking as the conditions in this paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
+Despite the high number of syndemic conditions studied in the literature, the impact of the seminal study by Stall et al.[@Stall2003] is striking.
+The conditions studied in that paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
 Furthermore, `r percent(nrow(.Stall_conditions)/nrow(summary_quantitative))` of the quantitative studies included in our review consider at least one of the four conditions studied by Stall and colleagues as part of a syndemic.
@@
 In order to better understand the connections between the syndemic conditions in the studies we elaborated a network plot (Figure \@ref(fig:SyndemicNetwork)).
-Nodes represent the syndemic conditions studied in the literature and edges are drawn between two nodes when two conditions are studied in the same research paper.
-Furthermore, edges between nodes are thicker as the two conditions are frequently studied together.
-Furthermore, circles around the nodes represent pie chart of their frequency in syndemic literature.
+Nodes represent the syndemic conditions studied in the literature and edges (connectors) are drawn between two nodes when two conditions are studied in the same research paper.
+Furthermore, edges between nodes are thicker if the two conditions are frequently studied together.
+Furthermore, the outline of the nodes represent pie chart of their frequency in syndemic literature.
 For example, depression, the most studied condition, appears in `r percent((nodes$studies[nodes$label == "depression"])/nrow(summary_quantitative))` of our sample.
 As such, the node is circled by a chart representing this proportion.
-Moreover, as a force-directed graph, the location of the nodes gives an indication regarding their importance.
+Moreover, as a force-directed graph, the location of the nodes gives an indication regarding their importance in terms of frequency and linkage to other conditions.
 As such, depression occupies a more central position than ADHD which was only studied once.
 
-In this graph, we divided each conditions into 4 categories : mental health (e.g.
-depression, anxiety, PTSD), social conditions (e.g.
-substance use, loneliness), structural conditions (e.g.
-unemployment, healthcare access) and physical health (e.g.
-STI, HIV) .
-When viewing this graph, it is readily apparent that structural syndemic conditions and physical health-related syndemic conditions are much less central than social syndemic conditions and mental health-related syndemic conditions.
+In this figure, we divided the conditions studied into 4 categories : mental health (e.g.
+depression, anxiety, PTSD) in blue, social conditions (e.g.
+substance use, loneliness) in teal, structural conditions (e.g.
+unemployment, healthcare access) in orange and physical health (e.g.
+STI, HIV) in red .
+The figure shows that structural syndemic conditions and physical health-related syndemic conditions are much less central, therefore much less studied, than social syndemic conditions and mental health-related syndemic conditions which are located towards the center of the figure.
 
@@
 
-We also computed centrality indices for this network, namely degree centrality, the sum of weight in the network, closeness centrality, the inverse of the total length of the paths from a node to all other nodes, and betweenness, the number of shortest path passing through a node[@opsahl2010].\
-Because the weight of the nodes in this network corresponds to the number of studies in which the syndemic conditions appear, degree centrality of each node does is nearly perfectly correlated to the number of studies in which the syndemic condition was studied (`r paste0("r(", .cor_degree$parameter,")", " = ", round(.cor_degree$estimate, digits = 2), ", ", pvalue(.cor_degree$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE))`).\
+In order to obtain a deeper understanding of the relation between the syndemic conditions, we also computed centrality indices for this network, namely degree centrality, the sum of weight in the network, closeness centrality, the inverse of the total length of the paths from a node to all other nodes, and betweenness, the number of shortest path passing through a node[@opsahl2010].\
+Because the weight of the nodes in this network corresponds to the number of studies in which the syndemic conditions appear, degree centrality of each node is nearly perfectly correlated to the number of studies in which the syndemic condition was studied (`r paste0("r(", .cor_degree$parameter,")", " = ", round(.cor_degree$estimate, digits = 2), ", ", pvalue(.cor_degree$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE))`).\
 Closeness centrality and betweenness centrality are also strongly correlated to the number of studies `r paste0("(r(", .cor_closeness$parameter,")", " = ", round(.cor_closeness$estimate, digits = 2), ", ", pvalue(.cor_closeness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " and r(", .cor_betweenness$parameter,")", " = ", round(.cor_betweenness$estimate, digits = 2), ", ", pvalue(.cor_betweenness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " respectively)")`.
-Interestingly, the betweenness centrality of unstable housing is notably high given the low number of studies taking this syndemic condition into account (N = `r nodes$studies[nodes$label == "unstable_housing"]`).
+Interestingly, the betweenness centrality of unstable housing is notably high given the low number of studies focusing on this syndemic condition (N = `r nodes$studies[nodes$label == "unstable_housing"]`).
 Betweenness centrality can be seen as the extent of brokerage a node can exert on a network [@zweig2016].
-Moreover, the three structural syndemic conditions "unstable housing", "incarceration" and "poverty" are grouped together, indicating that they are frequently studied together.
-In other words, in syndemic literature, unstable housing acts as a bridge, notably between the two aforementioned structural syndemic conditions and the rest of the syndemic conditions.
+Moreover in \@ref(fig:SyndemicNetwork) we see that the three structural syndemic conditions "unstable housing", "incarceration" and "poverty" are grouped together, indicating that they are frequently studied together.
+In other words, in syndemic literature, unstable housing seems to act as a bridge between the two aforementioned structural syndemic conditions and the rest of the syndemic conditions.
 Indeed, unstable housing has been studied alongside `r nrow(.edges_UH)` other syndemic conditions : depression, substance use, IPV, binge drinking, sexual compulsivity, IDU, CSA, polysubstance use, incarceration, poverty, unemployment, discrimination, poor healthcare access, alcohol use and violence.
@@
 Moreover, each node is circled by a pie chart of their frequency in the review.
-The thickness of the edges linking two nodes depends on the number of studies in which the two conditions were studied together.", fig.id="SyndemicNetwork", fig.width=7.45, fig.height=5.32, fig.align='center'}
+The thickness of the edges linking two nodes reflects the number of studies in which the two conditions were studied together.", fig.id="SyndemicNetwork", fig.width=7.45, fig.height=5.32, fig.align='center'}
 
@@
 Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies.
-For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our studies sample.
+For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our sample.
+Detailed information about each of the papers included is presented in the supplementary material, part B ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).
 
@@
 Cutoff for these scales varied the most for the CESD (range : 16 to 27) and the PHQ-9 (range : 5 to 15).\
-When a scale was not used, the most frequent criteria to assess the presence of depression was the participant being on medication for depression in the past 12 months (N = 4).\
-See \@ref(tab:DepressionTab) for more details.
+When a scale was not used, the most frequent criteria to assess the presence of depression was the participant being on medication for depression in the past 12 months (N = 4).
 
@@
 threats to disclose the partner's serologic status ; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`).
-Reference period varied from past month to lifetime.\
-Furthermore, 7 studies used a scale to assess the presence of IPV : the HITS scale (N = 3) the Revised Conflict Tactics Scale [CTS2] (N= 3) and a scale developed by the authors of the study, assessing physical and psychological violence[@Yu2013].\
-See \@ref(tab:IPVTab) for more details.
+Reference periods varied from past month to lifetime.\
+Furthermore, 7 studies used a scale to assess the presence of IPV : the HITS scale (N = 3) the Revised Conflict Tactics Scale [CTS2] (N= 3) and a scale developed by the authors of the study, assessing physical and psychological violence[@Yu2013].
 
@@
 synthetic cannabinoids, cathinones ; N = `r .substances_prev$sum[["NPS"]]`).\
-Reference period ranged from the past month to over the lifetime.\
-See \@ref(tab:SubstanceTab) for more details.
+Reference period ranged from the past month to over the lifetime.
 
@@
 The various definitions differed on the age at which the sexual intercourse occurred to be qualified as childhood sexual abuse, the age gap between the victim and the perpetrator and whether the sexual intercourse was unwanted.
-The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (N = 7).\
-See \@ref(tab:CSATab) for more details.
+The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (N = 7).
 
-For polysubstance use, 17 studies considered there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
-Furthermore, 4 studies excluded marijuana from the class of substances screened and 1 study excluded stimulants, because stimulants were already screened in another syndemic condition.\
-See \@ref(tab:PolysubstanceTab) for more details.
+For polysubstance use, 17 studies considered that there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
+Furthermore, 4 studies excluded marijuana from the class of substances screened and 1 study excluded stimulants, because stimulants were already screened in another syndemic condition.
 
 For binge drinking, we identified `r length(unique(.binge_measurement$binge_episodes))` different thresholds for binge drinking, differing on the number and frequency of binge drinking episodes.
-The threshold ranged from one episode in the past 12 months to more than one episode per week, every week in the past 12 months.\
-See \@ref(tab:BingeTab) for more details.
+The threshold ranged from one episode in the past 12 months to more than one episode per week, every week in the past 12 months.
 
@@
 
-Regarding suicide, `r sum(is.na(measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered only suicidal thoughts , `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered both suicidal thoughts and suicide attempts and `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & is.na(measurement$suicidal_thoughts))` studies considered only suicide attempts.
+Regarding suicide, `r sum(is.na(measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered only suicidal thoughts, `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered both suicidal thoughts and suicide attempts and `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & is.na(measurement$suicidal_thoughts))` studies considered only suicide attempts.
 Furthermore, one study used the Positive and Negative Suicide Ideation scale (PANSI) and one study used the Suicide Behaviors Questionnaire-Revised (SBQ-R).
@@
 The condomless anal sex criteria has been refined in three studies, two of them taking into account the type of partner (regular versus casual) and one, the serologic status of both partners.\
-Other criteria such as condomless oral sex, condomless vaginal sex, STI diagnosis, engagement in sex work and sexual intercourse with a HIV positive partner have been used.
+Other criteria such as condomless oral sex, condomless vaginal sex, STI diagnosis, engagement in sex work and sexual intercourse with an HIV positive partner have been used.
 Finally, one study used the Kalichman's Sexual Sensation Seeking Scale to assess the propensity of participants to engage in novel or risky sexual stimulation.
@@
 For violence `r .violence_prevalence$sum[["sexual"]]` studies looked at sexual violence, `r .violence_prevalence$sum[["physical"]]`, at physical violence and `r .violence_prevalence$sum[["psychological"]]` at psychological violence.
-One Indian study also took into account sexual and physical harassment by the police.\
-See \@ref(tab:ViolenceTab) for more details.
+One Indian study also took into account sexual and physical harassment by the police.
 
@@
 `r length(unique(.anxiety_measurement$criteria))` different criteria were used to assess the presence of an anxiety disorder among the `r nodes$studies[nodes$label == "anxiety"]` studies considering anxiety as a syndemic condition.
-The most frequent criteria was a score equal or greater than 10 on the 7-items version of the Generalized Anxiety Disorder screening test (GAD-7 ; N = `r sum(!is.na(measurement$"GAD-7"))`).\
-See \@ref(tab:AnxietyTab) for more details.
+The most frequent criteria was a score equal or greater than 10 on the 7-items version of the Generalized Anxiety Disorder screening test (GAD-7 ; N = `r sum(!is.na(measurement$"GAD-7"))`).
 
@@
 Finally, for discrimination, there were as many criteria as there were research papers studying this condition.
-Most of the studies only considered discrimination based on sexual orientation, except for two studies examining racist discrimination, one study examining HIV-based discrimination and one study which did not distinguish between discrimination based on sexuality, race/ethnicity or any other factor.
+Most of the studies only considered discrimination based on sexual orientation, except for two studies examining racial discrimination, one study examining HIV-based discrimination and one study which did not distinguish between discrimination based on sexuality, race/ethnicity or any other factor.
 
@@
 We identified `r ncol(.outcomes) - 1` different outcomes in our sample of quantitative studies.
-Sexual risk behaviors was the most frequent outcome as it appeared in `r sum(!is.na(.outcomes$outcome_sexual_risk))` research papers.
+Sexual risk behaviors was the most frequently studied outcome, appearing in `r sum(!is.na(.outcomes$outcome_sexual_risk))` research papers.
 The second most studied outcome was HIV diagnosis (N = `r sum(!is.na(.outcomes$outcome_HIV))`), followed by STI diagnosis (N = `r sum(!is.na(.outcomes$outcome_STI))`), adherence to antiretroviral therapy (N = `r sum(!is.na(.outcomes$outcome_adherence))`), pre-exposure prophylaxis (PrEP) use (N = `r sum(!is.na(.outcomes$outcome_PrEP))`), healthcare use (N = `r sum(!is.na(.outcomes$outcome_healthcare))`) and the syndemic conditions themselves (N = `r sum(!is.na(.outcomes$outcome_syndemic))`).
@@
 
-Every other outcome were only studied once : HIV screening[@Chandler2019b], physical activity[@Zhang2019], hypothalamic-pituitary-adrenal (HPA) axis dysregulation[@carrico2018], sexual violence[@semple2017], glycemic control[@Byg2016], engagement in HIV care[@Biello2016], engagement in chemsex[@friedman2014], having sexual intercourse with both men and women[@eaton2013] , help-seeking behaviors[@achterbergh2021] and substance use[@turpin2020].
+Every other outcome was only studied once : HIV screening[@Chandler2019b], physical activity[@Zhang2019], hypothalamic-pituitary-adrenal (HPA) axis dysregulation[@carrico2018], sexual violence[@semple2017], glycemic control[@Byg2016], engagement in HIV care[@Biello2016], engagement in chemsex[@friedman2014], having sexual intercourse with both men and women[@eaton2013] , help-seeking behaviors[@achterbergh2021] and substance use[@turpin2020].
 
@@
 
-When HIV was used as an outcome, it was self-reported in nearly half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-report was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`).
+When HIV was used as an outcome, it was self-reported in nearly half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`).
 
@@
 Chakrapani et al.
-used a pre-test/post-test non-equivalent group design and the intervention consisted in motivational-interviews.
+used a pre-test/post-test non-equivalent group design and the intervention consisted of motivational-interviews.
 The goal of this intervention was to reduce condomless anal intercourse by enhancing condom self-efficacy and addressing co-occurring syndemic conditions.
@@
 Achterbergh et al.
-conducted a randomized controlled trial and the intervention consisted in tailored feedback and help-seeking advice on mental health screening.
+conducted a randomized controlled trial and the intervention consisted of tailored feedback and help-seeking advice on mental health screening.
 The primary endpoint was to increase help-seeking behaviors ; the secondary endpoints were reducing sexual risk behaviors and STI incidence.
 
-Intervention in both studies lasted for 12 months.
+The intervention lasted for 12 months in both studies.
 
@@
 
-On the other hand, the RCT of Achterbergh et al. failed to affect the primary endpoint and the two secondary endpoints.
+On the other hand, the RCT conducted by Achterbergh et al. failed to affect the primary endpoint nor the two secondary endpoints.
 
@@
 Woodward et al.
-tried to identify a set of resilience resources among MSM burdened with minority stress and psychosocial condition in order to improve HIV prevention.
+aimed to identify a set of resilience resources among MSM burdened with minority stress and psychosocial condition in order to improve HIV prevention [@woodward2017].
 They included `r summary_reviews$studies_included[summary_reviews$authors== "Woodward et al."]` in their reviews and identified 31 resilience resources, with social support and incomes as the two most frequently cited.
@@
 Lassiter et al.
-wanted to propose a framework to include religion and spirituality into HIV research with MSM.
+aimed to propose a framework to include religion and spirituality into HIV research with MSM [@Lassiter2016].
 They found that religion and spirituality had mixed effect on syndemic conditions but could be more beneficial for MSM of color than for white MSM.
-Of note, they only included `r summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."]` as these two factors were very sparse in syndemic literature.
+Of note, they only included `r summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."]` studies as these two factors were very sparse in syndemic literature.
 
 Lewis et al.
-sought to examine the HIV prevalence and associated risk behaviors among migrant and ethnic minority MSM in North America and Europe.
+sought to examine the HIV prevalence and associated risk behaviors among migrant and ethnic minority MSM in North America and Europe [@lewis2017].
 They found high rates of HIV prevalence and associated risk factors and proposed that transnational migration could be part of a syndemic.
@@
 In their meta-analysis, Rooney et al.
-tried to determine the syndemic conditions associated with sexual compulsivity among MSM and to compute the mean effect size as well as if this effect varied as a function of the type of syndemic conditions.
+studied the syndemic conditions associated with sexual compulsivity among MSM and computed the mean effect size as well as whether this effect varied as a function of the type of syndemic conditions associated [@Rooney2018a].
 They included `r summary_reviews$studies_included[summary_reviews$authors== "Rooney et al."]` papers and found that sexual compulsivity was significantly associated with 7 syndemic conditions (anxiety, depression, CSA, alcohol use, substance use, IPV and sexual risk behaviors).
@@
 Finally, Pantalone et al.
-sought to have a better understanding of the state of interventions co-targeting interconnected syndemic conditions and HIV-related health behaviors of MSM.
+sought to have a better understanding of the state of interventions co-targeting interconnected syndemic conditions and HIV-related health behaviors of MSM [@Pantalone2020].
 They included `r summary_reviews$studies_included[summary_reviews$authors== "Pantalone et al."]` studies and found a small significant positive effect of combined behavioral interventions to improve mental health, substance use, alcohol use and sexual risk behaviors, with significant heterogeneity.
 Interestingly, a greater number of sessions (at least 9) and individual rather than group interventions showed greater efficacy.
+
+### Additional framework used in the studies
+
+`r nrow(.framework)` studies used an additional framework alongside syndemic theory.
+The most widely used was resilience theory (N = 10), followed by minority stress model (N = 5), intersectionality (N=2), social-cognitive theory (N=2) and salutogenesis (N=1).
 
@@
 It should be stated that, when we speak of interaction between syndemic conditions we don't necessarily mean "synergy", though synergy is indeed one of the interaction we consider.
-As such, we consider that a statistic method such as mediation analysis to show interaction between variables as it sheds light on the mechanism by which syndemic conditions may influence an outcome or on how syndemic conditions may influence each others.
+Drawing from the works of authors such as Tsai and Chakrapani, we consider three types of interaction : synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics [@Tsai2018a; @Chakrapani2019].
+As such, statistical methods such as mediation analysis, path analysis or structural equation modeling are also considered.
 
-Our review revealed a great degree of variability in statistic analysis too.
-The most frequently used statistic method was to conduct regression analysis using a summation score of the syndemic conditions (N = `r sum(!is.na(.statistics_data$score))`).
-Among studies employing this method, `r nrow(.score_data)` did not use any other method to determine the degree of interaction between syndemic conditions and the outcome.
+Our review revealed a high degree of variability in the statistic analyses.
+The most frequently used statistical method was to conduct regression analysis using a summation score of the syndemic conditions (N = `r sum(!is.na(summary_quantitative$score))`).
+Among studies employing this method, `r .score_data` did not use any other method to determine the degree of interaction between syndemic conditions.
 
-In comparison, only `r .N_additivity` studies tried to evaluate departure from additivity on the additive and/or multiplicative scales, as recommended by Tsai [@tsai2015] to show synergy between syndemic conditions.
+In comparison, only `r .N_additivity` studies tried to evaluate departure from additivity on the additive and/or multiplicative scales, as recommended by Tsai [@tsai2015] to demonstrate synergy between syndemic conditions.
 
-Furthermore, some studies sought to get a better understanding on the mechanism of interaction between the syndemic conditions and the outcome by using mediation analysis (N = `r sum(!is.na(.statistics_data$mediation))`), moderation analysis (N = `r sum(!is.na(.statistics_data$moderation))`), Structural Equation Modeling (N = `r sum(!is.na(.statistics_data$SEM))`) or path analysis (N = `r sum(!is.na(.statistics_data$path))`).
+Furthermore, some studies sought to get a better understanding on the mechanism of interaction between the syndemic conditions and the outcome by using mediation analysis (N = `r sum(!is.na(summary_quantitative$mediation))`), moderation analysis (N = `r sum(!is.na(summary_quantitative$moderation))`), Structural Equation Modeling (N = `r sum(!is.na(summary_quantitative$SEM))`) or path analysis (N = `r sum(!is.na(summary_quantitative$path))`).
 
@@
 
-Using a different approach, `r sum(!is.na(.statistics_data$network))` studies conducted by Lee and colleagues [@lee2020; @Lee] used network analysis, in which syndemic is conceptualized as a network and the syndemic conditions as interconnected nodes reinforcing each others.
+Using a different approach, `r sum(!is.na(summary_quantitative$network))` studies conducted by Lee and colleagues [@lee2020; @Lee] used network analysis, in which syndemic is conceptualized as a network and the syndemic conditions as interconnected nodes reinforcing each others.
 
-Finally, other statistic analysis used to assess interaction were observed/expected ratio (N = `r sum(!is.na(.statistics_data$O_E))`), cluster analysis (N = `r sum(!is.na(.statistics_data$cluster))`) and point-biserial correlation matrix (N= `r sum(!is.na(.statistics_data$biserial))`).
+Finally, other statistic analysis used to assess interaction were observed/expected ratio (N = `r sum(!is.na(summary_quantitative$O_E))`), cluster analysis (N = `r sum(!is.na(summary_quantitative$cluster))`) and point-biserial correlation matrix (N= `r sum(!is.na(summary_quantitative$biserial))`).
 
@@
 
-Qualitative studies proposed mechanism of bio-social interaction more often than quantitative studies as we identified `r sum(!is.na(summary_qualitative$bio_social_interaction))` papers with such hypothesis of interaction.
-On the other hand, we did not found any qualitative paper exploring biological interaction.
+Qualitative studies proposed mechanisms of bio-social interaction more often than quantitative studies as we identified `r sum(!is.na(summary_qualitative$bio_social_interaction))` papers with such hypothesis of interaction.
+On the other hand, we did not find any qualitative paper exploring biological interaction.
 
-Stigma and structural inequalities were pointed out as the root causes of syndemic conditions and HIV risk behaviors.
+Stigma and structural inequalities were indicated by the 5 papers as the root causes of syndemic conditions and HIV risk behaviors.
 Maionara et al.
 showed that economic dependency and fear of violence may maintain YBMSM in dysfunctional relationships plagued by IPV and substance abuse which increase their odds of incarceration and HIV infection [@Maiorana].
-Furthermore, methamphetamine is used as a coping strategy against this structural violence and HIV diagnosis while representing a potential factor in acquiring or transmitting HIV to others, notably during sex parties.
-This finding of substance use as a coping mechanism was supported by the study of Pollard et al.
+Furthermore, methamphetamine is used as a coping strategy while simultaneously representing a potential factor in acquiring or transmitting HIV to others, notably during sex parties.\
+This finding of substance use as a coping mechanism was supported by the study by Pollard et al.
 who found that maladaptive coping strategies to minority stress and the performative resistant space of the gay scene contributed to chemsex use [@Pollard2018a].
+
 For Black MSM, other sources of structural violence such as racial neighborhood segregation contributed, alongside poverty, unemployment, violence, unstable housing, incarceration and poor healthcare access to expectations surrounding masculinity which may conflict with the sexual orientation of BMSM, leading to internalised homophobia [@Quinn].
@@
 Lyons et al.
-also showed that the marginalization of YMSM withing their school, communities of origin and families resulted in a lack of gay-specific HIV prevention education, role-model and productive goal-related activities [@Lyons2013].
+also showed that the marginalization of YMSM within their school, communities of origin and families resulted in a lack of gay-specific HIV prevention education, role-model and productive goal-related activities [@Lyons2013].
 The HIV-positive MSM youth in this study linked these factors to their HIV acquisition.
@@
 On the topic of synergy, results were conflicting between studies.
-Chakrapani and colleagues found support to the three models of interacting epidemics (synergistically interactig epidemics, serially causal epidemics and mutually causal epidemics) with the strongest support for the model of synergistically interacting epidemics [@Chakrapani2019].
+Chakrapani and colleagues found support for the three models of interacting epidemics (synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics) with the strongest support for the model of synergistically interacting epidemics [@Chakrapani2019].
 These findings were supported by other studies who found synergy when using significant product terms in the additive and/or multiplicative scales [@Chakrapani; @chandler2020; @Chandler2019; @tomori2018].
@@
 Card et al found no association between the AUDIT score and sexual risk behaviors [@Card2018] while another study using latent class analysis found that the class with alcohol misuse had a lower level of risk behaviors [@scheer2021].
-Nonetheless, alcohol misuse was found to be associated with PrEP nonadherence [@shuper2020].
+Nonetheless, alcohol misuse was found to be associated with PrEP non-adherence [@shuper2020].
 
@@
 
-Finally, social was shown to moderate the effect of syndemic conditions on viral load, providing a significant protective effect [@friedman2016].
-Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic condition on substance use showed that Black MSM with more social support had higher odds of staying in the low-risk class or transitioning from the high risk class to the low-risk class [@turpin2020].
+Social support was shown to moderate the effect of syndemic conditions on viral load, providing a significant protective effect [@friedman2016].
+Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic conditions on substance use showed that Black MSM with more social support were more likely to stay in the low-risk class or transitioning from the high risk class to the low-risk class [@turpin2020].
 However, Chakrapani et al.
 found no moderation of social support on the relationship between syndemic conditions and risk taking [@Chakrapani2017].
+
+On the topic of resilience resources, Zhang et al didn't find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
+O'Leary et al.
+didn't find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviors, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
+On the other hand, Kurtz et al found that, among MSM living with HIV, serosorting was positively associated with higher levels of two resilience factors : coping self-efficacy and positive coping skills [@Kurtz2012].
+Similarly, Hart et al.
+found that psychosocial strengths were associated with lesser odds of engaging in condomless anal sex, despite the presence of syndemic conditions [@Hart2017].

### 2021-10-05 _bookdown_files/05-discussion.Rmd
Working on the discussion

---
bibliography: references.bib
---

# Discussion

What stands out the most when we consider syndemic literature applied to MSM is that it is both too homogeneous in some aspects while being not focused enough in other parts. As we will discuss in more depth below, the location, design, subpopulation and outcomes should be more diverse that it currently is. On the other hand, the syndemic conditions and ways of measurement should be more focused to improve the robustness and reproducibility of the findings.

More concerning, maybe, is the fact that a substantial part of the literature doesn't provide empirical data to support one of the core tenets of syndemic theory - namely disease interaction- as was already pointed out in a previous review [@tsai2015].

## Design and location

Design and location are two aspects of syndemic literature suffering from too much homogeneity. Indeed, `r percent(.N_cross_sec/.N_QualQuant)` of the syndemic literature employs a cross-sectional design while `r percent(.North_America_studies/.N_QualQuant)` of studies are conducted in North America. Taken together, all studies conducted in the Global South represents only `r percent(.GlobalSouth_studies/.N_QualQuant)` of our sample.

Three issues arise from this. First, under-representation of the Global South is inherently an issue as it precludes us to better understand the health of MSM living in these countries. Furthermore, as aptly pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting. As syndemics are driven by the sociocultural forces of a given place at a given time, these potential biases need to be addressed in order to conduct meaningful research outside Europe and North America.

Moreover, even for studies conducted in Europe and North America, a large portion of the studies conflate data from different cities, counties, states or even countries in order to obtain a sample big enough to conduct statistical analyses. However, geographical variations in syndemic burden are likely to be missed. Migration of MSM to larger cities is a well-known phenomenon and thought to be an important part of syndemic production among MSM as well as a source of resilience [@stall2007; @Bruce2011].

Grandes villes ==\> plus de stress mais aussi plus de résilience

Parler de l'importance d'intégerer des notions d'épidémiologie spatiale.

## Subpopulations

## Syndemic conditions

## Outcomes

## Statistics and interaction

## Additional framework

### 2021-10-05 _bookdown_files/06-conclusion.Rmd
Working on the discussion

# Strengths and limitations

# Conclusion and recommendations

Le fait qu'un effet reste marqué malgré à travers toutes les méthodologies, conditions étudiées, populations étudiées, lieux étudiés montre une robustesse importante. Néanmoins, il faut mieux faire à l'avenir

1.  Plus d'études hors USA et plus d'études dans le Sud. Plus d'études à petites échelles géographiques pour mieux saisir l'impact des dynamiques géographiques locales sur la syndémie. Des mesures adaptées selon les pays

Le champ de la recherche syndémique gagnerait à étudier davantage de sous-populations de HSH dans des contextes géographiques plus divers et locaux tout en incorporant d'autres méthodes telles que l'analyse en réseau ou l'épidémiologie spatiale. En outre, davantage de données qualitatives et mixtes aideraient à faire avancer la compréhension de l'impact de la syndémie sur le vécu des personnes. Les outcomes devraient moins se focaliser sur la santé sexuelle et explorer d'autres impacts de la syndémie sur la santé des individus. Enfin, il est urgent de définir plus précisément les contours des conditions qui constituent réellement une syndémie et la meilleure manière de les mesurer en prenant en compte les difficultés de transposer certaines mesures dans des contextes socio-culturels différents.

### 2021-10-05 Scripts/create_location_data.R

@@ -36,3 +36,5 @@ year_continent <- year_continent%>%
 .South_America_studies <- max(year_continent$cumulative_continent[year_continent$continent == "South America"])
 
 .Africa_studies <- max(year_continent$cumulative_continent[year_continent$continent == "Africa"])
+
+.GlobalSouth_studies <- .Asia_studies + .South_America_studies + .Africa_studies

### 2021-10-05 Scripts/create_statistics_data.R

@@ -1,16 +1,18 @@
-.statistics_data <- summary_quantitative %>%
-  select(1:3, 259:274, 276:278) %>%
-  unite(col = "author_year", c(authors, year), sep = " ") %>%
-  unite(col = "reference", c(author_year, letter), sep = "", na.rm = TRUE) 
+.N_latent <- summary_quantitative %>%
+  filter(summary_quantitative$LCA_LPA == "LCA_LPA" |
+           summary_quantitative$EFA == "EFA"| 
+           summary_quantitative$CFA == "CFA" | 
+           summary_quantitative$LTA == "LTA") %>%
+  nrow()
 
-.N_latent <- sum(!is.na(.statistics_data$LCA_LPA)) +
-  sum(!is.na(.statistics_data$EFA)) +
-  sum(!is.na(.statistics_data$CFA)) + 
-  sum(!is.na(.statistics_data$LTA))
+.N_additivity <- summary_quantitative %>%
+  filter(summary_quantitative$RERI == "RERI" | 
+           summary_quantitative$product_term == "product_term") %>%
+  nrow()
+  
 
-.N_additivity <- sum(!is.na(.statistics_data$RERI)) +
-  sum(!is.na(.statistics_data$product_term))
-
-.score_data <- .statistics_data %>%
-  unite(col = "statistics", 2:20, sep = ", ", na.rm = TRUE) %>%
-  filter(statistics == "score")
+.score_data <- summary_quantitative %>%
+  select(259:274, 276:278) %>%
+  unite(col = "statistics", 1:19, sep = ", ", na.rm = TRUE) %>%
+  filter(statistics == "score") %>%
+  nrow()

### 2021-10-05 Scripts/create_year_design.R

@@ -26,3 +26,4 @@ year_design <- year_design %>%
 .N_qual <- max(year_design$cumulative[year_design$design == "Qualitative"])
 .N_int <- max(year_design$cumulative[year_design$design == "Interventional"])
 .N_SR <- max(year_design$cumulative[year_design$design == "Systematic reviews, meta-analyses"])
+.N_QualQuant <- nrow(summary_qualitative) + nrow(summary_quantitative)

### 2021-10-05 Scripts/create_framework_data.R
Adding a part on framework

@@ -1,0 +1,23 @@
+.framework_quantitative <- summary_quantitative %>%
+  select(1:3, 286:290) %>%
+  unite("reference", 1:3, na.rm = T, sep = " ") %>%
+  filter(!is.na(minority_stress)|!is.na(social_cognitive)|
+           !is.na(salutogenesis)|
+           !is.na(resilience)|
+           !is.na(intersectionality)) %>%
+  unite("additional_framework", 2:6, sep = " ", na.rm = T) 
+  
+
+.framework_qualitative <- summary_qualitative %>%
+  select(1:2, 19) %>%
+  unite("reference", 1:2, sep = " ", na.rm = T) %>%
+  filter(!is.na(additional_framework))
+
+.framework_reviews <- summary_reviews %>%
+  select(1:2, 11) %>%
+  unite("reference", 1:2, sep = " ", na.rm = T) %>%
+  filter(!is.na(additional_framework))
+
+.framework <- bind_rows(.framework_qualitative, 
+                       .framework_quantitative, 
+                       .framework_reviews)

### 2021-10-14 _bookdown_files/04-results.Rmd
End of discussion

@@
 
-When HIV was used as an outcome, it was self-reported in nearly half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`).
+When HIV was used as an outcome, it was self-reported in nearly half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`.
 
@@
 In a longitudinal study [@Mustanski2017] Black MSM were found to have the highest HIV incidence while having a lower burden of syndemic condition than White MSM, raising the question of the need to focus on syndemic conditions specific to Black MSM.
-
-Social support was shown to moderate the effect of syndemic conditions on viral load, providing a significant protective effect [@friedman2016].
-Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic conditions on substance use showed that Black MSM with more social support were more likely to stay in the low-risk class or transitioning from the high risk class to the low-risk class [@turpin2020].
-However, Chakrapani et al.
-found no moderation of social support on the relationship between syndemic conditions and risk taking [@Chakrapani2017].
-
-On the topic of resilience resources, Zhang et al didn't find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
-O'Leary et al.
-didn't find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviors, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
-On the other hand, Kurtz et al found that, among MSM living with HIV, serosorting was positively associated with higher levels of two resilience factors : coping self-efficacy and positive coping skills [@Kurtz2012].
-Similarly, Hart et al.
-found that psychosocial strengths were associated with lesser odds of engaging in condomless anal sex, despite the presence of syndemic conditions [@Hart2017].

### 2021-10-14 _bookdown_files/05-discussion.Rmd
End of discussion

@@
 
-## Design and location
+## Location
 
-Design and location are two aspects of syndemic literature suffering from too much homogeneity.
-Indeed, `r percent(.N_cross_sec/.N_QualQuant)` of the syndemic literature employs a cross-sectional design while `r percent(.North_America_studies/.N_QualQuant)` of studies are conducted in North America.
-Taken together, all studies conducted in the Global South represents only `r percent(.GlobalSouth_studies/.N_QualQuant)` of our sample.
+The location of study is an aspect of syndemic literature suffering from too much homogeneity.
+Indeed `r percent(.North_America_studies/.N_QualQuant)` of studies are conducted in North America alone while all studies conducted in the Global South represents only `r percent(.GlobalSouth_studies/.N_QualQuant)` of our sample.
 
@@
 First, under-representation of the Global South is inherently an issue as it precludes us to better understand the health of MSM living in these countries.
-Furthermore, as aptly pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting.
+Furthermore, as aptly pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
 As syndemics are driven by the sociocultural forces of a given place at a given time, these potential biases need to be addressed in order to conduct meaningful research outside Europe and North America.
@@
 Migration of MSM to larger cities is a well-known phenomenon and thought to be an important part of syndemic production among MSM as well as a source of resilience [@stall2007; @Bruce2011].
+Differences in the density of gay social venues and peer organizations as well as exposure to discrimination and violence or an easier access to substances need to be taken into account when studying a syndemic.
+Thus, as @shrestha2020 suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence the health of MSM.
 
-Grandes villes ==\> plus de stress mais aussi plus de résilience
+## Design
 
-Parler de l'importance d'intégerer des notions d'épidémiologie spatiale.
+The design of syndemic studies is another point suffering from a lack of diversity.
+The field is dominated by quantitative studies as qualitative papers represent only `r percent(.N_qual/nrow(overview_of_studies))` of our sample.
+Quantitative studies, on their part, employ a cross-sectional design in `r percent(.N_cross_sec/.N_QualQuant)` of the papers.
+As vulnerability to syndemic conditions is suspected to arise from early adverse experience @stall2007 longitudinal studies running on a long period of time are probably needed to study syndemic production among MSM.
+
+Moreover, as shown in our result, qualitative paper are more prone to discuss the potential interactions between syndemic conditions.
+Some concepts and experiences needed to understand syndemic production in MSM can only be studied through a qualitative lens.
+For example, the complex narratives surrounding drug use and its link to loneliness, marginalization, personal affirmation, resistance and lack of meaningful emotional connections @Pollard2018a would be hard to measure and model using quantitative data.
+As Alexander Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to over-simplification of diseases dynamics @Tsai2018a .
+As such, we concur that mixed method are direly needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
+Unfortunately, our review only identified `r max(year_design$cumulative[year_design$design == "Mixed"])` studies employing such mixed methodology.
+Future research would gain to take advantage of qualitative data to support and deepen their quantitative findings.
+
+Finally, we identified `r .N_int` interventional studies with mixed results.
+While co-targeting interconnected syndemic conditions is supported by a meta-analysis @Pantalone2020, a better understanding of how syndemic operate may be needed before offering efficient syndemic-based interventions.
 
@@
 
+Studying the health of MSM pose a challenge regarding the diversity of this population.
+While nearly half of the studies included in our sample studied a subpopulation of MSM, the number of MSM subpopulation is such that most MSM subpopulation remain undeserved.
+For example, Young Black MSM are specifically studied in `r .N_YBMSM` studies while representing 52% of the new HIV diagnosis among MSM aged 13-24 years in 2018 @centerfordiseasecontrolandprevention2020.
+
+This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic condition such as HIV infection is even more concerning when considering that dual-minority identity may expose to different stressors and outcomes.
+For example, some study found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to less syndemic conditions @Mustanski2017 .
+These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM @Quinn .
+
+MSMW are another example of undeserved population with conflicting results.
+In a cross-sectional study using syndemic sum count, Latino MSMW with two or more syndemic conditions had a 7.09 Odds Ratio to engage in receptive condomless anal sex but no statistically significant difference were found for insertive condomless anal sex or condomless vaginal sex @Munoz-Laboy2018.
+On the other hand, in another study the number of syndemic conditions was associated with HIV diagnosis for MSM but not for MSW or MSMW @Branstrom2018.
+Among young MSM and MSMW, one study found more syndemic conditions and a greater association between them for MSMW compared to MSM @Mustanski2014.
+On the contrary, Ferlatte et al.
+found that MSM were more likely than MSMW to suffer from two or more syndemic conditions @ferlatte2018.
+These conflicting findings may be partly due to the difficulty to define and operate bisexuality in research @swan2018, difference between age groups or differences in syndemic mechanism for MSMW compared to MSM.
+Outside the field of syndemic literature, studies suggest that bisexual men suffer from a similar or higher burden in mental health condition compared to gay men [@salway2019; @Chaudhry2019; @ross2018] and literature specific to bisexual men remains scarce.
+Syndemic theory should thus seek to study forward the specificity of this population.
+First, there's a need to better conceptualize and define bisexuality in the field - should we still use solely behavior-based definition (as in MSMW) or should we incorporate self-definition of one's sexual orientation ?
+Then, researchers should see to disaggregate data concerning MSMW/bisexual men from data concerning MSM/gay men whenever possible.
+Lastly, more research focused on MSMW/bisexual men is needed.
+
+Finally transgender MSM were included in only one study of our sample.
+As stated in our result, this is concerning, especially when every other study exclude transgender men by design.
+As such, this population of MSM is the one we know the less about.
+The study from Reisner and colleagues suggested that transgender MSM who had socially affirmed their gender were exposed to similar risk patterns as cisgender MSM @Reisner2016a.
+The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence @Testa2012, suicide attempts @Haas2014, chlamydial and gonoccocal infections @Pitasi2019 and HIV infection @Becasen2019.
+Researcher should therefore include transgender men in their studies and conduct research focused on transgender MSM.
+Indeed, syndemic theory represents a promising framework for transgender men as its premises of social adversities producing and concentrating diseases in a population allows to explore the health of transgender men without pathologizing them.
+
 ## Syndemic conditions
+
+A clear lack of consensus exists in the choice of syndemic conditions and the way they should be measured.
+We identified `r nrow(nodes)` different conditions in our quantitative sample and `r nrow(nodes %>% filter(studies == 1))` of them were only studied once.
+Some of these conditions are past event (e.g.
+history of trauma or childhood sexual abuse) while most were current conditions.
+Given the cross-sectional nature of `r percent(.N_cross_sec/nrow(summary_quantitative))` of the quantitative paper, we can't disentangle how past experiences may influence the emergence of a syndemic.
+
+Furthermore, studies diverge on what represents a syndemic condition and what may lead to the emergence of a syndemic.
+For example, childhood sexual abuse is mostly seen as a syndemic condition per se but may very well be a risk factor to the emergence of a syndemic, as hypothesized by some authors @Herrick2013.
+The same question may be asked for discrimination, trauma, impulsivity, bullying, poor social support, loneliness, childhood abuse, poor healthcare access, etc.
+Qualitative and longitudinal studies are needed to distinguish between syndemic conditions and pathways to the emergence of a syndemic.
+Conflating the two in cross-sectional studies does very little to advance our understanding of syndemic theory or to implement public health interventions.
+
+Furthermore, even when the same condition was studied in multiple papers, the differences in measurement methods impedes greatly the reproducibility of the results.
+For example, let us imagine a participant with a CESD score of 16, who uses marijuana on a regular basis and cocaine once in a while and who is victim of sexual intimate partner violence.
+This man would have been classified as depressed in `r percent(sum(.depression_measurement$depression_cutoff == 16 & .depression_measurement$depression_scale_criteria == "CESD")/sum(.depression_measurement$depression_scale_criteria == "CESD"))` of studies using the CESD, a polysubstance user in `r percent(sum(.polysubstance_measurement$polysubstance_number == "More than one category of substance use" & .polysubstance_measurement$polysubstance_marijuana == "Marijuana included")/nrow(.polysubstance_measurement))` of studies considering polysubstance use and as a victim of intimate partner violence in `r .IPV_prevalence$perc[["sexual IPV"]]` of studies taking IPV into account.
+In other words, the same person could have been classified as having 0, 1, 2 or even 3 syndemic conditions, depending on the study.
+Considering that most studies use a summation score of the number of syndemic conditions to conduct regression analysis, it seems evident that the results would greatly vary according to the way the syndemic conditions are measured.
+
+It is beyond the scope of this paper to discuss in details which syndemic conditions should be retained for future research and how to best measure them, but without a greater homogeneity in the field, the confidence and reproducibility of the results will remain an issue.
 
@@
 
+Taken together, `r percent(.HIV_number/nrow(summary_quantitative))` of the quantitative studies in our sample had an HIV-related outcome, whether in the form of sexual risk behaviors, HIV diagnosis, HIV screening, adherence to antiretroviral therapy, PrEP use, viral load or engagement in HIV care.
+
+This omnipresence of HIV in syndemic literature applied to MSM is doubly understandable.
+The first description of a syndemic, the SAVA syndemic, incorporated AIDS as part of a syndemic @singer1996.
+Then, a few years later, the first paper on syndemic in the MSM population had HIV-related outcomes, in the form of HIV serostatus and CAS @Stall2003.
+Furthermore MSM were the first and most severely affected population when the AIDS epidemic started @decock2012.
+Nowadays, male-to-male sexual contact still represents nearly 70% of the new HIV cases in the USA @centerfordiseasecontrolandprevention2020.
+While we can't deny the importance of the HIV pandemic, notably for MSM, we would argue that HIV is not the only issue in need of attention.
+
+Indeed, MSM are also disproportionately affected by suicide, anxiety, depression and substance use to name a few [@ross2018; @luo2017; @Medley2016].
+Moreover, with the advances in antiretroviral therapy and the subsequent decline in HIV-related mortality, gay men were more likely to die from suicide than from HIV in Canada in 2011 @hottes2015.
+Even if the estimates in this paper overestimated suicide's mortality among MSM, suicide would still be a leading cause of death in this population while being studied as an outcome in only `r sum(!is.na(.outcomes$outcome_suicide))` papers in our sample.
+
+Furthermore, when studying HIV as an outcome, we would argue that condomless anal sex should be replaced by better proxies.
+First, without refinement, this outcome fails to capture the changes in HIV prevention strategies such as PrEP or Treatment as Prevention (TasP).
+Only `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))` studies in our sample took PrEP use and an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.
+When the first paper on syndemic theory applied to MSM were published, engaging condomless anal sex would have led to a high risk of acquiring HIV.
+Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV @calabrese2017 and our methodologies should reflect this change.
+In addition, qualitative research gives insight in risk practices and offers a more nuanced view on this topic than a binary variable of consistent condom use for anal intercourses.
+One such paper published in 2017 showed that risk practice fell into different subjectivities such as active and consistent pursuit of condomless sex, lack of assertiveness to a partner's initiative of condomless anal sex and combination of episodic risk practices and reduction strategies @Adam2017.
+Besides, some studies showed that participants with a greater number of syndemic conditions would engage more frequently in condomless anal sex while not being more likely to test positive for HIV [@Mustanski2017; @Pitpitan2016].
+On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated to HIV self-report but not to condomless anal sex @chuang2018.
+Taken together, we thus postulate that condomless anal sex should at least be replaced by "condomless anal sex without consistent PrEP use or with a detectable viral load" when an investigator seek to use sexual risk behaviors as an outcome.
+
+In summary, we recommend that future research should focus on other aspects of MSM's health than HIV infection and, when studying HIV as an outcome to prefer laboratory-based outcomes or more refined sexual risk variables than condomless anal sex.
+
 ## Statistics and interaction
 
+One of the tenets of syndemic theory is that there exists some form of biological, social and/or psychological interaction between the diseases @mendenhall2020.
+As others have already pointed before us, the extent to which syndemic literature had proved this core principle remains very limited @tsai2015.
+Indeed, `r percent(.score_data/nrow(summary_quantitative))` of our quantitative sample of studies used solely a summation score of the syndemic conditions to conduct regression analysis.
+Two issues arise from this statistical approach.
+First, summation score are additive by essence, thus unsuitable to demonstrate an interaction @tsai2015.
+Secondly, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting @Halkitis2013a.
+Put simply, using a summation score would imply that (1) every condition form a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having an history of childhood sexual abuse would contribute equally to a syndemic).
+The unidimensionality aspect of the construct has received some empirical support by Mustanski et al.
+as well as by Starks et al.
+using respectively Structural Equation Modeling and Latent Class Analysis [@Mustanski2014; @Starks2014].
+However constraining factor loadings to be equal resulted in worse fit in both studies.
+
+In short, the result of our review suggests that as much as `r percent(.score_data/nrow(summary_quantitative))` of the quantitative literature on syndemic theory applied to MSM doesn't empirically support the presence of a syndemic and employs questionable statistical assumptions.
+Those studies are more an exploration of psychosocial risk factors associated to HIV acquisition or progression than the holistic framework syndemic is supposed to be.
+
+As mentioned in the results, two statistically distinct models may be envisioned apart from synergistically interacting epidemics : mutually causal epidemics and serially causal epidemics [@Tsai2018a].
+As such, mediation analysis, path analysis or structural equation modeling may prove useful to assess an interaction.
+
+More recently, a new statistical approach inspired from research in psychopathology has been used to model syndemics : network analysis [@Lee; @lee2020].
+The core principle of this approach is that mental disorders arise from causal interactions between symptoms in a network @borsboom2017.
+Applied to syndemic theory, a syndemic would then be the network and the various conditions would then be the nodes of the network.
+Furthermore, one of the benefits of this approach reside in the theoretical possibility to identify influential nodes in a network : nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network @robinaugh2016.
+In short, in addition to be statistically sound and coherent with the model of mutually causal epidemics, network analysis could offer actionable data to improve the health of MSM by identifying which conditions should be prioritized for interventions.
+
+We recommend that future work should let go of the summation score approach and attempt to clarify which model of interaction receives the most empirical support in order to implement effective public health interventions.
+Indeed as reminded by Chakrapani et al.
+the three models have different programmatic implications @Chakrapani2019.
+In the case of synergistically interacting epidemics, a single intervention may yield greater health improvement than if no interaction was present.
+For mutually causal epidemics, multicomponent interventions addressing the various epidemics should be implemented in order to produce an improvement.
+Finally, for serially causal epidemics, intervening at the root cause of a syndemic may prevent the development of a syndemic cascade.
+
 ## Additional framework
+
+Resilience theory was the most frequently used framework to compliment syndemic theory.
+
+Social support was shown to moderate the effect of syndemic conditions on viral load, providing a significant protective effect [@friedman2016].
+Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic conditions on substance use showed that Black MSM with more social support were more likely to stay in the low-risk class or transitioning from the high risk class to the low-risk class [@turpin2020].
+However, Chakrapani et al.
+found no moderation of social support on the relationship between syndemic conditions and risk taking [@Chakrapani2017].
+
+On the topic of resilience resources, Zhang et al didn't find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
+O'Leary et al.
+didn't find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviors, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
+On the other hand, Kurtz et al found that, among MSM living with HIV, serosorting was positively associated with higher levels of two resilience factors : coping self-efficacy and positive coping skills [@Kurtz2012].
+Similarly, Hart et al.
+found that psychosocial strengths were associated with lesser odds of engaging in condomless anal sex, despite the presence of syndemic conditions [@Hart2017].
+
+In qualitative studies, resilience was also found to exert a protective effect against syndemic conditions [@Chakrapani2019a; @Reed2016; @adam2018].
+Besides, the review by Woodwards et al.
+found a protective effect of most resilience resources identified against HIV @woodward2017.
+
+Minority stress represents another interesting framework as it allows to explain how social stigma can get into the skin of minorized populations @Meyer2003.
+Finally, as aforementioned, intersectionality may offer an useful framework to explore how syndemics operate among different subpopulations of MSM, especially MSM living with a dual-minority identity such as Black MSM.
+
+We recommend that future work continue to explore the impact of resilience in partially counteracting syndemic to develop public health intervention that aim at fostering resilience resources among MSM.
+Furthermore, an intersectional lens should be used more often to elucidate the mechanisms of syndemic among MSM with a dual-minority identity.

### 2021-10-14 _bookdown_files/06-conclusion.Rmd
End of discussion

@@
 # Strengths and limitations
+
+1.  On a pu rater de la littérature
+2.  Caractère arbitraire du classement "syndémie central à la publication"
+3.  Limitations d'un scoping review : pas d'analyse sur les risques de biais ou la force des preuves
+4.  Premier scoping review sur le sujet
+5.  Stratégie de recherche exhaustive et validée par Durieux
+6.  Transparence
+7.  Détails
 

### 2021-10-14 Scripts/create_outcomes_data.R

@@ -17,3 +17,11 @@
   sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_CAS)) +
   sum(!is.na(.outcomes_sex_risk_measurement$outcome_casual_CAS)) +
   sum(!is.na(.outcomes_sex_risk_measurement$outcome_current_CAS))
+
+.HIV_number <- sum(!is.na(.outcomes$outcome_adherence)) +
+  sum(!is.na(.outcomes$outcome_sexual_risk)) +
+  sum(!is.na(.outcomes$outcome_PrEP)) +
+  sum(!is.na(.outcomes$outcome_HIV)) +
+  sum(!is.na(.outcomes$outcome_VL)) +
+  sum(!is.na(.outcomes$outcome_screening)) +
+  sum(!is.na(.outcomes$outcome_HIV_care))

### 2021-10-19 _bookdown_files/06-conclusion.Rmd
Conclusion

--- 2021-10-05 _bookdown_files/06-conclusion.Rmd
@@
 # Strengths and limitations
+
+This review is the first Scoping Review to map the current knowledge in Syndemic Theory applied to MSM.
+We charted and presented detailed data regarding the way research has been done.
+As such, we offer a precious insight and actionable recommendations for the future of the field.
+Our search strategy of electronic databases was comprehensive and developed with the help of the director of health sciences library of our institution.
+We combined this database search with a secondary hand-search of references lists of the included studies.
+Moreover, we conducted a fully transparent and reproducible review.
+Other researchers may freely reuse our data and scripts to conduct their own work.
+To this end, we created a SQL database from our data.
+Other researchers may thus perform complex queries on our database of included studies to quickly identify studies relevant for their work (e.g.
+every study using the CESD to measure depression on Black MSM between 2014 and 2019).
+
+However, even though we took several steps to ensure the comprehensiveness of our search strategy, we may still have missed some relevant literature.
+Furthermore, one of our inclusion criteria was the centrality of syndemic theory to the screened paper.
+Even if two reviewers screened a part of the studies independently, this criteria may be somewhat arbitrary and other researchers may have chosen to include papers we rejected or the contrary.
+Finally, usual limitations of a scoping review apply such as the lack of risk of bias and strength of evidence assessment.
 
@@
 
-Le fait qu'un effet reste marqué malgré à travers toutes les méthodologies, conditions étudiées, populations étudiées, lieux étudiés montre une robustesse importante.
-Néanmoins, il faut mieux faire à l'avenir
+Our review of syndemic research applied to MSM revealed some important limitations that must be addressed in future work.
+The field of syndemic research would gain to study more MSM subpopulations, in more diverse geographical settings, especially in the Global South.
+Furthermore, promising methods such as spatial epidemiology or network analysis may help to advance the field while methods such as summary count should be abandoned.
+Besides, more qualitative and mixed data may enhance our understanding of the complex interactions of a syndemic on the living experiences of marginalized people suffering from it.
+Moreover, outcomes should be less focused on sexual health and start to explore other potential impact of a syndemic on health.
+Finally, conditions that constitute a syndemic should be more precisely defined and the measurement of said conditions should be more standardized while taking into account the difficulties of transposing some measures in different sociocultural contexts.
 
-1.
-Plus d'études hors USA et plus d'études dans le Sud.
-Plus d'études à petites échelles géographiques pour mieux saisir l'impact des dynamiques géographiques locales sur la syndémie.
-Des mesures adaptées selon les pays
-
-Le champ de la recherche syndémique gagnerait à étudier davantage de sous-populations de HSH dans des contextes géographiques plus divers et locaux tout en incorporant d'autres méthodes telles que l'analyse en réseau ou l'épidémiologie spatiale.
-En outre, davantage de données qualitatives et mixtes aideraient à faire avancer la compréhension de l'impact de la syndémie sur le vécu des personnes.
-Les outcomes devraient moins se focaliser sur la santé sexuelle et explorer d'autres impacts de la syndémie sur la santé des individus.
-Enfin, il est urgent de définir plus précisément les contours des conditions qui constituent réellement une syndémie et la meilleure manière de les mesurer en prenant en compte les difficultés de transposer certaines mesures dans des contextes socio-culturels différents.
+Though we took a critic stance on the current literature, we still consider syndemic to be an useful framework to study the global health of marginalized populations and the current research still offered valuable insights on the health of MSM.
+It is up to scholars in the field to continue to push research forward in order to improve the health of marginalized populations worldwide.

### 2021-11-04 _bookdown_files/06-conclusion.Rmd
Minor correction

@@
 
-Though we took a critic stance on the current literature, we still consider syndemic to be an useful framework to study the global health of marginalized populations and the current research still offered valuable insights on the health of MSM.
+Though we took a critical stance on the current literature, we still consider syndemic to be an useful framework to study the global health of marginalized populations and the current research still offered valuable insights on the health of MSM.
 It is up to scholars in the field to continue to push research forward in order to improve the health of marginalized populations worldwide.

### 2021-11-04 _bookdown_files/02-introduction.Rmd
Introduction

---
bibliography: references.bib
---

# Introduction

## Background

Men who have sex with men (MSM) represent a vulnerable population disproportionately affected by numerous health conditions. First, they represent 70% of new HIV diagnoses @centerfordiseasecontrolandprevention2020 in the United States of America and more than half of new HIV diagnoses in European Union/European Economic area @europeancentrefordiseasepreventionandcontrol2019. They are also more prone to contract other sexually transmitted diseases and *Nesseria Gonorrhea* strains from MSM exhibit higher antimicrobial resistance @centersfordiseasecontrolandprevention2019. Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their straight counterpart @Medley2016. Moreover, those adverse and oftentimes preventable health outcomes are enmeshed with structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020]

For more than twenty years, syndemic theory have provided a framework to examine these interrelations between social conditions, mental health and physical health @singer2017. Described for the first time in 1996 by Merrill Singer @singer1996, a syndemic consists in two more interacting epidemics producing an excess burden in a population because of harmful social conditions @singer2003. To speak of a syndemic, three conditions must be met @mendenhall2020 :

1.  Two or more conditions cluster in a given population

2.  This clustering is due to an adverse social context such as poverty or stigmatization

3.  There is some form of biological, social and/or behavioral interaction between the conditions, significantly worsening the health of the affected population

Syndemic is thus an holistic framework, describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread @singer2017. As such its value for studying the health of marginalized population such as MSM is undeniable.

## Rationale

However, this theory is not without its flaws. A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenet @tsai2015. Indeed, this paper by Tsai and colleagues demonstrated that, although synergistic interaction between diseases lies in the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy. More recently, a scoping review published in 2020 confirmed this finding as most recently-published citations failed to describe the interactions between diseases needed to account for a true syndemic @Singer2020. Scholars in the field have been calling for a greater clarity in the use of the concept and urged for researchers to describe more precisely the interactions they observe between health conditions [@singer2021 ; @mendenhall2020].

However, to our knowledge none of the existing reviews or recommendations were focused on syndemic literature applied specifically on MSM. We thus sought to fill this gap by publishing the first scoping review dedicated to this important topic. Doing so, our goals were to map :

1.  the study design used ;

2.  the subpopulations of MSM studied ;

3.  the psychosocial conditions considered as forming a syndemic and how they were measured;

4.  the outcomes studied;

5.  the statistics used to evaluate the concept of interaction;

6.  the hypothesis for biological and sociobiological interactions proposed by the authors, when available;

7.  relevant frameworks that may compliment syndemic theory to better understand the health of MSM and

8.  the key findings of these studies

With these data, we wanted to better comprehend the state of the art in the current literature, identify knowledge gaps and suggest recommendations to guide future research in the field.

### 2021-11-04 _bookdown_files/04-results.Rmd
Bookdown rendering
Inclusion of PRISMA checklist

@@
 For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our sample.
-Detailed information about each of the papers included is presented in the supplementary material, part B ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).
+Detailed information about each of the papers included is presented in the supplementary material, part C ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).
 
@@
 
+```{r framework_data, include=FALSE}
+source("./scripts/create_framework_data.R", local = knitr::knit_global())
+
+```
+
 `r nrow(.framework)` studies used an additional framework alongside syndemic theory.

### 2021-11-04 Scripts/supplementary_tables/PRISMA-ScR.R

@@ -1,0 +1,15 @@
+library(readxl)
+source("./scripts/supplementary_tables/general.R")
+
+.PRISMA_Scr_Checklist <- read_excel("Files/PRISMA_Scr_Checklist.xlsx")
+.PRISMA_FT <- flextable(.PRISMA_Scr_Checklist, cwidth = c(2, 0.5, 4.5, 0.9)) %>%
+  border_inner(part="body", border = .borders) %>%
+  border_outer(part="body", border = .big.border) %>%
+  border_outer(part="header", border = .outer.border) %>%
+  bg(part="header", bg="#45ADA8") %>%
+  bold(part="header") %>%
+  color(part="header", color="white") 
+
+.PRISMA_ft <- set_caption(.CSA_ft, 
+                          "Preferred Reporting Items for Systematic reviews and Meta-Analyses extension for Scoping Reviews (PRISMA-ScR) Checklist",
+                       autonum = .supp_autonum)

### 2021-11-04 _bookdown_files/03-methodology.Rmd
Methodology

---
bibliography: references.bib
---

# Methodology

The complete protocol of this scoping review was already published elsewhere [Anonymous 2020].

Briefly, we applied the framework suggested by Arskey and O'Malley @arksey2005, with enhancements from Levac et al. @levac2010. We also took into account the recommendations formulated by Colqhoun et al. @colquhoun2014 and the updated guidance by Peters and colleagues @peters2020. We also followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses etension for Scoping Reviews (PRISMA-ScR) @Tricco2018. The completed checklist can be found in \@ref(tab:PRISMA-ScR) of the supplementary materials.

Screening and data charting was completed using DistillerSR (Evidence Partners, Ottawa, Canada). Scripts, statistics, charts, tables and the present paper was generated using R @rcoreteam2020, RStudio @rstudioteam2020 and appropriate packages. To ensure the complete transparency and reproducibility of this article, our data manager uploaded every data used to generate this article on Open Science Framework (DOI : [masked for the anonymity of the review])

Our main research question, *"What is known about Syndemic Theory applied to MSM"* was subdivided into three sub-questions :

1.  *"How are studies concerning Syndemic Theory applied to MSM conducted ?"*;
2.  *"How is the concept of interaction explored in syndemic research applied to MSM ?"* and
3.  *"What were the key findings of these studies ?"*.

To answer those questions, we conducted a systematic search strategy in the following databases : Medline, PsycInfo, Scopus, Cochrane Central Register of Controlled Trials and ProQuest Sociological Abstracts using complex search equations to include every synonym for "men who have sex with men". The complete search strategy for every database can be found in the Supplementary Material of our protocol. No date limit was applied given the relative novelty of the syndemic literature. A first search using this strategy was conducted the 11th of June 2020 and was subsequently updated on the 09th of February 2021 and finally on the 09th of November 2021.

Search results were downloaded into .RIS files and imported into DistillerSR. After duplicate removal, we screened the title and abstracts for eligibility, using forms generated with DistillerSR by the authors. Articles that met the inclusion criteria or for which eligibility was unclear passed through a second wave in which the full texts were assessed for eligibility. As per protocol, 10% of the titles and abstracts were screened by two reviewers. A Kappa inter-rater reliability score was computed using DistillerSR and was equal to 0.86. As it exceeded our cutoff of 0.8, the rest of the screening process was conducted by the main investigator only. Research were included if they met the following criteria :

-   MSM were either the only population studied in the paper or, if studied alongside other populations, such as transgender women, disaggregated data must have been available for MSM

-   Syndemic framework was the main focus of the study

-   Studies were cohort, case-control, cross-sectional, controlled trials, mixed studies, qualitative studies, systematic reviews or meta-analyses. We excluded letters, commentaries, conference abstracts, editorials or narrative reviews

-   Language was English

-   The article was published in a peer-reviewed journal

After inclusion of relevant studies, we hand-searched the reference lists to manually add pertinent studies. The same selection process was then applied and these papers are marked as "Additional records identified through other sources" in the study selection flow diagram.

Data charting was also performed using forms generated in DistillerSR by the authors. The complete list of all variables for which data were sought can be found in our protocol. Furthermore, the README file of our *Data* subdirectory contains an exhaustive definition of every variable included. Two departures were made from our initial protocol :

1.  We included a variable to chart any additional framework the authors might have used

2.  We included variables to chart data for systematic reviews and meta-analyses. These two kind of studies were omitted from our initial protocol as we were not aware of the existence of systematic reviews on syndemic theory applied to MSM by the time we published the protocol. The variables included were general characteristics (authors, year, location, design, total sample size), purpose of the review, number of studies included, hypothesis for biological or bio-social interaction, key findings and additional framework.

Data was then collated, summarised and reported using R, RStudio and relevant packages. Charts were generated to better visualize year of publication, location, population and syndemic conditions studied. Tables were generated to summarise the main variables of every article as well as the measurement methods of the most studied syndemic conditions. These tables can be found respectively in part B and C of the supplementary materials of this paper. Unfortunately, due do time constraints, we did not create any evidence map. However, we generated a SQL database alongside our data. This database contains every study included and provide scholars in the field the opportunity to search relevant studies using complex queries (e.g. to find every study using the CESD to measure depression on Black MSM between 2014 and 2021).

### 2021-11-04 _bookdown_files/06-conclusion.Rmd
Methodology

@@
 Moreover, we conducted a fully transparent and reproducible review.
-Other researchers may freely reuse our data and scripts to conduct their own work.
-To this end, we created a SQL database from our data.
-Other researchers may thus perform complex queries on our database of included studies to quickly identify studies relevant for their work (e.g.
-every study using the CESD to measure depression on Black MSM between 2014 and 2019).
+Other researchers may freely reuse our data and scripts to conduct their own work or use our database to identify papers pertinent for their research projects.
 

### 2021-11-04 Scripts/supplementary_tables/PRISMA-ScR.R
Cross-reference issue fixed

@@ -2,7 +2,7 @@ library(readxl)
 source("./scripts/supplementary_tables/general.R")
 
 .PRISMA_Scr_Checklist <- read_excel("Files/PRISMA_Scr_Checklist.xlsx")
-.PRISMA_FT <- flextable(.PRISMA_Scr_Checklist, cwidth = c(2, 0.5, 4.5, 0.9)) %>%
+.PRISMA_ft <- flextable(.PRISMA_Scr_Checklist, cwidth = c(2, 0.5, 4.5, 0.9)) %>%
   border_inner(part="body", border = .borders) %>%
   border_outer(part="body", border = .big.border) %>%
   border_outer(part="header", border = .outer.border) %>%
@@ -10,6 +10,6 @@ source("./scripts/supplementary_tables/general.R")
   bold(part="header") %>%
   color(part="header", color="white") 
 
-.PRISMA_ft <- set_caption(.CSA_ft, 
+.PRISMA_ft <- set_caption(.PRISMA_ft, 
                           "Preferred Reporting Items for Systematic reviews and Meta-Analyses extension for Scoping Reviews (PRISMA-ScR) Checklist",
                        autonum = .supp_autonum)

### 2022-01-13 _bookdown_files/01-abstract.Rmd
Complete draft

---
bibliography: ./_bookdown_files/references.bib
---

# Abstract

### 2022-01-13 _bookdown_files/02-introduction.Rmd
Complete draft

@@
 ---
-bibliography: references.bib
+bibliography: ./_bookdown_files/references.bib
 ---
@@
 Men who have sex with men (MSM) represent a vulnerable population disproportionately affected by numerous health conditions.
-First, they represent 70% of new HIV diagnoses @centerfordiseasecontrolandprevention2020 in the United States of America and more than half of new HIV diagnoses in European Union/European Economic area @europeancentrefordiseasepreventionandcontrol2019.
+They represent 70% of new HIV diagnoses @centerfordiseasecontrolandprevention2020 in the United States of America and more than half of new HIV diagnoses in European Union/European Economic area @europeancentrefordiseasepreventionandcontrol2019.
 They are also more prone to contract other sexually transmitted diseases and *Nesseria Gonorrhea* strains from MSM exhibit higher antimicrobial resistance @centersfordiseasecontrolandprevention2019.
-Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their straight counterpart @Medley2016.
-Moreover, those adverse and oftentimes preventable health outcomes are enmeshed with structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020]
+Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their heterosexual counterparts @Medley2016.
+Moreover, those adverse health outcomes are enmeshed within structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020]
 
-For more than twenty years, syndemic theory have provided a framework to examine these interrelations between social conditions, mental health and physical health @singer2017.
+For more than 20 years, syndemic theory have provided a framework to examine the interrelations between social conditions, mental health and physical health @singer2017.
 Described for the first time in 1996 by Merrill Singer @singer1996, a syndemic consists in two more interacting epidemics producing an excess burden in a population because of harmful social conditions @singer2003.
@@
 Syndemic is thus an holistic framework, describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread @singer2017.
-As such its value for studying the health of marginalized population such as MSM is undeniable.
+As such its value for studying the health of marginalized populations such as MSM is undeniable.
 
@@
 A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenet @tsai2015.
-Indeed, this paper by Tsai and colleagues demonstrated that, although synergistic interaction between diseases lies in the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy.
+Indeed, this paper demonstrated that, although synergistic interaction between diseases lies in the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy.
 More recently, a scoping review published in 2020 confirmed this finding as most recently-published citations failed to describe the interactions between diseases needed to account for a true syndemic @Singer2020.
-Scholars in the field have been calling for a greater clarity in the use of the concept and urged for researchers to describe more precisely the interactions they observe between health conditions [@singer2021 ; @mendenhall2020].
+Scholars in the field have been calling for greater clarity in the use of the concept and urged researchers to describe more precisely the interactions they observe between health conditions [@singer2021 ; @mendenhall2020].
 
-However, to our knowledge none of the existing reviews or recommendations were focused on syndemic literature applied specifically on MSM.
-We thus sought to fill this gap by publishing the first scoping review dedicated to this important topic.
-Doing so, our goals were to map :
+However, to our knowledge none of the existing reviews or recommendations have focused on syndemic literature applied specifically on MSM.
+We thus sought to fill this gap by conducting a scoping review with the objective to map the following :
 

### 2022-01-13 _bookdown_files/03-methodology.Rmd
Complete draft

@@
 
-The complete protocol of this scoping review was already published elsewhere [Anonymous 2020].
+The complete protocol of this scoping review was published in 2020 [Anonymous 2020].
 
-Briefly, we applied the framework suggested by Arskey and O'Malley @arksey2005, with enhancements from Levac et al.
+We applied the framework suggested by Arskey and O'Malley @arksey2005, with enhancements from Levac et al.
 @levac2010.
@@
 @colquhoun2014 and the updated guidance by Peters and colleagues @peters2020.
-We also followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses etension for Scoping Reviews (PRISMA-ScR) @Tricco2018.
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses extension for Scoping Reviews (PRISMA-ScR) @Tricco2018.
 The completed checklist can be found in \@ref(tab:PRISMA-ScR) of the supplementary materials.
@@
 
-Our main research question, *"What is known about Syndemic Theory applied to MSM"* was subdivided into three sub-questions :
+Our main research question : *"What is known about Syndemic Theory applied to MSM"* was subdivided into three sub-questions :
 
@@
 No date limit was applied given the relative novelty of the syndemic literature.
-A first search using this strategy was conducted the 11th of June 2020 and was subsequently updated on the 09th of February 2021 and finally on the 09th of November 2021.
+A first search using this strategy was conducted the 11th of June 2020 and was subsequently updated on the 9th of February 2021 and finally on the 11th of November 2021.
 
@@
 After duplicate removal, we screened the title and abstracts for eligibility, using forms generated with DistillerSR by the authors.
-Articles that met the inclusion criteria or for which eligibility was unclear passed through a second wave in which the full texts were assessed for eligibility.
-As per protocol, 10% of the titles and abstracts were screened by two reviewers.
+Articles that met the inclusion criteria or for which eligibility was unclear underwent a second screening in which the full texts were assessed for eligibility.
+As per the protocol, 10% of the titles and abstracts were screened by two reviewers.
 A Kappa inter-rater reliability score was computed using DistillerSR and was equal to 0.86.
 As it exceeded our cutoff of 0.8, the rest of the screening process was conducted by the main investigator only.
-Research were included if they met the following criteria :
+Articles were included if they met the following criteria :
 
--   MSM were either the only population studied in the paper or, if studied alongside other populations, such as transgender women, disaggregated data must have been available for MSM
+-   MSM was either the only population studied in the paper or, if studied alongside other populations, such as transgender women, disaggregated data must have been available for MSM
 
@@
 Data charting was also performed using forms generated in DistillerSR by the authors.
-The complete list of all variables for which data were sought can be found in our protocol.
+The complete list of all variables for which data were sought can be found in our protocol [Anonymous 2020].
 Furthermore, the README file of our *Data* subdirectory contains an exhaustive definition of every variable included.
@@
 However, we generated a SQL database alongside our data.
-This database contains every study included and provide scholars in the field the opportunity to search relevant studies using complex queries (e.g.
-to find every study using the CESD to measure depression on Black MSM between 2014 and 2021).
+This database contains every study included and provide scholars in the field the opportunity to search relevant studies using complex queries.

### 2022-01-13 _bookdown_files/04-results.Rmd
Complete draft

@@
 
-The electronic search identified 769 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
-After removing duplicates, 277 records were screened for inclusion.
+The electronic search identified 840 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
+After removing duplicates, 305 records were screened for inclusion.
 
-After screening the title and abstract, 109 records were excluded.
-The two main reasons for exclusion at this stage were that MSM was not the main study population (n=46) and that syndemic was not the main focus of the paper (n=34).
-29 studies were excluded because the type of publication did not meet our inclusion criteria.
+After screening the title and abstract, 124 records were excluded.
+The two main reasons for exclusion at this stage were that MSM was not the main study population (n=49) and that syndemic was not the main focus of the paper (n=37).
+38 studies were excluded because the type of publication did not meet our inclusion criteria.
 
-The full texts of the 168 remaining references were obtained and read; 59 were excluded after this phase.
+The full texts of the 181 remaining references were obtained and read; 66 were excluded after this phase.
 During the previous step, we had decided to tentatively include papers in which the sample was not entirely comprised of MSM.
-After reviewing the full paper, we decided to exclude studies if the MSM data was aggregated with data from another population (n=9), most commonly transgender women.
+After reviewing the full paper, we decided to exclude studies if the MSM data was aggregated with data from another population (n=11), most commonly transgender women.
 The rationale for this decision was to keep the focus clearly on MSM.
@@
 The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`).
-South America (N = `r .South_America_studies`) and Africa (N = `r .Africa_studies`)were the least represented continents.
+South America (N = `r .South_America_studies`) and Africa (N = `r .Africa_studies`) were the least represented continents.
 
@@
 In terms of analysis method, the most common was thematic (content) analysis (N= `r sum(!is.na(summary_qualitative$thematic_content)) + sum(!is.na(summary_qualitative$thematic))`).
-The rest of the studies consisted in framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and constant comparative analysis (N = `r sum(!is.na(summary_qualitative$comparative))`).
+The rest of the studies consisted of framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and constant comparative analysis (N = `r sum(!is.na(summary_qualitative$comparative))`).
 
-We only identified 2 papers employing mixed methods design [@buttram2015; @Halkitis2012]; Buttram et al.
+We identified 2 papers employing mixed methods design [@buttram2015; @Halkitis2012]; Buttram et al.
 used a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part while Halkitis et al used a cross-sectional quantitative survey and in-depth discovery interviews.
 
-The first systematic reviews and meta-analyses were published, in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])`, while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.
+The first systematic reviews and meta-analyses were published in `r min(year_design$year[year_design$design == "Systematic reviews, meta-analyses"])`, while the first interventional studies were published in `r min(year_design$year[year_design$design == "Interventional"])`.
 
@@
 
-Finally, the least represented subpopulation of MSM in this review are MSMW (N = `r sum(population$sex_behav == "MSMW")`), MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
+Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
 Strikingly, transgender MSM, in addition to being the focus of only one study [@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.
@@
 
-We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "CSA"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
+We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "PTSD"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
 
@@
 However, nearly half of these pairs of conditions (N = `r nrow(.edges_1)`) appear in only one research paper.
-On the other hand , the most studied pairs of syndemic conditions were depression and IPV (N = `r edges$weight[edges$from == 1 & edges$to == 4]`), depression and substance use (N = (N = `r edges$weight[edges$from == 1 & edges$to == 2]`), depression and CSA (N = `r edges$weight[edges$from == 1 & edges$to == 10]`), depression and polysubstance use (N = `r edges$weight[edges$from == 1 & edges$to == 11]`) and IPV and CSA (N = `r edges$weight[edges$from == 4 & edges$to == 10]`).
-
-In order to obtain a deeper understanding of the relation between the syndemic conditions, we also computed centrality indices for this network, namely degree centrality, the sum of weight in the network, closeness centrality, the inverse of the total length of the paths from a node to all other nodes, and betweenness, the number of shortest path passing through a node[@opsahl2010].\
-Because the weight of the nodes in this network corresponds to the number of studies in which the syndemic conditions appear, degree centrality of each node is nearly perfectly correlated to the number of studies in which the syndemic condition was studied (`r paste0("r(", .cor_degree$parameter,")", " = ", round(.cor_degree$estimate, digits = 2), ", ", pvalue(.cor_degree$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE))`).\
-Closeness centrality and betweenness centrality are also strongly correlated to the number of studies `r paste0("(r(", .cor_closeness$parameter,")", " = ", round(.cor_closeness$estimate, digits = 2), ", ", pvalue(.cor_closeness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " and r(", .cor_betweenness$parameter,")", " = ", round(.cor_betweenness$estimate, digits = 2), ", ", pvalue(.cor_betweenness$p.value, accuracy = 0.01, decimal.mark = ".", add_p = TRUE), " respectively)")`.
-Interestingly, the betweenness centrality of unstable housing is notably high given the low number of studies focusing on this syndemic condition (N = `r nodes$studies[nodes$label == "unstable_housing"]`).
-Betweenness centrality can be seen as the extent of brokerage a node can exert on a network [@zweig2016].
-Moreover in \@ref(fig:SyndemicNetwork) we see that the three structural syndemic conditions "unstable housing", "incarceration" and "poverty" are grouped together, indicating that they are frequently studied together.
-In other words, in syndemic literature, unstable housing seems to act as a bridge between the two aforementioned structural syndemic conditions and the rest of the syndemic conditions.
-Indeed, unstable housing has been studied alongside `r nrow(.edges_UH)` other syndemic conditions : depression, substance use, IPV, binge drinking, sexual compulsivity, IDU, CSA, polysubstance use, incarceration, poverty, unemployment, discrimination, poor healthcare access, alcohol use and violence.
+On the other hand , the most studied pairs of syndemic conditions were depression and IPV (N = `r edges$weight[edges$from == 1 & edges$to == 4]`), depression and substance use (N = (N = `r edges$weight[edges$from == 1 & edges$to == 2]`), depression and CSA (N = `r edges$weight[edges$from == 1 & edges$to == 10]`), IPV and CSA (N = `r edges$weight[edges$from == 4 & edges$to == 10]`) and depression and polysubstance use (N = `r edges$weight[edges$from == 1 & edges$to == 11]`).
 
@@
 Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies.
-For the sake of brevity, we will not provide a detailed description of the measurement method of the syndemic conditions studied in fewer than 10% of our sample.
-Detailed information about each of the papers included is presented in the supplementary material, part C ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).
+For the sake of brevity, we will only provide a detailed description of the measurement method for the 5 most studied syndemic conditions.
+Detailed information on the syndemic conditions most impacted by methodology heterogeneity is presented in the supplementary material, part C ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).
 
-For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria were used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.\
-66 studies used scales while 10 studies used criteria to assess the presence of depression or depressive symptoms among the participants.
-The most frequently used scales were the full Center for Epidemiologic Studies-Depression scale [CESD] (N = 24) and the 10-items version of this scale [CESD-10] (N=10), the 9-items version of the Patient Health Questionnaire [PHQ-9] (N=8) and the Beck Depression Inventory [BDI-II] (N = 5).\
+For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria were used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.
+70 studies used scales while 10 studies used criteria to assess the presence of depression or depressive symptoms among the participants.
+The most frequently used scales were the full Center for Epidemiologic Studies-Depression scale [CESD] (N = 26) and the 10-items version of this scale [CESD-10] (N=11), the 9-items version of the Patient Health Questionnaire [PHQ-9] (N=9) and the Beck Depression Inventory [BDI-II] (N = 5).\
 Cutoff for these scales varied the most for the CESD (range : 16 to 27) and the PHQ-9 (range : 5 to 15).\
 When a scale was not used, the most frequent criteria to assess the presence of depression was the participant being on medication for depression in the past 12 months (N = 4).
-
-For IPV, 5 types of intimate partner violence were identified : physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), gay-related violence (e.g.
-threats to reveal the partner's sexual orientation ; N = `r .IPV_prevalence$sum[["gay-related IPV"]]`) and HIV-related violence (e.g.
-threats to disclose the partner's serologic status ; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`).
-Reference periods varied from past month to lifetime.\
-Furthermore, 7 studies used a scale to assess the presence of IPV : the HITS scale (N = 3) the Revised Conflict Tactics Scale [CTS2] (N= 3) and a scale developed by the authors of the study, assessing physical and psychological violence[@Yu2013].
 
@@
 GHB/GBL, benzodiazepines without prescriptions ; (N = `r .substances_prev$sum[["depressants"]]`), opioids (i.e.
-opioids misuse and ecstasy ; N = `r .substances_prev$sum[["opioids"]]`), marijuana (N = `r .substances_prev$sum[["marijuana"]]`), ecstasy /MDMA (N = `r .substances_prev$sum[["ecstasy"]]`), hallucinogens (i.e.
+opioids misuse and heroin ; N = `r .substances_prev$sum[["opioids"]]`), marijuana (N = `r .substances_prev$sum[["marijuana"]]`), ecstasy /MDMA (N = `r .substances_prev$sum[["ecstasy"]]`), hallucinogens (i.e.
 ketamine, psilocybine, phencyclidine ; N = `r .substances_prev$sum[["hallucinogens"]]`), inhalants (nitrous oxyde, Popper ; N = `r .substances_prev$sum[["inhalants"]]`) and new psychoactive substances (i.e.
@@
 Reference period ranged from the past month to over the lifetime.
+
+For IPV, 5 types of intimate partner violence were identified : physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), gay-related violence (e.g.
+threats to reveal the partner's sexual orientation ; N = `r .IPV_prevalence$sum[["gay-related IPV"]]`) and HIV-related violence (e.g.
+threats to disclose the partner's serologic status ; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`).
+Reference periods varied from past month to lifetime.
 
@@
 
-For polysubstance use, 17 studies considered that there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
-Furthermore, 4 studies excluded marijuana from the class of substances screened and 1 study excluded stimulants, because stimulants were already screened in another syndemic condition.
-
-For binge drinking, we identified `r length(unique(.binge_measurement$binge_episodes))` different thresholds for binge drinking, differing on the number and frequency of binge drinking episodes.
-The threshold ranged from one episode in the past 12 months to more than one episode per week, every week in the past 12 months.
-
-Measurement of sexual compulsivity was relatively standardized, compared to the rest of the syndemic conditions.
-Nearly every study used the Kalichman's Sexual Compulsivity Scale, with cutoff ranging from 20 to 26, except for two studies using the Compulsive Sexual Behavior Inventory[@Herrick2013; @Dyer2012] and one study using a scale devised by the authors @Wang2017.
-
-For AUD, we identified 4 different definitions.
-`r sum(str_count(measurement$AUD_scale, pattern = "AUDIT-10"), na.rm = T)` studies used the full Alcohol Use Disorder Identification Test (AUDIT-10), `r sum(str_count(measurement$AUD_scale, pattern = "AUDIT-C"), na.rm = T)` studies used the 3-items version of this screening test (AUDIT-C), `r sum(str_count(measurement$AUD_scale, pattern = "CAGE"), na.rm = T)` studies used the CAGE questionnaire and one study used clinical diagnosis based on the DSM-IV criteria.
-
-Regarding suicide, `r sum(is.na(measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered only suicidal thoughts, `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & grepl(pattern = "suicidal_thoughts", measurement$suicidal_thoughts))` studies considered both suicidal thoughts and suicide attempts and `r sum(grepl(pattern = "suicide_attempts", measurement$suicide_attempts) & is.na(measurement$suicidal_thoughts))` studies considered only suicide attempts.
-Furthermore, one study used the Positive and Negative Suicide Ideation scale (PANSI) and one study used the Suicide Behaviors Questionnaire-Revised (SBQ-R).
-
-A number of behaviors have been used to define sexual risk behaviors as a syndemic condition.
-The most widely used of these criteria is condomless anal sex (N = `r sum(!is.na(measurement$CAS))`), followed by the number of partners (N = `r sum(!is.na(measurement$number_partners))`).
-The condomless anal sex criteria has been refined in three studies, two of them taking into account the type of partner (regular versus casual) and one, the serologic status of both partners.\
-Other criteria such as condomless oral sex, condomless vaginal sex, STI diagnosis, engagement in sex work and sexual intercourse with an HIV positive partner have been used.
-Finally, one study used the Kalichman's Sexual Sensation Seeking Scale to assess the propensity of participants to engage in novel or risky sexual stimulation.
-
-For violence `r .violence_prevalence$sum[["sexual"]]` studies looked at sexual violence, `r .violence_prevalence$sum[["physical"]]`, at physical violence and `r .violence_prevalence$sum[["psychological"]]` at psychological violence.
-One Indian study also took into account sexual and physical harassment by the police.
-
-Several types of anxiety disorder were studied : generalized anxiety disorder (N = `r sum(!is.na(measurement$"generalized anxiety disorder"))`), social phobia (N = `r sum(!is.na(measurement$"social phobia"))`) and panic disorder (N = `r sum(!is.na(measurement$"panic disorder"))`).
-The type of anxiety disorder screened was not specified in `r sum(!is.na(measurement$"not specified"))` studies.\
-`r length(unique(.anxiety_measurement$criteria))` different criteria were used to assess the presence of an anxiety disorder among the `r nodes$studies[nodes$label == "anxiety"]` studies considering anxiety as a syndemic condition.
-The most frequent criteria was a score equal or greater than 10 on the 7-items version of the Generalized Anxiety Disorder screening test (GAD-7 ; N = `r sum(!is.na(measurement$"GAD-7"))`).
-
-SUD was screened through a clinical diagnosis based on the DSM-IV, mention of substance abuse in the electronic medical record or the participant thinking he should reduce his substance use.
-Several screening test were also used : the Drug Use Disorder Identification Test (DUDIT), the Texas Christian University Drug Screen (TCUDS), the Mini International Neuropsychiatric Interview (MINI) and the 10-items Drug Abuse Screening Test (DAST-10).
-
-Outside of binge drinking and alcohol use disorder, which represents two distinct syndemic conditions, we aggregated three aspects of alcohol use studied in syndemic literature to form a generic "alcohol use" syndemic condition : alcohol consumption, alcohol use until intoxication and early alcohol use.
-
-Finally, for discrimination, there were as many criteria as there were research papers studying this condition.
-Most of the studies only considered discrimination based on sexual orientation, except for two studies examining racial discrimination, one study examining HIV-based discrimination and one study which did not distinguish between discrimination based on sexuality, race/ethnicity or any other factor.
+For polysubstance use, 18 studies considered that there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
+Furthermore, 6 studies excluded marijuana from the class of substances screened and 2 study excluded stimulants, because stimulants were already screened in another syndemic condition.
 
@@
 
-Every other outcome was only studied once : HIV screening[@Chandler2019b], physical activity[@Zhang2019], hypothalamic-pituitary-adrenal (HPA) axis dysregulation[@carrico2018], sexual violence[@semple2017], glycemic control[@Byg2016], engagement in HIV care[@Biello2016], engagement in chemsex[@friedman2014], having sexual intercourse with both men and women[@eaton2013] , help-seeking behaviors[@achterbergh2021] and substance use[@turpin2020].
+Every other outcome was only studied once : HIV screening [@Chandler2019b], physical activity [@Zhang2019], hypothalamic-pituitary-adrenal (HPA) axis dysregulation [@carrico2018], sexual violence [@semple2017], glycemic control [@Byg2016], engagement in HIV care [@Biello2016], engagement in chemsex [@friedman2014], having sexual intercourse with both men and women [@eaton2013] , help-seeking behaviors [@achterbergh2021], substance use [@turpin2020], HIV transmission [@satyanarayana2021] and elevation in rectal cytokines/chemokines [@tapia2021].
 
@@
 
-When HIV was used as an outcome, it was self-reported in nearly half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`.
+When HIV was used as an outcome, it was self-reported in more than half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`.
 
@@
 aimed to identify a set of resilience resources among MSM burdened with minority stress and psychosocial condition in order to improve HIV prevention [@woodward2017].
-They included `r summary_reviews$studies_included[summary_reviews$authors== "Woodward et al."]` in their reviews and identified 31 resilience resources, with social support and incomes as the two most frequently cited.
+They included `r summary_reviews$studies_included[summary_reviews$authors== "Woodward et al."]` studies in their reviews and identified 31 resilience resources, with social support and financial incomes as the two most frequently cited.
 Of note, most of these resources were associated with a lower HIV risk.
@@
 They found that religion and spirituality had mixed effect on syndemic conditions but could be more beneficial for MSM of color than for white MSM.
-Of note, they only included `r summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."]` studies as these two factors were very sparse in syndemic literature.
+Of note, the review was relatively small (including `r summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."]` studies) as these two factors are very sparse in syndemic literature.
 
@@
 `r nrow(.framework)` studies used an additional framework alongside syndemic theory.
-The most widely used was resilience theory (N = 10), followed by minority stress model (N = 5), intersectionality (N=2), social-cognitive theory (N=2) and salutogenesis (N=1).
+The most widely used was resilience theory (N = 10), followed by minority stress model (N = 5), intersectionality (N=2), social-cognitive theory (N=2), salutogenesis (N=1) and ecological framework (N=1).
 
@@
 
-It should be stated that, when we speak of interaction between syndemic conditions we don't necessarily mean "synergy", though synergy is indeed one of the interaction we consider.
+It should be stated that, when we speak of interaction between syndemic conditions we don't necessarily mean "synergy", though synergy is indeed one of the interactions we consider.
 Drawing from the works of authors such as Tsai and Chakrapani, we consider three types of interaction : synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics [@Tsai2018a; @Chakrapani2019].
@@
 
-Our review revealed a high degree of variability in the statistic analyses.
+Our review revealed a high degree of variability in the statistical analyses.
 The most frequently used statistical method was to conduct regression analysis using a summation score of the syndemic conditions (N = `r sum(!is.na(summary_quantitative$score))`).
@@
 
-Finally, other statistic analysis used to assess interaction were observed/expected ratio (N = `r sum(!is.na(summary_quantitative$O_E))`), cluster analysis (N = `r sum(!is.na(summary_quantitative$cluster))`) and point-biserial correlation matrix (N= `r sum(!is.na(summary_quantitative$biserial))`).
+Finally, other statistic analysis used to assess interaction were observed/expected ratio (N = `r sum(!is.na(summary_quantitative$O_E))`), cluster analysis (N = `r sum(!is.na(summary_quantitative$cluster))`), point-biserial correlation matrix (N= `r sum(!is.na(summary_quantitative$biserial))`) and synergy factor analysis (N=1).
 
@@
 
-In our sample of quantitative studies, we found only one study offering a mechanism of biological interaction @carrico2018 and one study offering a mechanism of bio-social interaction [@Klein2011].
+In our sample of quantitative studies, we found only one study offering a mechanism of biological interaction @carrico2018 and two studies offering a mechanism of bio-social interaction [@Klein2011; @tapia2021].
 
 Carrico et al.
-showed that the combined effects of HIV infection and methamphetamine use were detrimental for the functioning of the Hypothalamic-Pituitary-Adrenal axis which is thought to play an important part in the reinforcing effect of stimulants.
+showed that the combined effects of HIV infection and methamphetamine use were detrimental for the functioning of the Hypothalamic-Pituitary-Adrenal axis which is thought to play an important role in the reinforcing effect of stimulants.
 
-Klein proposed that attitudes towards condom was one of the key factor contributing to condomless sex and, subsequently, HIV infection.
+Klein proposed that attitudes toward condom use was one of the key factors contributing to condomless sex and, subsequently, HIV infection.
 In their study, attitudes toward condoms was predicted by low self-esteem, as condom use represents a self-protecting mechanism, as well as by sexual preferences, substance use, race and education.
 Furthermore, childhood emotional neglect had a negative influence on self esteem thus indirectly contributing to sexual risk taking.
+
+Finally, Tapia et al.
+demonstrated that a higher number of syndemic conditions was associated with elevation in rectal cytokines/chemokines relevant to HIV/STI transmission.
+This finding presents a pathway through which depression, alcohol use disorder, substance use and PTSD may increase the biological susceptibility to HIV/STI.
+Unfortunately, using solely a summation score to conduct regression analysis, no synergy between the conditions was evaluated.
 
@@
 showed that economic dependency and fear of violence may maintain YBMSM in dysfunctional relationships plagued by IPV and substance abuse which increase their odds of incarceration and HIV infection [@Maiorana].
-Furthermore, methamphetamine is used as a coping strategy while simultaneously representing a potential factor in acquiring or transmitting HIV to others, notably during sex parties.\
+Furthermore, methamphetamine is used as a coping strategy while simultaneously representing a potential factor in acquiring or transmitting HIV to others, notably during sex parties.
+
 This finding of substance use as a coping mechanism was supported by the study by Pollard et al.
@@
 Chakrapani and colleagues found support for the three models of interacting epidemics (synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics) with the strongest support for the model of synergistically interacting epidemics [@Chakrapani2019].
-These findings were supported by other studies who found synergy when using significant product terms in the additive and/or multiplicative scales [@Chakrapani; @chandler2020; @Chandler2019; @tomori2018].
+These findings were supported by other studies who found synergy when using significant product terms in the additive and/or multiplicative scales [@Chakrapani; @chandler2020; @Chandler2019; @tomori2018; @chuang2021; @bulled2021].
 However, other studies found no synergy between the syndemic conditions using the same statistical approach [@Batchelder2019; @shuper2020; @Ferlatte2018a].
@@
 Furthermore, Dyer et al.
-found more STI in the Black MSM compared to the Black MSMW [@dyer2020] and Ferlatte found more syndemic conditions in the MSM compared to the MSM [@ferlatte2018], mainly driven by party drug use and treatment for depression or anxiety.
+found more STI in the Black MSM compared to the Black MSMW [@dyer2020] and Ferlatte found more syndemic conditions in the MSM compared to the MSMW [@ferlatte2018], mainly driven by party drug use and treatment for depression or anxiety.
 Finally, in a sample of Latino MSMW, having two syndemic conditions predicted receptive condomless anal sex and STI diagnosis but not insertive nor vaginal condomless sex [@Munoz-Laboy2018].
+
+In a longitudinal study [@Mustanski2017] Black MSM were found to have the highest HIV incidence while having a lower burden of syndemic condition than White MSM, raising the question of the need to focus on syndemic conditions specific to Black MSM.
+Interestingly, Bulled et al observed a synergy only for White MSM in their reanalysis of Stall's data [@bulled2021].
+The authors proposed that, for racial minority MSM, structural disadvantage limiting access to healthcare may be more important than substance use and violence.
 
@@
 Nonetheless, alcohol misuse was found to be associated with PrEP non-adherence [@shuper2020].
-
-In a longitudinal study [@Mustanski2017] Black MSM were found to have the highest HIV incidence while having a lower burden of syndemic condition than White MSM, raising the question of the need to focus on syndemic conditions specific to Black MSM.

### 2022-01-13 _bookdown_files/05-discussion.Rmd
Complete draft

@@
 
-What stands out the most when we consider syndemic literature applied to MSM is that it is both too homogeneous in some aspects while being not focused enough in other parts.
-As we will discuss in more depth below, the location, design, subpopulation and outcomes should be more diverse that it currently is.
-On the other hand, the syndemic conditions and ways of measurement should be more focused to improve the robustness and reproducibility of the findings.
-
-More concerning, maybe, is the fact that a substantial part of the literature doesn't provide empirical data to support one of the core tenets of syndemic theory - namely disease interaction- as was already pointed out in a previous review [@tsai2015].
+The objective of this scoping review was to map the current knowledge on syndemic research applied to MSM.
+To this end, we analysed 115 articles and found out that the literature was both too homogeneous in some aspects while being not focused enough in other parts.
+As we will discuss in more depth below, the location, design, subpopulation and outcomes lacked diversity.
+On the other hand, the syndemic conditions and ways of measurement were not focused enough to ensure the robustness and reproducibility of the findings.
+Furthermore a substantial part of the literature doesn't provide empirical data to support one of the core tenets of syndemic theory - namely disease interaction- as was already pointed out in a previous review [@tsai2015].
 
@@
 Three issues arise from this.
-First, under-representation of the Global South is inherently an issue as it precludes us to better understand the health of MSM living in these countries.
+First, under-representation of the Global South is inherently an issue as it prevents us from better understanding the health of MSM living in these countries.
 Furthermore, as aptly pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
@@
 
-The design of syndemic studies is another point suffering from a lack of diversity.
+The design of syndemic studies is another element suffering from a lack of diversity.
 The field is dominated by quantitative studies as qualitative papers represent only `r percent(.N_qual/nrow(overview_of_studies))` of our sample.
-Quantitative studies, on their part, employ a cross-sectional design in `r percent(.N_cross_sec/.N_QualQuant)` of the papers.
+Moreover `r percent(.N_cross_sec/nrow(summary_quantitative))` of the quantitative studies were cross-sectional.
 As vulnerability to syndemic conditions is suspected to arise from early adverse experience @stall2007 longitudinal studies running on a long period of time are probably needed to study syndemic production among MSM.
@@
 For example, the complex narratives surrounding drug use and its link to loneliness, marginalization, personal affirmation, resistance and lack of meaningful emotional connections @Pollard2018a would be hard to measure and model using quantitative data.
-As Alexander Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to over-simplification of diseases dynamics @Tsai2018a .
-As such, we concur that mixed method are direly needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
+As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to over-simplification of diseases dynamics @Tsai2018a .
+Mixed method are needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
 Unfortunately, our review only identified `r max(year_design$cumulative[year_design$design == "Mixed"])` studies employing such mixed methodology.
-Future research would gain to take advantage of qualitative data to support and deepen their quantitative findings.
+Future research would benefit from generating and analysing qualitative data to support and enrich their quantitative findings.
 
 Finally, we identified `r .N_int` interventional studies with mixed results.
-While co-targeting interconnected syndemic conditions is supported by a meta-analysis @Pantalone2020, a better understanding of how syndemic operate may be needed before offering efficient syndemic-based interventions.
+While co-targeting interconnected syndemic conditions is supported by a meta-analysis @Pantalone2020, a better understanding of how syndemics operate may be needed before we are able to offer efficient syndemic-based interventions.
 
@@
 
-Studying the health of MSM pose a challenge regarding the diversity of this population.
-While nearly half of the studies included in our sample studied a subpopulation of MSM, the number of MSM subpopulation is such that most MSM subpopulation remain undeserved.
+Studying the health of MSM poses a challenge regarding the diversity of this population.
+While nearly half of the studies included in our sample studied a subpopulation of MSM, the number of MSM subpopulation is such that most MSM subpopulation remains under-served.
 For example, Young Black MSM are specifically studied in `r .N_YBMSM` studies while representing 52% of the new HIV diagnosis among MSM aged 13-24 years in 2018 @centerfordiseasecontrolandprevention2020.
 
-This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic condition such as HIV infection is even more concerning when considering that dual-minority identity may expose to different stressors and outcomes.
-For example, some study found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to less syndemic conditions @Mustanski2017 .
+This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic condition such as HIV infection is even more concerning when considering that dual-minority identity may expose a person to different stressors and outcomes.
+For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to less syndemic conditions @Mustanski2017 .
 These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM @Quinn .
+Furthermore, the findings from Bulled and colleagues suggest that structural disadvantage may have more weight on the lives of Black MSM than individual factors such as substance use @bulled2021
 
-MSMW are another example of undeserved population with conflicting results.
-In a cross-sectional study using syndemic sum count, Latino MSMW with two or more syndemic conditions had a 7.09 Odds Ratio to engage in receptive condomless anal sex but no statistically significant difference were found for insertive condomless anal sex or condomless vaginal sex @Munoz-Laboy2018.
+MSMW are another example of an under-served population with conflicting results.
+In a cross-sectional study using syndemic sum count, Latino MSMW with two or more syndemic conditions had a 7.09 Odds Ratio to engage in receptive condomless anal sex but no statistically significant difference was found for insertive condomless anal sex or condomless vaginal sex @Munoz-Laboy2018.
 On the other hand, in another study the number of syndemic conditions was associated with HIV diagnosis for MSM but not for MSW or MSMW @Branstrom2018.
@@
 These conflicting findings may be partly due to the difficulty to define and operate bisexuality in research @swan2018, difference between age groups or differences in syndemic mechanism for MSMW compared to MSM.
-Outside the field of syndemic literature, studies suggest that bisexual men suffer from a similar or higher burden in mental health condition compared to gay men [@salway2019; @Chaudhry2019; @ross2018] and literature specific to bisexual men remains scarce.
-Syndemic theory should thus seek to study forward the specificity of this population.
-First, there's a need to better conceptualize and define bisexuality in the field - should we still use solely behavior-based definition (as in MSMW) or should we incorporate self-definition of one's sexual orientation ?
-Then, researchers should see to disaggregate data concerning MSMW/bisexual men from data concerning MSM/gay men whenever possible.
-Lastly, more research focused on MSMW/bisexual men is needed.
+Outside the field of syndemic literature, studies suggest that bisexual men suffer from a similar or higher burden of mental health condition compared to gay men [@salway2019; @Chaudhry2019; @ross2018] and literature specific to bisexual men remains scarce.
+In the future, syndemic theory should thus seek to study the specificity of this population.
+First, there's a need to better conceptualize and define bisexuality in the field - should we still use solely behavior-based definition (as in MSMW) or should we incorporate a self-definition of one's sexual orientation ?
+Then, researchers should aim to disaggregate data concerning MSMW/bisexual men from data concerning MSM/gay men whenever possible.
+Lastly, more research focusing on MSMW/bisexual men is needed.
 
 Finally transgender MSM were included in only one study of our sample.
-As stated in our result, this is concerning, especially when every other study exclude transgender men by design.
-As such, this population of MSM is the one we know the less about.
+As stated in our results, this is concerning, especially when every other study excludes transgender men by design.
+As such, this population of MSM is the one we know the least about.
 The study from Reisner and colleagues suggested that transgender MSM who had socially affirmed their gender were exposed to similar risk patterns as cisgender MSM @Reisner2016a.
-The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence @Testa2012, suicide attempts @Haas2014, chlamydial and gonoccocal infections @Pitasi2019 and HIV infection @Becasen2019.
-Researcher should therefore include transgender men in their studies and conduct research focused on transgender MSM.
-Indeed, syndemic theory represents a promising framework for transgender men as its premises of social adversities producing and concentrating diseases in a population allows to explore the health of transgender men without pathologizing them.
+The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence @Testa2012, suicide attempts @Haas2014, chlamydial and gonoccocal infections @Pitasi2019, intimate partner violence [@peitzmeier2020] and HIV infection @Becasen2019.
+Researchers should be encouraged to include transgender men in their studies and to conduct research focused on transgender MSM.
+Indeed, syndemic theory represents a promising framework for research on transgender men as its premises of social adversities producing and concentrating diseases in a population allows us to explore the health of transgender men without pathologizing them.
 
@@
 
-A clear lack of consensus exists in the choice of syndemic conditions and the way they should be measured.
-We identified `r nrow(nodes)` different conditions in our quantitative sample and `r nrow(nodes %>% filter(studies == 1))` of them were only studied once.
+There is a lack of consensus in the choice of syndemic conditions and the way they should be measured.
+We identified `r nrow(nodes)` different conditions in our quantitative sample, `r nrow(nodes %>% filter(studies == 1))` of them were only studied once.
 Some of these conditions are past event (e.g.
 history of trauma or childhood sexual abuse) while most were current conditions.
-Given the cross-sectional nature of `r percent(.N_cross_sec/nrow(summary_quantitative))` of the quantitative paper, we can't disentangle how past experiences may influence the emergence of a syndemic.
+Given the cross-sectional nature of `r percent(.N_cross_sec/nrow(summary_quantitative))` of the quantitative papers, we cannot disentangle how past experiences may influence the emergence of a syndemic.
 
 Furthermore, studies diverge on what represents a syndemic condition and what may lead to the emergence of a syndemic.
-For example, childhood sexual abuse is mostly seen as a syndemic condition per se but may very well be a risk factor to the emergence of a syndemic, as hypothesized by some authors @Herrick2013.
+For example, childhood sexual abuse is mostly seen as a syndemic condition per se but may very well be a risk factor to the emergence of a syndemic, as hypothesized by some authors [@Herrick2013; @leblanc2021].
 The same question may be asked for discrimination, trauma, impulsivity, bullying, poor social support, loneliness, childhood abuse, poor healthcare access, etc.
@@
 
-Furthermore, even when the same condition was studied in multiple papers, the differences in measurement methods impedes greatly the reproducibility of the results.
-For example, let us imagine a participant with a CESD score of 16, who uses marijuana on a regular basis and cocaine once in a while and who is victim of sexual intimate partner violence.
-This man would have been classified as depressed in `r percent(sum(.depression_measurement$depression_cutoff == 16 & .depression_measurement$depression_scale_criteria == "CESD")/sum(.depression_measurement$depression_scale_criteria == "CESD"))` of studies using the CESD, a polysubstance user in `r percent(sum(.polysubstance_measurement$polysubstance_number == "More than one category of substance use" & .polysubstance_measurement$polysubstance_marijuana == "Marijuana included")/nrow(.polysubstance_measurement))` of studies considering polysubstance use and as a victim of intimate partner violence in `r .IPV_prevalence$perc[["sexual IPV"]]` of studies taking IPV into account.
+Furthermore, even when the same condition was studied in multiple papers, the differences in measurement methods impedes the reproducibility of the results.
+For example, a participant with a CESD score of 16, who uses marijuana on a regular basis and cocaine once in a while and who is a victim of sexual intimate partner violence.
+This man would have been classified as depressed in `r percent(sum(.depression_measurement$depression_cutoff == 16 & .depression_measurement$depression_scale_criteria == "CESD", na.rm = T)/sum(.depression_measurement$depression_scale_criteria == "CESD"))` of studies using the CESD, a polysubstance user in `r percent(sum(.polysubstance_measurement$polysubstance_number == "More than one category of substance use" & .polysubstance_measurement$polysubstance_marijuana == "Marijuana included")/nrow(.polysubstance_measurement))` of studies considering polysubstance use and as a victim of intimate partner violence in `r .IPV_prevalence$perc[["sexual IPV"]]` of studies taking IPV into account.
 In other words, the same person could have been classified as having 0, 1, 2 or even 3 syndemic conditions, depending on the study.
@@
 
-It is beyond the scope of this paper to discuss in details which syndemic conditions should be retained for future research and how to best measure them, but without a greater homogeneity in the field, the confidence and reproducibility of the results will remain an issue.
+It is beyond the scope of this paper to discuss in detail which syndemic conditions should be retained for future research and how to best measure them, but without a greater homogeneity in the field, the confidence and reproducibility of the results will remain an issue.
 
@@
 
-This omnipresence of HIV in syndemic literature applied to MSM is doubly understandable.
+This omnipresence of HIV in syndemic literature applied to MSM is understandable.
 The first description of a syndemic, the SAVA syndemic, incorporated AIDS as part of a syndemic @singer1996.
@@
 
-Indeed, MSM are also disproportionately affected by suicide, anxiety, depression and substance use to name a few [@ross2018; @luo2017; @Medley2016].
-Moreover, with the advances in antiretroviral therapy and the subsequent decline in HIV-related mortality, gay men were more likely to die from suicide than from HIV in Canada in 2011 @hottes2015.
-Even if the estimates in this paper overestimated suicide's mortality among MSM, suicide would still be a leading cause of death in this population while being studied as an outcome in only `r sum(!is.na(.outcomes$outcome_suicide))` papers in our sample.
+Indeed, MSM are also disproportionately affected by, amongst others, suicide, anxiety, depression and substance use[@ross2018; @luo2017; @Medley2016].
+Moreover, with the advances in antiretroviral therapy and the subsequent decline in HIV-related mortality, a Canadian study showed that gay men were more likely to die from suicide than from HIV in 2011 @hottes2015.
+Even if the estimates Hottes' paper overestimated the mortality due to suicide among MSM, suicide would still be a leading cause of death in this population while being studied as an outcome in only `r sum(!is.na(.outcomes$outcome_suicide))` papers in our sample.
 
-Furthermore, when studying HIV as an outcome, we would argue that condomless anal sex should be replaced by better proxies.
+Furthermore, when studying HIV as an outcome, we would argue that using condomless anal sex as a proxy should be reviewed and better proxies sought.
 First, without refinement, this outcome fails to capture the changes in HIV prevention strategies such as PrEP or Treatment as Prevention (TasP).
 Only `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))` studies in our sample took PrEP use and an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.
-When the first paper on syndemic theory applied to MSM were published, engaging condomless anal sex would have led to a high risk of acquiring HIV.
-Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV @calabrese2017 and our methodologies should reflect this change.
-In addition, qualitative research gives insight in risk practices and offers a more nuanced view on this topic than a binary variable of consistent condom use for anal intercourses.
-One such paper published in 2017 showed that risk practice fell into different subjectivities such as active and consistent pursuit of condomless sex, lack of assertiveness to a partner's initiative of condomless anal sex and combination of episodic risk practices and reduction strategies @Adam2017.
+When the first paper on syndemic theory applied to MSM was published, engaging in condomless anal sex would have led to a high risk of acquiring HIV.
+Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV @calabrese2017 and our methodologies in syndemic research should reflect this evolution.
+In addition, qualitative research gives an insight into risk behaviors and offers a more nuanced view on this topic than a binary variable of consistent condom use for anal intercourse.
+One such paper published in 2017 showed that risk practices fell into different subjectivities such as active and consistent pursuit of condomless sex, lack of assertiveness to a partner's initiative of condomless anal sex and combination of episodic risk practices and reduction strategies @Adam2017.
 Besides, some studies showed that participants with a greater number of syndemic conditions would engage more frequently in condomless anal sex while not being more likely to test positive for HIV [@Mustanski2017; @Pitpitan2016].
-On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated to HIV self-report but not to condomless anal sex @chuang2018.
+On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated to self-reported HIV but not to condomless anal sex @chuang2018.
 Taken together, we thus postulate that condomless anal sex should at least be replaced by "condomless anal sex without consistent PrEP use or with a detectable viral load" when an investigator seek to use sexual risk behaviors as an outcome.
@@
 One of the tenets of syndemic theory is that there exists some form of biological, social and/or psychological interaction between the diseases @mendenhall2020.
-As others have already pointed before us, the extent to which syndemic literature had proved this core principle remains very limited @tsai2015.
+As others have already pointed out, the extent to which syndemic literature had proved this core principle remains very limited @tsai2015.
 Indeed, `r percent(.score_data/nrow(summary_quantitative))` of our quantitative sample of studies used solely a summation score of the syndemic conditions to conduct regression analysis.
@@
 Secondly, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting @Halkitis2013a.
-Put simply, using a summation score would imply that (1) every condition form a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having an history of childhood sexual abuse would contribute equally to a syndemic).
+Put simply, using a summation score would imply that (1) every condition forms a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having an history of childhood sexual abuse would contribute equally to a syndemic).
 The unidimensionality aspect of the construct has received some empirical support by Mustanski et al.
@@
 using respectively Structural Equation Modeling and Latent Class Analysis [@Mustanski2014; @Starks2014].
-However constraining factor loadings to be equal resulted in worse fit in both studies.
+On the contrary, Leblanc et al.
+failed to construct a single latent syndemic variable in their analysis [@leblanc2021].
+Moreover constraining factor loadings to be equal resulted in worse fit in the studies by Mustanski and Starks.
 
@@
 Applied to syndemic theory, a syndemic would then be the network and the various conditions would then be the nodes of the network.
-Furthermore, one of the benefits of this approach reside in the theoretical possibility to identify influential nodes in a network : nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network @robinaugh2016.
-In short, in addition to be statistically sound and coherent with the model of mutually causal epidemics, network analysis could offer actionable data to improve the health of MSM by identifying which conditions should be prioritized for interventions.
+Furthermore, one of the benefits of this approach resides in the theoretical possibility to identify influential nodes in a network : nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network @robinaugh2016.
+In short, in addition to being statistically sound and coherent with the model of mutually causal epidemics, network analysis could offer actionable data to improve the health of MSM by identifying which conditions should be prioritized for interventions [@Tsai2018a].
 
-We recommend that future work should let go of the summation score approach and attempt to clarify which model of interaction receives the most empirical support in order to implement effective public health interventions.
+We recommend that future research should abandon the summation score approach and attempt to clarify which model of interaction receives the most empirical support in order to implement effective public health interventions.
 Indeed as reminded by Chakrapani et al.
@@
 
-## Additional framework
+## Additional frameworks
 
@@
 
-On the topic of resilience resources, Zhang et al didn't find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
+On the topic of resilience resources, Zhang et al did not find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
 O'Leary et al.
-didn't find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviors, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
+did not find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviors, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
 On the other hand, Kurtz et al found that, among MSM living with HIV, serosorting was positively associated with higher levels of two resilience factors : coping self-efficacy and positive coping skills [@Kurtz2012].
 Similarly, Hart et al.
-found that psychosocial strengths were associated with lesser odds of engaging in condomless anal sex, despite the presence of syndemic conditions [@Hart2017].
+found that psychosocial strengths were associated with lower likelihood of engaging in condomless anal sex, despite the presence of syndemic conditions [@Hart2017].
 
 In qualitative studies, resilience was also found to exert a protective effect against syndemic conditions [@Chakrapani2019a; @Reed2016; @adam2018].
-Besides, the review by Woodwards et al.
+Furthermore, the review by Woodwards et al.
 found a protective effect of most resilience resources identified against HIV @woodward2017.
 
-Minority stress represents another interesting framework as it allows to explain how social stigma can get into the skin of minorized populations @Meyer2003.
-Finally, as aforementioned, intersectionality may offer an useful framework to explore how syndemics operate among different subpopulations of MSM, especially MSM living with a dual-minority identity such as Black MSM.
+We recommend that future work continues to explore the impact of resilience in partially counteracting syndemics to develop public health interventions that aim to foster resilience resources among MSM.
+Moreover, as pointed out by Namer and Razum, focusing on risk rather than resilience and survivorship poses the threat of alienating minority groups rather than prioritizing them [@namer2021].
 
-We recommend that future work continue to explore the impact of resilience in partially counteracting syndemic to develop public health intervention that aim at fostering resilience resources among MSM.
-Furthermore, an intersectional lens should be used more often to elucidate the mechanisms of syndemic among MSM with a dual-minority identity.
+Minority stress represents another interesting framework as it allows to explain how social stigma can get under the skin of minorized populations @Meyer2003.
+
+Finally, although intersectionality was only used by two studies [@ferlatte2018; @Quinn] we believe the field would benefit from this framework .
+Indeed as shown in our results, there is some discrepancy in the results for MSM's subpopulation, especially for MSMW/bisexual men, Black MSM and Latino MSM.
+We believe that the inattention to systemic inequalities and structural disadvantage in the field may partly explain these discrepancies.
+In fact, only `r percent((summary_quantitative %>% filter(!is.na(unstable_housing) | !is.na(discrimination) | !is.na(incarceration) | !is.na(poverty)| !is.na (unemployment) | !is.na(healthcare_access)) %>% nrow())/nrow(summary_quantitative))` of the quantitative studies examine a structural condition such as discrimination, poverty or access to healthcare.
+
+Some scholars are skeptical on the usefulness of syndemic theory to intersectionality and question the possibility of a conversation between the two fields @sangaramoorthy2021.
+As pertinent as the authors commentary is, we do believe in the possibility of making the two field converse.
+As Quinn pointed out in her response, incorporating an intersectional framework into syndemic research may address issues of power, oppression and structural violence, neglected thus far in the field @quinn2021.
+Doing so, we may attend to some gap in the literature and disentangle the complex web of stigma and structural violence faced by sexual minority men, especially MSM situated at the intersection of multiple form of systemic discrimination such as racism, homophobia, biphobia, transphobia, classism, ableism or stigma against sex workers or people living with HIV.

### 2022-01-13 _bookdown_files/06-conclusion.Rmd
Funding added
Complete draft

@@
 
-However, even though we took several steps to ensure the comprehensiveness of our search strategy, we may still have missed some relevant literature.
+Nevertheless, even though we took several steps to ensure the comprehensiveness of our search strategy, we may still have missed some relevant literature.
 Furthermore, one of our inclusion criteria was the centrality of syndemic theory to the screened paper.
-Even if two reviewers screened a part of the studies independently, this criteria may be somewhat arbitrary and other researchers may have chosen to include papers we rejected or the contrary.
-Finally, usual limitations of a scoping review apply such as the lack of risk of bias and strength of evidence assessment.
+Although two reviewers screened a part of the studies independently, this criteria may be somewhat arbitrary and other researchers may have chosen to include papers we rejected or the contrary.
+Finally, the usual limitations of a scoping review apply such as the lack of risk of bias and strength of evidence assessment.
 
@@
 Our review of syndemic research applied to MSM revealed some important limitations that must be addressed in future work.
-The field of syndemic research would gain to study more MSM subpopulations, in more diverse geographical settings, especially in the Global South.
+The field of syndemic research would benefit from studying more MSM subpopulations, in more diverse geographical settings, especially in the Global South.
 Furthermore, promising methods such as spatial epidemiology or network analysis may help to advance the field while methods such as summary count should be abandoned.
-Besides, more qualitative and mixed data may enhance our understanding of the complex interactions of a syndemic on the living experiences of marginalized people suffering from it.
-Moreover, outcomes should be less focused on sexual health and start to explore other potential impact of a syndemic on health.
-Finally, conditions that constitute a syndemic should be more precisely defined and the measurement of said conditions should be more standardized while taking into account the difficulties of transposing some measures in different sociocultural contexts.
+More qualitative and mixed design may enhance our understanding of the complex interactions of a syndemic on the lived experiences of marginalized people.
+Outcomes should be less focused on sexual health and start to explore other potential impacts of a syndemic on health.
+Finally, conditions that constitute a syndemic should be more precisely defined and the measurement of those conditions should be more standardized while taking into account the difficulties of transposing some measures in different sociocultural contexts.
 
-Though we took a critical stance on the current literature, we still consider syndemic to be an useful framework to study the global health of marginalized populations and the current research still offered valuable insights on the health of MSM.
-It is up to scholars in the field to continue to push research forward in order to improve the health of marginalized populations worldwide.
+Despite our critical stance on the current literature, we remained convinced that syndemic is a useful framework to study the health of marginalized populations in a holistic way and the current research still offered valuable insights on the health of MSM.
+It is vital that research continues to evolve in order to deepen our understanding and, by consequence, improve the health of marginalized populations worldwide.
+
+# Funding
+
+We did not receive any specific grant for this research from any funding agency in the public, commercial or not-for-profit sectors.

### 2022-01-13 _bookdown_files/08-appendix.Rmd
Inclusion of PRISMA checklist
Cross-reference issue fixed
Complete draft

@@
+# Supplementary Materials
+
+## A. PRISMA-ScR checklist
+
+```{r PRISMA-ScR, tab.id = "PRISMA-ScR", echo=FALSE, message= FALSE,warning=FALSE}
+source("./scripts/supplementary_tables/PRISMA-ScR.R", local = knitr::knit_global())
+
+.PRISMA_ft
+
+```
+
+\newpage
+
 <!---BLOCK_LANDSCAPE_START--->
 
-# Supplementary Materials
-
-### A. Reference tables
+## B. Reference tables
 
@@
 
-#### List of references included in the review
+### List of references included in the review
 
-Achterbergh, R.C.A., van Rooijen, M.S.,
-van den Brink, W., Boyd, A., e Vries, H.J.C., 2021. Enhancing help-seeking
-behaviour among men who have sex with men at risk for sexually transmitted
-infections: the syn.bas.in randomised controlled trial. Sex Transm Infect 97,
-11--17. <https://doi.org/10.1136/sextrans-2020-054438>
+Achterbergh, R.C.A., van Rooijen, M.S., van den Brink, W., Boyd, A., e Vries, H.J.C., 2021.
+Enhancing help-seeking behaviour among men who have sex with men at risk for sexually transmitted infections: the syn.bas.in randomised controlled trial.
+Sex Transm Infect 97, 11--17.
+<https://doi.org/10.1136/sextrans-2020-054438>
 
-Adam, B.D., Hart, T.A., Mohr, J., Coleman,
-T., Vernon, J., 2018. Resilience pathways, childhood escape routes, and mentors
-reported by gay and bisexual men affected by syndemic conditions. Sexualities
-22, 642. <https://doi.org/10.1177/1363460718758663>
+Adam, B.D., Hart, T.A., Mohr, J., Coleman, T., Vernon, J., 2018.
+Resilience pathways, childhood escape routes, and mentors reported by gay and bisexual men affected by syndemic conditions.
+Sexualities 22, 642.
+<https://doi.org/10.1177/1363460718758663>
 
-Adam, B.D., Hart, T.A., Mohr, J., Coleman,
-T., Vernon, J., 2017. HIV-related syndemic pathways and risk subjectivities
-among gay and bisexual men: a qualitative investigation. Cult Health Sex 19,
-1254--1267. <https://doi.org/10.1080/13691058.2017.1309461>
+Adam, B.D., Hart, T.A., Mohr, J., Coleman, T., Vernon, J., 2017.
+HIV-related syndemic pathways and risk subjectivities among gay and bisexual men: a qualitative investigation.
+Cult Health Sex 19, 1254--1267.
+<https://doi.org/10.1080/13691058.2017.1309461>
 
-Batchelder, A.W., Choi, K., Dale, S.K.,
-Pierre-Louis, C., Sweek, E.W., Ironson, G., Safren, S.A., O'Cleirigh, C., 2019.
-Effects of syndemic psychiatric diagnoses on health indicators in men who have
-sex with men. Health Psychology 38, 509--517. <https://doi.org/10.1037/hea0000724>
+Batchelder, A.W., Choi, K., Dale, S.K., Pierre-Louis, C., Sweek, E.W., Ironson, G., Safren, S.A., O'Cleirigh, C., 2019.
+Effects of syndemic psychiatric diagnoses on health indicators in men who have sex with men.
+Health Psychology 38, 509--517.
+<https://doi.org/10.1037/hea0000724>
 
-Beymer, M.R., Weiss, R.E., Halkitis, P.N.,
-Kapadia, F., Ompad, D.C., Bourque, L., Bolan, R.K., 2016. Disparities Within
-the Disparity-Determining HIV Risk Factors Among Latino Gay and Bisexual Men
-Attending a Community-Based Clinic in Los Angeles, CA. J Acquir Immune Defic
-Syndr 73, 237--244. <https://doi.org/10.1097/QAI.0000000000001072>
+Beymer, M.R., Weiss, R.E., Halkitis, P.N., Kapadia, F., Ompad, D.C., Bourque, L., Bolan, R.K., 2016.
+Disparities Within the Disparity-Determining HIV Risk Factors Among Latino Gay and Bisexual Men Attending a Community-Based Clinic in Los Angeles, CA.
+J Acquir Immune Defic Syndr 73, 237--244.
+<https://doi.org/10.1097/QAI.0000000000001072>
 
-Biello, K.B., Colby, D., Closson, E.,
-Mimiaga, M.J., 2014. The syndemic condition of psychosocial problems and HIV
-risk among male sex workers in Ho Chi Minh City, Vietnam. AIDS Behav 18, 1264--1271.
+Biello, K.B., Colby, D., Closson, E., Mimiaga, M.J., 2014.
+The syndemic condition of psychosocial problems and HIV risk among male sex workers in Ho Chi Minh City, Vietnam.
+AIDS Behav 18, 1264--1271.
 <https://doi.org/10.1007/s10461-013-0632-8>
 
-Biello, K.B., Oldenburg, C.E., Safren,
-S.A., Rosenberger, J.G., Novak, D.S., Mayer, K.H., Mimiaga, M.J., 2016.
-Multiple syndemic psychosocial factors are associated with reduced engagement
-in HIV care among a multinational, online sample of HIV-infected MSM in Latin
-America. AIDS Care 28 Suppl 1, 84--91.
+Biello, K.B., Oldenburg, C.E., Safren, S.A., Rosenberger, J.G., Novak, D.S., Mayer, K.H., Mimiaga, M.J., 2016.
+Multiple syndemic psychosocial factors are associated with reduced engagement in HIV care among a multinational, online sample of HIV-infected MSM in Latin America.
+AIDS Care 28 Suppl 1, 84--91.
 <https://doi.org/10.1080/09540121.2016.1146205>
 
-Blashill, A.J., Brady, J.P., Rooney, B.M.,
-Rodriguez-Diaz, C.E., Horvath, K.J., Blumenthal, J., Morris, S., Moore, D.J.,
-Safren, S.A., 2020. Syndemics and the PrEP Cascade: Results from a Sample of
-Young Latino Men Who Have Sex with Men. Arch Sex Behav 49, 125--135.
+Blashill, A.J., Brady, J.P., Rooney, B.M., Rodriguez-Diaz, C.E., Horvath, K.J., Blumenthal, J., Morris, S., Moore, D.J., Safren, S.A., 2020.
+Syndemics and the PrEP Cascade: Results from a Sample of Young Latino Men Who Have Sex with Men.
+Arch Sex Behav 49, 125--135.
 <https://doi.org/10.1007/s10508-019-01470-7>
 
-Blondeel, K., Dias, S., Furegato, M.,
-Seuc, A., Gama, A., Fuertes, R., Mendao, L., Temmerman, M., Toskin, I., 2021.
-Sexual behaviour patterns and STI risk: results of a cluster analysis among men
-who have sex with men in Portugal. BMJ Open 11, e033290.
+Blondeel, K., Dias, S., Furegato, M., Seuc, A., Gama, A., Fuertes, R., Mendao, L., Temmerman, M., Toskin, I., 2021.
+Sexual behaviour patterns and STI risk: results of a cluster analysis among men who have sex with men in Portugal.
+BMJ Open 11, e033290.
 <https://doi.org/10.1136/bmjopen-2019-033290>
@@
 Bränström, R., Pachankis, J.E., 2018.
-Validating the Syndemic Threat Surrounding Sexual Minority Men's Health in a
-Population-Based Study With National Registry Linkage and a Heterosexual
-Comparison. J. Acquir. Immune Defic. Syndr. 78, 376--382.
+Validating the Syndemic Threat Surrounding Sexual Minority Men's Health in a Population-Based Study With National Registry Linkage and a Heterosexual Comparison.
+J.
+Acquir.
+Immune Defic.
+Syndr.
+78, 376--382.
 <https://doi.org/10.1097/QAI.0000000000001697>
 
-Bruce, D., Harper, G.W., Interventions,
-A.M.T.N. for H., 2011. Operating without a safety net: gay male adolescents and
-emerging adults' experiences of marginalization and migration, and implications
-for theory of syndemic production of health disparities. Health Educ Behav 38,
-367--378. <https://doi.org/10.1177/1090198110375911>
+Bruce, D., Harper, G.W., Interventions, A.M.T.N.
+for H., 2011.
+Operating without a safety net: gay male adolescents and emerging adults' experiences of marginalization and migration, and implications for theory of syndemic production of health disparities.
+Health Educ Behav 38, 367--378.
+<https://doi.org/10.1177/1090198110375911>
 
-Buttram, M.E., Kurtz, S.P., 2015. A mixed
-methods study of health and social disparities among substance-using African
-American/Black men who have sex with men. J Racial Ethn Health Disparities 2, 1--10.
+Bulled, N., 2021.
+A new approach to measuring the synergy in a syndemic: Revisiting the SAVA syndemic among urban MSM in the United States.
+Glob Public Health 1--11.
+<https://doi.org/10.1080/17441692.2021.1974513>
+
+Buttram, M.E., Kurtz, S.P., 2015.
+A mixed methods study of health and social disparities among substance-using African American/Black men who have sex with men.
+J Racial Ethn Health Disparities 2, 1--10.
 <https://doi.org/10.1007/s40615-014-0042-2>
 
-Byg, B., Bazzi, A.R., Funk, D., James, B.,
-Potter, J., 2016. The Utility of a Syndemic Framework in Understanding Chronic
-Disease Management Among HIV-Infected and Type 2 Diabetic Men Who Have Sex with
-Men. J. Community Health 41, 1204--1211.
+Byg, B., Bazzi, A.R., Funk, D., James, B., Potter, J., 2016.
+The Utility of a Syndemic Framework in Understanding Chronic Disease Management Among HIV-Infected and Type 2 Diabetic Men Who Have Sex with Men.
+J.
+Community Health 41, 1204--1211.
 <https://doi.org/10.1007/s10900-016-0202-x>
 
-Card, K.G., Lachowsky, N.J., Armstrong,
-H.L., Cui, Z., Wang, L., Sereda, P., Jollimore, J., Patterson, T.L., Corneil,
-T., Hogg, R.S., Roth, E.A., Moore, D.M., 2018. The additive effects of
-depressive symptoms and polysubstance use on HIV risk among gay, bisexual, and
-other men who have sex with men. Addict. Behav 82, 158--165.
+Card, K.G., Lachowsky, N.J., Armstrong, H.L., Cui, Z., Wang, L., Sereda, P., Jollimore, J., Patterson, T.L., Corneil, T., Hogg, R.S., Roth, E.A., Moore, D.M., 2018.
+The additive effects of depressive symptoms and polysubstance use on HIV risk among gay, bisexual, and other men who have sex with men.
+Addict.
+Behav 82, 158--165.
 <https://doi.org/10.1016/j.addbeh.2018.03.005>
 
-Carrico, A.W., Rodriguez, V.J., Jones,
-D.L., Kumar, M., 2018. Short circuit: Disaggregation of adrenocorticotropic
-hormone and cortisol levels in HIV-positive, methamphetamine-using men who have
-sex with men. Human psychopharmacology 33. <https://doi.org/10.1002/hup.2645>
+Carrico, A.W., Rodriguez, V.J., Jones, D.L., Kumar, M., 2018.
+Short circuit: Disaggregation of adrenocorticotropic hormone and cortisol levels in HIV-positive, methamphetamine-using men who have sex with men.
+Human psychopharmacology 33.
+<https://doi.org/10.1002/hup.2645>
 
-Cassels, S., Meltzer, D., Loustalot, C.,
-Ragsdale, A., Shoptaw, S., Gorbach, P.M., 2020. Geographic Mobility, Place
-Attachment, and the Changing Geography of Sex among African American and Latinx
-MSM Who Use Substances in Los Angeles. J Urban Health 97, 609--622.
+Cassels, S., Meltzer, D., Loustalot, C., Ragsdale, A., Shoptaw, S., Gorbach, P.M., 2020.
+Geographic Mobility, Place Attachment, and the Changing Geography of Sex among African American and Latinx MSM Who Use Substances in Los Angeles.
+J Urban Health 97, 609--622.
 <https://doi.org/10.1007/s11524-020-00481-3>
 
-Chakrapani, V., Kaur, M., Newman, P.A.,
-Mittal, S., Kumar, R., 2019a. Syndemics and HIV-related sexual risk among men
-who have sex with men in India: influences of stigma and resilience. Cult
-Health Sex 21, 416--431. <https://doi.org/10.1080/13691058.2018.1486458>
+Chakrapani, V., Kaur, M., Newman, P.A., Mittal, S., Kumar, R., 2019a.
+Syndemics and HIV-related sexual risk among men who have sex with men in India: influences of stigma and resilience.
+Cult Health Sex 21, 416--431.
+<https://doi.org/10.1080/13691058.2018.1486458>
 
-Chakrapani, V., Kaur, M., Tsai, A.C.,
-Newman, P.A., Kumar, R., 2020. The impact of a syndemic theory-based
-intervention on HIV transmission risk behaviour among men who have sex with men
-in India: Findings from a pretest-posttest non-equivalent comparison group
-trial. Soc Sci Med. <https://doi.org/10.1016/j.socscimed.2020.112817>
+Chakrapani, V., Kaur, M., Tsai, A.C., Newman, P.A., Kumar, R., 2020.
+The impact of a syndemic theory-based intervention on HIV transmission risk behaviour among men who have sex with men in India: Findings from a pretest-posttest non-equivalent comparison group trial.
+Soc Sci Med.
+<https://doi.org/10.1016/j.socscimed.2020.112817>
 
-Chakrapani, V., Lakshmi, P.V.M., Tsai,
-A.C., Vijin, P.P., Kumar, P., Srinivas, V., 2019b. The syndemic of violence
-victimisation, drug use, frequent alcohol use, and HIV transmission risk
-behaviour among men who have sex with men: Cross-sectional, population-based
-study in India. SSM Popul Health 7, 100348.
+Chakrapani, V., Lakshmi, P.V.M., Tsai, A.C., Vijin, P.P., Kumar, P., Srinivas, V., 2019b.
+The syndemic of violence victimisation, drug use, frequent alcohol use, and HIV transmission risk behaviour among men who have sex with men: Cross-sectional, population-based study in India.
+SSM Popul Health 7, 100348.
 <https://doi.org/10.1016/j.ssmph.2018.100348>
 
-Chakrapani, V., Newman, P.A., Shunmugam,
-M., Logie, C.H., Samuel, M., 2017. Syndemics of depression, alcohol use, and
-victimisation, and their association with HIV-related sexual risk among men who
-have sex with men and transgender women in India. Glob. Public Health 12, 250--265.
+Chakrapani, V., Newman, P.A., Shunmugam, M., Logie, C.H., Samuel, M., 2017.
+Syndemics of depression, alcohol use, and victimisation, and their association with HIV-related sexual risk among men who have sex with men and transgender women in India.
+Glob.
+Public Health 12, 250--265.
 <https://doi.org/10.1080/17441692.2015.1091024>
 
-Chandler, Cristian J., Bukowski, L.A.,
-Matthews, D.D., Hawk, M.E., Markovic, N., Egan, J.E., Stall, R.D., 2020a.
-Examining the Impact of a Psychosocial Syndemic on Past Six-Month HIV Screening
-Behavior of Black Men who have Sex with Men in the United States: Results from
-the POWER Study. AIDS Behav 28, 428--436.
+Chandler, C.J., Bukowski, L.A., Matthews, D.D., Hawk, M.E., Markovic, N., Egan, J.E., Stall, R.D., 2020a.
+Examining the Impact of a Psychosocial Syndemic on Past Six-Month HIV Screening Behavior of Black Men who have Sex with Men in the United States: Results from the POWER Study.
+AIDS Behav 28, 428--436.
 <https://doi.org/10.1007/s10461-019-02458-z>
 
-Chandler, Cristian J., Bukowski, L.A.,
-Matthews, D.D., Hawk, M.E., Markovic, N., Stall, R.D., Egan, J.E., 2020b.
-Understanding the impact of a syndemic on the use of pre-exposure prophylaxis
-in a community-based sample of behaviorally PrEP-eligible BMSM in the United
-States. AIDS Care 32, 551--556. <https://doi.org/10.1080/09540121.2019.1659921>
+Chandler, C.J., Bukowski, L.A., Matthews, D.D., Hawk, M.E., Markovic, N., Stall, R.D., Egan, J.E., 2020b.
+Understanding the impact of a syndemic on the use of pre-exposure prophylaxis in a community-based sample of behaviorally PrEP-eligible BMSM in the United States.
+AIDS Care 32, 551--556.
+<https://doi.org/10.1080/09540121.2019.1659921>
 
-Chandler, Cristian J, Meunier, E., Eaton,
-L.A., Andrade, E., Bukowski, L.A., Matthews, D.D., Raymond, H.F., Stall, R.D.,
-Friedman, M.R., 2020. Syndemic health disparities and sexually transmitted
-infection burden among black men who have sex with men engaged in sex work in
-the u.S. Arch Sex Behav. <https://doi.org/10.1007/s10508-020-01828-2>
+Chandler, C.J., Meunier, É., Eaton, L.A., Andrade, E., Bukowski, L.A., Matthews, D.D., Raymond, H.F., Stall, R.D., Friedman, M.R., 2021.
+Syndemic Health Disparities and Sexually Transmitted Infection Burden Among Black Men Who Have Sex with Men Engaged in Sex Work in the U.S.
+Arch Sex Behav 50, 1627--1640.
+<https://doi.org/10.1007/s10508-020-01828-2>
 
-Chuang, D.-M., Newman, P.A., Li, A.T.-W.,
-2018. Syndemic factors and HIV infection among men who have sex with men in
-Taiwan. J HIV AIDS Soc Serv 17, 337--352. <https://doi.org/10.1080/15381501.2018.1454866>
+Chuang, D.-M., Newman, P.A., Fang, L., Lai, M.-C., 2021.
+Syndemic Conditions, Sexual Risk Behavior, and HIV Infection Among Men Who Have Sex with Men in Taiwan.
+AIDS BEHAV 25, 3503--3518.
+<https://doi.org/10.1007/s10461-021-03269-x>
 
-Dyer, T.P., Shoptaw, S., Guadamuz, T.E.,
-Plankey, M., Kao, U., Ostrow, D., Chmiel, J.S., Herrick, A., Stall, R., 2012.
-Application of syndemic theory to black men who have sex with men in the
-Multicenter AIDS Cohort Study. J Urban Health 89, 697--708.
+Chuang, D.-M., Newman, P.A., Li, A.T.-W., 2018.
+Syndemic factors and HIV infection among men who have sex with men in Taiwan.
+J HIV AIDS Soc Serv 17, 337--352.
+<https://doi.org/10.1080/15381501.2018.1454866>
+
+Dyer, T.P., Shoptaw, S., Guadamuz, T.E., Plankey, M., Kao, U., Ostrow, D., Chmiel, J.S., Herrick, A., Stall, R., 2012.
+Application of syndemic theory to black men who have sex with men in the Multicenter AIDS Cohort Study.
+J Urban Health 89, 697--708.
 <https://doi.org/10.1007/s11524-012-9674-x>
 
-Dyer, T.V., Turpin, R.E., Stall, R., Khan,
-M.R., Nelson, L.E., Brewer, R., Friedman, M.R., Mimiaga, M.J., Cook, R.L., O'Cleirigh,
-C., Mayer, K.H., 2020. Latent Profile Analysis of a Syndemic of Vulnerability
-Factors on Incident Sexually Transmitted Infection in a Cohort of Black Men Who
-Have Sex With Men Only and Black Men Who Have Sex With Men and Women in the HIV
-Prevention Trials Network 061 Study. Sex Transm Dis 47, 571--579.
-<https://doi.org/10.1097/OLQ.0000000000001208>
+Dyer, T.V., Turpin, R.E., Stall, R., Khan, M.R., Nelson, L.E., Brewer, R., Friedman, M.R., Mimiaga, M.J., Cook, R.L., O'Cleirigh, C., Mayer, K.H., 2020.
+Latent Profile Analysis of a Syndemic of Vulnerability Factors on Incident Sexually Transmitted Infection in a Cohort of Black Men Who Have Sex With Men Only and Black Men Who Have Sex With Men and Women in the HIV Prevention Trials Network 061 Study.
+Sexually Transmitted Diseases 47, 571--579.
+<https://doi.org/10.1097/olq.0000000000001208>
 
-Eaton, L.A., Pitpitan, E.V., Kalichman,
-S.C., Sikkema, K.J., Skinner, D., Watt, M.H., Pieterse, D., 2013. Men who
-report recent male and female sex partners in Cape Town, South Africa: an
-understudied and underserved population. Arch Sex Behav 42, 1299--1308.
+Eaton, L.A., Pitpitan, E.V., Kalichman, S.C., Sikkema, K.J., Skinner, D., Watt, M.H., Pieterse, D., 2013.
+Men who report recent male and female sex partners in Cape Town, South Africa: an understudied and underserved population.
+Arch Sex Behav 42, 1299--1308.
 <https://doi.org/10.1007/s10508-013-0077-1>
 
-Ferlatte, O., Dulai, J., Hottes, T.S.,
-Trussler, T., Marchand, R., 2015. Suicide related ideation and behavior among
-Canadian gay and bisexual men: a syndemic analysis. BMC public health 15, 597.
+Ferlatte, O., Dulai, J., Hottes, T.S., Trussler, T., Marchand, R., 2015.
+Suicide related ideation and behavior among Canadian gay and bisexual men: a syndemic analysis.
+BMC public health 15, 597.
 <https://doi.org/10.1186/s12889-015-1961-5>
 
-Ferlatte, O., Hottes, T.S., Trussler, T.,
-Marchand, R., 2014. Evidence of a syndemic among young Canadian gay and
-bisexual men: uncovering the associations between anti-gay experiences,
-psychosocial issues, and HIV risk. AIDS Behav 18, 1256--1263. <https://doi.org/10.1007/s10461-013-0639-1>
+Ferlatte, O., Hottes, T.S., Trussler, T., Marchand, R., 2014.
+Evidence of a syndemic among young Canadian gay and bisexual men: uncovering the associations between anti-gay experiences, psychosocial issues, and HIV risk.
+AIDS Behav 18, 1256--1263.
+<https://doi.org/10.1007/s10461-013-0639-1>
 
-Ferlatte, O., Salway, T., Samji, H., Dove,
-N., Gesink, D., Gilbert, M., Oliffe, J.L., Grennan, T., Wong, J., 2018a. An
-Application of Syndemic Theory to Identify Drivers of the Syphilis Epidemic
-among Gay, Bisexual, and Other Men Who Have Sex with Men. Sexually Transmitted
-Diseases 45, 163--168. <https://doi.org/10.1097/OLQ.0000000000000713>
+Ferlatte, O., Salway, T., Samji, H., Dove, N., Gesink, D., Gilbert, M., Oliffe, J.L., Grennan, T., Wong, J., 2018a.
+An Application of Syndemic Theory to Identify Drivers of the Syphilis Epidemic among Gay, Bisexual, and Other Men Who Have Sex with Men.
+Sexually Transmitted Diseases 45, 163--168.
+<https://doi.org/10.1097/OLQ.0000000000000713>
 
-Ferlatte, O., Salway, T., Trussler, T.,
-Oliffe, J.L., Gilbert, M., 2018b. Combining intersectionality and syndemic
-theory to advance understandings of health inequities among Canadian gay,
-bisexual and other men who have sex with men. Crit Public Health 28, 509--521.
+Ferlatte, O., Salway, T., Trussler, T., Oliffe, J.L., Gilbert, M., 2018b.
+Combining intersectionality and syndemic theory to advance understandings of health inequities among Canadian gay, bisexual and other men who have sex with men.
+Crit Public Health 28, 509--521.
 <https://doi.org/10.1080/09581596.2017.1380298>
 
-Friedman, M.R., Coulter, R.W.S.,
-Silvestre, A.J., Stall, R., Teplin, L., Shoptaw, S., Surkan, P.J., Plankey,
-M.W., 2016. Someone to count on: social support as an effect modifier of viral
-load suppression in a prospective cohort study. AIDS Care 29, 469--480.
+Friedman, M.R., Coulter, R.W.S., Silvestre, A.J., Stall, R., Teplin, L., Shoptaw, S., Surkan, P.J., Plankey, M.W., 2016.
+Someone to count on: social support as an effect modifier of viral load suppression in a prospective cohort study.
+AIDS Care 29, 469--480.
 <https://doi.org/10.1080/09540121.2016.1211614>
 
-Friedman, M.R., Kurtz, S.P., Buttram,
-M.E., Wei, C., Silvestre, A.J., Stall, R., 2014. HIV risk among substance-using
-men who have sex with men and women (MSMW): findings from South Florida. AIDS
-Behav 111--19. <https://doi.org/10.1007/s10461-013-0495-z>
+Friedman, M.R., Kurtz, S.P., Buttram, M.E., Wei, C., Silvestre, A.J., Stall, R., 2014.
+HIV risk among substance-using men who have sex with men and women (MSMW): findings from South Florida.
+AIDS Behav 111--19.
+<https://doi.org/10.1007/s10461-013-0495-z>
 
-Friedman, M.R., Stall, R., Silvestre,
-A.J., Wei, C., Shoptaw, S., Herrick, A., Surkan, P.J., Teplin, L., Plankey,
-M.W., 2015. Effects of syndemics on HIV viral load and medication adherence in
-the multicentre AIDS cohort study. AIDS 29, 1087--1096.
+Friedman, M.R., Stall, R., Silvestre, A.J., Wei, C., Shoptaw, S., Herrick, A., Surkan, P.J., Teplin, L., Plankey, M.W., 2015.
+Effects of syndemics on HIV viral load and medication adherence in the multicentre AIDS cohort study.
+AIDS 29, 1087--1096.
 <https://doi.org/10.1097/QAD.0000000000000657>
 
-Guadamuz, T.E., McCarthy, K., Wimonsate,
-W., Thienkrua, W., Varangrat, A., Chaikummao, S., Sangiamkittikul, A., Stall,
-R.D., van Griensven, F., 2014. Psychosocial Health Conditions and HIV
-Prevalence and Incidence in a Cohort of Men Who have Sex with Men in Bangkok,
-Thailand: Evidence of a Syndemic Effect. AIDS Behav 18, 2089--2096.
+Guadamuz, T.E., McCarthy, K., Wimonsate, W., Thienkrua, W., Varangrat, A., Chaikummao, S., Sangiamkittikul, A., Stall, R.D., van Griensven, F., 2014.
+Psychosocial Health Conditions and HIV Prevalence and Incidence in a Cohort of Men Who have Sex with Men in Bangkok, Thailand: Evidence of a Syndemic Effect.
+AIDS Behav 18, 2089--2096.
 <https://doi.org/10.1007/s10461-014-0826-8>
 
-Halkitis, P.N., Kapadia, F., Bub, K.L.,
-Barton, S., Moreira, A.D., Stults, C.B., 2015. A Longitudinal Investigation of
-Syndemic Conditions Among Young Gay, Bisexual, and Other MSM: The P18 Cohort
-Study. AIDS Behav 19, 970--980. <https://doi.org/10.1007/s10461-014-0892-y>
+Halkitis, P.N., Kapadia, F., Bub, K.L., Barton, S., Moreira, A.D., Stults, C.B., 2015.
+A Longitudinal Investigation of Syndemic Conditions Among Young Gay, Bisexual, and Other MSM: The P18 Cohort Study.
+AIDS Behav 19, 970--980.
+<https://doi.org/10.1007/s10461-014-0892-y>
 
-Halkitis, P.N., Kupprat, S.A., Hampton,
-M.B., Perez-Figueroa, R., Kingdon, M., Eddy, J.A., Ompad, D.C., 2012. Evidence
-for a Syndemic in Aging HIV-positive Gay, Bisexual, and Other MSM: Implications
-for a Holistic Approach to Prevention and Healthcare. Ann Anthropol Pract 36,
-365--386. <https://doi.org/10.1111/napa.12009>
+Halkitis, P.N., Kupprat, S.A., Hampton, M.B., Perez-Figueroa, R., Kingdon, M., Eddy, J.A., Ompad, D.C., 2012.
+Evidence for a Syndemic in Aging HIV-positive Gay, Bisexual, and Other MSM: Implications for a Holistic Approach to Prevention and Healthcare.
+Ann Anthropol Pract 36, 365--386.
+<https://doi.org/10.1111/napa.12009>
 
-Halkitis, P.N., Moeller, R.W., Siconolfi,
-D.E., Storholm, E.D., Solomon, T.M., Bub, K.L., 2013. Measurement model
-exploring a syndemic in emerging adult gay and bisexual men. AIDS Behav 17, 662--673.
+Halkitis, P.N., Moeller, R.W., Siconolfi, D.E., Storholm, E.D., Solomon, T.M., Bub, K.L., 2013.
+Measurement model exploring a syndemic in emerging adult gay and bisexual men.
+AIDS Behav 17, 662--673.
 <https://doi.org/10.1007/s10461-012-0273-3>
 
-Harkness, A., Bainter, S.A., O'Cleirigh,
-C., Albright, C., Mayer, K.H., Safren, S.A., 2019. Longitudinal Effects of
-Syndemics on HIV-Positive Sexual Minority Men's Sexual Health Behaviors. Arch
-Sex Behav 48, 1159--1170. <https://doi.org/10.1007/s10508-018-1329-x>
+Harkness, A., Bainter, S.A., O'Cleirigh, C., Albright, C., Mayer, K.H., Safren, S.A., 2019.
+Longitudinal Effects of Syndemics on HIV-Positive Sexual Minority Men's Sexual Health Behaviors.
+Arch Sex Behav 48, 1159--1170.
+<https://doi.org/10.1007/s10508-018-1329-x>
 
-Harkness, A., Bainter, S.A., O'Cleirigh,
-C., Mendez, N.A., Mayer, K.H., Safren, S.A., 2018. Longitudinal Effects of
-Syndemics on ART Non-adherence Among Sexual Minority Men. AIDS Behav 22, 2564--2574.
+Harkness, A., Bainter, S.A., O'Cleirigh, C., Mendez, N.A., Mayer, K.H., Safren, S.A., 2018.
+Longitudinal Effects of Syndemics on ART Non-adherence Among Sexual Minority Men.
+AIDS Behav 22, 2564--2574.
 <https://doi.org/10.1007/s10461-018-2180-8>
 
-Hart, T.A., Noor, S.W., Adam, B.D.,
-Vernon, J.R.G., Brennan, D.J., Gardner, S., Husbands, W., Myers, T., 2017.
-Number of Psychosocial Strengths Predicts Reduced HIV Sexual Risk Behaviors
-Above and Beyond Syndemic Problems Among Gay and Bisexual Men. AIDS Behav 21,
-3035--3046. <https://doi.org/10.1007/s10461-016-1669-2>
+Hart, T.A., Noor, S.W., Adam, B.D., Vernon, J.R.G., Brennan, D.J., Gardner, S., Husbands, W., Myers, T., 2017.
+Number of Psychosocial Strengths Predicts Reduced HIV Sexual Risk Behaviors Above and Beyond Syndemic Problems Among Gay and Bisexual Men.
+AIDS Behav 21, 3035--3046.
+<https://doi.org/10.1007/s10461-016-1669-2>
 
-Herrick, A., Stall, R., Egan, J.,
-Schrager, S., Kipke, M., 2014. Pathways towards risk: syndemic conditions
-mediate the effect of adversity on HIV risk behaviors among young men who have
-sex with men (YMSM). J Urban Health 91, 969--982.
+Herrick, A., Stall, R., Egan, J., Schrager, S., Kipke, M., 2014.
+Pathways towards risk: syndemic conditions mediate the effect of adversity on HIV risk behaviors among young men who have sex with men (YMSM).
+J Urban Health 91, 969--982.
 <https://doi.org/10.1007/s11524-014-9896-1>
 
-Herrick, A.L., Lim, S.H., Plankey, M.W.,
-Chmiel, J.S., Guadamuz, T.E., Kao, U., Shoptaw, S., Carrico, A., Ostrow, D.,
-Stall, R., 2013. Adversity and syndemic production among men participating in
-the multicenter AIDS cohort study: a life-course approach. Am J Public Health
-103, 79--85. <https://doi.org/10.2105/AJPH.2012.300810>
+Herrick, A.L., Lim, S.H., Plankey, M.W., Chmiel, J.S., Guadamuz, T.E., Kao, U., Shoptaw, S., Carrico, A., Ostrow, D., Stall, R., 2013.
+Adversity and syndemic production among men participating in the multicenter AIDS cohort study: a life-course approach.
+Am J Public Health 103, 79--85.
+<https://doi.org/10.2105/AJPH.2012.300810>
 
-Hirshfield, S., Schrimshaw, E.W., Stall,
-R.D., Margolis, A.D., Downing  Jr, M.J.,
-Chiasson, M.A., 2015. Drug Use, Sexual Risk, and Syndemic Production Among Men
-Who Have Sex With Men Who Engage in Group Sexual Encounters. Am J Public Health
-105, 1849--1858. <https://doi.org/10.2105/AJPH.2014.302346>
+Hirshfield, S., Schrimshaw, E.W., Stall, R.D., Margolis, A.D., Downing  Jr, M.J., Chiasson, M.A., 2015.
+Drug Use, Sexual Risk, and Syndemic Production Among Men Who Have Sex With Men Who Engage in Group Sexual Encounters.
+Am J Public Health 105, 1849--1858.
+<https://doi.org/10.2105/AJPH.2014.302346>
 
-Jiang, H., Li, J., Tan, Z., Chen, X.,
-Cheng, W., Gong, X., Yang, Y., 2020. Syndemic Factors and HIV Risk Among Men
-Who Have Sex with Men in Guangzhou, China: Evidence from Synergy and Moderated
-Analyses. Arch Sex Behav 49, 311--320.
+Jiang, H., Li, J., Tan, Z., Chen, X., Cheng, W., Gong, X., Yang, Y., 2020.
+Syndemic Factors and HIV Risk Among Men Who Have Sex with Men in Guangzhou, China: Evidence from Synergy and Moderated Analyses.
+Arch Sex Behav 49, 311--320.
 <https://doi.org/10.1007/s10508-019-01488-x>
 
-Jie, W., Ciyong, L., Xueqing, D., Hui, W.,
-Lingyao, H., 2012. A syndemic of psychosocial problems places the MSM (men who
-have sex with men) population at greater risk of HIV infection. PLoS ONE 7,
-e32312. <https://doi.org/10.1371/journal.pone.0032312>
+Jie, W., Ciyong, L., Xueqing, D., Hui, W., Lingyao, H., 2012.
+A syndemic of psychosocial problems places the MSM (men who have sex with men) population at greater risk of HIV infection.
+PLoS ONE 7, e32312.
+<https://doi.org/10.1371/journal.pone.0032312>
 
-Klein, H., 2011. Using a syndemics theory
-approach to study HIV risk taking in a population of men who use the internet
-to find partners for unprotected sex. Am J Men's Health 5, 466--476.
+Klein, H., 2011.
+Using a syndemics theory approach to study HIV risk taking in a population of men who use the internet to find partners for unprotected sex.
+Am J Men's Health 5, 466--476.
 <https://doi.org/10.1177/1557988311398472>
 
-Kurtz, S.P., Buttram, M.E., Surratt, H.L.,
-Stall, R.D., 2012. Resilience, syndemic factors, and serosorting behaviors
-among HIV-positive and HIV-negative substance-using MSM. AIDS Educ Prev 24, 193--205.
+Kurtz, S.P., Buttram, M.E., Surratt, H.L., Stall, R.D., 2012.
+Resilience, syndemic factors, and serosorting behaviors among HIV-positive and HIV-negative substance-using MSM.
+AIDS Educ Prev 24, 193--205.
 <https://doi.org/10.1521/aeap.2012.24.3.193>
@@
 Lassiter, J.M., Parsons, J.T., 2016.
-Religion and Spirituality's Influences on HIV Syndemics Among MSM: A Systematic
-Review and Conceptual Model. AIDS Behav 20, 461--472.
+Religion and Spirituality's Influences on HIV Syndemics Among MSM: A Systematic Review and Conceptual Model.
+AIDS Behav 20, 461--472.
 <https://doi.org/10.1007/s10461-015-1173-0>
 
-Lee, J S, Bainter, S.A., Carrico, A.W.,
-Glynn, T.R., Rogers, B.G., Albright, C., O'Cleirigh, C., Mayer, K.H., Safren,
-S.A., 2020. Connecting the dots: a comparison of network analysis and
-exploratory factor analysis to examine psychosocial syndemic indicators among
-HIV-negative sexual minority men. J Behav Med.
+Leblanc, N.M., Crean, H.F., Dyer, T.P., Zhang, C., Turpin, R., Zhang, N., Smith, M.D.R., McMahon, J., Nelson, L., 2021.
+Ecological and Syndemic Predictors of Drug Use During Sex and Transactional Sex among U.S.
+Black Men Who Have Sex with Men: A Secondary Data Analysis from the HPTN 061 Study.
+Arch Sex Behav, Erratum in: Arch Sex Behav.
+2021 May 11;:; PMID: 33974202 [[https://www.ncbi.nlm.nih.gov/pubmed/33974202]](https://www.ncbi.nlm.nih.gov/pubmed/33974202]) 50, 2031--2047.
+<https://doi.org/10.1007/s10508-020-01871-z>
+
+Lee, J.S., Bainter, S.A., Carrico, A.W., Glynn, T.R., Rogers, B.G., Albright, C., O'Cleirigh, C., Mayer, K.H., Safren, S.A., 2020a.
+Connecting the dots: a comparison of network analysis and exploratory factor analysis to examine psychosocial syndemic indicators among HIV-negative sexual minority men.
+J Behav Med.
 <https://doi.org/10.1007/s10865-020-00148-z>
 
-Lee, Jasper S., Safren, S.A., Bainter,
-S.A., Rodríguez-Díaz, C.E., Horvath, K.J., Blashill, A.J., 2020. Examining a
-Syndemics Network Among Young Latino Men Who Have Sex with Men. Int J Behav Med
-27, 39--51. <https://doi.org/10.1007/s12529-019-09831-1>
+Lee, J.S., Safren, S.A., Bainter, S.A., Rodríguez-Díaz, C.E., Horvath, K.J., Blashill, A.J., 2020b.
+Examining a Syndemics Network Among Young Latino Men Who Have Sex with Men.
+Int J Behav Med 27, 39--51.
+<https://doi.org/10.1007/s12529-019-09831-1>
 
-Lewis, N.M., Wilson, K., 2017. HIV risk
-behaviours among immigrant and ethnic minority gay and bisexual men in North
-America and Europe: A systematic review. Soc Sci Med 179, 115--128.
+Lewis, N.M., Wilson, K., 2017.
+HIV risk behaviours among immigrant and ethnic minority gay and bisexual men in North America and Europe: A systematic review.
+Soc Sci Med 179, 115--128.
 <https://doi.org/10.1016/j.socscimed.2017.02.033>
 
-Li, R., Cai, Y., Wang, Y., Sun, Z., Zhu,
-C., Tian, Y., Jiang, X., Gan, F., 2016. Psychosocial syndemic associated with
-increased suicidal ideation among men who have sex with men in Shanghai, China.
-Health Psychol 35, 148--156. <https://doi.org/10.1037/hea0000265>
+Li, R., Cai, Y., Wang, Y., Sun, Z., Zhu, C., Tian, Y., Jiang, X., Gan, F., 2016.
+Psychosocial syndemic associated with increased suicidal ideation among men who have sex with men in Shanghai, China.
+Health Psychol 35, 148--156.
+<https://doi.org/10.1037/hea0000265>
 
-Lyons, T., Johnson, A.K., Garofalo, R.,
-2013. "What Could Have Been Different": A Qualitative Study of Syndemic Theory
-and HIV Prevention among Young Men Who Have Sex with Men. J HIV AIDS Soc Serv
-12, 368--383. <https://doi.org/10.1080/15381501.2013.816211>
+Lyons, T., Johnson, A.K., Garofalo, R., 2013.
+"What Could Have Been Different": A Qualitative Study of Syndemic Theory and HIV Prevention among Young Men Who Have Sex with Men.
+J HIV AIDS Soc Serv 12, 368--383.
+<https://doi.org/10.1080/15381501.2013.816211>
 
-Maiorana, A., Kegeles, S.M., Brown, S.,
-Williams, R., Arnold, E.A., 2020. Substance use, intimate partner violence,
-history of incarceration and vulnerability to HIV among young Black men who
-have sex with men in a Southern US city. Cult Health Sex.
+Maiorana, A., Kegeles, S.M., Brown, S., Williams, R., Arnold, E.A., 2020.
+Substance use, intimate partner violence, history of incarceration and vulnerability to HIV among young Black men who have sex with men in a Southern US city.
+Cult Health Sex.
 <https://doi.org/10.1080/13691058.2019.1688395>
 
-Martinez, O., Arreola, S., Wu, E., Muñoz-Laboy,
-M., Levine, E.C., Rutledge, S.E., Hausmann-Stabile, C., Icard, L., Rhodes,
-S.D., Carballo-Diéguez, A., Rodríguez-Díaz, C.E., Fernandez, M.I., Sandfort,
-T., 2016. Syndemic factors associated with adult sexual HIV risk behaviors in a
-sample of Latino men who have sex with men in New York City. Drug Alcohol
-Depend 166, 258--262. <https://doi.org/10.1016/j.drugalcdep.2016.06.033>
+Martinez, O., Arreola, S., Wu, E., Muñoz-Laboy, M., Levine, E.C., Rutledge, S.E., Hausmann-Stabile, C., Icard, L., Rhodes, S.D., Carballo-Diéguez, A., Rodríguez-Díaz, C.E., Fernandez, M.I., Sandfort, T., 2016.
+Syndemic factors associated with adult sexual HIV risk behaviors in a sample of Latino men who have sex with men in New York City.
+Drug Alcohol Depend 166, 258--262.
+<https://doi.org/10.1016/j.drugalcdep.2016.06.033>
 
-Martinez, O., Brady, K.A., Levine, E.,
-Page, K.R., Zea, M.C., Yamanis, T.J., Grieb, S., Shinefeld, J., Ortiz, K.,
-Davis, W.W., Mattera, B., Martinez-Donate, A., Chavez-Baray, S., Moya, E.M.,
-2020. Using Syndemics Theory to Examine HIV Sexual Risk Among Latinx Men Who
-Have Sex with Men in Philadelphia, PA: Findings from the National HIV
-Behavioral Surveillance. EHQUIDAD 13, 217--236.
+Martinez, O., Brady, K.A., Levine, E., Page, K.R., Zea, M.C., Yamanis, T.J., Grieb, S., Shinefeld, J., Ortiz, K., Davis, W.W., Mattera, B., Martinez-Donate, A., Chavez-Baray, S., Moya, E.M., 2020.
+Using Syndemics Theory to Examine HIV Sexual Risk Among Latinx Men Who Have Sex with Men in Philadelphia, PA: Findings from the National HIV Behavioral Surveillance.
+EHQUIDAD 13, 217--236.
 <https://doi.org/10.15257/ehquidad.2020.0009>
 
-McDaid, L.M., Flowers, P., Ferlatte, O.,
-McAloney-Kocaman, K., Gilbert, M., Frankis, J., 2019. Informing theoretical
-development of salutogenic, asset-based health improvement to reduce syndemics
-among gay, bisexual and other men who have sex with men: Empirical evidence
-from secondary analysis of multi-national, online cross-sectional surveys. SSM
-Popul Health 10, 100519. <https://doi.org/10.1016/j.ssmph.2019.100519>
+McDaid, L.M., Flowers, P., Ferlatte, O., McAloney-Kocaman, K., Gilbert, M., Frankis, J., 2019.
+Informing theoretical development of salutogenic, asset-based health improvement to reduce syndemics among gay, bisexual and other men who have sex with men: Empirical evidence from secondary analysis of multi-national, online cross-sectional surveys.
+SSM Popul Health 10, 100519.
+<https://doi.org/10.1016/j.ssmph.2019.100519>
 
-Mimiaga, Matthew J, Biello, K.B.,
-Robertson, A.M., Oldenburg, C.E., Rosenberger, J.G., O'Cleirigh, C., Novak,
-D.S., Mayer, K.H., Safren, S.A., 2015. High prevalence of multiple syndemic
-conditions associated with sexual risk behavior and HIV infection among a large
-sample of Spanish- and Portuguese-speaking men who have sex with men in Latin
-America. Archives of Sexual Behavior 44, 1869--1878.
+Mimiaga, Matthew J, Biello, K.B., Robertson, A.M., Oldenburg, C.E., Rosenberger, J.G., O'Cleirigh, C., Novak, D.S., Mayer, K.H., Safren, S.A., 2015.
+High prevalence of multiple syndemic conditions associated with sexual risk behavior and HIV infection among a large sample of Spanish- and Portuguese-speaking men who have sex with men in Latin America.
+Archives of Sexual Behavior 44, 1869--1878.
 <https://doi.org/10.1007/s10508-015-0488-2>
 
-Mimiaga, Matthew J., OʼCleirigh, C.,
-Biello, K.B., Robertson, A.M., Safren, S.A., Coates, T.J., Koblin, B.A.,
-Chesney, M.A., Donnell, D.J., Stall, R.D., Mayer, K.H., 2015. The Effect of
-Psychosocial Syndemic Production on 4-Year HIV Incidence and Risk Behavior in a
-Large Cohort of Sexually Active Men Who Have Sex With Men. J Acquir Immune
-Defic Syndr 68, 329--336. <https://doi.org/10.1097/QAI.0000000000000475>
+Mimiaga, M.J., Hughto, J.M.W., Klasko-Foster, L., Jin, H., Mayer, K.H., Safren, S.A., Biello, K.B., 2021.
+Substance Use, Mental Health Problems, and Physical and Sexual Violence Additively Increase HIV Risk Between Male Sex Workers and Their Male Clients in Northeastern United States.
+J Acquir Immune Defic Syndr 86, 305--312.
+<https://doi.org/10.1097/QAI.0000000000002563>
 
-Moeller, R.W., Halkitis, P.N., Surrence,
-K., n.d. The interplay of syndemic production and serosorting in drug-using gay
-and bisexual men. J. Gay Lesbian Soc. Serv 23, 89--106.
+Mimiaga, Matthew J., OʼCleirigh, C., Biello, K.B., Robertson, A.M., Safren, S.A., Coates, T.J., Koblin, B.A., Chesney, M.A., Donnell, D.J., Stall, R.D., Mayer, K.H., 2015.
+The Effect of Psychosocial Syndemic Production on 4-Year HIV Incidence and Risk Behavior in a Large Cohort of Sexually Active Men Who Have Sex With Men.
+J Acquir Immune Defic Syndr 68, 329--336.
+<https://doi.org/10.1097/QAI.0000000000000475>
+
+Moeller, R.W., Halkitis, P.N., Surrence, K., 2011.
+The interplay of syndemic production and serosorting in drug-using gay and bisexual men.
+J.
+Gay Lesbian Soc.
+Serv 23, 89--106.
 <https://doi.org/10.1080/10538720.2010.538007>
 
-Morrison, S.A., Yoong, D., Hart, T.A.,
-MacPherson, P., Bogoch, I., Sivarajah, V., Gough, K., Naccarato, M., Tan,
-D.H.S., 2018. High prevalence of syndemic health problems in patients seeking
-post-exposure prophylaxis for sexual exposures to HIV. PLoS ONE 13, e0197998.
+Morrison, S.A., Yoong, D., Hart, T.A., MacPherson, P., Bogoch, I., Sivarajah, V., Gough, K., Naccarato, M., Tan, D.H.S., 2018.
+High prevalence of syndemic health problems in patients seeking post-exposure prophylaxis for sexual exposures to HIV.
+PLoS ONE 13, e0197998.
 <https://doi.org/10.1371/journal.pone.0197998>
 
-Muñoz-Laboy, M., Martinez, O., Levine,
-E.C., Mattera, B.T., Isabel Fernandez, M., 2018. Syndemic Conditions
-Reinforcing Disparities in HIV and Other STIs in an Urban Sample of
-Behaviorally Bisexual Latino Men. J Immigr Minor Health 20, 497--501.
+Muñoz-Laboy, M., Martinez, O., Levine, E.C., Mattera, B.T., Isabel Fernandez, M., 2018.
+Syndemic Conditions Reinforcing Disparities in HIV and Other STIs in an Urban Sample of Behaviorally Bisexual Latino Men.
+J Immigr Minor Health 20, 497--501.
 <https://doi.org/10.1007/s10903-017-0568-6>
 
-Mustanski, B., Andrews, R., Herrick, A.,
-Stall, R., Schnarrs, P.W., 2014. A Syndemic of Psychosocial Health Disparities
-and Associations With Risk for Attempting Suicide Among Young Sexual Minority
-Men. Am J Public Health 104, 287--294. <https://doi.org/10.2105/AJPH.2013.301744>
+Mustanski, B., Andrews, R., Herrick, A., Stall, R., Schnarrs, P.W., 2014.
+A Syndemic of Psychosocial Health Disparities and Associations With Risk for Attempting Suicide Among Young Sexual Minority Men.
+Am J Public Health 104, 287--294.
+<https://doi.org/10.2105/AJPH.2013.301744>
 
-Mustanski, B., Garofalo, R., Herrick, A.,
-Donenberg, G., 2007. Psychosocial health problems increase risk for HIV among
-urban young men who have sex with men: preliminary evidence of a syndemic in
-need of attention. Ann Behav Med 34, 37--45. <https://doi.org/10.1007/bf02879919>
+Mustanski, B., Garofalo, R., Herrick, A., Donenberg, G., 2007.
+Psychosocial health problems increase risk for HIV among urban young men who have sex with men: preliminary evidence of a syndemic in need of attention.
+Ann Behav Med 34, 37--45.
+<https://doi.org/10.1007/bf02879919>
 
-Mustanski, B., Phillips, G., Ryan, D.T.,
-Swann, G., Kuhns, L., Garofalo, R., 2017. Prospective Effects of a Syndemic on
-HIV and STI Incidence and Risk Behaviors in a Cohort of Young Men Who Have Sex
-with Men. AIDS Behav 21, 845--857. <https://doi.org/10.1007/s10461-016-1607-3>
+Mustanski, B., Phillips, G., Ryan, D.T., Swann, G., Kuhns, L., Garofalo, R., 2017.
+Prospective Effects of a Syndemic on HIV and STI Incidence and Risk Behaviors in a Cohort of Young Men Who Have Sex with Men.
+AIDS Behav 21, 845--857.
+<https://doi.org/10.1007/s10461-016-1607-3>
 
-Ng, R.X., Guadamuz, T.E., Akbar, M.,
-Kamarulzaman, A., Lim, S.H., 2020. Association of co-occurring psychosocial
-health conditions and HIV infection among MSM in Malaysia: Implication of a
-syndemic effect. Int. J. STD AIDS 31, 568--578.
+Ng, R.X., Guadamuz, T.E., Akbar, M., Kamarulzaman, A., Lim, S.H., 2020.
+Association of co-occurring psychosocial health conditions and HIV infection among MSM in Malaysia: Implication of a syndemic effect.
+Int.
+J.
+STD AIDS 31, 568--578.
 <https://doi.org/10.1177/0956462420913444>
 
-Nostlinger, C., Reyniers, T., Smekens, T.,
-Apers, H., Laga, M., Wouters, K., Vuylsteke, B., 2020. Drug use, depression and
-sexual risk behaviour: a syndemic among early pre-exposure prophylaxis (PrEP)
-adopters in Belgium?. AIDS Care 32, 57--64.
+Nostlinger, C., Reyniers, T., Smekens, T., Apers, H., Laga, M., Wouters, K., Vuylsteke, B., 2020.
+Drug use, depression and sexual risk behaviour: a syndemic among early pre-exposure prophylaxis (PrEP) adopters in Belgium?.
+AIDS Care 32, 57--64.
 <https://doi.org/10.1080/09540121.2020.1739218>
 
-O'Cleirigh, C., Pantalone, D.W.,
-Batchelder, A.W., Hatzenbuehler, M.L., Marquez, S.M., Grasso, C., Safren, S.A.,
-Mayer, K.H., 2018. Co-occurring psychosocial problems predict HIV status and
-increased health care costs and utilization among sexual minority men. J Behav
-Med 41, 450--457. <https://doi.org/10.1007/s10865-018-9913-z>
+O'Cleirigh, C., Pantalone, D.W., Batchelder, A.W., Hatzenbuehler, M.L., Marquez, S.M., Grasso, C., Safren, S.A., Mayer, K.H., 2018.
+Co-occurring psychosocial problems predict HIV status and increased health care costs and utilization among sexual minority men.
+J Behav Med 41, 450--457.
+<https://doi.org/10.1007/s10865-018-9913-z>
 
-Oginni, O.A., Mapayi, B.M., Afolabi, O.T.,
-Ebuenyi, I.D., Akinsulore, A., Mosaku, K.S., 2019. Association between risky
-sexual behavior and a psychosocial syndemic among nigerian men who have sex
-with men. J Gay Lesbian Ment Health, Journal of Gay & Lesbian Psychotherapy
-23, 168--185. <https://doi.org/10.1080/19359705.2018.1552640>
+Oginni, O.A., Mapayi, B.M., Afolabi, O.T., Ebuenyi, I.D., Akinsulore, A., Mosaku, K.S., 2019.
+Association between risky sexual behavior and a psychosocial syndemic among nigerian men who have sex with men.
+J Gay Lesbian Ment Health, Journal of Gay & Lesbian Psychotherapy 23, 168--185.
+<https://doi.org/10.1080/19359705.2018.1552640>
 
-Ogunbajo, A., Oke, T., Jin, H., Rashidi,
-W., Iwuagwu, S., Harper, G.W., Biello, K.B., Mimiaga, M.J., 2019. A syndemic of
-psychosocial health problems is associated with increased HIV sexual risk among
-Nigerian gay, bisexual, and other men who have sex with men (GBMSM). AIDS Care
-32, 337--342. <https://doi.org/10.1080/09540121.2019.1678722>
+Ogunbajo, A., Oke, T., Jin, H., Rashidi, W., Iwuagwu, S., Harper, G.W., Biello, K.B., Mimiaga, M.J., 2019.
+A syndemic of psychosocial health problems is associated with increased HIV sexual risk among Nigerian gay, bisexual, and other men who have sex with men (GBMSM).
+AIDS Care 32, 337--342.
+<https://doi.org/10.1080/09540121.2019.1678722>
 
-O'Leary, A., Jemmott  3rd, J.B., Stevens, R., Rutledge, S.E.,
-Icard, L.D., 2014. Optimism and education buffer the effects of syndemic
-conditions on HIV status among African American men who have sex with men. AIDS
-Behav 18, 2080--2088. <https://doi.org/10.1007/s10461-014-0708-0>
+O'Leary, A., Jemmott  3rd, J.B., Stevens, R., Rutledge, S.E., Icard, L.D., 2014.
+Optimism and education buffer the effects of syndemic conditions on HIV status among African American men who have sex with men.
+AIDS Behav 18, 2080--2088.
+<https://doi.org/10.1007/s10461-014-0708-0>
 
-Pantalone, D.W., Nelson, K.M., Batchelder,
-A.W., Chiu, C., Gunn, H.A., Horvath, K.J., 2020. A Systematic Review and
-Meta-Analysis of Combination Behavioral Interventions Co-Targeting Psychosocial
-Syndemics and HIV-Related Health Behaviors for Sexual Minority Men. J Sex Res
-57, 681--708. <https://doi.org/10.1080/00224499.2020.1728514>
+Pantalone, D.W., Nelson, K.M., Batchelder, A.W., Chiu, C., Gunn, H.A., Horvath, K.J., 2020.
+A Systematic Review and Meta-Analysis of Combination Behavioral Interventions Co-Targeting Psychosocial Syndemics and HIV-Related Health Behaviors for Sexual Minority Men.
+J Sex Res 57, 681--708.
+<https://doi.org/10.1080/00224499.2020.1728514>
 
-Pantalone, D.W., Valentine, S.E.,
-Woodward, E.N., O'Cleirigh, C., 2018. Syndemic Indicators Predict Poor
-Medication Adherence and Increased Health Care Utilization for Urban
-HIV-Positive Men Who Have Sex with Men. J Gay Lesbian Ment Health 22, 71--87.
+Pantalone, D.W., Valentine, S.E., Woodward, E.N., O'Cleirigh, C., 2018.
+Syndemic Indicators Predict Poor Medication Adherence and Increased Health Care Utilization for Urban HIV-Positive Men Who Have Sex with Men.
+J Gay Lesbian Ment Health 22, 71--87.
 <https://doi.org/10.1080/19359705.2017.1389794>
 
-Parsons, J.T., Grov, C., Golub, S.A.,
-2012. Sexual compulsivity, co-occurring psychosocial health problems, and HIV
-risk among gay and bisexual men: further evidence of a syndemic. Am J Public Health
-102, 156--162. <https://doi.org/10.2105/AJPH.2011.300284>
+Parsons, J.T., Grov, C., Golub, S.A., 2012.
+Sexual compulsivity, co-occurring psychosocial health problems, and HIV risk among gay and bisexual men: further evidence of a syndemic.
+Am J Public Health 102, 156--162.
+<https://doi.org/10.2105/AJPH.2011.300284>
 
-Parsons, J.T., Millar, B.M., Moody, R.L.,
-Starks, T.J., Rendina, H.J., Grov, C., 2017. Syndemic conditions and HIV
-transmission risk behavior among HIV-negative gay and bisexual men in a U.S. national
-sample. Health Psychol 36, 695--703. <https://doi.org/10.1037/hea0000509>
+Parsons, J.T., Millar, B.M., Moody, R.L., Starks, T.J., Rendina, H.J., Grov, C., 2017.
+Syndemic conditions and HIV transmission risk behavior among HIV-negative gay and bisexual men in a U.S.
+national sample.
+Health Psychol 36, 695--703.
+<https://doi.org/10.1037/hea0000509>
 
-Parsons, J.T., Rendina, H.J., Moody, R.L.,
-Ventuneac, A., Grov, C., 2015. Syndemic production and sexual
-compulsivity/hypersexuality in highly sexually active gay and bisexual men:
-further evidence for a three group conceptualization. Arch Sex Behav 44, 1903--1913.
+Parsons, J.T., Rendina, H.J., Moody, R.L., Ventuneac, A., Grov, C., 2015.
+Syndemic production and sexual compulsivity/hypersexuality in highly sexually active gay and bisexual men: further evidence for a three group conceptualization.
+Arch Sex Behav 44, 1903--1913.
 <https://doi.org/10.1007/s10508-015-0574-5>
 
-Perry, N.S., Nelson, K.M., Carey, M.P.,
-2019. Diversity of Psychosocial Syndemic Indicators and Associations with
-Sexual Behavior with Male and Female Partners Among Early Adolescent Sexual
-Minority Males. LGBT Health 6, 386--392. <https://doi.org/10.1089/lgbt.2019.0113>
+Perry, N.S., Nelson, K.M., Carey, M.P., 2019.
+Diversity of Psychosocial Syndemic Indicators and Associations with Sexual Behavior with Male and Female Partners Among Early Adolescent Sexual Minority Males.
+LGBT Health 6, 386--392.
+<https://doi.org/10.1089/lgbt.2019.0113>
 
-Pitpitan, E.V., Smith, L.R., Goodman-Meza,
-D., Torres, K., Semple, S.J., Strathdee, S.A., Patterson, T.L., 2016. "Outness"
-as a Moderator of the Association Between Syndemic Conditions and HIV
-Risk-Taking Behavior Among Men Who Have Sex with Men in Tijuana, Mexico. AIDS
-Behav 20, 431--438. <https://doi.org/10.1007/s10461-015-1172-1>
+Pitpitan, E.V., Smith, L.R., Goodman-Meza, D., Torres, K., Semple, S.J., Strathdee, S.A., Patterson, T.L., 2016.
+"Outness" as a Moderator of the Association Between Syndemic Conditions and HIV Risk-Taking Behavior Among Men Who Have Sex with Men in Tijuana, Mexico.
+AIDS Behav 20, 431--438.
+<https://doi.org/10.1007/s10461-015-1172-1>
 
-Pollard, A., Nadarzynski, T., Llewellyn,
-C., 2018. Syndemics of stigma, minority-stress, maladaptive coping, risk
-environments and littoral spaces among men who have sex with men using chemsex.
-Cult Health Sex 20, 411--427. <https://doi.org/10.1080/13691058.2017.1350751>
+Pollard, A., Nadarzynski, T., Llewellyn, C., 2018.
+Syndemics of stigma, minority-stress, maladaptive coping, risk environments and littoral spaces among men who have sex with men using chemsex.
+Cult Health Sex 20, 411--427.
+<https://doi.org/10.1080/13691058.2017.1350751>
 
-Quinn, B., Gorbach, P.M., Okafor, C.N.,
-Heinzerling, K.G., Shoptaw, S., 2020. Investigating possible syndemic
-relationships between structural and drug use factors, sexual HIV transmission
-and viral load among men of colour who have sex with men in Los Angeles County.
-Drug Alcohol Rev. 39, 116--127. <https://doi.org/10.1111/dar.13026>
+Quinn, B., Gorbach, P.M., Okafor, C.N., Heinzerling, K.G., Shoptaw, S., 2020.
+Investigating possible syndemic relationships between structural and drug use factors, sexual HIV transmission and viral load among men of colour who have sex with men in Los Angeles County.
+Drug Alcohol Rev.
+39, 116--127.
+<https://doi.org/10.1111/dar.13026>
 
-Quinn, K.G., 2019. Applying an
-intersectional framework to understand syndemic conditions among young Black
-gay, bisexual, and other men who have sex with men. Soc Sci Med.
+Quinn, K.G., 2019.
+Applying an intersectional framework to understand syndemic conditions among young Black gay, bisexual, and other men who have sex with men.
+Soc Sci Med.
 <https://doi.org/10.1016/j.socscimed.2019.112779>
 
-Reed, S.J., Miller, R.L., 2016. Thriving
-and Adapting: Resilience, Sense of Community, and Syndemics among Young Black
-Gay and Bisexual Men. Am J Community Psychol 57, 129--143.
+Reed, S.J., Miller, R.L., 2016.
+Thriving and Adapting: Resilience, Sense of Community, and Syndemics among Young Black Gay and Bisexual Men.
+Am J Community Psychol 57, 129--143.
 <https://doi.org/10.1002/ajcp.12028>
 
-Reisner, S.L., White Hughto, J.M., Pardee,
-D., Sevelius, J., 2016. Syndemics and gender affirmation: HIV sexual risk in
-female-to-male trans masculine adults reporting sexual contact with cisgender
-males. Int J STD AIDS 27, 955--966. <https://doi.org/10.1177/0956462415602418>
+Reisner, S.L., White Hughto, J.M., Pardee, D., Sevelius, J., 2016.
+Syndemics and gender affirmation: HIV sexual risk in female-to-male trans masculine adults reporting sexual contact with cisgender males.
+Int J STD AIDS 27, 955--966.
+<https://doi.org/10.1177/0956462415602418>
 
-Rooney, B.M., Tulloch, T.G., Blashill,
-A.J., 2018. Psychosocial Syndemic Correlates of Sexual Compulsivity Among Men
-Who Have Sex with Men: A Meta-Analysis. Arch Sex Behav 47, 75--93.
+Rooney, B.M., Tulloch, T.G., Blashill, A.J., 2018.
+Psychosocial Syndemic Correlates of Sexual Compulsivity Among Men Who Have Sex with Men: A Meta-Analysis.
+Arch Sex Behav 47, 75--93.
 <https://doi.org/10.1007/s10508-017-1032-3>
 
-Safren, S.A., Blashill, A.J., Lee, J.S., O'Cleirigh,
-C., Tomassili, J., Biello, K.B., Mimiaga, M.J., Mayer, K.H., 2018. Condom-use
-self-efficacy as a mediator between syndemics and condomless sex in men who
-have sex with men (MSM). Health Psychol 37, 820--827.
+Safren, S.A., Blashill, A.J., Lee, J.S., O'Cleirigh, C., Tomassili, J., Biello, K.B., Mimiaga, M.J., Mayer, K.H., 2018.
+Condom-use self-efficacy as a mediator between syndemics and condomless sex in men who have sex with men (MSM).
+Health Psychol 37, 820--827.
 <https://doi.org/10.1037/hea0000617>
 
-Santos, G.-M., Do, T., Beck, J., Makofane,
-K., Arreola, S., Pyun, T., Hebert, P., Wilson, P.A., Ayala, G., 2014. Syndemic
-conditions associated with increased HIV risk in a global sample of men who
-have sex with men. Sex Transm Infect 90, 250--253. <https://doi.org/10.1136/sextrans-2013-051318>
+Santos, G.-M., Do, T., Beck, J., Makofane, K., Arreola, S., Pyun, T., Hebert, P., Wilson, P.A., Ayala, G., 2014.
+Syndemic conditions associated with increased HIV risk in a global sample of men who have sex with men.
+Sex Transm Infect 90, 250--253.
+<https://doi.org/10.1136/sextrans-2013-051318>
 
-Scheer, J.R., Clark, K.A., Maiolatesi,
-A.J., Pachankis, J.E., 2021. Syndemic profiles and sexual minority men's
-hiv-risk behavior: A latent class analysis. Arch Sex Behav.
+Satyanarayana, S., Safren, S.A., Rogers, B.G., Bainter, S.A., Christopoulos, K.A., Fredericksen, R.J., Mathews, W.C., Moore, R.D., Mugavero, M.J., Napravnik, S., Carrico, A.W., Mimiaga, M.J., Mayer, K.H., Crane, H.M., 2021.
+Estimating HIV transmissions in a large U.S.
+clinic-based sample: effects of time and syndemic conditions.
+J Int AIDS Soc 24, e25679.
+<https://doi.org/10.1002/jia2.25679>
+
+Scheer, J.R., Clark, K.A., Maiolatesi, A.J., Pachankis, J.E., 2021.
+Syndemic profiles and sexual minority men's hiv-risk behavior: A latent class analysis.
+Arch Sex Behav.
 <https://doi.org/10.1007/s10508-020-01850-4>
 
-Semple, S.J., Stockman, J.K.,
-Goodman-Meza, D., Pitpitan, E.V., Strathdee, S.A., Chavarin, C.V., Rangel, G.,
-Torres, K., Patterson, T.L., 2017. Correlates of Sexual Violence Among Men Who
-Have Sex With Men in Tijuana, Mexico. Arch Sex Behav 46, 1011--1023.
+Semple, S.J., Stockman, J.K., Goodman-Meza, D., Pitpitan, E.V., Strathdee, S.A., Chavarin, C.V., Rangel, G., Torres, K., Patterson, T.L., 2017.
+Correlates of Sexual Violence Among Men Who Have Sex With Men in Tijuana, Mexico.
+Arch Sex Behav 46, 1011--1023.
 <https://doi.org/10.1007/s10508-016-0747-x>
 
-Shuper, P.A., Joharchi, N., Bogoch, I.I.,
-Loutfy, M., Crouzat, F., El-Helou, P., Knox, D.C., Woodward, K., Rehm, J.,
-2020. Alcohol consumption, substance use, and depression in relation to HIV
-Pre-Exposure Prophylaxis (PrEP) nonadherence among gay, bisexual, and other
-men-who-have-sex-with-men. BMC Public Health 20, 1782.
+Shuper, P.A., Joharchi, N., Bogoch, I.I., Loutfy, M., Crouzat, F., El-Helou, P., Knox, D.C., Woodward, K., Rehm, J., 2020.
+Alcohol consumption, substance use, and depression in relation to HIV Pre-Exposure Prophylaxis (PrEP) nonadherence among gay, bisexual, and other men-who-have-sex-with-men.
+BMC Public Health 20, 1782.
 <https://doi.org/10.1186/s12889-020-09883-z>
 
-Stall, R., Mills, T.C., Williamson, J.,
-Hart, T., Greenwood, G., Paul, J., Pollack, L., Binson, D., Osmond, D.,
-Catania, J.A., 2003. Association of Co-Occurring Psychosocial Health Problems
-and Increased Vulnerability to HIV/AIDS among Urban Men Who Have Sex with Men.
-Am J Public Health 93, 939--942. <https://doi.org/10.2105/AJPH.93.6.939>
+Stall, R., Mills, T.C., Williamson, J., Hart, T., Greenwood, G., Paul, J., Pollack, L., Binson, D., Osmond, D., Catania, J.A., 2003.
+Association of Co-Occurring Psychosocial Health Problems and Increased Vulnerability to HIV/AIDS among Urban Men Who Have Sex with Men.
+Am J Public Health 93, 939--942.
+<https://doi.org/10.2105/AJPH.93.6.939>
 
-Starks, T.J., Millar, B.M., Eggleston, J.J.,
-Parsons, J.T., 2014. Syndemic factors associated with HIV risk for gay and
-bisexual men: comparing latent class and latent factor modeling. AIDS Behav 18,
-2075--2079. <https://doi.org/10.1007/s10461-014-0841-9>
+Starks, T.J., Millar, B.M., Eggleston, J.J., Parsons, J.T., 2014.
+Syndemic factors associated with HIV risk for gay and bisexual men: comparing latent class and latent factor modeling.
+AIDS Behav 18, 2075--2079.
+<https://doi.org/10.1007/s10461-014-0841-9>
 
-Starks, T.J., Tuck, A.N., Millar, B.M.,
-Parsons, J.T., 2016. Linking Syndemic Stress and Behavioral Indicators of Main
-Partner HIV Transmission Risk in Gay Male Couples. AIDS Behav 20, 439--448.
+Starks, T.J., Tuck, A.N., Millar, B.M., Parsons, J.T., 2016.
+Linking Syndemic Stress and Behavioral Indicators of Main Partner HIV Transmission Risk in Gay Male Couples.
+AIDS Behav 20, 439--448.
 <https://doi.org/10.1007/s10461-015-1248-y>
 
-Storholm, E.D., Halkitis, P.N., Siconolfi,
-D.E., Moeller, R.W., 2011. Cigarette smoking as part of a syndemic among young
-men who have sex with men ages 13-29 in New York City. J Urban Health 88, 663--676.
+Storholm, E.D., Halkitis, P.N., Siconolfi, D.E., Moeller, R.W., 2011.
+Cigarette smoking as part of a syndemic among young men who have sex with men ages 13-29 in New York City.
+J Urban Health 88, 663--676.
 <https://doi.org/10.1007/s11524-011-9563-8>
@@
 Sullivan, M.C., Eaton, L.A., 2020.
-Intersecting barriers to prep awareness and uptake in black men who have sex
-with men in atlanta, ga: A syndemic perspective. Int J Behav Med.
+Intersecting barriers to prep awareness and uptake in black men who have sex with men in atlanta, ga: A syndemic perspective.
+Int J Behav Med.
 <https://doi.org/10.1007/s12529-020-09925-1>
 
-Tan, D.H.S., Leon-Carlyle, M., Mills, R.,
-Moses, E., Carvalhal, A., 2016. Self-administered screening for syndemic mental
-health problems should be routinely implemented among MSM PrEP users. J Gay
-Lesbian Ment Health, Journal of Gay & Lesbian Mental Health 20, 13--20.
+Tan, D.H.S., Leon-Carlyle, M., Mills, R., Moses, E., Carvalhal, A., 2016.
+Self-administered screening for syndemic mental health problems should be routinely implemented among MSM PrEP users.
+J Gay Lesbian Ment Health, Journal of Gay & Lesbian Mental Health 20, 13--20.
 <https://doi.org/10.1080/19359705.2015.1105765>
 
-Tomori, C., McFall, A.M., Solomon, S.S.,
-Srikrishnan, A.K., Anand, S., Balakrishnan, P., Mehta, S.H., Celentano, D.D.,
-2018. Is there synergy in syndemics? Psychosocial conditions and sexual risk
-among men who have sex with men in India. Soc Sci Med 206, 110--116.
+Tapia, G.R., Glynn, T.R., Miller, C., Manuzak, J.A., Broedlow, C.A., Mcgaugh, A., Cherenack, E.M., Bauermeister, J.A., Grov, C., Dilworth, S.E., Parisi, R., Martinez, D., Klatt, N.R., Carrico, A.W., 2021.
+Syndemics and preexposure prophylaxis are independently associated with rectal immune dysregulation in sexual minority men.
+AIDS 35, 1295--1300.
+<https://doi.org/10.1097/QAD.0000000000002866>
+
+Tomori, C., McFall, A.M., Solomon, S.S., Srikrishnan, A.K., Anand, S., Balakrishnan, P., Mehta, S.H., Celentano, D.D., 2018.
+Is there synergy in syndemics?
+Psychosocial conditions and sexual risk among men who have sex with men in India.
+Soc Sci Med 206, 110--116.
 <https://doi.org/10.1016/j.socscimed.2018.03.032>
 
-Tulloch, T.G., Rotondi, N.K., Ing, S.,
-Myers, T., Calzavara, L.M., Loutfy, M.R., Hart, T.A., 2015. Retrospective
-reports of developmental stressors, syndemics, and their association with
-sexual risk outcomes among gay men. Arch Sex Behav 44, 1879--1889.
+Tulloch, T.G., Rotondi, N.K., Ing, S., Myers, T., Calzavara, L.M., Loutfy, M.R., Hart, T.A., 2015.
+Retrospective reports of developmental stressors, syndemics, and their association with sexual risk outcomes among gay men.
+Arch Sex Behav 44, 1879--1889.
 <https://doi.org/10.1007/s10508-015-0479-3>
 
-Turpin, R.E., Dyer, T.V., Dangerfield,
-D.T. 2nd, Liu, H., Mayer, K.H., 2020a. Syndemic latent transition analysis in
-the HPTN 061 cohort: Prospective interactions between trauma, mental health,
-social support, and substance use. Drug Alcohol Depend 214.
+Turpin, R.E., Dyer, T.V., Dangerfield, D.T.
+2nd, Liu, H., Mayer, K.H., 2020a.
+Syndemic latent transition analysis in the HPTN 061 cohort: Prospective interactions between trauma, mental health, social support, and substance use.
+Drug Alcohol Depend 214.
 <https://doi.org/10.1016/j.drugalcdep.2020.108106>
 
-Turpin, R.E., Salerno, J.P., Rosario,
-A.D., Boekeloo, B., 2020b. Victimization, Substance Use, Depression, and Sexual
-Risk in Adolescent Males Who Have Sex with Males: A Syndemic Latent Profile
-Analysis. Arch Sex Behav. <https://doi.org/10.1007/s10508-020-01685-z>
+Turpin, R.E., Salerno, J.P., Rosario, A.D., Boekeloo, B., 2020b.
+Victimization, Substance Use, Depression, and Sexual Risk in Adolescent Males Who Have Sex with Males: A Syndemic Latent Profile Analysis.
+Arch Sex Behav.
+<https://doi.org/10.1007/s10508-020-01685-z>
 
-Van den Berghe, W., Nöstlinger, C., Laga,
-M., 2014. Syndemic and other risk factors for unprotected anal intercourse
-among an online sample of belgian HIV negative men who have sex with men. AIDS
-Behav 18, 50--58. <https://doi.org/10.1007/s10461-013-0516-y>
+Van den Berghe, W., Nöstlinger, C., Laga, M., 2014.
+Syndemic and other risk factors for unprotected anal intercourse among an online sample of belgian HIV negative men who have sex with men.
+AIDS Behav 18, 50--58.
+<https://doi.org/10.1007/s10461-013-0516-y>
 
-Walters, S.M., Braksmajer, A., Coston, B.,
-Yoon, I., Grov, C., Downing, M.J., Teran, R., Hirshfield, S., 2020. A Syndemic
-Model of Exchange Sex Among HIV-Positive Men Who Have Sex With Men. Arch Sex
-Behav 49, 1965--1978. <https://doi.org/10.1007/s10508-020-01628-8>
+Walters, S.M., Braksmajer, A., Coston, B., Yoon, I., Grov, C., Downing, M.J., Teran, R., Hirshfield, S., 2020.
+A Syndemic Model of Exchange Sex Among HIV-Positive Men Who Have Sex With Men.
+Arch Sex Behav 49, 1965--1978.
+<https://doi.org/10.1007/s10508-020-01628-8>
 
-Wang, Ying, Wang, Z., Jia, M., Liang, A.,
-Yuan, D., Sun, Z., Gan, F., Wang, Yichen, Cai, Y., Zhang, Z., 2017. Association
-between a syndemic of psychosocial problems and unprotected anal intercourse
-among men who have sex with men in Shanghai, China. BMC Infect Dis 17, 46.
+Wang, Ying, Wang, Z., Jia, M., Liang, A., Yuan, D., Sun, Z., Gan, F., Wang, Yichen, Cai, Y., Zhang, Z., 2017.
+Association between a syndemic of psychosocial problems and unprotected anal intercourse among men who have sex with men in Shanghai, China.
+BMC Infect Dis 17, 46.
 <https://doi.org/10.1186/s12879-016-2132-8>
 
-Wang, Z., Zhao, X., Zhang, Z., Luo, M.,
-Shen, Q., Dong, Y., Wang, Y., Cai, Y., 2018. Co-Occurring Psychosocial Problems
-and Multiple Sexual Partners among Men Who Have Sex with Men in Shanghai,
-China: A Syndemic Approach. J Sex Res 55, 892--901.
+Wang, Z., Zhao, X., Zhang, Z., Luo, M., Shen, Q., Dong, Y., Wang, Y., Cai, Y., 2018.
+Co-Occurring Psychosocial Problems and Multiple Sexual Partners among Men Who Have Sex with Men in Shanghai, China: A Syndemic Approach.
+J Sex Res 55, 892--901.
 <https://doi.org/10.1080/00224499.2017.1399333>
 
-Woodward, E.N., Banks, R.J., Marks, A.K.,
-Pantalone, D.W., 2017. Identifying Resilience Resources for HIV Prevention
-Among Sexual Minority Men: A Systematic Review. AIDS Behav 2860--2873.
+Woodward, E.N., Banks, R.J., Marks, A.K., Pantalone, D.W., 2017.
+Identifying Resilience Resources for HIV Prevention Among Sexual Minority Men: A Systematic Review.
+AIDS Behav 2860--2873.
 <https://doi.org/10.1007/s10461-016-1608-2>
 
-Wu, E., 2018. Childhood sexual abuse among
-Black men who have sex with men: A cornerstone of a syndemic? PLoS ONE 13,
-e0206746--e0206746. <https://doi.org/10.1371/journal.pone.0206746>
+Wu, E., 2018. Childhood sexual abuse among Black men who have sex with men: A cornerstone of a syndemic? PLoS ONE 13, e0206746--e0206746. <https://doi.org/10.1371/journal.pone.0206746>
 
-Yu, F., Nehl, E.J., Zheng, T., He, N.,
-Berg, C.J., Lemieux, A.F., Lin, L., Tran, A., Sullivan, P.S., Wong, F.Y., 2013.
-A syndemic including cigarette smoking and sexual risk behaviors among a sample
-of MSM in Shanghai, China. Drug Alcohol Depend 132, 265--270.
+Yu, F., Nehl, E.J., Zheng, T., He, N., Berg, C.J., Lemieux, A.F., Lin, L., Tran, A., Sullivan, P.S., Wong, F.Y., 2013.
+A syndemic including cigarette smoking and sexual risk behaviors among a sample of MSM in Shanghai, China.
+Drug Alcohol Depend 132, 265--270.
 <https://doi.org/10.1016/j.drugalcdep.2013.02.016>
 
-Zepf, R., Greene, M., Hessol, N.A.,
-Johnson, M.O., Santos, G.M., John, M.D., Dawson-Rose, C., 2020. Syndemic
-conditions and medication adherence in older men living with HIV who have sex
-with men. AIDS Care 32, 1610--1616.
+Zepf, R., Greene, M., Hessol, N.A., Johnson, M.O., Santos, G.M., John, M.D., Dawson-Rose, C., 2020.
+Syndemic conditions and medication adherence in older men living with HIV who have sex with men.
+AIDS Care 32, 1610--1616.
 <https://doi.org/10.1080/09540121.2020.1772954>
@@
 Zhang, J., O'Leary, A., Jemmott  3rd, J.B., Icard, L.D., Rutledge, S.E., 2019.
-Syndemic conditions predict lower levels of physical activity among African
-American men who have sex with men: A prospective survey study. PLOS One 14,
-e0213439--e0213439. <https://doi.org/10.1371/journal.pone.0213439>
+Syndemic conditions predict lower levels of physical activity among African American men who have sex with men: A prospective survey study.
+PLOS One 14, e0213439--e0213439.
+<https://doi.org/10.1371/journal.pone.0213439>
 
@@
 
-### B. Measurement tables
+## C. Measurement tables
 

### 2022-01-13 _bookdown_files/index.Rmd
Complete draft

@@
 - "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
-- "^1^ Corresponding author at : General Practice Department - Primary Care and Health Research Unit, MD - PhD student,  University of Liège, Liège, Belgium <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
-- "^2^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, research assistant, University of Liège, Liège, Belgium <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
-- "^3^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, lecturer, University of Liège, Liège, Belgium <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
-- "^4^ General Practice Department - Primary Care and Health Research Unit, Postdoctoral Researcher,  University of Liège, Liège, Belgium <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
+- "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
+- "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
+- "^3^  <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
+- "^4^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
+- "*corresponding author: maxence.ouafik@uliege.be https://orcid.org/0000-0002-9795-5721"
 

### 2022-01-13 Scripts/create_framework_data.R

@@ -1,11 +1,12 @@
 .framework_quantitative <- summary_quantitative %>%
-  select(1:3, 286:290) %>%
+  select(1:3, 291:296) %>%
   unite("reference", 1:3, na.rm = T, sep = " ") %>%
   filter(!is.na(minority_stress)|!is.na(social_cognitive)|
            !is.na(salutogenesis)|
            !is.na(resilience)|
-           !is.na(intersectionality)) %>%
-  unite("additional_framework", 2:6, sep = " ", na.rm = T) 
+           !is.na(intersectionality)|
+           !is.na(ecological)) %>%
+  unite("additional_framework", 2:7, sep = " ", na.rm = T) 
   
 
 .framework_qualitative <- summary_qualitative %>%

### 2022-01-13 Scripts/create_outcomes_data.R

@@ -1,9 +1,9 @@
 .outcomes <- summary_quantitative %>%
-  select(1:3, 182:201) %>%
+  select(1:3, 184:205) %>%
   unite("reference", 1:3, sep =" ", na.rm = T)
 
 .outcomes_measurement <- summary_quantitative %>%
-  select(1:3, 202:251) %>%
+  select(1:3, 206:255) %>%
   unite("reference", 1:3, sep =" ", na.rm = T)
 
 .outcomes_sex_risk_measurement <- .outcomes_measurement %>%
@@ -24,4 +24,6 @@
   sum(!is.na(.outcomes$outcome_HIV)) +
   sum(!is.na(.outcomes$outcome_VL)) +
   sum(!is.na(.outcomes$outcome_screening)) +
-  sum(!is.na(.outcomes$outcome_HIV_care))
+  sum(!is.na(.outcomes$outcome_HIV_care)) +
+  sum(!is.na(.outcomes$transmission)) +
+  sum(!is.na(.outcomes$rectal_cytokines))

### 2022-01-13 Scripts/create_statistics_data.R

@@ -12,7 +12,7 @@
   
 
 .score_data <- summary_quantitative %>%
-  select(259:274, 276:278) %>%
-  unite(col = "statistics", 1:19, sep = ", ", na.rm = TRUE) %>%
+  select(263:278, 280:283) %>%
+  unite(col = "statistics", 1:20, sep = ", ", na.rm = TRUE) %>%
   filter(statistics == "score") %>%
   nrow()

### 2022-01-13 Scripts/supplementary_tables/CSA.R

@@ -1,7 +1,7 @@
 source("./scripts/supplementary_tables/general.R")
 
 .CSA_measurement <- measurement %>%
-  select(c(1, 61:63)) %>%
+  select(c(1, 63:65)) %>%
   filter(!is.na(CSA_type)) %>%
   add_count(CSA_type, name = "type_n") %>%
   add_count(CSA_scale_criteria, name = "criteria_n") %>%
@@ -37,16 +37,12 @@ source("./scripts/supplementary_tables/general.R")
   footnote(i = 1, j = 3, part = "header", 
            value = as_paragraph("Finkelhor definition : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (Finkelhor 1994)")) %>%
   merge_v(j = c(1:3, 5), part = "body") %>%
-  merge_at(j = 4, i = 1:6, part = "body") %>%
-  merge_at(j = 4, i = 7:12, part = "body") %>%
-  merge_at(j = 4, i = 13:16, part = "body") %>%
-  merge_at(j = 4, i = 17:18, part = "body") %>%
-  merge_at(j = 4, i = 29:31, part = "body") %>%
-  merge_at(j = 4, i = 32:33, part = "body") %>%
-  merge_h_range(i = 1:28, j1 = 3, j2=5, part = "body") %>%
+  merge_at(j = 4, i = 32:34, part = "body") %>%
+  merge_at(j = 4, i = 35:36, part = "body") %>%
+  merge_h_range(i = 1:31, j1 = 3, j2=5, part = "body") %>%
   hline(j = 3, border = .borders, part = "body") %>%
   hline(j = 5:6, border = .borders, part = "body") %>%
-  hline(i = 28, border = .big.border, part = "body") %>%
+  hline(i = 31, border = .big.border, part = "body") %>%
   align(align = "center", j=1:5, part = "body") %>%
   vline(j = 5, border = .borders, part = "body") %>%
   align(align = "right", j = 6, part = "body") %>%

### 2022-01-13 Scripts/supplementary_tables/IPV.R

@@ -2,7 +2,7 @@ source("./scripts/supplementary_tables/general.R")
 
 
 .IPV_measurement <- measurement %>%
-  select(c(1, 24:34)) %>%
+  select(c(1, 25:35)) %>%
   filter(!is.na(IPV_type)) %>%
   add_count(IPV_type, name = "type_n") %>%
   unite(col = IPV_scale_criteria, 3:11, sep = ", ", na.rm = T) %>%
@@ -14,11 +14,11 @@ source("./scripts/supplementary_tables/general.R")
 
 
 .IPV_prevalence <- list()
-for (i in 25:29) {
-  .IPV_prevalence$sum[[i-24]] <- sum(!is.na(measurement[i]))
-  .IPV_prevalence$perc[[i-24]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$IPV_type))))
-  names(.IPV_prevalence[["sum"]])[[i-24]] <- names(measurement[i])
-  names(.IPV_prevalence[["perc"]])[[i-24]] <- names(measurement[i])
+for (i in 26:30) {
+  .IPV_prevalence$sum[[i-25]] <- sum(!is.na(measurement[i]))
+  .IPV_prevalence$perc[[i-25]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$IPV_type))))
+  names(.IPV_prevalence[["sum"]])[[i-25]] <- names(measurement[i])
+  names(.IPV_prevalence[["perc"]])[[i-25]] <- names(measurement[i])
 }
 .IPV_prevalence$footer <- c(paste0("Physical intimate partner violence: ", 
                                   .IPV_prevalence[["sum"]][["physical IPV"]],
@@ -73,17 +73,17 @@ for (i in 25:29) {
                     reference = "References") %>%
   add_footer_lines(values = .IPV_prevalence[["footer"]]) %>%
   merge_v(j = c(1, 2, 3, 5), part = "body") %>%
-  merge_at(j = 4, i = 1:12, part = "body") %>%
-  merge_at(j = 4, i = 13:20, part = "body") %>%
-  merge_at(j = 4, i = 21:27, part = "body") %>%
-  merge_at(j = 4, i = 28:33, part = "body") %>%
-  merge_at(j = 4, i = 34:35, part = "body") %>%
+  merge_at(j = 4, i = 1:14, part = "body") %>%
+  merge_at(j = 4, i = 15:22, part = "body") %>%
[…]

### 2022-01-13 Scripts/supplementary_tables/anxiety.R

@@ -2,9 +2,9 @@ source("./scripts/supplementary_tables/general.R")
 
 .anxiety_measurement <- measurement %>%
   filter(!is.na(anxiety_type)) %>%
-  select(c(1, 42:45, 47:56)) %>%
+  select(c(1, 43:46, 48:58)) %>%
   unite(col = disorder, 2:5, sep = ", ", na.rm = T) %>%
-  unite(col = criteria, 3:11, sep = ", ", na.rm = T) %>%
+  unite(col = criteria, 3:12, sep = ", ", na.rm = T) %>%
   add_count(disorder, name = "disorder_n") %>%
   add_count(criteria, name = "criteria_n") %>%
   relocate("reference", .after = "anxiety_cutoff_period") %>%

### 2022-01-13 Scripts/supplementary_tables/binge.R

@@ -1,7 +1,7 @@
 source("./scripts/supplementary_tables/general.R")
 
 .binge_measurement <- measurement %>%
-  select(c(1, 35:36)) %>%
+  select(c(1, 36:37)) %>%
   filter(!is.na(binge_episodes)) %>%
   add_count(binge_episodes, name = "episodes_n") %>%
   relocate("episodes_n", .after = "binge_episodes") %>%

### 2022-01-13 Scripts/supplementary_tables/depression.R

@@ -35,32 +35,31 @@ source("./scripts/supplementary_tables/general.R")
                     depression_cutoff = "Cutoff used",
                     reference = "References") %>%
   merge_v(j = c(1, 2, 3), part = "body") %>%
-  merge_at(j = 4, i = 1:24, part = "body") %>%
-  merge_at(j = 4, i = 25:34, part = "body") %>%
-  merge_at(j = 4, i = 35:42, part = "body") %>%
-  merge_at(j = 4, i = 43:47, part = "body") %>%
-  merge_at(j = 4, i = 48:51, part = "body") %>%
-  merge_at(j = 4, i = 52:54, part = "body") %>%
-  merge_at(j = 4, i = 55:57, part = "body") %>%
-  merge_at(j = 4, i = 58:59, part = "body") %>%
-  merge_at(j = 4, i = 60:61, part = "body") %>%
-  merge_at(j = 4, i = 67:69, part = "body") %>%
-  merge_at(j = 4, i = 70:71, part = "body") %>%
-  merge_at(j = 4, i = 72:73, part = "body") %>%
-  merge_at(j = 5, i = 1:11, part = "body") %>%
-  merge_at(j = 5, i = 1:11, part = "body") %>%
-  merge_at(j = 5, i = 13:20, part = "body") %>%
-  merge_at(j = 5, i = 22:24, part = "body") %>%
-  merge_at(j = 5, i = 25:34, part = "body") %>%
-  merge_at(j = 5, i = 35:38, part = "body") %>%
-  merge_at(j = 5, i = 40:41, part = "body") %>%
-  merge_at(j = 5, i = 45:47, part = "body") %>%
-  merge_at(j = 5, i = 52:54, part = "body") %>%
-  merge_at(j = 5, i = 56:57, part = "body") %>%
-  merge_h_range(i = 66:76, j1 = 3, j2=5, part = "body") %>%
+  merge_at(j = 4, i = 1:26, part = "body") %>%
+  merge_at(j = 4, i = 27:37, part = "body") %>%
+  merge_at(j = 4, i = 38:46, part = "body") %>%
+  merge_at(j = 4, i = 47:51, part = "body") %>%
+  merge_at(j = 4, i = 52:55, part = "body") %>%
+  merge_at(j = 4, i = 56:58, part = "body") %>%
+  merge_at(j = 4, i = 59:61, part = "body") %>%
+  merge_at(j = 4, i = 62:63, part = "body") %>%
[…]

### 2022-01-13 Scripts/supplementary_tables/general.R

@@ -2,7 +2,7 @@ library(flextable)
 library(officer)
 
 measurement <- summary_quantitative %>%
-  select (c(1:3, 57:179))
+  select (c(1:3, 57:183))
 measurement <- measurement %>%
   unite(col = "author_year", c(authors, year), sep = " ") %>%
   unite(col = "reference", c(author_year, letter), sep = "", na.rm = TRUE)

### 2022-01-13 Scripts/supplementary_tables/polysubstance.R

@@ -1,7 +1,7 @@
 source("./scripts/supplementary_tables/general.R")
 
 .polysubstance_measurement <- measurement %>%
-  select(c(1, 64:66)) %>%
+  select(c(1, 66:68)) %>%
   filter(!is.na(polysubstance_number)) %>%
   add_count(polysubstance_number, name = "number_n") %>%
   relocate("number_n", .after = "polysubstance_number") %>%
@@ -30,6 +30,7 @@ source("./scripts/supplementary_tables/general.R")
   merge_at(j = 3, i = 5:16, part = "body") %>%
   merge_at(j = 3, i = 17:18, part = "body") %>%
   merge_at(j = 3, i = 19:25, part = "body") %>%
+  merge_at(j = 3, i = 26:27, part = "body") %>%
   hline(j = c(1, 3:5), border = .borders, part = "body") %>%
   align(align = "center", j=1:5, part = "body") %>%
   vline(j = 3:4, border = .borders, part = "body") %>%

### 2022-01-13 Scripts/supplementary_tables/reference_quantitative.R

@@ -1,5 +1,5 @@
 reference_table_quantitative <- summary_quantitative %>%
-  select(1:6, 8, 10, 11:56, 182:201, 252:254, 259:278, 285) 
+  select(1:6, 8, 10, 11:56, 184:205, 256:258, 263:283, 290) 
 
 # Human readable data for subpopulation
 reference_table_quantitative[reference_table_quantitative == "AMSM"] <- "Adolescent MSM"
@@ -67,6 +67,9 @@ reference_table_quantitative[reference_table_quantitative == "outcome_MSMW"] <- 
 reference_table_quantitative[reference_table_quantitative == "outcome_syndemic"] <- "syndemic conditions as the outcomes"
 reference_table_quantitative[reference_table_quantitative == "outcome_help"] <- "help-seeking behaviors"
 reference_table_quantitative[reference_table_quantitative == "outcome_substance"] <- "substance use"
+reference_table_quantitative[reference_table_quantitative == "transmission"] <- "HIV transmission"
+reference_table_quantitative[reference_table_quantitative == "rectal_cytokines"] <- "elevation in rectal cytokines/chemokines"
+
 
 #Human readable data for statistics
 reference_table_quantitative[reference_table_quantitative == "score"] <- "regression analysis using a summation score"
@@ -89,6 +92,7 @@ reference_table_quantitative[reference_table_quantitative == "not_interaction"] 
 reference_table_quantitative[reference_table_quantitative == "hierarchical"] <- "hierarchical negative binomial regression"
 reference_table_quantitative[reference_table_quantitative == "logistic"] <- "multivariate logistic regression"
 reference_table_quantitative[reference_table_quantitative == "biserial"] <- "point-biserial correlation"
+reference_table_quantitative[reference_table_quantitative == "synergy_factor"] <- "synergy factor analysis"
 
 
 reference_table_quantitative <- reference_table_quantitative %>%
@@ -101,8 +105,8 @@ reference_table_quantitative <- reference_table_quantitative %>%
                           intervention_control), sep = " ", na.rm = TRUE) %>%
   unite(col = "subpopulation", c(subpopulation, disaggregated), sep = ", ", na.rm = TRUE) %>%
   unite(col = "syndemic_conditions", 5:50, sep = ", ", na.rm = TRUE) %>%
[…]

### 2022-01-13 Scripts/supplementary_tables/substance.R

@@ -76,15 +76,15 @@ for (i in 5:12) {
                     reference = "References") %>%
   add_footer_lines(values = .substances_prev[["footer"]]) %>%
   merge_v(j = c(1, 3), part = "body") %>%
-  merge_at(j = 2, i = 1:6, part = "body") %>%
-  merge_at(j = 2, i = 7:10, part = "body") %>%
-  merge_at(j = 2, i = 11:13, part = "body") %>%
-  merge_at(j = 2, i = 14:16, part = "body") %>%
-  merge_at(j = 2, i = 17:18, part = "body") %>%
-  merge_at(j = 2, i = 19:20, part = "body") %>%
+  merge_at(j = 2, i = 1:9, part = "body") %>%
+  merge_at(j = 2, i = 10:13, part = "body") %>%
+  merge_at(j = 2, i = 14:17, part = "body") %>%
+  merge_at(j = 2, i = 18:20, part = "body") %>%
   merge_at(j = 2, i = 21:22, part = "body") %>%
+  merge_at(j = 2, i = 23:24, part = "body") %>%
+  merge_at(j = 2, i = 25:26, part = "body") %>%
+  merge_at(j = 2, i = 27:28, part = "body") %>%
   hline(j = c(1, 3, 4), border = .borders, part = "body") %>%
-  hline(i = 43, border = .big.border, part = "body") %>%
   align(align = "center", j=1:4, part = "body") %>%
   vline(j = 3, border = .borders, part = "body") %>%
   align(align = "right", j = 4, part = "body") %>%

### 2022-01-13 Scripts/supplementary_tables/violence.R

@@ -1,19 +1,21 @@
 source("./scripts/supplementary_tables/general.R")
 
 .violence_measurement <- measurement %>%
-  select(c(1, 18:23)) %>%
+  select(c(1, 18:24)) %>%
   filter(!is.na(violence_period)) %>%
-  unite(col = violence_criteria, 2:6, sep = ", ", na.rm = T) %>%
+  unite(col = violence_criteria, 2:7, sep = ", ", na.rm = T) %>%
   add_count(violence_criteria, name = "criteria_n") %>%
   relocate("criteria_n", .after = "violence_criteria") %>%
   relocate("reference", .after = "violence_period") %>%
   arrange(desc(criteria_n), desc(violence_criteria), desc(violence_period))
 
+.violence_measurement[.violence_measurement == "not specified_violence"] <- "not specified"
+
 
 .violence_prevalence <- list()
 for (i in 18:22) {
   .violence_prevalence$sum[[i-17]] <- sum(!is.na(measurement[i]))
-  .violence_prevalence$perc[[i-17]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$IPV_type))))
+  .violence_prevalence$perc[[i-17]] <-  percent(sum((!is.na(measurement[i]))/sum(!is.na(measurement$violence_period))))
   names(.violence_prevalence[["sum"]])[[i-17]] <- names(measurement[i])
   names(.violence_prevalence[["perc"]])[[i-17]] <- names(measurement[i])
 }
@@ -63,9 +65,9 @@ for (i in 18:22) {
   add_footer_lines(values = .violence_prevalence[["footer"]]) %>%
   merge_v(j = c(1,3), part = "body") %>%
   merge_at(j = 2, i = 1:5, part = "body") %>%
-  merge_at(j = 2, i = 6:9, part = "body") %>%
-  merge_at(j = 2, i = 10:11, part = "body") %>%
-  merge_at(j = 2, i = 12:13, part = "body") %>%
+  merge_at(j = 2, i = 6:10, part = "body") %>%
+  merge_at(j = 2, i = 11:12, part = "body") %>%
+  merge_at(j = 2, i = 13:14, part = "body") %>%
   hline(j = c(1, 3,4), border = .borders, part = "body") %>%
   align(align = "center", j=1:4, part = "body") %>%
   vline(j = 3, border = .borders, part = "body") %>%

### 2022-01-13 _bookdown_files/01-abstract.Rmd
Final draft

@@
 # Abstract
+
+Men who have sex with Men (MSM) represent a vulnerable population affected by numerous health conditions.
+Syndemic theory has been used as a framework to study the health of MSM for nearly 20 years.
+However, the literature is plagued by a lack of consensus regarding what constitutes a synergy in syndemic and recent reviews showed that most of the papers published thus far failed to demonstrate a synergy or describe the bio-social interaction needed to account for a true syndemic.
+Moreover, to our knowledge, none of the existing reviews have focused specifically on MSM.
+
+This scoping review thus aimed to fill this gap by mapping in details how syndemic research on MSM was conducted.
+A systematic database search was conducted and 115 studies were included.
+Our findings showed a lack of diversity regarding the location, design, subpopulation and outcomes studied.
+In addition, the syndemic conditions as well as their measurement were not focused enough to ensure the robustness and reproducibility of the findings.
+Furthermore, our results support previous reviews showing a lac of empirical data to support disease interaction in syndemic research applied to MSM.
+Our review offers some important recommendations to help move the field forward in future work and describes some promising methodological advancement.

### 2022-01-13 _bookdown_files/04-results.Rmd
Final draft

@@
 Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r sum(population$age == "Older men")` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r sum(population$age == "Adolescent")` study focuses on adolescents[@Perry].
-Of note, the two studies on older MSM are both entirely composed of a sample of older MSM living with HIV.
 
-Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.
-Among these studies, `r .N_YBMSM` studies are composed of young BMSM[@Maiorana; @Reed2016] and `r .N_MSM_SW` study focuses on Black MSM engaged in sex work[@chandler2020].\
-`r sum(population$race_ethnicity == "Latino")` studies focus on Latino MSM (LMSM) and `r .N_LMSMW` of these studies focus on Latino MSMW[@Munoz-Laboy2018].
-Furthermore, `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].
+Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.\
+`r sum(population$race_ethnicity == "Latino")` studies focus on Latino MSM (LMSM) and `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].
 
 Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV.
-Apart from the studies mentioned above on older MSM living with HIV, `r sum(population$serologic_status == "HIV-positive" & population$age == "Young adult")` studies focus on young MSM living with HIV[@Lyons2013; @Bruce2011] .
 Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.
@@
 Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
-Strikingly, transgender MSM, in addition to being the focus of only one study [@Reisner2016a] are, by design, excluded from every other study whereas other MSM subpopulation are at least partially represented in most of the samples.
 
@@
 
-We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression or depressive symptoms (N = `r nodes$studies[nodes$label == "depression"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "PTSD"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
+We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression (N = `r nodes$studies[nodes$label == "depression"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "PTSD"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
 
@@
 ```
-
-Despite the high number of syndemic conditions studied in the literature, the impact of the seminal study by Stall et al.[@Stall2003] is striking.
-The conditions studied in that paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
-Furthermore, `r percent(nrow(.Stall_conditions)/nrow(summary_quantitative))` of the quantitative studies included in our review consider at least one of the four conditions studied by Stall and colleagues as part of a syndemic.
 
@@
 For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria were used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.
-70 studies used scales while 10 studies used criteria to assess the presence of depression or depressive symptoms among the participants.
 The most frequently used scales were the full Center for Epidemiologic Studies-Depression scale [CESD] (N = 26) and the 10-items version of this scale [CESD-10] (N=11), the 9-items version of the Patient Health Questionnaire [PHQ-9] (N=9) and the Beck Depression Inventory [BDI-II] (N = 5).\
@@
 
+For polysubstance use, 18 studies considered that there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
+Furthermore, 6 studies excluded marijuana from the class of substances screened and 2 study excluded stimulants, because stimulants were already screened in another syndemic condition.
+
 For IPV, 5 types of intimate partner violence were identified : physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), gay-related violence (e.g.
@@
 The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (N = 7).
-
-For polysubstance use, 18 studies considered that there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
-Furthermore, 6 studies excluded marijuana from the class of substances screened and 2 study excluded stimulants, because stimulants were already screened in another syndemic condition.
 
@@
 
-Every other outcome was only studied once : HIV screening [@Chandler2019b], physical activity [@Zhang2019], hypothalamic-pituitary-adrenal (HPA) axis dysregulation [@carrico2018], sexual violence [@semple2017], glycemic control [@Byg2016], engagement in HIV care [@Biello2016], engagement in chemsex [@friedman2014], having sexual intercourse with both men and women [@eaton2013] , help-seeking behaviors [@achterbergh2021], substance use [@turpin2020], HIV transmission [@satyanarayana2021] and elevation in rectal cytokines/chemokines [@tapia2021].
+Every other outcome was only studied once : HIV screening [@Chandler2019b], HIV transmission [@satyanarayana2021], engagement in HIV care [@Biello2016], sexual violence [@semple2017], substance use [@turpin2020], engagement in chemsex [@friedman2014], having sexual intercourse with both men and women [@eaton2013] , help-seeking behaviors [@achterbergh2021], physical activity [@Zhang2019], glycemic control [@Byg2016], hypothalamic-pituitary-adrenal (HPA) axis dysregulation [@carrico2018] and elevation in rectal cytokines/chemokines [@tapia2021].
 
-There was a high degree of variability in the definition of what constitutes a sexual risk behaviors though the most frequently used proxy was, by far, condomless anal sex.
-Indeed, condomless anal sex was one of the criteria in `r .CAS_number` studies out of the `r sum(!is.na(.outcomes$outcome_sexual_risk))` with sexual risk behaviors as an outcome.
-While `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CAS))` studies considered all form of condomless anal sex as a risk behavior, the other tried to refine the criteria.
-The most frequent of such refinement was to consider only serodiscordant condomless anal sex as a risk behavior (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_serodiscodant_CAS))`).
-Other options were to only consider condomless anal sex with casual partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_casual_CAS))`), condomless anal sex without PrEP or with a detectable viral load, if HIV-positive (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_CAS)) + sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))`), receptive condomless anal sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_receptive_CAS))`) or condomless anal sex at first sexual intercourse with the current male partner (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_current_CAS))`).
+There was a high degree of variability in the definition of what constitutes a sexual risk behaviors though the most frequently used proxy was, by far, condomless anal sex (N = `r .CAS_number`).
 

### 2022-01-13 _bookdown_files/05-discussion.Rmd
Final draft

@@
 Three issues arise from this.
-First, under-representation of the Global South is inherently an issue as it prevents us from better understanding the health of MSM living in these countries.
+First, under-representation of the Global South compromises our understanding of the health of MSM living in these countries.
 Furthermore, as aptly pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
@@
 We identified `r nrow(nodes)` different conditions in our quantitative sample, `r nrow(nodes %>% filter(studies == 1))` of them were only studied once.
+Despite this diversity of syndemic conditions, the impact of the seminal study by Stall et al.[@Stall2003] is striking.
+The conditions studied in that paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
+Furthermore, `r percent(nrow(.Stall_conditions)/nrow(summary_quantitative))` of the quantitative studies included in our review consider at least one of the four conditions studied by Stall and colleagues as part of a syndemic.
+
 Some of these conditions are past event (e.g.
@@
 Furthermore, when studying HIV as an outcome, we would argue that using condomless anal sex as a proxy should be reviewed and better proxies sought.
-First, without refinement, this outcome fails to capture the changes in HIV prevention strategies such as PrEP or Treatment as Prevention (TasP).
+Indeed, condomless anal sex was one of the criteria in `r .CAS_number` studies out of the `r sum(!is.na(.outcomes$outcome_sexual_risk))` with sexual risk behaviors as an outcome and `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CAS))` studies considered all form of condomless anal sex as a risk behavior.
+However, without refinement, this outcome fails to capture the changes in HIV prevention strategies such as PrEP or Treatment as Prevention (TasP).
 Only `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))` studies in our sample took PrEP use and an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.

### 2022-01-23 _bookdown_files/01-abstract.Rmd
Final version

@@
 Syndemic theory has been used as a framework to study the health of MSM for nearly 20 years.
-However, the literature is plagued by a lack of consensus regarding what constitutes a synergy in syndemic and recent reviews showed that most of the papers published thus far failed to demonstrate a synergy or describe the bio-social interaction needed to account for a true syndemic.
+However, the literature is plagued by a lack of consensus regarding what constitutes a synergy in a syndemic and recent reviews have shown that most of the papers published thus far failed to demonstrate a synergy nor describe the bio-social interaction needed to account for a true syndemic.
 Moreover, to our knowledge, none of the existing reviews have focused specifically on MSM.
 
-This scoping review thus aimed to fill this gap by mapping in details how syndemic research on MSM was conducted.
-A systematic database search was conducted and 115 studies were included.
+This scoping review aims to fill this gap by mapping in details how syndemic research on MSM was conducted.
+A systematic database search was conducted between 2020 and 2021 and 115 studies were included.
 Our findings showed a lack of diversity regarding the location, design, subpopulation and outcomes studied.
 In addition, the syndemic conditions as well as their measurement were not focused enough to ensure the robustness and reproducibility of the findings.
-Furthermore, our results support previous reviews showing a lac of empirical data to support disease interaction in syndemic research applied to MSM.
+Furthermore, our results support previous reviews showing a lack of empirical data to support disease interaction in syndemic research applied to MSM.
 Our review offers some important recommendations to help move the field forward in future work and describes some promising methodological advancement.

### 2022-01-23 _bookdown_files/02-introduction.Rmd
Final version

@@
 Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their heterosexual counterparts @Medley2016.
-Moreover, those adverse health outcomes are enmeshed within structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020]
+Moreover, those adverse health outcomes are enmeshed within structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020].
 
-For more than 20 years, syndemic theory have provided a framework to examine the interrelations between social conditions, mental health and physical health @singer2017.
-Described for the first time in 1996 by Merrill Singer @singer1996, a syndemic consists in two more interacting epidemics producing an excess burden in a population because of harmful social conditions @singer2003.
+For more than 20 years, syndemic theory has provided a framework to examine the interrelations between social conditions, mental health and physical health @singer2017.
+Described for the first time in 1996 by Merrill Singer @singer1996, a syndemic consists of two more interacting epidemics producing an excess burden in a population because of harmful social conditions @singer2003.
 To speak of a syndemic, three conditions must be met @mendenhall2020 :
@@
 Syndemic is thus an holistic framework, describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread @singer2017.
-As such its value for studying the health of marginalized populations such as MSM is undeniable.
+As such, its value for studying the health of marginalized populations such as MSM is undeniable.
 
@@
 However, this theory is not without its flaws.
-A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenet @tsai2015.
+A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenets @tsai2015.
 Indeed, this paper demonstrated that, although synergistic interaction between diseases lies in the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy.
@@
 
-With these data, we wanted to better comprehend the state of the art in the current literature, identify knowledge gaps and suggest recommendations to guide future research in the field.
+With these data, we wanted to better understand the state of the art in the current literature, identify knowledge gaps and suggest recommendations to guide future research in the field.

### 2022-01-23 _bookdown_files/03-methodology.Rmd
Final version

@@
 Scripts, statistics, charts, tables and the present paper was generated using R @rcoreteam2020, RStudio @rstudioteam2020 and appropriate packages.
-To ensure the complete transparency and reproducibility of this article, our data manager uploaded every data used to generate this article on Open Science Framework (DOI : [masked for the anonymity of the review])
+To ensure the complete transparency and reproducibility of this article, our data manager (M.O.) uploaded every data used to generate this article on Open Science Framework (DOI : [masked for the anonymity of the review])
 
@@
 
-To answer those questions, we conducted a systematic search strategy in the following databases : Medline, PsycInfo, Scopus, Cochrane Central Register of Controlled Trials and ProQuest Sociological Abstracts using complex search equations to include every synonym for "men who have sex with men".
+To answer these questions, we conducted a systematic search strategy in the following databases : Medline, PsycInfo, Scopus, Cochrane Central Register of Controlled Trials and ProQuest Sociological Abstracts using complex search equations to include every synonym for "men who have sex with men".
 The complete search strategy for every database can be found in the Supplementary Material of our protocol.
@@
 Furthermore, the README file of our *Data* subdirectory contains an exhaustive definition of every variable included.
-Two departures were made from our initial protocol :
+Two amendments were made to our initial protocol :
 
@@
 These tables can be found respectively in part B and C of the supplementary materials of this paper.
-Unfortunately, due do time constraints, we did not create any evidence map.
-However, we generated a SQL database alongside our data.
-This database contains every study included and provide scholars in the field the opportunity to search relevant studies using complex queries.
+Additionally, we generated an online report accessible at <https://datastudio.google.com/u/0/reporting/56c1e17a-fa3f-47e9-9516-d3d0eef7ec1> This report contains every study included and provide scholars in the field the opportunity to search relevant studies using multiple filters.

### 2022-01-23 _bookdown_files/04-results.Rmd
Final version

@@
 
-This section summarizes the findings relevant to our aforementioned research questions.
-\@ref(tab:RefTabQuant), \@ref(tab:RefTabQual) and \@ref(tab:RefTabRev) in our supplementary material, summarize every reference identified and the variables extracted to answer our research questions for quantitative studies, qualitative studies and reviews, respectively.
+This section summarizes the findings relevant to our research questions.
+\@ref(tab:RefTabQuant), \@ref(tab:RefTabQual) and \@ref(tab:RefTabRev) in the supplementary material, summarize every reference identified and the variables extracted to answer our research questions for quantitative studies, qualitative studies and reviews, respectively.
 
@@
 
-Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.
-
-Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r sum(population$age == "Older men")` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r sum(population$age == "Adolescent")` study focuses on adolescents[@Perry].
-
+Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.\
+Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents[@Perry].\
 Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.\
-`r sum(population$race_ethnicity == "Latino")` studies focus on Latino MSM (LMSM) and `r sum(population$race_ethnicity == "Latino & Black")` study focus on both BMSM and LMSM[@cassels2020].
-
+`r english(sum(population$race_ethnicity == "Latino"))` studies focus on Latino MSM (LMSM) and `r english(sum(population$race_ethnicity == "Latino & Black"))` study focus on both BMSM and LMSM[@cassels2020].\
 Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV.
-Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.
-
-Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
-
-Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.
-
+Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.\
+Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).\
+Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.\
 In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulations.\
@@
 Nodes represent the syndemic conditions studied in the literature and edges (connectors) are drawn between two nodes when two conditions are studied in the same research paper.
-Furthermore, edges between nodes are thicker if the two conditions are frequently studied together.
-Furthermore, the outline of the nodes represent pie chart of their frequency in syndemic literature.
+Edges between nodes are thicker if the two conditions are frequently studied together and the outline of the nodes represent pie chart of their frequency in syndemic literature.
 For example, depression, the most studied condition, appears in `r percent((nodes$studies[nodes$label == "depression"])/nrow(summary_quantitative))` of our sample.
@@
 
-In this figure, we divided the conditions studied into 4 categories : mental health (e.g.
+In this figure, we divided the conditions studied into four categories : mental health (e.g.
 depression, anxiety, PTSD) in blue, social conditions (e.g.
@@
 Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies.
-For the sake of brevity, we will only provide a detailed description of the measurement method for the 5 most studied syndemic conditions.
+For the sake of brevity, we will only provide a detailed description of the measurement method for the five most studied syndemic conditions.
 Detailed information on the syndemic conditions most impacted by methodology heterogeneity is presented in the supplementary material, part C ( \@ref(tab:DepressionTab) to \@ref(tab:AnxietyTab)).
@@
 
-For polysubstance use, 18 studies considered that there was polysubstance use when 3 or more classes of substances were used while 9 studies defined polysubstance use as more than one class of substance being used.
-Furthermore, 6 studies excluded marijuana from the class of substances screened and 2 study excluded stimulants, because stimulants were already screened in another syndemic condition.
+For polysubstance use, 18 studies considered that there was polysubstance use when three or more classes of substances were used while nine studies defined polysubstance use as more than one class of substance being used.
+Furthermore, six studies excluded marijuana from the class of substances screened and two studies excluded stimulants, because stimulants were already screened in another syndemic condition.
 
@@
 
-For CSA, we identified `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Definition"]))` different definitions and `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Scale"]))` scales among the `r nodes$studies[nodes$label == "CSA"]` studies.
+For CSA, we identified `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Definition"]))` different definitions and `r english(length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Scale"])))` scales among the `r nodes$studies[nodes$label == "CSA"]` studies.
 The various definitions differed on the age at which the sexual intercourse occurred to be qualified as childhood sexual abuse, the age gap between the victim and the perpetrator and whether the sexual intercourse was unwanted.
-The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least 5 years older or any sexual experience between 13 and 17 years old with someone at least 10 years older (N = 7).
+The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least five years older or any sexual experience between 13 and 17 years old with someone at least ten years older (N = 7).
 
@@
 
-When HIV was used as an outcome, it was self-reported in more than half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T)` papers out of `r sum(!is.na(.outcomes$outcome_STI))`.
+When HIV was used as an outcome, it was self-reported in more than half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r english(sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T))` papers out of `r english(sum(!is.na(.outcomes$outcome_STI)))`.
 
@@
 
-We identified only `r .N_int` interventional studies guided by syndemic theory [@Chakrapani; @achterbergh2021].
+We identified only `r english(.N_int)` interventional studies guided by syndemic theory [@Chakrapani; @achterbergh2021].
 Chakrapani et al.
@@
 
-We found `r sum(summary_reviews$design == "Systematic review")` systematic reviews [@lewis2017; @woodward2017; @Lassiter2016] and 2 meta-analysis [@Rooney2018a; @Pantalone2020] in our review.
+We found `r english(sum(summary_reviews$design == "Systematic review"))` systematic reviews [@lewis2017; @woodward2017; @Lassiter2016] and two meta-analyses [@Rooney2018a; @Pantalone2020] in our review.
 
@@
 They found that religion and spirituality had mixed effect on syndemic conditions but could be more beneficial for MSM of color than for white MSM.
-Of note, the review was relatively small (including `r summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."]` studies) as these two factors are very sparse in syndemic literature.
+Of note, the review was relatively small (including `r english(summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."])` studies) as these two factors are very sparse in syndemic literature.
 
@@
 
-Moreover, `r .N_latent` studies used latent variables modeling such as Exploratory/Confirmatory Factor Analysis, Latent Profile Analysis, Latent Class Analysis or Latent Transition Analysis.
+Moreover, `r english(.N_latent)` studies used latent variables modeling such as Exploratory/Confirmatory Factor Analysis, Latent Profile Analysis, Latent Class Analysis or Latent Transition Analysis.
 
-Using a different approach, `r sum(!is.na(summary_quantitative$network))` studies conducted by Lee and colleagues [@lee2020; @Lee] used network analysis, in which syndemic is conceptualized as a network and the syndemic conditions as interconnected nodes reinforcing each others.
+Using a different approach, `r english(sum(!is.na(summary_quantitative$network)))` studies conducted by Lee and colleagues [@lee2020; @Lee] used network analysis, in which syndemic is conceptualized as a network and the syndemic conditions as interconnected nodes reinforcing each others.
 
@@
 
-Qualitative studies proposed mechanisms of bio-social interaction more often than quantitative studies as we identified `r sum(!is.na(summary_qualitative$bio_social_interaction))` papers with such hypothesis of interaction.
+Qualitative studies proposed mechanisms of bio-social interaction more often than quantitative studies as we identified `r english(sum(!is.na(summary_qualitative$bio_social_interaction)))` papers with such hypothesis of interaction.
 On the other hand, we did not find any qualitative paper exploring biological interaction.
 
-Stigma and structural inequalities were indicated by the 5 papers as the root causes of syndemic conditions and HIV risk behaviors.
+Stigma and structural inequalities were indicated by the five papers as the root causes of syndemic conditions and HIV risk behaviors.
 Maionara et al.

### 2022-01-23 _bookdown_files/05-discussion.Rmd
Final version

@@
 The objective of this scoping review was to map the current knowledge on syndemic research applied to MSM.
-To this end, we analysed 115 articles and found out that the literature was both too homogeneous in some aspects while being not focused enough in other parts.
+To this end, we analysed 115 articles and found that the literature was both too homogeneous in some aspects while being not focused enough in other aspects.
 As we will discuss in more depth below, the location, design, subpopulation and outcomes lacked diversity.
-On the other hand, the syndemic conditions and ways of measurement were not focused enough to ensure the robustness and reproducibility of the findings.
-Furthermore a substantial part of the literature doesn't provide empirical data to support one of the core tenets of syndemic theory - namely disease interaction- as was already pointed out in a previous review [@tsai2015].
+On the other hand, the syndemic conditions and ways of measurement were not standardised enough to ensure the robustness, reproducibility and comparability of the findings.
+Furthermore a substantial part of the literature doesn't provide empirical data to support one of the core tenets of syndemic theory - namely disease interaction- as has been pointed out in a previous review [@tsai2015].
 
@@
 First, under-representation of the Global South compromises our understanding of the health of MSM living in these countries.
-Furthermore, as aptly pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
+Furthermore, as pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
 As syndemics are driven by the sociocultural forces of a given place at a given time, these potential biases need to be addressed in order to conduct meaningful research outside Europe and North America.
@@
 Differences in the density of gay social venues and peer organizations as well as exposure to discrimination and violence or an easier access to substances need to be taken into account when studying a syndemic.
-Thus, as @shrestha2020 suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence the health of MSM.
+As @shrestha2020 suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence the health of MSM.
 
@@
 Moreover `r percent(.N_cross_sec/nrow(summary_quantitative))` of the quantitative studies were cross-sectional.
-As vulnerability to syndemic conditions is suspected to arise from early adverse experience @stall2007 longitudinal studies running on a long period of time are probably needed to study syndemic production among MSM.
+As vulnerability to syndemic conditions is suspected to arise from early adverse experience @stall2007 longitudinal studies running over a long period of time are probably needed to study syndemic production among MSM.
 
-Moreover, as shown in our result, qualitative paper are more prone to discuss the potential interactions between syndemic conditions.
-Some concepts and experiences needed to understand syndemic production in MSM can only be studied through a qualitative lens.
+Moreover, as shown in our result, qualitative papers are more prone to discuss the potential interactions between syndemic conditions.
+Some concepts and experiences needed to understand syndemic production in MSM can only be studied through a qualitative approach.
 For example, the complex narratives surrounding drug use and its link to loneliness, marginalization, personal affirmation, resistance and lack of meaningful emotional connections @Pollard2018a would be hard to measure and model using quantitative data.
-As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to over-simplification of diseases dynamics @Tsai2018a .
+As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to an over-simplification of diseases dynamics @Tsai2018a .
 Mixed method are needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
@@
 This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic condition such as HIV infection is even more concerning when considering that dual-minority identity may expose a person to different stressors and outcomes.
-For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to less syndemic conditions @Mustanski2017 .
-These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM @Quinn .
+For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to fewer syndemic conditions @Mustanski2017 .
+These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM @Quinn.
 Furthermore, the findings from Bulled and colleagues suggest that structural disadvantage may have more weight on the lives of Black MSM than individual factors such as substance use @bulled2021
@@
 found that MSM were more likely than MSMW to suffer from two or more syndemic conditions @ferlatte2018.
-These conflicting findings may be partly due to the difficulty to define and operate bisexuality in research @swan2018, difference between age groups or differences in syndemic mechanism for MSMW compared to MSM.
-Outside the field of syndemic literature, studies suggest that bisexual men suffer from a similar or higher burden of mental health condition compared to gay men [@salway2019; @Chaudhry2019; @ross2018] and literature specific to bisexual men remains scarce.
+These conflicting findings may be partly due to the difficulty to define and operate bisexuality in research @swan2018, differences between age groups or differences in syndemic mechanism for MSMW compared to MSM.
+Outside the field of syndemic literature, studies suggest that bisexual men suffer from a similar or higher burden of mental health conditions compared to gay men [@salway2019; @Chaudhry2019; @ross2018] and literature specific to bisexual men remains scarce.
 In the future, syndemic theory should thus seek to study the specificity of this population.
@@
 
-Finally transgender MSM were included in only one study of our sample.
+Finally transgender MSM were included in only one study in our sample.
 As stated in our results, this is concerning, especially when every other study excludes transgender men by design.
@@
 This man would have been classified as depressed in `r percent(sum(.depression_measurement$depression_cutoff == 16 & .depression_measurement$depression_scale_criteria == "CESD", na.rm = T)/sum(.depression_measurement$depression_scale_criteria == "CESD"))` of studies using the CESD, a polysubstance user in `r percent(sum(.polysubstance_measurement$polysubstance_number == "More than one category of substance use" & .polysubstance_measurement$polysubstance_marijuana == "Marijuana included")/nrow(.polysubstance_measurement))` of studies considering polysubstance use and as a victim of intimate partner violence in `r .IPV_prevalence$perc[["sexual IPV"]]` of studies taking IPV into account.
-In other words, the same person could have been classified as having 0, 1, 2 or even 3 syndemic conditions, depending on the study.
+In other words, the same person could have been classified as having 0, 1, 2 or even 3 syndemic conditions, depending on the study design.
 Considering that most studies use a summation score of the number of syndemic conditions to conduct regression analysis, it seems evident that the results would greatly vary according to the way the syndemic conditions are measured.
@@
 However, without refinement, this outcome fails to capture the changes in HIV prevention strategies such as PrEP or Treatment as Prevention (TasP).
-Only `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))` studies in our sample took PrEP use and an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.
+Only `r english(sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS)))` studies in our sample took PrEP use and an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.
 When the first paper on syndemic theory applied to MSM was published, engaging in condomless anal sex would have led to a high risk of acquiring HIV.
@@
 First, summation score are additive by essence, thus unsuitable to demonstrate an interaction @tsai2015.
-Secondly, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting @Halkitis2013a.
+Second, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting @Halkitis2013a.
 Put simply, using a summation score would imply that (1) every condition forms a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having an history of childhood sexual abuse would contribute equally to a syndemic).
@@
 
-Finally, although intersectionality was only used by two studies [@ferlatte2018; @Quinn] we believe the field would benefit from this framework .
+Finally, although intersectionality was only used by two studies [@ferlatte2018; @Quinn] we believe the field would benefit from this framework.
 Indeed as shown in our results, there is some discrepancy in the results for MSM's subpopulation, especially for MSMW/bisexual men, Black MSM and Latino MSM.

### 2022-01-23 _bookdown_files/06-conclusion.Rmd
Final version

@@
 Moreover, we conducted a fully transparent and reproducible review.
-Other researchers may freely reuse our data and scripts to conduct their own work or use our database to identify papers pertinent for their research projects.
+Other researchers may freely reuse our data and scripts to conduct their own work or use our online visualizations to identify papers pertinent for their research projects.
 
@@
 
-Despite our critical stance on the current literature, we remained convinced that syndemic is a useful framework to study the health of marginalized populations in a holistic way and the current research still offered valuable insights on the health of MSM.
+Despite our critical stance on the current literature, we remain convinced that syndemic is a useful framework to study the health of marginalized populations in a holistic way and the current research still offers valuable insights on the health of MSM.
 It is vital that research continues to evolve in order to deepen our understanding and, by consequence, improve the health of marginalized populations worldwide.

### 2022-01-23 _bookdown_files/04-results.Rmd
Final version

@@
 library(d3r)
+library(english)
 
@@
 
-Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.\
-Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents[@Perry].\
+Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.
+
+\
+Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents[@Perry].
+
+\
 Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.\
 `r english(sum(population$race_ethnicity == "Latino"))` studies focus on Latino MSM (LMSM) and `r english(sum(population$race_ethnicity == "Latino & Black"))` study focus on both BMSM and LMSM[@cassels2020].\
+
 Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV.
-Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.\
-Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).\
-Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.\
+Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.
+
+\
+Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
+
+\
+Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.
+
+\
 In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulations.\

### 2022-01-23 _bookdown_files/index.Rmd
Final version

@@
 author: 
-- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
-- "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
+- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Beatrice Scholtes^3^"
+- "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
 - "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
-- "^3^  <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
-- "^4^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
+- "^3^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
 - "*corresponding author: maxence.ouafik@uliege.be https://orcid.org/0000-0002-9795-5721"

### 2022-03-31 _bookdown_files/02-introduction.Rmd
References correction

@@
 Men who have sex with men (MSM) represent a vulnerable population disproportionately affected by numerous health conditions.
-They represent 70% of new HIV diagnoses @centerfordiseasecontrolandprevention2020 in the United States of America and more than half of new HIV diagnoses in European Union/European Economic area @europeancentrefordiseasepreventionandcontrol2019.
-They are also more prone to contract other sexually transmitted diseases and *Nesseria Gonorrhea* strains from MSM exhibit higher antimicrobial resistance @centersfordiseasecontrolandprevention2019.
-Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their heterosexual counterparts @Medley2016.
+They represent 70% of new HIV diagnoses [@centerfordiseasecontrolandprevention2020] in the United States of America and more than half of new HIV diagnoses in European Union/European Economic area [@europeancentrefordiseasepreventionandcontrol2019].
+They are also more prone to contract other sexually transmitted diseases and *Nesseria Gonorrhea* strains from MSM exhibit higher antimicrobial resistance [@centersfordiseasecontrolandprevention2019].
+Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their heterosexual counterparts[@Medley2016].
 Moreover, those adverse health outcomes are enmeshed within structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020].
 
-For more than 20 years, syndemic theory has provided a framework to examine the interrelations between social conditions, mental health and physical health @singer2017.
-Described for the first time in 1996 by Merrill Singer @singer1996, a syndemic consists of two more interacting epidemics producing an excess burden in a population because of harmful social conditions @singer2003.
-To speak of a syndemic, three conditions must be met @mendenhall2020 :
+For more than 20 years, syndemic theory has provided a framework to examine the interrelations between social conditions, mental health and physical health [@singer2017].
+Described for the first time in 1996 by Merrill Singer [@singer1996], a syndemic consists of two more interacting epidemics producing an excess burden in a population because of harmful social conditions [@singer2003]To speak of a syndemic, three conditions must be met [@mendenhall2020] :
 
@@
 
-Syndemic is thus an holistic framework, describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread @singer2017.
+Syndemic is thus an holistic framework, describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread [@singer2017].
 As such, its value for studying the health of marginalized populations such as MSM is undeniable.
@@
 
-However, this theory is not without its flaws.
-A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenets @tsai2015.
+However this framework is frequently misused by researchers.
+A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenets [@tsai2015].
 Indeed, this paper demonstrated that, although synergistic interaction between diseases lies in the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy.
-More recently, a scoping review published in 2020 confirmed this finding as most recently-published citations failed to describe the interactions between diseases needed to account for a true syndemic @Singer2020.
+More recently, a scoping review published in 2020 confirmed this finding as most recently-published citations failed to describe the interactions between diseases needed to account for a true syndemic [@Singer2020].
 Scholars in the field have been calling for greater clarity in the use of the concept and urged researchers to describe more precisely the interactions they observe between health conditions [@singer2021 ; @mendenhall2020].

### 2022-03-31 _bookdown_files/03-methodology.Rmd
References correction

@@
 
-We applied the framework suggested by Arskey and O'Malley @arksey2005, with enhancements from Levac et al.
-@levac2010.
+We applied the framework suggested by Arskey and O'Malley [@arksey2005], with enhancements from Levac et al.
+[@levac2010].
 We also took into account the recommendations formulated by Colqhoun et al.
-@colquhoun2014 and the updated guidance by Peters and colleagues @peters2020.
-We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses extension for Scoping Reviews (PRISMA-ScR) @Tricco2018.
+[@colquhoun2014] and the updated guidance by Peters and colleagues [@peters2020].
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses extension for Scoping Reviews (PRISMA-ScR) [@Tricco2018].
 The completed checklist can be found in \@ref(tab:PRISMA-ScR) of the supplementary materials.
@@
 Screening and data charting was completed using DistillerSR (Evidence Partners, Ottawa, Canada).
-Scripts, statistics, charts, tables and the present paper was generated using R @rcoreteam2020, RStudio @rstudioteam2020 and appropriate packages.
+Scripts, statistics, charts, tables and the present paper was generated using R [@rcoreteam2020], RStudio [@rstudioteam2020] and appropriate packages.
 To ensure the complete transparency and reproducibility of this article, our data manager (M.O.) uploaded every data used to generate this article on Open Science Framework (DOI : [masked for the anonymity of the review])

### 2022-03-31 _bookdown_files/04-results.Rmd
References correction

@@
 
-The electronic search identified 840 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
+The electronic search identified 840 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague [@Stall2003].
 After removing duplicates, 305 records were screened for inclusion.

### 2022-03-31 _bookdown_files/05-discussion.Rmd
References correction

@@
 First, under-representation of the Global South compromises our understanding of the health of MSM living in these countries.
-Furthermore, as pointed out by @weaver2020, the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
+Furthermore, as pointed out by [@weaver2020], the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
 As syndemics are driven by the sociocultural forces of a given place at a given time, these potential biases need to be addressed in order to conduct meaningful research outside Europe and North America.
@@
 Differences in the density of gay social venues and peer organizations as well as exposure to discrimination and violence or an easier access to substances need to be taken into account when studying a syndemic.
-As @shrestha2020 suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence the health of MSM.
+As [@shrestha2020] suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence the health of MSM.
 
@@
 Moreover `r percent(.N_cross_sec/nrow(summary_quantitative))` of the quantitative studies were cross-sectional.
-As vulnerability to syndemic conditions is suspected to arise from early adverse experience @stall2007 longitudinal studies running over a long period of time are probably needed to study syndemic production among MSM.
+As vulnerability to syndemic conditions is suspected to arise from early adverse experience [@stall2007] longitudinal studies running over a long period of time are probably needed to study syndemic production among MSM.
 
@@
 Some concepts and experiences needed to understand syndemic production in MSM can only be studied through a qualitative approach.
-For example, the complex narratives surrounding drug use and its link to loneliness, marginalization, personal affirmation, resistance and lack of meaningful emotional connections @Pollard2018a would be hard to measure and model using quantitative data.
-As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to an over-simplification of diseases dynamics @Tsai2018a .
+For example, the complex narratives surrounding drug use and its link to loneliness, marginalization, personal affirmation, resistance and lack of meaningful emotional connections [@Pollard2018a] would be hard to measure and model using quantitative data.
+As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to an over-simplification of diseases dynamics [@Tsai2018a].
 Mixed method are needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
@@
 Finally, we identified `r .N_int` interventional studies with mixed results.
-While co-targeting interconnected syndemic conditions is supported by a meta-analysis @Pantalone2020, a better understanding of how syndemics operate may be needed before we are able to offer efficient syndemic-based interventions.
+While co-targeting interconnected syndemic conditions is supported by a meta-analysis [@Pantalone2020], a better understanding of how syndemics operate may be needed before we are able to offer efficient syndemic-based interventions.
 
@@
 While nearly half of the studies included in our sample studied a subpopulation of MSM, the number of MSM subpopulation is such that most MSM subpopulation remains under-served.
-For example, Young Black MSM are specifically studied in `r .N_YBMSM` studies while representing 52% of the new HIV diagnosis among MSM aged 13-24 years in 2018 @centerfordiseasecontrolandprevention2020.
+For example, Young Black MSM are specifically studied in `r .N_YBMSM` studies while representing 52% of the new HIV diagnosis among MSM aged 13-24 years in 2018 [@centerfordiseasecontrolandprevention2020].
 
 This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic condition such as HIV infection is even more concerning when considering that dual-minority identity may expose a person to different stressors and outcomes.
-For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to fewer syndemic conditions @Mustanski2017 .
-These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM @Quinn.
-Furthermore, the findings from Bulled and colleagues suggest that structural disadvantage may have more weight on the lives of Black MSM than individual factors such as substance use @bulled2021
+For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to fewer syndemic conditions [@Mustanski2017] .
+These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM [@Quinn].
+Furthermore, the findings from Bulled and colleagues suggest that structural disadvantage may have more weight on the lives of Black MSM than individual factors such as substance use [@bulled2021]
 
 MSMW are another example of an under-served population with conflicting results.
-In a cross-sectional study using syndemic sum count, Latino MSMW with two or more syndemic conditions had a 7.09 Odds Ratio to engage in receptive condomless anal sex but no statistically significant difference was found for insertive condomless anal sex or condomless vaginal sex @Munoz-Laboy2018.
-On the other hand, in another study the number of syndemic conditions was associated with HIV diagnosis for MSM but not for MSW or MSMW @Branstrom2018.
-Among young MSM and MSMW, one study found more syndemic conditions and a greater association between them for MSMW compared to MSM @Mustanski2014.
+In a cross-sectional study using syndemic sum count, Latino MSMW with two or more syndemic conditions had a 7.09 Odds Ratio to engage in receptive condomless anal sex but no statistically significant difference was found for insertive condomless anal sex or condomless vaginal sex [@Munoz-Laboy2018].
+On the other hand, in another study the number of syndemic conditions was associated with HIV diagnosis for MSM but not for MSW or MSMW [@Branstrom2018].
+Among young MSM and MSMW, one study found more syndemic conditions and a greater association between them for MSMW compared to MSM [@Mustanski2014].
 On the contrary, Ferlatte et al.
-found that MSM were more likely than MSMW to suffer from two or more syndemic conditions @ferlatte2018.
-These conflicting findings may be partly due to the difficulty to define and operate bisexuality in research @swan2018, differences between age groups or differences in syndemic mechanism for MSMW compared to MSM.
+found that MSM were more likely than MSMW to suffer from two or more syndemic conditions [@ferlatte2018].
+These conflicting findings may be partly due to the difficulty to define and operate bisexuality in research [@swan2018], differences between age groups or differences in syndemic mechanism for MSMW compared to MSM.
 Outside the field of syndemic literature, studies suggest that bisexual men suffer from a similar or higher burden of mental health conditions compared to gay men [@salway2019; @Chaudhry2019; @ross2018] and literature specific to bisexual men remains scarce.
@@
 As such, this population of MSM is the one we know the least about.
-The study from Reisner and colleagues suggested that transgender MSM who had socially affirmed their gender were exposed to similar risk patterns as cisgender MSM @Reisner2016a.
-The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence @Testa2012, suicide attempts @Haas2014, chlamydial and gonoccocal infections @Pitasi2019, intimate partner violence [@peitzmeier2020] and HIV infection @Becasen2019.
+The study from Reisner and colleagues suggested that transgender MSM who had socially affirmed their gender were exposed to similar risk patterns as cisgender MSM [@Reisner2016a].
+The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence [@Testa2012], suicide attempts [@Haas2014], chlamydial and gonoccocal infections [@Pitasi2019], intimate partner violence [@peitzmeier2020] and HIV infection [@Becasen2019].
 Researchers should be encouraged to include transgender men in their studies and to conduct research focused on transgender MSM.
@@
 This omnipresence of HIV in syndemic literature applied to MSM is understandable.
-The first description of a syndemic, the SAVA syndemic, incorporated AIDS as part of a syndemic @singer1996.
-Then, a few years later, the first paper on syndemic in the MSM population had HIV-related outcomes, in the form of HIV serostatus and CAS @Stall2003.
-Furthermore MSM were the first and most severely affected population when the AIDS epidemic started @decock2012.
-Nowadays, male-to-male sexual contact still represents nearly 70% of the new HIV cases in the USA @centerfordiseasecontrolandprevention2020.
+The first description of a syndemic, the SAVA syndemic, incorporated AIDS as part of a syndemic [@singer1996].
+Then, a few years later, the first paper on syndemic in the MSM population had HIV-related outcomes, in the form of HIV serostatus and CAS [@Stall2003].
+Furthermore MSM were the first and most severely affected population when the AIDS epidemic started [@decock2012].
+Nowadays, male-to-male sexual contact still represents nearly 70% of the new HIV cases in the USA [@centerfordiseasecontrolandprevention2020].
 While we can't deny the importance of the HIV pandemic, notably for MSM, we would argue that HIV is not the only issue in need of attention.
@@
 Indeed, MSM are also disproportionately affected by, amongst others, suicide, anxiety, depression and substance use[@ross2018; @luo2017; @Medley2016].
-Moreover, with the advances in antiretroviral therapy and the subsequent decline in HIV-related mortality, a Canadian study showed that gay men were more likely to die from suicide than from HIV in 2011 @hottes2015.
+Moreover, with the advances in antiretroviral therapy and the subsequent decline in HIV-related mortality, a Canadian study showed that gay men were more likely to die from suicide than from HIV in 2011 [@hottes2015].
 Even if the estimates Hottes' paper overestimated the mortality due to suicide among MSM, suicide would still be a leading cause of death in this population while being studied as an outcome in only `r sum(!is.na(.outcomes$outcome_suicide))` papers in our sample.
@@
 When the first paper on syndemic theory applied to MSM was published, engaging in condomless anal sex would have led to a high risk of acquiring HIV.
-Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV @calabrese2017 and our methodologies in syndemic research should reflect this evolution.
+Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV [@calabrese2017] and our methodologies in syndemic research should reflect this evolution.
 In addition, qualitative research gives an insight into risk behaviors and offers a more nuanced view on this topic than a binary variable of consistent condom use for anal intercourse.
-One such paper published in 2017 showed that risk practices fell into different subjectivities such as active and consistent pursuit of condomless sex, lack of assertiveness to a partner's initiative of condomless anal sex and combination of episodic risk practices and reduction strategies @Adam2017.
+One such paper published in 2017 showed that risk practices fell into different subjectivities such as active and consistent pursuit of condomless sex, lack of assertiveness to a partner's initiative of condomless anal sex and combination of episodic risk practices and reduction strategies [@Adam2017].
 Besides, some studies showed that participants with a greater number of syndemic conditions would engage more frequently in condomless anal sex while not being more likely to test positive for HIV [@Mustanski2017; @Pitpitan2016].
-On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated to self-reported HIV but not to condomless anal sex @chuang2018.
+On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated to self-reported HIV but not to condomless anal sex [@chuang2018].
 Taken together, we thus postulate that condomless anal sex should at least be replaced by "condomless anal sex without consistent PrEP use or with a detectable viral load" when an investigator seek to use sexual risk behaviors as an outcome.
@@
 
-One of the tenets of syndemic theory is that there exists some form of biological, social and/or psychological interaction between the diseases @mendenhall2020.
-As others have already pointed out, the extent to which syndemic literature had proved this core principle remains very limited @tsai2015.
+One of the tenets of syndemic theory is that there exists some form of biological, social and/or psychological interaction between the diseases [@mendenhall2020].
+As others have already pointed out, the extent to which syndemic literature had proved this core principle remains very limited [@tsai2015].
 Indeed, `r percent(.score_data/nrow(summary_quantitative))` of our quantitative sample of studies used solely a summation score of the syndemic conditions to conduct regression analysis.
 Two issues arise from this statistical approach.
-First, summation score are additive by essence, thus unsuitable to demonstrate an interaction @tsai2015.
-Second, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting @Halkitis2013a.
+First, summation score are additive by essence, thus unsuitable to demonstrate an interaction [@tsai2015].
+Second, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting [@Halkitis2013a].
 Put simply, using a summation score would imply that (1) every condition forms a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having an history of childhood sexual abuse would contribute equally to a syndemic).
@@
 More recently, a new statistical approach inspired from research in psychopathology has been used to model syndemics : network analysis [@Lee; @lee2020].
-The core principle of this approach is that mental disorders arise from causal interactions between symptoms in a network @borsboom2017.
+The core principle of this approach is that mental disorders arise from causal interactions between symptoms in a network [@borsboom2017].
 Applied to syndemic theory, a syndemic would then be the network and the various conditions would then be the nodes of the network.
-Furthermore, one of the benefits of this approach resides in the theoretical possibility to identify influential nodes in a network : nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network @robinaugh2016.
+Furthermore, one of the benefits of this approach resides in the theoretical possibility to identify influential nodes in a network : nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network [@robinaugh2016].
 In short, in addition to being statistically sound and coherent with the model of mutually causal epidemics, network analysis could offer actionable data to improve the health of MSM by identifying which conditions should be prioritized for interventions [@Tsai2018a].
@@
 Indeed as reminded by Chakrapani et al.
-the three models have different programmatic implications @Chakrapani2019.
+the three models have different programmatic implications [@Chakrapani2019].
 In the case of synergistically interacting epidemics, a single intervention may yield greater health improvement than if no interaction was present.
@@
 Furthermore, the review by Woodwards et al.
-found a protective effect of most resilience resources identified against HIV @woodward2017.
+found a protective effect of most resilience resources identified against HIV [@woodward2017].
 
@@
 
-Minority stress represents another interesting framework as it allows to explain how social stigma can get under the skin of minorized populations @Meyer2003.
+Minority stress represents another interesting framework as it allows to explain how social stigma can get under the skin of minorized populations [@Meyer2003].
 
@@
 
-Some scholars are skeptical on the usefulness of syndemic theory to intersectionality and question the possibility of a conversation between the two fields @sangaramoorthy2021.
+Some scholars are skeptical on the usefulness of syndemic theory to intersectionality and question the possibility of a conversation between the two fields [@sangaramoorthy2021].
 As pertinent as the authors commentary is, we do believe in the possibility of making the two field converse.
-As Quinn pointed out in her response, incorporating an intersectional framework into syndemic research may address issues of power, oppression and structural violence, neglected thus far in the field @quinn2021.
+As Quinn pointed out in her response, incorporating an intersectional framework into syndemic research may address issues of power, oppression and structural violence, neglected thus far in the field [@quinn2021].
 Doing so, we may attend to some gap in the literature and disentangle the complex web of stigma and structural violence faced by sexual minority men, especially MSM situated at the intersection of multiple form of systemic discrimination such as racism, homophobia, biphobia, transphobia, classism, ableism or stigma against sex workers or people living with HIV.

### 2022-04-22 _bookdown_files/01-abstract.Rmd
Reviews [1st round]

@@
 
-Men who have sex with Men (MSM) represent a vulnerable population affected by numerous health conditions.
+Men who have sex with Men (MSM) represent a population affected by numerous health conditions.
 Syndemic theory has been used as a framework to study the health of MSM for nearly 20 years.
-However, the literature is plagued by a lack of consensus regarding what constitutes a synergy in a syndemic and recent reviews have shown that most of the papers published thus far failed to demonstrate a synergy nor describe the bio-social interaction needed to account for a true syndemic.
+However, the literature is plagued by a lack of consensus regarding what constitutes a synergy in a syndemic and recent reviews have shown that most of the papers published thus far have failed to demonstrate a synergy nor describe the bio-social interaction needed to account for a true syndemic.
 Moreover, to our knowledge, none of the existing reviews have focused specifically on MSM.
 
-This scoping review aims to fill this gap by mapping in details how syndemic research on MSM was conducted.
+This scoping review aims to fill this gap by mapping in detail how syndemic research on MSM has been conducted.
 A systematic database search was conducted between 2020 and 2021 and 115 studies were included.
@@
 Furthermore, our results support previous reviews showing a lack of empirical data to support disease interaction in syndemic research applied to MSM.
-Our review offers some important recommendations to help move the field forward in future work and describes some promising methodological advancement.
+Our review offers some important recommendations to help move the field forward in future work and describes some promising methodological advances.

### 2022-04-22 _bookdown_files/02-introduction.Rmd
Reviews [1st round]

@@
 
-Men who have sex with men (MSM) represent a vulnerable population disproportionately affected by numerous health conditions.
-They represent 70% of new HIV diagnoses [@centerfordiseasecontrolandprevention2020] in the United States of America and more than half of new HIV diagnoses in European Union/European Economic area [@europeancentrefordiseasepreventionandcontrol2019].
-They are also more prone to contract other sexually transmitted diseases and *Nesseria Gonorrhea* strains from MSM exhibit higher antimicrobial resistance [@centersfordiseasecontrolandprevention2019].
-Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their heterosexual counterparts[@Medley2016].
-Moreover, those adverse health outcomes are enmeshed within structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor healthcare access [@closson2018; @ayhan2020].
+Men who have sex with men (MSM) represent a population disproportionately affected by numerous health conditions.
+They represent 70% of new HIV diagnoses [@centerfordiseasecontrolandprevention2020] in the United States of America (USA) and more than half of new HIV diagnoses in the European Union/European Economic area [@europeancentrefordiseasepreventionandcontrol2019].
+They are also more prone to contract other sexually transmitted diseases and *Nesseria Gonorrhoea* strains from MSM exhibit higher antimicrobial resistance [@centersfordiseasecontrolandprevention2019].
+Furthermore, mental health conditions such as depression, anxiety, suicide attempts or self-harm are more prevalent among MSM [@ross2018; @Liu2019; @luo2017] and substance use is more common than for their heterosexual counterparts [@Medley2016].
+Moreover, those adverse health outcomes are enmeshed within structural disadvantages such as violence, stigma, discrimination [@collier2013; @Lee2016; @Lea2014] as well as with poverty, unemployment, unstable housing and poor access to healthcare [@closson2018; @ayhan2020].
 
 For more than 20 years, syndemic theory has provided a framework to examine the interrelations between social conditions, mental health and physical health [@singer2017].
-Described for the first time in 1996 by Merrill Singer [@singer1996], a syndemic consists of two more interacting epidemics producing an excess burden in a population because of harmful social conditions [@singer2003]To speak of a syndemic, three conditions must be met [@mendenhall2020] :
+Described for the first time in 1996 by Merrill Singer [@singer1996], a syndemic consists of two or more interacting epidemics producing an excess burden in a population due to harmful social conditions [@singer2003].
+To speak of a syndemic, three conditions must be met [@mendenhall2020] :
 
-1.  Two or more conditions cluster in a given population
+1.  Two or more conditions cluster in a given population.
 
-2.  This clustering is due to an adverse social context such as poverty or stigmatization
+2.  This clustering is due to an adverse social context such as poverty or stigmatisation.
 
-3.  There is some form of biological, social and/or behavioral interaction between the conditions, significantly worsening the health of the affected population
+3.  There is some form of biological, social and/or behavioural interaction between the conditions, significantly worsening the health of the affected population.
 
-Syndemic is thus an holistic framework, describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread [@singer2017].
-As such, its value for studying the health of marginalized populations such as MSM is undeniable.
+A syndemic is thus a holistic framework describing interactions both between diseases themselves and between diseases and the social environment contributing to their emergence, clustering and spread [@singer2017].
+As such, its value for studying the health of marginalised populations such as MSM is undeniable.
 
@@
 
-However this framework is frequently misused by researchers.
+Nevertheless, this framework is frequently misused by researchers.
 A systematic review conducted in 2015 showed the inadequacy of most of the literature in supporting one of its core tenets [@tsai2015].
-Indeed, this paper demonstrated that, although synergistic interaction between diseases lies in the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy.
-More recently, a scoping review published in 2020 confirmed this finding as most recently-published citations failed to describe the interactions between diseases needed to account for a true syndemic [@Singer2020].
-Scholars in the field have been calling for greater clarity in the use of the concept and urged researchers to describe more precisely the interactions they observe between health conditions [@singer2021 ; @mendenhall2020].
+Indeed, that paper demonstrated that, although synergistic interaction between diseases lies at the core of the theory, most papers failed to use relevant statistics to demonstrate the existence of a synergy.
+More recently, a scoping review published in 2020 confirmed this finding that most recently published citations did not describe the interactions between diseases needed to account for a true syndemic [@Singer2020].
+Scholars in the field have been calling for greater clarity in the use of the concept and have urged researchers to describe more precisely the interactions they observe between health conditions [@singer2021 ; @mendenhall2020].
 
-However, to our knowledge none of the existing reviews or recommendations have focused on syndemic literature applied specifically on MSM.
-We thus sought to fill this gap by conducting a scoping review with the objective to map the following :
+However, to our knowledge none of the existing reviews or recommendations have focused on syndemic literature applied specifically to MSM.
+We thus sought to fill this gap by conducting a scoping review with the objective to map the following:
 
-1.  the study design used ;
+1.  the study design used,
 
-2.  the subpopulations of MSM studied ;
+2.  the subpopulations of MSM studied,
 
-3.  the psychosocial conditions considered as forming a syndemic and how they were measured;
+3.  the psychosocial conditions considered as forming a syndemic and how they were measured,
 
-4.  the outcomes studied;
+4.  the outcomes studied,
 
-5.  the statistics used to evaluate the concept of interaction;
+5.  the statistics used to evaluate the concept of interaction,
 
-6.  the hypothesis for biological and sociobiological interactions proposed by the authors, when available;
+6.  the hypothesis for biological and sociobiological interactions proposed by the authors, when available,
 
-7.  relevant frameworks that may compliment syndemic theory to better understand the health of MSM and
+7.  relevant frameworks that may compliment syndemic theory to better understand the health of MSM and,
 
-8.  the key findings of these studies
+8.  the key findings of these studies.
 

### 2022-04-22 _bookdown_files/03-methodology.Rmd
Reviews [1st round]

@@
 
-# Methodology
+# Materials and Methods
 
-The complete protocol of this scoping review was published in 2020 [Anonymous 2020].
+The complete protocol of this scoping review was published in 2020 [Author (2020 of publication) Details omitted for double-blind review.].
 
@@
 [@levac2010].
-We also took into account the recommendations formulated by Colqhoun et al.
+We also considered the recommendations formulated by Colquhoun et al.
 [@colquhoun2014] and the updated guidance by Peters and colleagues [@peters2020].
 We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses extension for Scoping Reviews (PRISMA-ScR) [@Tricco2018].
-The completed checklist can be found in \@ref(tab:PRISMA-ScR) of the supplementary materials.
+The completed checklist can be found in Table \@ref(tab:PRISMA-ScR) of the supplementary materials.
 
-Screening and data charting was completed using DistillerSR (Evidence Partners, Ottawa, Canada).
-Scripts, statistics, charts, tables and the present paper was generated using R [@rcoreteam2020], RStudio [@rstudioteam2020] and appropriate packages.
-To ensure the complete transparency and reproducibility of this article, our data manager (M.O.) uploaded every data used to generate this article on Open Science Framework (DOI : [masked for the anonymity of the review])
+Screening and data charting were completed using DistillerSR (Evidence Partners, Ottawa, Canada).
+Scripts, statistics, charts, tables and the present paper was generated using R [@rcoreteam2020], RStudio [@rstudioteam2020] and the appropriate packages.
+To ensure the complete transparency and reproducibility of this article, the lead author (M.O.) uploaded all data used to generate this article on Open Science Framework ([[DOI:[masked](DOI:%5Bmasked](DOI:%5Bmasked%5D(DOI:%5Bmasked)%7B.uri%7D){.uri} for the anonymity of the review])
 
-Our main research question : *"What is known about Syndemic Theory applied to MSM"* was subdivided into three sub-questions :
+Our main research question was: *"What is known about Syndemic Theory applied to MSM"* was subdivided into three sub-questions:
 
-1.  *"How are studies concerning Syndemic Theory applied to MSM conducted ?"*;
-2.  *"How is the concept of interaction explored in syndemic research applied to MSM ?"* and
-3.  *"What were the key findings of these studies ?"*.
+1.  *"How are studies concerning Syndemic Theory applied to MSM conducted?"*;
+2.  *"How is the concept of interaction explored in syndemic research applied to MSM?"* and
+3.  *"What were the key findings of these studies?"*
 
-To answer these questions, we conducted a systematic search strategy in the following databases : Medline, PsycInfo, Scopus, Cochrane Central Register of Controlled Trials and ProQuest Sociological Abstracts using complex search equations to include every synonym for "men who have sex with men".
-The complete search strategy for every database can be found in the Supplementary Material of our protocol.
+To answer these questions, we conducted a systematic search strategy in the following databases: Medline, PsycInfo, Scopus, Cochrane Central Register of Controlled Trials and ProQuest Sociological Abstracts using complex search equations to include every synonym for "men who have sex with men." The complete search strategy for each database can be found in the Supplementary Material of our protocol.
 No date limit was applied given the relative novelty of the syndemic literature.
-A first search using this strategy was conducted the 11th of June 2020 and was subsequently updated on the 9th of February 2021 and finally on the 11th of November 2021.
+A first search using this strategy was conducted on the 11th of June 2020 and was subsequently updated on the 9th of February 2021 and finally on the 11th of November 2021.
 
@@
 As it exceeded our cutoff of 0.8, the rest of the screening process was conducted by the main investigator only.
-Articles were included if they met the following criteria :
+Articles were included if they met the following criteria:
 
--   MSM was either the only population studied in the paper or, if studied alongside other populations, such as transgender women, disaggregated data must have been available for MSM
+-   MSM was either the only population studied in the paper or, if studied alongside other populations, such as transgender women, disaggregated data must have been available for MSM.
 
--   Syndemic framework was the main focus of the study
+-   The syndemic framework was the main focus of the study.
 
 -   Studies were cohort, case-control, cross-sectional, controlled trials, mixed studies, qualitative studies, systematic reviews or meta-analyses.
-We excluded letters, commentaries, conference abstracts, editorials or narrative reviews
+We excluded letters, commentaries, conference abstracts, editorials or narrative reviews.
 
@@
 After inclusion of relevant studies, we hand-searched the reference lists to manually add pertinent studies.
-The same selection process was then applied and these papers are marked as "Additional records identified through other sources" in the study selection flow diagram.
+The same selection process was then applied, and these papers are marked as "Additional records identified through other sources" in the study selection flow diagram (Figure \@ref(fig:PRISMA)).
 
 Data charting was also performed using forms generated in DistillerSR by the authors.
-The complete list of all variables for which data were sought can be found in our protocol [Anonymous 2020].
+The complete list of all variables for which data were sought can be found in our protocol[Anonymous 2020].
 Furthermore, the README file of our *Data* subdirectory contains an exhaustive definition of every variable included.
-Two amendments were made to our initial protocol :
+Two amendments were made to our initial protocol:
 
-1.  We included a variable to chart any additional framework the authors might have used
+1.  We included a variable to chart any additional frameworks the authors might have used.
 
@@
 We included variables to chart data for systematic reviews and meta-analyses.
-These two kind of studies were omitted from our initial protocol as we were not aware of the existence of systematic reviews on syndemic theory applied to MSM by the time we published the protocol.
-The variables included were general characteristics (authors, year, location, design, total sample size), purpose of the review, number of studies included, hypothesis for biological or bio-social interaction, key findings and additional framework.
+These two kinds of studies were omitted from our initial protocol as we were not aware of the existence of systematic reviews on syndemic theory applied to MSM at the time we published the protocol.
+The variables included were general characteristics (authors, years, location, design, total sample size), purpose of the review, number of studies included, hypotheses for biological or bio-social interaction, key findings and additional frameworks.
 
-Data was then collated, summarised and reported using R, RStudio and relevant packages.
-Charts were generated to better visualize year of publication, location, population and syndemic conditions studied.
+Data were then collated, summarised and reported using R, RStudio and relevant packages.
+Charts were generated to better visualise years of publication, location, population and syndemic conditions studied.
 Tables were generated to summarise the main variables of every article as well as the measurement methods of the most studied syndemic conditions.
 These tables can be found respectively in part B and C of the supplementary materials of this paper.
-Additionally, we generated an online report accessible at <https://datastudio.google.com/u/0/reporting/56c1e17a-fa3f-47e9-9516-d3d0eef7ec1> This report contains every study included and provide scholars in the field the opportunity to search relevant studies using multiple filters.
+Additionally, we generated an online report accessible at (link omitted for double-blind review).
+This report contains all studies included in the review and provides researchers in the field the opportunity to search relevant studies using multiple filters.

### 2022-04-22 _bookdown_files/04-results.Rmd
Reviews [1st round]

--- 2022-01-23 _bookdown_files/04-results.Rmd
@@
 
-#Load required packages :
+#Load required packages:
 library(tidyverse)
@@
 
-#Load the data from the .csv files
+#Load the data from the.csv files
 source("./scripts/read_data.R", local = knitr::knit_global())
@@
 
-This section summarizes the findings relevant to our research questions.
-\@ref(tab:RefTabQuant), \@ref(tab:RefTabQual) and \@ref(tab:RefTabRev) in the supplementary material, summarize every reference identified and the variables extracted to answer our research questions for quantitative studies, qualitative studies and reviews, respectively.
+This section summarises the findings relevant to our research questions.
+Table \@ref(tab:RefTabQuant), \@ref(tab:RefTabQual) and \@ref(tab:RefTabRev) in the supplementary material, summarise every reference identified and the variables extracted to answer our research questions for quantitative studies, qualitative studies and reviews, respectively.
 
-## Literature search
+## Literature Search
 
-The electronic search identified 840 references and our handsearch of reference lists resulted in the addition of the seminal study by Stall and colleague @Stall2003 .
+The electronic search identified 840 references and our hand search of reference lists resulted in the addition of the seminal study by Stall and colleague [@Stall2003].
 After removing duplicates, 305 records were screened for inclusion.
@@
 After screening the title and abstract, 124 records were excluded.
-The two main reasons for exclusion at this stage were that MSM was not the main study population (n=49) and that syndemic was not the main focus of the paper (n=37).
-38 studies were excluded because the type of publication did not meet our inclusion criteria.
+The two main reasons for the exclusion at this stage were that MSM were not the main study population (n=49) and that syndemic was not the main focus of the paper (n=37).
+Thirty-eight studies were excluded because the type of publication did not meet our inclusion criteria.
 
-The full texts of the 181 remaining references were obtained and read; 66 were excluded after this phase.
+The full texts of the 181 remaining references were obtained and read; Sixty-six were excluded after this phase.
 During the previous step, we had decided to tentatively include papers in which the sample was not entirely comprised of MSM.
-After reviewing the full paper, we decided to exclude studies if the MSM data was aggregated with data from another population (n=11), most commonly transgender women.
+After reviewing the full paper, we decided to exclude studies if the MSM data were aggregated with data from another population (n=11), most commonly transgender women.
 The rationale for this decision was to keep the focus clearly on MSM.
@@
 
-#Source the scripts used to manipulate the data from the .csv files
+#Source the scripts used to manipulate the data from the.csv files
 source("./scripts/create_year_design.R", local = knitr::knit_global())
@@
 
-The publication date of the studies ranges from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number papers published annually from 2013 onward as illustrated in Figure \@ref(fig:PlotYear).
+The publication date of the studies ranges from `r min(year_design$year)` to `r max(year_design$year)` with a marked increase in the number of papers published annually from 2013 onward as illustrated in Figure \@ref(fig:PlotYear).
 There is also an increase in the diversity of the studies, both in the study design used and the continents where the studies were conducted.
@@
 
-However, despite the increasing diversity, the vast majority of the studies were conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the United States of America (N= `r .USA_studies`).
+However, despite the increasing diversity, the vast majority of the studies were conducted in North America (N = `r .North_America_studies`), with a large predominance of studies in the USA (N= `r .USA_studies`).
 The majority of the remaining studies were then located in Asia (N = `r .Asia_studies`) or in Europe (N = `r .Europe_studies`).
-South America (N = `r .South_America_studies`) and Africa (N = `r .Africa_studies`) were the least represented continents.
+South America (N = `r .South_America_studies`) and Africa (N = `r .Africa_studies`) are the least represented continents.
 
-In terms of design, a similar pattern appears, with most of the studies employing a cross-sectional design (N = `r .N_cross_sec`).
+In terms of design, a similar pattern appears, with most of the studies employed a cross-sectional design (N = `r .N_cross_sec`).
 The number of longitudinal studies has grown steadily since 2014 and represents `r percent(.N_long/nrow(overview_of_studies))` of the papers.
@@
 Compared to quantitative studies, qualitative studies are under-represented, with only `r .N_qual` papers.
-In terms of analysis method, the most common was thematic (content) analysis (N= `r sum(!is.na(summary_qualitative$thematic_content)) + sum(!is.na(summary_qualitative$thematic))`).
-The rest of the studies consisted of framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and constant comparative analysis (N = `r sum(!is.na(summary_qualitative$comparative))`).
+In terms of analysis method, the most common is thematic (content) analysis (N= `r sum(!is.na(summary_qualitative$thematic_content)) + sum(!is.na(summary_qualitative$thematic))`).
+The rest of the studies consists of framework analysis (N = `r sum(!is.na(summary_qualitative$framework))`), grounded theory (N = `r sum(!is.na(summary_qualitative$grounded))`), analytic induction (N = `r sum(!is.na(summary_qualitative$analytic_induction))`) and constant comparative analysis (N = `r sum(!is.na(summary_qualitative$comparative))`).
 
 We identified 2 papers employing mixed methods design [@buttram2015; @Halkitis2012]; Buttram et al.
-used a cross-sectional design for the quantitative part and in-depth interviews analyzed through grounded theory for the qualitative part while Halkitis et al used a cross-sectional quantitative survey and in-depth discovery interviews.
+used a cross-sectional design for the quantitative part and in-depth interviews analysed through grounded theory for the qualitative part while Halkitis et al.
+used a cross-sectional quantitative survey and in-depth discovery interviews.
 
@@
 
-Finally, the median sample size of the studies was `r median(sample$sample_size)` (range : `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported, ranged from `r min(sample$age, na.rm = T)` to `r round(max(sample$age, na.rm = T), digits = 0)` years.
+Finally, the median sample size of the studies is `r median(sample$sample_size)` (range: `r min(sample$sample_size)` - `r number(max(sample$sample_size))`) and the mean age of the participants, when reported, ranges from `r min(sample$age, na.rm = T)` to `r round(max(sample$age, na.rm = T), digits = 0)` years.
 
@@
 
-Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.
-
-\
-Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents[@Perry].
-
-\
+Less than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focus on a subpopulation of MSM; of those, we identified seven types of MSM subpopulations: (a) young MSM; (b) older MSM; (c) MSM from a racial/ethnic minority; (d) MSM living with HIV; (e) MSM engaged in sex work; (f) Men who have Sex with Men and Women (MSMW); and (g) transgender MSM.\
+Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM [@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents [@Perry].\
 Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.\
-`r english(sum(population$race_ethnicity == "Latino"))` studies focus on Latino MSM (LMSM) and `r english(sum(population$race_ethnicity == "Latino & Black"))` study focus on both BMSM and LMSM[@cassels2020].\
+`r english(sum(population$race_ethnicity == "Latino"))` studies focus on Latino MSM (LMSM) and `r english(sum(population$race_ethnicity == "Latino & Black"))` study focus on both BMSM and LMSM [@cassels2020].
 
 Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV.
-Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.
-
-\
+Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.\
 Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).
@@
 \
-In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulations.\
-`r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].
+In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that do not focus on any subpopulation in particular but present disaggregated data and analyses for one or more MSM subpopulations.\
+`r .N_disaggregated` studies present such data: `r .N_dis_BMSMW` for Black MSMW [@dyer2020], `r .N_dis_MSMW` for MSMW [@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV [@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM [@Mustanski2017].
 
@@
 
-We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included : depression (N = `r nodes$studies[nodes$label == "depression"]`), substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), intimate partner violence [IPV] (N = `r nodes$studies[nodes$label == "IPV"]`), childhood sexual abuse [CSA] (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`) , binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), alcohol use disorder [AUD] (N = `r nodes$studies[nodes$label == "AUD"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), sexual risk behaviors (N = `r nodes$studies[nodes$label == "sexual_risk"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder [SUD] (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), post-traumatic stress disorder [PTSD] (N = `r nodes$studies[nodes$label == "PTSD"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), sexually transmitted infections [STI] (N = `r nodes$studies[nodes$label == "STI"]`), intravenous drug use [IDU] (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder [ADHD] (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`), school bullying (N = `r nodes$studies[nodes$label == "bullying"]`), and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
+We identified `r nrow(nodes)` different syndemic conditions in the `r nrow(summary_quantitative)` quantitative studies we included.
 
-We chose to distinguish between alcohol use disorder, binge drinking and alcohol use instead of merging them into a broad "alcohol-related syndemic condition".
-Some authors also considered "heavy drinking" [@Martinez2016a; @martinez2020] or "heavy alcohol use"[@Mimiaga2015b] but we chose to aggregate these conditions under "binge drinking" for clarity.
+The health-related conditions we identified are : depression (N = `r nodes$studies[nodes$label == "depression"]`), alcohol use disorder (AUD) (N = `r nodes$studies[nodes$label == "AUD"]`), sexual compulsivity (N = `r nodes$studies[nodes$label == "sex_comp"]`), suicidal thoughts and/or attempts (N = `r nodes$studies[nodes$label == "suicide"]`), anxiety (N = `r nodes$studies[nodes$label == "anxiety"]`), substance use disorder (SUD) (N = `r nodes$studies[nodes$label == "substance_use_disorder"]`), post-traumatic stress disorder (PTSD) (N = `r nodes$studies[nodes$label == "PTSD"]`), general mental distress (N = `r nodes$studies[nodes$label == "distress"]`), internalised homophobia (N = `r nodes$studies[nodes$label == "internalised_homophobia"]`), low self-esteem (N = `r nodes$studies[nodes$label == "esteem"]`), sexually transmitted infections (STI) (N = `r nodes$studies[nodes$label == "STI"]`), involuntary subordination (N = `r nodes$studies[nodes$label == "subordination"]`), HIV diagnosis (N = `r nodes$studies[nodes$label == "HIV"]`), hostility (N = `r nodes$studies[nodes$label == "hostility"]`), stress (N = `r nodes$studies[nodes$label == "stress"]`), experience of trauma (N = `r nodes$studies[nodes$label == "trauma"]`), alexithymia (N = `r nodes$studies[nodes$label == "alexithymia"]`), attention deficit hyperactivity disorder (ADHD) (N = `r nodes$studies[nodes$label == "ADHD"]`), cognitive escape (N = `r nodes$studies[nodes$label == "escape"]`), hypersexuality (N = `r nodes$studies[nodes$label == "hypersexuality"]`), impulsivity (N = `r nodes$studies[nodes$label == "impulsivity"]`), poor physical health (N = `r nodes$studies[nodes$label == "physical_health"]`) and sleep disturbance (N = `r nodes$studies[nodes$label == "sleep_disturbance"]`).
+
+Alongside these health-related conditions, we also identified numerous social conditions: substance use (N = `r nodes$studies[nodes$label == "substance_use"]`), intimate partner violence (IPV) (N = `r nodes$studies[nodes$label == "IPV"]`), childhood sexual abuse (CSA) (N = `r nodes$studies[nodes$label == "CSA"]`), polysubstance use (N = `r nodes$studies[nodes$label == "polysubstance"]`), binge drinking (N = `r nodes$studies[nodes$label == "binge"]`), experiences of violence (N = `r nodes$studies[nodes$label == "violence"]`), sexual risk behaviours (N = `r nodes$studies[nodes$label == "sexual_risk"]`), alcohol use (N = `r nodes$studies[nodes$label == "alcohol_use"]`), discrimination (N = `r nodes$studies[nodes$label == "discrimination"]`), chemsex (N = `r nodes$studies[nodes$label == "chemsex"]`), loneliness (N = `r nodes$studies[nodes$label == "loneliness"]`), incarceration (N = `r nodes$studies[nodes$label == "incarceration"]`), unstable housing (N = `r nodes$studies[nodes$label == "unstable_housing"]`), tobacco use (N = `r nodes$studies[nodes$label == "tobacco_use"]`), childhood abuse (N = `r nodes$studies[nodes$label == "childhood"]`), low social support (N = `r nodes$studies[nodes$label == "social_support"]`), exchange sex (N = `r nodes$studies[nodes$label == "exchange_sex"]`), intravenous drug use (IDU) (N = `r nodes$studies[nodes$label == "IDU"]`), poverty (N = `r nodes$studies[nodes$label == "poverty"]`), unemployment (N = `r nodes$studies[nodes$label == "unemployment"]`), poor healthcare access (N = `r nodes$studies[nodes$label == "healthcare_access"]`), frequenting gay social venues (N = `r nodes$studies[nodes$label == "venues"]`) and school bullying (N = `r nodes$studies[nodes$label == "bullying"]`).
+
+We chose to distinguish between AUD, binge drinking and alcohol use instead of merging them into a broad 'alcohol-related syndemic condition'.
+Some authors also considered 'heavy drinking' [@Martinez2016a; @martinez2020] or 'heavy alcohol use' [@Mimiaga2015b] but we chose to aggregate these conditions under 'binge drinking' for clarity.
 Similarly, we distinguish between substance use, substance use disorder, intravenous drug use, polysubstance use, marijuana use, tobacco use and chemsex since they differ in terms of potential harm and the context of use.
@@
 
-In order to better understand the connections between the syndemic conditions in the studies we elaborated a network plot (Figure \@ref(fig:SyndemicNetwork)).
+In order to better understand the connections between the syndemic conditions in the studies, we elaborated a network plot (Figure \@ref(fig:SyndemicNetwork)).
 Nodes represent the syndemic conditions studied in the literature and edges (connectors) are drawn between two nodes when two conditions are studied in the same research paper.
@@
 Moreover, as a force-directed graph, the location of the nodes gives an indication regarding their importance in terms of frequency and linkage to other conditions.
-As such, depression occupies a more central position than ADHD which was only studied once.
+As such, depression occupies a more central position than ADHD, which was only studied once.
 
-In this figure, we divided the conditions studied into four categories : mental health (e.g.
+In this figure, we divided the conditions studied into four categories: mental health (e.g.
 depression, anxiety, PTSD) in blue, social conditions (e.g.
@@
 unemployment, healthcare access) in orange and physical health (e.g.
-STI, HIV) in red .
-The figure shows that structural syndemic conditions and physical health-related syndemic conditions are much less central, therefore much less studied, than social syndemic conditions and mental health-related syndemic conditions which are located towards the center of the figure.
+STI, HIV) in red.
+The figure shows that structural syndemic conditions and physical health-related syndemic conditions are much less central, therefore much less studied, than social syndemic conditions and mental health-related syndemic conditions which are located toward the center of the figure.
 
@@
 However, nearly half of these pairs of conditions (N = `r nrow(.edges_1)`) appear in only one research paper.
-On the other hand , the most studied pairs of syndemic conditions were depression and IPV (N = `r edges$weight[edges$from == 1 & edges$to == 4]`), depression and substance use (N = (N = `r edges$weight[edges$from == 1 & edges$to == 2]`), depression and CSA (N = `r edges$weight[edges$from == 1 & edges$to == 10]`), IPV and CSA (N = `r edges$weight[edges$from == 4 & edges$to == 10]`) and depression and polysubstance use (N = `r edges$weight[edges$from == 1 & edges$to == 11]`).
+On the other hand, the most studied pairs of syndemic conditions were depression and IPV (N = `r edges$weight[edges$from == 1 & edges$to == 4]`), depression and substance use (N = (N = `r edges$weight[edges$from == 1 & edges$to == 2]`), depression and CSA (N = `r edges$weight[edges$from == 1 & edges$to == 10]`), IPV and CSA (N = `r edges$weight[edges$from == 4 & edges$to == 10]`) and depression and polysubstance use (N = `r edges$weight[edges$from == 1 & edges$to == 11]`).
 
@@
 As a force-directed network, the most studied and interconnected conditions are the most central.
-Moreover, each node is circled by a pie chart of their frequency in the review.
+Additionally, each node is circled by a pie chart of their frequency in the review.
 The thickness of the edges linking two nodes reflects the number of studies in which the two conditions were studied together.", fig.id="SyndemicNetwork", fig.width=7.45, fig.height=5.32, fig.align='center'}
@@
 For the most often studied syndemic conditions, we found a high degree of variability in their measurement.
-Different authors used different scales or criteria and, even when the same scale or criteria was used, the cutoff or reference period differed among studies.
+Different authors used different scales or criteria and, even when the same scale or criteria were used, the cutoff or reference period differed among studies.
 For the sake of brevity, we will only provide a detailed description of the measurement method for the five most studied syndemic conditions.
@@
 
-For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria were used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.
-The most frequently used scales were the full Center for Epidemiologic Studies-Depression scale [CESD] (N = 26) and the 10-items version of this scale [CESD-10] (N=11), the 9-items version of the Patient Health Questionnaire [PHQ-9] (N=9) and the Beck Depression Inventory [BDI-II] (N = 5).\
-Cutoff for these scales varied the most for the CESD (range : 16 to 27) and the PHQ-9 (range : 5 to 15).\
-When a scale was not used, the most frequent criteria to assess the presence of depression was the participant being on medication for depression in the past 12 months (N = 4).
+For depression, `r length(unique(.depression_measurement$depression_scale_criteria))` different scales or criteria are used among the `r nodes$studies[nodes$label == "depression"]` studies in which this condition was studied.
+The most frequently used scales are the full Center for Epidemiologic Studies-Depression scale (CESD) (N = 26) and the 10-item version of this scale (CESD-10) (N=11), the 9-item version of the Patient Health Questionnaire (PHQ-9) (N=9) and the Beck Depression Inventory (BDI-II) (N = 5).\
+Cutoff for these scales varied the most for the CESD (range: 16 to 27) and the PHQ-9 (range: 5 to 15).\
+When a scale is not used, the most frequent criteria to assess the presence of depression is the participant being on medication for depression in the past 12 months (N = 4).
 
 For substance use, we looked at the class of substances explicitly screened by the authors and the reference period used.
-The most frequently screened class of substance was stimulants (i.e.
-cocaine/crack, amphetamines ; N = `r .substances_prev$sum[["stimulants"]]`), followed by depressants (i.e.
-GHB/GBL, benzodiazepines without prescriptions ; (N = `r .substances_prev$sum[["depressants"]]`), opioids (i.e.
-opioids misuse and heroin ; N = `r .substances_prev$sum[["opioids"]]`), marijuana (N = `r .substances_prev$sum[["marijuana"]]`), ecstasy /MDMA (N = `r .substances_prev$sum[["ecstasy"]]`), hallucinogens (i.e.
-ketamine, psilocybine, phencyclidine ; N = `r .substances_prev$sum[["hallucinogens"]]`), inhalants (nitrous oxyde, Popper ; N = `r .substances_prev$sum[["inhalants"]]`) and new psychoactive substances (i.e.
-synthetic cannabinoids, cathinones ; N = `r .substances_prev$sum[["NPS"]]`).\
-Reference period ranged from the past month to over the lifetime.
+The most frequently screened class of substance is stimulants (i.e.
+cocaine/crack, amphetamines; N = `r .substances_prev$sum[["stimulants"]]`), followed by depressants (i.e.
+GHB/GBL, benzodiazepines without prescriptions; (N = `r .substances_prev$sum[["depressants"]]`), opioids (i.e.
+opioids misuse and heroin; N = `r .substances_prev$sum[["opioids"]]`), marijuana (N = `r .substances_prev$sum[["marijuana"]]`), ecstasy /MDMA (N = `r .substances_prev$sum[["ecstasy"]]`), hallucinogens (i.e.
+ketamine, psilocybin, phencyclidine; N = `r .substances_prev$sum[["hallucinogens"]]`), inhalants (nitrous oxide, popper; N = `r .substances_prev$sum[["inhalants"]]`) and new psychoactive substances (i.e.
+synthetic cannabinoids, cathinones; N = `r .substances_prev$sum[["NPS"]]`).\
+Reference periods range from the past month to over the lifetime.
 
-For polysubstance use, 18 studies considered that there was polysubstance use when three or more classes of substances were used while nine studies defined polysubstance use as more than one class of substance being used.
-Furthermore, six studies excluded marijuana from the class of substances screened and two studies excluded stimulants, because stimulants were already screened in another syndemic condition.
+For polysubstance use, 18 studies consider that there is polysubstance use when three or more classes of substances are used while nine studies define polysubstance use as more than one class of substance being used.
+Furthermore, six studies exclude marijuana from the class of substances screened and two studies exclude stimulants, because stimulants were already screened in another syndemic condition.
 
-For IPV, 5 types of intimate partner violence were identified : physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), gay-related violence (e.g.
-threats to reveal the partner's sexual orientation ; N = `r .IPV_prevalence$sum[["gay-related IPV"]]`) and HIV-related violence (e.g.
-threats to disclose the partner's serologic status ; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`).
-Reference periods varied from past month to lifetime.
+Five types of IPV were identified: physical violence (N = `r .IPV_prevalence$sum[["physical IPV"]]`), psychological violence (N = `r .IPV_prevalence$sum[["psychological IPV"]]`), sexual violence (N = `r .IPV_prevalence$sum[["sexual IPV"]]`), gay-related violence (e.g.
+threats to reveal the partner's sexual orientation; N = `r .IPV_prevalence$sum[["gay-related IPV"]]`) and HIV-related violence (e.g.
+threats to disclose the partner's serologic status; N = `r .IPV_prevalence$sum[["HIV-related IPV"]]`).
+Reference periods vary from the past month to over the lifetime.
 
 For CSA, we identified `r length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Definition"]))` different definitions and `r english(length(unique(.CSA_measurement$CSA_scale_criteria[.CSA_measurement$CSA_type == "Scale"])))` scales among the `r nodes$studies[nodes$label == "CSA"]` studies.
-The various definitions differed on the age at which the sexual intercourse occurred to be qualified as childhood sexual abuse, the age gap between the victim and the perpetrator and whether the sexual intercourse was unwanted.
-The most frequent definition was Finkelhor's definition[@finkelhor1994] : any sexual experience before 13 years old with someone at least five years older or any sexual experience between 13 and 17 years old with someone at least ten years older (N = 7).
+The various definitions differ regarding the age at which sexual intercourse occurred to be qualified as childhood sexual abuse, the age gap between the victim and the perpetrator and whether the sexual intercourse was unwanted.
+The most frequent definition is Finkelhor's definition [@finkelhor1994]: any sexual experience before 13 years old with someone at least five years older or any sexual experience between 13 and 17 years old with someone at least ten years older (N = 7).
 
@@
 We identified `r ncol(.outcomes) - 1` different outcomes in our sample of quantitative studies.
-Sexual risk behaviors was the most frequently studied outcome, appearing in `r sum(!is.na(.outcomes$outcome_sexual_risk))` research papers.
-The second most studied outcome was HIV diagnosis (N = `r sum(!is.na(.outcomes$outcome_HIV))`), followed by STI diagnosis (N = `r sum(!is.na(.outcomes$outcome_STI))`), adherence to antiretroviral therapy (N = `r sum(!is.na(.outcomes$outcome_adherence))`), pre-exposure prophylaxis (PrEP) use (N = `r sum(!is.na(.outcomes$outcome_PrEP))`), healthcare use (N = `r sum(!is.na(.outcomes$outcome_healthcare))`) and the syndemic conditions themselves (N = `r sum(!is.na(.outcomes$outcome_syndemic))`).
-Less often, researchers also used viral load (N = `r sum(!is.na(.outcomes$outcome_VL))`), suicidality (N = `r sum(!is.na(.outcomes$outcome_suicide))`) or engaging in exchange sex (N = `r sum(!is.na(.outcomes$outcome_exchange_sex))`) as outcomes.
+Sexual risk behaviour is the most frequently studied outcome, appearing in `r sum(!is.na(.outcomes$outcome_sexual_risk))` research papers.
+The second most studied outcome is HIV diagnosis (N = `r sum(!is.na(.outcomes$outcome_HIV))`), followed by STI diagnosis (N = `r sum(!is.na(.outcomes$outcome_STI))`), adherence to antiretroviral therapy (N = `r sum(!is.na(.outcomes$outcome_adherence))`), pre-exposure prophylaxis (PrEP) use (N = `r sum(!is.na(.outcomes$outcome_PrEP))`), healthcare use (N = `r sum(!is.na(.outcomes$outcome_healthcare))`) and the syndemic conditions themselves (N = `r sum(!is.na(.outcomes$outcome_syndemic))`).
+Less often, researchers also use viral load (N = `r sum(!is.na(.outcomes$outcome_VL))`), suicidality (N = `r sum(!is.na(.outcomes$outcome_suicide))`) or engaging in exchange sex (N = `r sum(!is.na(.outcomes$outcome_exchange_sex))`) as outcomes.
 
-Every other outcome was only studied once : HIV screening [@Chandler2019b], HIV transmission [@satyanarayana2021], engagement in HIV care [@Biello2016], sexual violence [@semple2017], substance use [@turpin2020], engagement in chemsex [@friedman2014], having sexual intercourse with both men and women [@eaton2013] , help-seeking behaviors [@achterbergh2021], physical activity [@Zhang2019], glycemic control [@Byg2016], hypothalamic-pituitary-adrenal (HPA) axis dysregulation [@carrico2018] and elevation in rectal cytokines/chemokines [@tapia2021].
+The other outcomes are only studied once: HIV screening [@Chandler2019b], HIV transmission [@satyanarayana2021], engagement in HIV care [@Biello2016], sexual violence [@semple2017], substance use [@turpin2020], engagement in chemsex [@friedman2014], having sexual intercourse with both men and women [@eaton2013] , help-seeking behaviours [@achterbergh2021], physical activity [@Zhang2019], glycaemic control [@Byg2016], hypothalamic-pituitary-adrenal (HPA) axis dysregulation [@carrico2018] and elevation in rectal cytokines/chemokines [@tapia2021].
 
-There was a high degree of variability in the definition of what constitutes a sexual risk behaviors though the most frequently used proxy was, by far, condomless anal sex (N = `r .CAS_number`).
+There is a high degree of variability in the definition of what constitutes sexual risk behaviours, though the most frequently used proxy is, by far, condomless anal sex (N = `r .CAS_number`).
 
-Used in conjunction with condomless anal sex, other proxies for sexual risk were number of partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_number_partners))`), substance use during sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_substance_sex))`), condomless vaginal sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CVS))`), condomless oral sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_COS))`), sexual intercourse with female partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_female_sex))`) , engaging in group sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_non_disclosure))`) and non-disclosure of HIV serostatus before first sexual intercourse with current main partner (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_non_disclosure))`).
+Used in conjunction with condomless anal sex, other proxies for sexual risk are number of partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_number_partners))`), substance use during sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_substance_sex))`), condomless vaginal sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CVS))`), condomless oral sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_COS))`), sexual intercourse with female partners (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_female_sex))`), engaging in group sex (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_group_sex))`) and non-disclosure of HIV serostatus before first sexual intercourse with current main partner (N = `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_non_disclosure))`).
 
-When HIV was used as an outcome, it was self-reported in more than half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting was used in `r english(sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T))` papers out of `r english(sum(!is.na(.outcomes$outcome_STI)))`.
+When HIV is used as an outcome, it is self-reported in more than half of the studies (`r sum(.outcomes_measurement$measurement_outcome_HIV == "Self-report of HIV status", na.rm = T)` studies out of `r sum(!is.na(.outcomes$outcome_HIV))`) Similarly, for STI diagnosis, self-reporting is used in `r english(sum(.outcomes_measurement$measurement_outcome_STI_report == "Self-reported", na.rm = T))` papers out of `r english(sum(!is.na(.outcomes$outcome_STI)))`.
 
@@
 Chakrapani et al.
-used a pre-test/post-test non-equivalent group design and the intervention consisted of motivational-interviews.
+used a pre-test/post-test non-equivalent group design and the intervention consisted of motivational interviews.
 The goal of this intervention was to reduce condomless anal intercourse by enhancing condom self-efficacy and addressing co-occurring syndemic conditions.
-
 Achterbergh et al.
-conducted a randomized controlled trial and the intervention consisted of tailored feedback and help-seeking advice on mental health screening.
-The primary endpoint was to increase help-seeking behaviors ; the secondary endpoints were reducing sexual risk behaviors and STI incidence.
-
+conducted a randomised controlled trial and the intervention consisted of tailored feedback and help-seeking advice on mental health screening.
+The primary endpoint was to increase help-seeking behaviours; the secondary endpoints were reducing sexual risk behaviour and STI incidence.
 The intervention lasted for 12 months in both studies.
@@
 the intervention was successful in reducing the psychosocial conditions investigated (depression, alcohol use and internalised homophobia) and improving condom use.
-Furthermore, synergy, as measured by interaction on the additive and multiplicative scales, was present for depression and alcohol use as well as for depression and internalised homophobia on inconsistent condom use.
-Finally, mediation analysis revealed that the improvement in consistent condom use was due to an improvement in condom self-efficacy caused by a reduction in alcohol use and internalised homophobia.
-
-On the other hand, the RCT conducted by Achterbergh et al. failed to affect the primary endpoint nor the two secondary endpoints.
+Furthermore, synergy, as measured by interaction on the additive and multiplicative scales, is present for depression and alcohol use as well as for depression and internalised homophobia on inconsistent condom use.
+Finally, a mediation analysis revealed that the improvement in consistent condom use was due to an improvement in condom self-efficacy caused by a reduction in alcohol use and internalised homophobia.
+On the other hand, the RCT conducted by Achterbergh et al.
+failed to impact the primary endpoint nor the two secondary endpoints.
 
@@
 
-We found `r english(sum(summary_reviews$design == "Systematic review"))` systematic reviews [@lewis2017; @woodward2017; @Lassiter2016] and two meta-analyses [@Rooney2018a; @Pantalone2020] in our review.
+We identified `r english(sum(summary_reviews$design == "Systematic review"))` systematic reviews [@lewis2017; @woodward2017; @Lassiter2016] and two meta-analyses [@Rooney2018a; @Pantalone2020] in our review.
 
@@
 They included `r summary_reviews$studies_included[summary_reviews$authors== "Woodward et al."]` studies in their reviews and identified 31 resilience resources, with social support and financial incomes as the two most frequently cited.
-Of note, most of these resources were associated with a lower HIV risk.
+Of note, most of these resources are associated with a lower HIV risk.
 
@@
 aimed to propose a framework to include religion and spirituality into HIV research with MSM [@Lassiter2016].
-They found that religion and spirituality had mixed effect on syndemic conditions but could be more beneficial for MSM of color than for white MSM.
-Of note, the review was relatively small (including `r english(summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."])` studies) as these two factors are very sparse in syndemic literature.
+They found that religion and spirituality had a mixed effect on syndemic conditions but could be more beneficial for MSM of colour than for white MSM.
+Of note, the review is relatively small (including `r english(summary_reviews$studies_included[summary_reviews$authors== "Lassiter et al."])` studies) as these two factors are very rarely studied in syndemic literature.
 
-Lewis et al.
-sought to examine the HIV prevalence and associated risk behaviors among migrant and ethnic minority MSM in North America and Europe [@lewis2017].
-They found high rates of HIV prevalence and associated risk factors and proposed that transnational migration could be part of a syndemic.
+Lewis and Wilson sought to examine the HIV prevalence and associated risk behaviours among migrants and ethnic minority MSM in North America and Europe [@lewis2017].
+They found high rates of HIV prevalence and associated risk factors and propose that transnational migration could be part of a syndemic.
 
 In their meta-analysis, Rooney et al.
-studied the syndemic conditions associated with sexual compulsivity among MSM and computed the mean effect size as well as whether this effect varied as a function of the type of syndemic conditions associated [@Rooney2018a].
-They included `r summary_reviews$studies_included[summary_reviews$authors== "Rooney et al."]` papers and found that sexual compulsivity was significantly associated with 7 syndemic conditions (anxiety, depression, CSA, alcohol use, substance use, IPV and sexual risk behaviors).
+studied the syndemic conditions associated with sexual compulsivity among MSM and computed the mean effect size as well as whether this effect varied depending on the type of syndemic conditions associated [@Rooney2018a].
+They included `r summary_reviews$studies_included[summary_reviews$authors== "Rooney et al."]` papers and found that sexual compulsivity was significantly associated with 7 syndemic conditions (anxiety, depression, CSA, alcohol use, substance use, IPV and sexual risk behaviours).
 The two strongest associations were with depression and anxiety.
@@
 Finally, Pantalone et al.
-sought to have a better understanding of the state of interventions co-targeting interconnected syndemic conditions and HIV-related health behaviors of MSM [@Pantalone2020].
-They included `r summary_reviews$studies_included[summary_reviews$authors== "Pantalone et al."]` studies and found a small significant positive effect of combined behavioral interventions to improve mental health, substance use, alcohol use and sexual risk behaviors, with significant heterogeneity.
+sought to have a better understanding of the state of interventions co-targeting interconnected syndemic conditions and HIV-related health behaviours of MSM [@Pantalone2020].
+They included `r summary_reviews$studies_included[summary_reviews$authors== "Pantalone et al."]` studies and found a small significant positive effect of combined behavioural interventions to improve mental health, substance use, alcohol use and sexual risk behaviours, with significant heterogeneity.
 Interestingly, a greater number of sessions (at least 9) and individual rather than group interventions showed greater efficacy.
 
-### Additional framework used in the studies
+### Additional frameworks used in the studies
 
@@
 
-`r nrow(.framework)` studies used an additional framework alongside syndemic theory.
-The most widely used was resilience theory (N = 10), followed by minority stress model (N = 5), intersectionality (N=2), social-cognitive theory (N=2), salutogenesis (N=1) and ecological framework (N=1).
+Twenty studies use an additional framework alongside syndemic theory.
+The most widely used is resilience theory (N = 10), followed by minority stress model (N = 5), intersectionality (N=2), social-cognitive theory (N=2), salutogenesis (N=1) and ecological framework (N=1).
 
@@
 
-It should be stated that, when we speak of interaction between syndemic conditions we don't necessarily mean "synergy", though synergy is indeed one of the interactions we consider.
-Drawing from the works of authors such as Tsai and Chakrapani, we consider three types of interaction : synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics [@Tsai2018a; @Chakrapani2019].
-As such, statistical methods such as mediation analysis, path analysis or structural equation modeling are also considered.
+It should be stated that, when we speak of an interaction between syndemic conditions, we do not necessarily mean 'synergy', though synergy is indeed one of the interactions we consider.
+Drawing from the works of authors such as Tsai and Chakrapani, we consider three types of interaction: synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics [@Tsai2018a; @Chakrapani2019].
+As such, statistical methods such as mediation analysis, path analysis or structural equation modelling are also considered.
 
-Our review revealed a high degree of variability in the statistical analyses.
-The most frequently used statistical method was to conduct regression analysis using a summation score of the syndemic conditions (N = `r sum(!is.na(summary_quantitative$score))`).
-Among studies employing this method, `r .score_data` did not use any other method to determine the degree of interaction between syndemic conditions.
-
+\
+Our review reveals a high degree of variability in the statistical analyses.
+The most frequently used statistical method is regression analysis using a summation score of the syndemic conditions (N = `r sum(!is.na(summary_quantitative$score))`).
+Among studies employing this method, `r .score_data` do not use any other method to determine the degree of interaction between syndemic conditions.
 In comparison, only `r .N_additivity` studies tried to evaluate departure from additivity on the additive and/or multiplicative scales, as recommended by Tsai [@tsai2015] to demonstrate synergy between syndemic conditions.
-
-Furthermore, some studies sought to get a better understanding on the mechanism of interaction between the syndemic conditions and the outcome by using mediation analysis (N = `r sum(!is.na(summary_quantitative$mediation))`), moderation analysis (N = `r sum(!is.na(summary_quantitative$moderation))`), Structural Equation Modeling (N = `r sum(!is.na(summary_quantitative$SEM))`) or path analysis (N = `r sum(!is.na(summary_quantitative$path))`).
-
-Moreover, `r english(.N_latent)` studies used latent variables modeling such as Exploratory/Confirmatory Factor Analysis, Latent Profile Analysis, Latent Class Analysis or Latent Transition Analysis.
-
-Using a different approach, `r english(sum(!is.na(summary_quantitative$network)))` studies conducted by Lee and colleagues [@lee2020; @Lee] used network analysis, in which syndemic is conceptualized as a network and the syndemic conditions as interconnected nodes reinforcing each others.
-
-Finally, other statistic analysis used to assess interaction were observed/expected ratio (N = `r sum(!is.na(summary_quantitative$O_E))`), cluster analysis (N = `r sum(!is.na(summary_quantitative$cluster))`), point-biserial correlation matrix (N= `r sum(!is.na(summary_quantitative$biserial))`) and synergy factor analysis (N=1).
+Examples of measures for assessing departure from additivity are relative excess risk due to interaction (RERI), attributable proportion due to interaction (AP), and the synergy index (S).
+Furthermore, some studies sought to obtain a better understanding of the mechanism of interaction between the syndemic conditions and the outcome by using mediation analysis (N = `r sum(!is.na(summary_quantitative$mediation))`), moderation analysis (N = `r sum(!is.na(summary_quantitative$moderation))`), Structural Equation Modelling (N = `r sum(!is.na(summary_quantitative$SEM))`) or path analysis (N = `r sum(!is.na(summary_quantitative$path))`).
+Additionally, `r english(.N_latent)` studies use latent variables modelling such as Exploratory/Confirmatory Factor Analysis, Latent Profile Analysis, Latent Class Analysis or Latent Transition Analysis.
+Using a different approach, `r english(sum(!is.na(summary_quantitative$network)))` studies conducted by Lee and colleagues [@lee2020; @Lee] use network analysis, in which syndemic is conceptualised as a network and the syndemic conditions as interconnected nodes reinforcing each other.
+Finally, other statistic analyses used to assess interaction are observed/expected ratio (N = `r sum(!is.na(summary_quantitative$O_E))`), cluster analysis (N = `r sum(!is.na(summary_quantitative$cluster))`), point-biserial correlation matrix (N= `r sum(!is.na(summary_quantitative$biserial))`) and synergy factor analysis (N=1).
 
@@
 
-In our sample of quantitative studies, we found only one study offering a mechanism of biological interaction @carrico2018 and two studies offering a mechanism of bio-social interaction [@Klein2011; @tapia2021].
+In our sample of quantitative studies, we found only one study offering a mechanism of biological interaction [@carrico2018] and two studies offering a mechanism of bio-social interaction [@Klein2011; @tapia2021].
 
 Carrico et al.
-showed that the combined effects of HIV infection and methamphetamine use were detrimental for the functioning of the Hypothalamic-Pituitary-Adrenal axis which is thought to play an important role in the reinforcing effect of stimulants.
+showed that the combined effects of HIV infection and methamphetamine use are detrimental for the functioning of the Hypothalamic-Pituitary-Adrenal axis which is thought to play an important role in the reinforcing effect of stimulants.
 
-Klein proposed that attitudes toward condom use was one of the key factors contributing to condomless sex and, subsequently, HIV infection.
-In their study, attitudes toward condoms was predicted by low self-esteem, as condom use represents a self-protecting mechanism, as well as by sexual preferences, substance use, race and education.
-Furthermore, childhood emotional neglect had a negative influence on self esteem thus indirectly contributing to sexual risk taking.
+Klein proposed that attitudes toward condom use is one of the key factors contributing to condomless sex and, subsequently, HIV infection.
+In their study, attitudes toward condoms are predicted by low self-esteem, as condom use represents a self-protecting mechanism, as well as by sexual preferences, substance use, race and education.
+Furthermore, childhood emotional neglect has a negative influence on self-esteem thus indirectly contributing to sexual risk taking.
 
 Finally, Tapia et al.
-demonstrated that a higher number of syndemic conditions was associated with elevation in rectal cytokines/chemokines relevant to HIV/STI transmission.
+demonstrated that a higher number of syndemic conditions are associated with elevation in rectal cytokines/chemokines relevant to HIV/STI transmission.
 This finding presents a pathway through which depression, alcohol use disorder, substance use and PTSD may increase the biological susceptibility to HIV/STI.
-Unfortunately, using solely a summation score to conduct regression analysis, no synergy between the conditions was evaluated.
+Unfortunately, using solely a summation score to conduct regression analysis, no synergy between the conditions is evaluated.
 
-Qualitative studies proposed mechanisms of bio-social interaction more often than quantitative studies as we identified `r english(sum(!is.na(summary_qualitative$bio_social_interaction)))` papers with such hypothesis of interaction.
+Qualitative studies propose mechanisms of bio-social interaction more often than quantitative studies.
+We identified `r english(sum(!is.na(summary_qualitative$bio_social_interaction)))` papers with such hypothesis of interaction [@Quinn; @Maiorana; @Lyons2013; @Chakrapani2019a; @Pollard2018a] .
 On the other hand, we did not find any qualitative paper exploring biological interaction.
 
-Stigma and structural inequalities were indicated by the five papers as the root causes of syndemic conditions and HIV risk behaviors.
+Stigma and structural inequalities are indicated by the five papers as the root causes of syndemic conditions and HIV risk behaviours.
 Maionara et al.
@@
 
-This finding of substance use as a coping mechanism was supported by the study by Pollard et al.
+This finding of substance use as a coping mechanism is supported by the study by Pollard et al.
 who found that maladaptive coping strategies to minority stress and the performative resistant space of the gay scene contributed to chemsex use [@Pollard2018a].
 
-For Black MSM, other sources of structural violence such as racial neighborhood segregation contributed, alongside poverty, unemployment, violence, unstable housing, incarceration and poor healthcare access to expectations surrounding masculinity which may conflict with the sexual orientation of BMSM, leading to internalised homophobia [@Quinn].
+For Black MSM, other sources of structural violence such as racial neighbourhood segregation contribute, alongside poverty, unemployment, violence, unstable housing, incarceration and poor healthcare access to expectations surrounding masculinity which may conflict with the sexual orientation of BMSM, leading to internalised homophobia [@Quinn].
 Internalised homophobia, in turn, may lead to poor mental health as well as to substance abuse and sexual risk taking as coping mechanisms.
-Moreover, the use of PrEP, perceived as a "gay pill" may negatively impact the use of PrEP in this community.
+Moreover, the use of PrEP, perceived as a 'gay pill' may negatively impact the use of PrEP in this community.
 Lyons et al.
-also showed that the marginalization of YMSM within their school, communities of origin and families resulted in a lack of gay-specific HIV prevention education, role-model and productive goal-related activities [@Lyons2013].
+also showed that the marginalisation of YMSM within their school, communities of origin and families resulted in a lack of gay-specific HIV prevention, education, role model and productive goal-related activities [@Lyons2013].
 The HIV-positive MSM youth in this study linked these factors to their HIV acquisition.
-Finally, [@Chakrapani2019a] showed the role of family support and communities of MSM to serve as resilience resource to counteract the negative effects of stigma and syndemic conditions.
+Finally, [@Chakrapani2019a] showed the role of family support and communities of MSM to serve as resilience resources to counteract the negative effects of stigma and syndemic conditions.
 
@@
 
-In nearly all of the quantitative studies, the syndemic conditions chosen by the authors were found to be associated to the outcomes of interest.
+In nearly all of the quantitative studies, the syndemic conditions chosen by the authors are associated with the outcomes of interest.
 
 However, some interesting discrepancies in the findings were found.
-On the topic of synergy, results were conflicting between studies.
-Chakrapani and colleagues found support for the three models of interacting epidemics (synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics) with the strongest support for the model of synergistically interacting epidemics [@Chakrapani2019].
-These findings were supported by other studies who found synergy when using significant product terms in the additive and/or multiplicative scales [@Chakrapani; @chandler2020; @Chandler2019; @tomori2018; @chuang2021; @bulled2021].
+On the topic of synergy, results are conflicting between studies.
+The findings of Chakrapani and colleagues support the three models of interacting epidemics (synergistically interacting epidemics, serially causal epidemics and mutually causal epidemics) with the strongest support for the model of synergistically interacting epidemics [@Chakrapani2019].
+These findings are supported by other studies that found synergy through departure from additivity, by using measures such as RERI, AP or S, or through a departure from multiplicativity by using significant product terms in the multiplicative scale [@Chakrapani; @chandler2020; @Chandler2019; @tomori2018; @chuang2021; @bulled2021].
 However, other studies found no synergy between the syndemic conditions using the same statistical approach [@Batchelder2019; @shuper2020; @Ferlatte2018a].
 
-Conflicting results were also found for MSMW.
+Conflicting results are also present for MSMW.
 Brandstrom and Pachankis found no clustering of syndemic conditions for MSMW [@Branstrom2018] while Mustanski et al.
-found a stronger clustering of syndemic conditions in YMSMW compared to YMSM[@Mustanski2014].
-Furthermore, Dyer et al.
-found more STI in the Black MSM compared to the Black MSMW [@dyer2020] and Ferlatte found more syndemic conditions in the MSM compared to the MSMW [@ferlatte2018], mainly driven by party drug use and treatment for depression or anxiety.
+found a stronger clustering of syndemic conditions in YMSMW compared to YMSM [@Mustanski2014].
+Furthermore, Black MSM in the study by Dyer et al.
+suffered from a higher burden of STI than Black MSMW [@dyer2020].
+Ferlatte et al.
+found more syndemic conditions in the MSM compared to the MSMW [@ferlatte2018], mainly driven by party drug use and treatment for depression or anxiety.
 Finally, in a sample of Latino MSMW, having two syndemic conditions predicted receptive condomless anal sex and STI diagnosis but not insertive nor vaginal condomless sex [@Munoz-Laboy2018].
@@
 In a longitudinal study [@Mustanski2017] Black MSM were found to have the highest HIV incidence while having a lower burden of syndemic condition than White MSM, raising the question of the need to focus on syndemic conditions specific to Black MSM.
-Interestingly, Bulled et al observed a synergy only for White MSM in their reanalysis of Stall's data [@bulled2021].
+Interestingly, Bulled observed a synergy only for White MSM in their reanalysis of Stall's data [@bulled2021].
 The authors proposed that, for racial minority MSM, structural disadvantage limiting access to healthcare may be more important than substance use and violence.
@@
 found an association between syndemic conditions and condomless anal sex but not with HIV diagnosis [@moeller].
-A similar pattern was found in a longitudinal study that found an association between syndemic conditions and sexual risk behaviors but not with HIV or STI incidence [@Mustanski2017].
+A similar pattern appears in a longitudinal study that found an association between syndemic conditions and sexual risk behaviours but not with HIV or STI incidence [@Mustanski2017].
 On the other hand, some authors found an association between syndemic conditions and HIV but not with condom use [@chuang2018].
 
-Alcohol misuse was inconsistently linked to risk taking.
-Card et al found no association between the AUDIT score and sexual risk behaviors [@Card2018] while another study using latent class analysis found that the class with alcohol misuse had a lower level of risk behaviors [@scheer2021].
-Nonetheless, alcohol misuse was found to be associated with PrEP non-adherence [@shuper2020].
+Alcohol misuse is inconsistently linked to risk taking.
+Card et al.
+found no association between the AUDIT score and sexual risk behaviours [@Card2018] while another study using latent class analysis found that the class with alcohol misuse has a lower level of risk behaviour [@scheer2021].
+Nonetheless, alcohol misuse is associated with PrEP non-adherence [@shuper2020].

### 2022-04-22 _bookdown_files/05-discussion.Rmd
Reviews [1st round]

@@
 To this end, we analysed 115 articles and found that the literature was both too homogeneous in some aspects while being not focused enough in other aspects.
-As we will discuss in more depth below, the location, design, subpopulation and outcomes lacked diversity.
+As we will discuss in more depth below, the location, design, subpopulations and outcomes lacked diversity.
 On the other hand, the syndemic conditions and ways of measurement were not standardised enough to ensure the robustness, reproducibility and comparability of the findings.
-Furthermore a substantial part of the literature doesn't provide empirical data to support one of the core tenets of syndemic theory - namely disease interaction- as has been pointed out in a previous review [@tsai2015].
+Furthermore, a substantial part of the literature does not provide empirical data to support one of the core tenets of syndemic theory---namely disease interaction---as has been pointed out in a previous review [@tsai2015].
 
@@
 
-The location of study is an aspect of syndemic literature suffering from too much homogeneity.
-Indeed `r percent(.North_America_studies/.N_QualQuant)` of studies are conducted in North America alone while all studies conducted in the Global South represents only `r percent(.GlobalSouth_studies/.N_QualQuant)` of our sample.
+The location of the study is an aspect of syndemic literature suffering from too much homogeneity.
+Indeed `r percent(.North_America_studies/.N_QualQuant)` of studies are conducted in North America alone while all studies conducted in the Global South represent only `r percent(.GlobalSouth_studies/.N_QualQuant)` of our sample.
 
@@
 First, under-representation of the Global South compromises our understanding of the health of MSM living in these countries.
-Furthermore, as pointed out by [@weaver2020], the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially in regard to mental health.
+Furthermore, as pointed out by [@weaver2020], the screening tool used to assess the presence of a syndemic condition in the Western context may not be efficient in another sociocultural setting, especially regarding mental health.
 As syndemics are driven by the sociocultural forces of a given place at a given time, these potential biases need to be addressed in order to conduct meaningful research outside Europe and North America.
@@
 Moreover, even for studies conducted in Europe and North America, a large portion of the studies conflate data from different cities, counties, states or even countries in order to obtain a sample big enough to conduct statistical analyses.
-However, geographical variations in syndemic burden are likely to be missed.
+However, geographical variations in syndemic burdens are likely to be missed.
 Migration of MSM to larger cities is a well-known phenomenon and thought to be an important part of syndemic production among MSM as well as a source of resilience [@stall2007; @Bruce2011].
-Differences in the density of gay social venues and peer organizations as well as exposure to discrimination and violence or an easier access to substances need to be taken into account when studying a syndemic.
-As [@shrestha2020] suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence the health of MSM.
+Differences in the density of gay social venues and peer organisations as well as exposure to discrimination and violence or an easier access to substances need to be taken into account when studying a syndemic.
+As Shresta et al.
+suggested, syndemic research needs to incorporate data from spatial epidemiology to better understand the interactions of socioeconomic forces in the physical space and how these forces can influence health [@shrestha2020].
+In their paper, they illustrate their framework with a "syringe-based syndemic" of HCV, HIV, and opioid-related deaths in West Virginia and describe how variables related to unique physical space such as local drug availability drove this syndemic.
 
@@
 Some concepts and experiences needed to understand syndemic production in MSM can only be studied through a qualitative approach.
-For example, the complex narratives surrounding drug use and its link to loneliness, marginalization, personal affirmation, resistance and lack of meaningful emotional connections [@Pollard2018a] would be hard to measure and model using quantitative data.
-As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to an over-simplification of diseases dynamics [@Tsai2018a].
-Mixed method are needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
-Unfortunately, our review only identified `r max(year_design$cumulative[year_design$design == "Mixed"])` studies employing such mixed methodology.
+For example, the complex narratives surrounding drug use and its link to loneliness, marginalisation, personal affirmation, resistance and lack of meaningful emotional connections [@Pollard2018a] would be hard to measure and model using quantitative data.
+As Tsai previously pointed out, the inevitable simplification needed to estimate statistical models may lead to an oversimplification of disease dynamics[@Tsai2018a].
+Mixed methods studies are needed to complement robust statistical estimation with insights on sociocultural mechanisms and on the lived experiences of people facing this clustering of adverse conditions.
+Our review only identified `r max(year_design$cumulative[year_design$design == "Mixed"])` studies employing such mixed methodology.
 Future research would benefit from generating and analysing qualitative data to support and enrich their quantitative findings.
@@
 Finally, we identified `r .N_int` interventional studies with mixed results.
-While co-targeting interconnected syndemic conditions is supported by a meta-analysis [@Pantalone2020], a better understanding of how syndemics operate may be needed before we are able to offer efficient syndemic-based interventions.
+The efficacy of interventions that target interconnected syndemic conditions is supported by a meta-analysis [@Pantalone2020], indicating that syndemic-based interventions hold promise for improving the health of marginalised populations.
+Nonetheless, the mixed results presented in our review probably reflect the current shallowness of our understanding of how syndemics operate in different populations across the globe.
+Therefore, we should strive to close this knowledge gap in order to improve the design of future interventions.
+However, we do not recommend researchers wait before designing and testing syndemic-based interventions as such interventions may also contribute to our understanding of disease interactions.
+In this regard, we share the view of Stall et al.
+in their response to Tsai's review [@Stall2015a].
+Given the harms caused to marginalised populations by a syndemic, we also agree with them when they state that"[w]e cannot wait until the methodological question of interaction is settled to develop interventions to address these co-morbidities within high risk populations.' Nonetheless only two interventions were conducted since this commentary was written seven years ago and we have made little progress in our understanding of disease interaction.
+This indicates an urgent need to move the field forward, both towards the comprehension of disease interaction and towards intervention development and implementation.
 
@@
 Studying the health of MSM poses a challenge regarding the diversity of this population.
-While nearly half of the studies included in our sample studied a subpopulation of MSM, the number of MSM subpopulation is such that most MSM subpopulation remains under-served.
-For example, Young Black MSM are specifically studied in `r .N_YBMSM` studies while representing 52% of the new HIV diagnosis among MSM aged 13-24 years in 2018 [@centerfordiseasecontrolandprevention2020].
+While nearly half of the studies included in our sample studied a subpopulation of MSM, the number of MSM subpopulations is such that most MSM subpopulations remain underserved.
+For example, Young Black MSM are specifically studied in `r .N_YBMSM` studies while representing 52% of the new HIV diagnosis among MSM aged 13--24 years in 2018 [@centerfordiseasecontrolandprevention2020].
 
-This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic condition such as HIV infection is even more concerning when considering that dual-minority identity may expose a person to different stressors and outcomes.
-For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to fewer syndemic conditions [@Mustanski2017] .
+This discrepancy between the number of studies focusing on a subpopulation and the very high prevalence of some syndemic conditions such as HIV infection is even more concerning when considering that dual-minority identity may expose a person to different stressors and outcomes.
+For example, some studies found that Black MSM had a higher rate of HIV seroconversion than White MSM while being exposed to fewer syndemic conditions [@Mustanski2017].
 These findings are supported by qualitative data suggesting that intersectional theory offers the context needed to understand syndemics among Black MSM which differ from syndemics among White MSM [@Quinn].
-Furthermore, the findings from Bulled and colleagues suggest that structural disadvantage may have more weight on the lives of Black MSM than individual factors such as substance use [@bulled2021]
+Furthermore, the findings from Bulled suggest that structural disadvantage may have more weight on the lives of Black MSM than individual factors such as substance use [@bulled2021].
+We agree with the views of these authors and believe that more attention should be given to structural disadvantages such as institutional racism and how it impacts the emergence of different syndemic conditions.
 
-MSMW are another example of an under-served population with conflicting results.
+MSMW are another example of an underserved population with conflicting results.
 In a cross-sectional study using syndemic sum count, Latino MSMW with two or more syndemic conditions had a 7.09 Odds Ratio to engage in receptive condomless anal sex but no statistically significant difference was found for insertive condomless anal sex or condomless vaginal sex [@Munoz-Laboy2018].
@@
 In the future, syndemic theory should thus seek to study the specificity of this population.
-First, there's a need to better conceptualize and define bisexuality in the field - should we still use solely behavior-based definition (as in MSMW) or should we incorporate a self-definition of one's sexual orientation ?
+First, there is a need to better conceptualise and define bisexuality in the field - should we still use solely a behaviour-based definition (as in MSMW) or should we incorporate a self-definition of one's sexual orientation?
 Then, researchers should aim to disaggregate data concerning MSMW/bisexual men from data concerning MSM/gay men whenever possible.
@@
 
-Finally transgender MSM were included in only one study in our sample.
+Finally, transgender MSM were included in only one study in our sample.
 As stated in our results, this is concerning, especially when every other study excludes transgender men by design.
 As such, this population of MSM is the one we know the least about.
-The study from Reisner and colleagues suggested that transgender MSM who had socially affirmed their gender were exposed to similar risk patterns as cisgender MSM [@Reisner2016a].
-The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence [@Testa2012], suicide attempts [@Haas2014], chlamydial and gonoccocal infections [@Pitasi2019], intimate partner violence [@peitzmeier2020] and HIV infection [@Becasen2019].
-Researchers should be encouraged to include transgender men in their studies and to conduct research focused on transgender MSM.
-Indeed, syndemic theory represents a promising framework for research on transgender men as its premises of social adversities producing and concentrating diseases in a population allows us to explore the health of transgender men without pathologizing them.
+It is striking that the number of studies we had to exclude due to merging transgender women and MSM was higher than the number of eligible studies found focusing on transgender men.
+This conflation of sex and gender has already been decried [@poteat2016] and contributed to our decision to exclude studies that reproduced this unfortunate practice.
+Linking transgender women and MSM on the assumption of shared biology and practices reduces transgender women to their birth assignation rather than their social identities.
+Conversely, excluding transgender MSM although they seem exposed to similar risk patterns as cisgender MSM [@Reisner2016a] because of their biological sex is, at best, revealing of a lack of knowledge about this population.
+Indeed, it seems counterproductive to give such precedent to the biological sex of participants over their social identifies while using a framework that considers diseases as socially caused.
+We believe that this practice is due to cissexist bias that should be avoided in future research.\
+The health of transgender men remains greatly understudied and the few available studies suggest high rates of adverse conditions such as violence, notably sexual violence [@Testa2012], suicide attempts [@Haas2014], chlamydia and gonococcal infections [@Pitasi2019], intimate partner violence [@peitzmeier2020] and HIV infection [@Becasen2019].
+Syndemic theory represents a promising framework for research on transgender men as its premises of social adversities producing and concentrating diseases in a population allows us to explore the health of transgender men without pathologising them.
 
@@
 
-There is a lack of consensus in the choice of syndemic conditions and the way they should be measured.
+There is a lack of consensus concerning the choice of syndemic conditions and the way they should be measured.
 We identified `r nrow(nodes)` different conditions in our quantitative sample, `r nrow(nodes %>% filter(studies == 1))` of them were only studied once.
-Despite this diversity of syndemic conditions, the impact of the seminal study by Stall et al.[@Stall2003] is striking.
+Despite this diversity of syndemic conditions, the impact of the seminal study by Stall et al.
+[@Stall2003] is striking.
 The conditions studied in that paper (depression, IPV, CSA and polysubstance use) are among the five most studied conditions in the field.
@@
 
-Some of these conditions are past event (e.g.
+Some of these conditions are past events (e.g.
 history of trauma or childhood sexual abuse) while most were current conditions.
@@
 Furthermore, studies diverge on what represents a syndemic condition and what may lead to the emergence of a syndemic.
-For example, childhood sexual abuse is mostly seen as a syndemic condition per se but may very well be a risk factor to the emergence of a syndemic, as hypothesized by some authors [@Herrick2013; @leblanc2021].
-The same question may be asked for discrimination, trauma, impulsivity, bullying, poor social support, loneliness, childhood abuse, poor healthcare access, etc.
-Qualitative and longitudinal studies are needed to distinguish between syndemic conditions and pathways to the emergence of a syndemic.
-Conflating the two in cross-sectional studies does very little to advance our understanding of syndemic theory or to implement public health interventions.
+For example, childhood sexual abuse is mostly seen as a syndemic condition per se but may very well be a risk factor to the emergence of a syndemic, as hypothesised by some authors [@Herrick2013; @leblanc2021].
+The same question may be asked for other conditions, including discrimination, trauma, impulsivity, bullying, poor social support, loneliness, childhood abuse, or poor access to healthcare.\
+Qualitative studies may help to distinguish between syndemic conditions and pathways to the emergence of a syndemic by drawing insights from the narratives of MSM.
+Life-story interviews, for example, offer the opportunity to explore how early challenges shaped the narratives and lives of individuals.
+Adam et al.
+conducted one such investigation and found one major pathway of syndemic production characterised by childhood adversity leading to depression, substance abuse and risk taking [@adam2018].
+Two minor pathways characterised by migration stress, or transition stress from home to college/work were also described.
+These findings are in line with Stall's theory of syndemic production in which early socially produced harms, beginning in childhood, continue through adolescence and adult life and are aggravated by the stresses associated with migration to large urban centres [@stall2007].
+Given that the childhood damages are socially produced, the experiences that produce a syndemic may differ across generations or subpopulations of MSM [@stall2007].
+As such, it may be possible that one condition, such as poor social support, participates in the emergence of a syndemic in a subpopulation of MSM while being part of a syndemic in another.
+As this theory is first and foremost a developmental theory of syndemic production, longitudinal studies may also help to disentangle pathways and syndemic conditions by surveying participants over an extended period of time.
+However, conflating the two in cross-sectional studies does very little to advance our understanding of syndemic theory or to contribute to the implementation of public health interventions.
 
-Furthermore, even when the same condition was studied in multiple papers, the differences in measurement methods impedes the reproducibility of the results.
-For example, a participant with a CESD score of 16, who uses marijuana on a regular basis and cocaine once in a while and who is a victim of sexual intimate partner violence.
-This man would have been classified as depressed in `r percent(sum(.depression_measurement$depression_cutoff == 16 & .depression_measurement$depression_scale_criteria == "CESD", na.rm = T)/sum(.depression_measurement$depression_scale_criteria == "CESD"))` of studies using the CESD, a polysubstance user in `r percent(sum(.polysubstance_measurement$polysubstance_number == "More than one category of substance use" & .polysubstance_measurement$polysubstance_marijuana == "Marijuana included")/nrow(.polysubstance_measurement))` of studies considering polysubstance use and as a victim of intimate partner violence in `r .IPV_prevalence$perc[["sexual IPV"]]` of studies taking IPV into account.
-In other words, the same person could have been classified as having 0, 1, 2 or even 3 syndemic conditions, depending on the study design.
-Considering that most studies use a summation score of the number of syndemic conditions to conduct regression analysis, it seems evident that the results would greatly vary according to the way the syndemic conditions are measured.
+Furthermore, even when the same condition was studied in multiple papers, the differences in measurement methods impede the reproducibility of the results.
+For example, let's imagine a survivor of sexual intimate partner violence with a CESD score of 16, who uses marijuana on a regular basis and cocaine occasionally.
+This man would have been classified as depressed in `r percent(sum(.depression_measurement$depression_cutoff == 16 & .depression_measurement$depression_scale_criteria == "CESD", na.rm = T)/sum(.depression_measurement$depression_scale_criteria == "CESD"))` of studies using the CESD, a polysubstance user in `r percent(sum(.polysubstance_measurement$polysubstance_number == "More than one category of substance use" & .polysubstance_measurement$polysubstance_marijuana == "Marijuana included")/nrow(.polysubstance_measurement))` of studies considering polysubstance use and as a survivor of intimate partner violence in `r .IPV_prevalence$perc[["sexual IPV"]]` of studies considering IPV.
+In other words, the same person could have been classified as having zero, one, two or even three syndemic conditions, depending on the study design.
+Considering that most studies use a summation score of the number of syndemic conditions to conduct regression analysis, it seems evident that the results would vary greatly according to the way the syndemic conditions are measured.
 
-It is beyond the scope of this paper to discuss in detail which syndemic conditions should be retained for future research and how to best measure them, but without a greater homogeneity in the field, the confidence and reproducibility of the results will remain an issue.
+It is beyond the scope of this paper to provide an exhaustive list of syndemic conditions researchers should use from now on or to determine the best scale or set of criteria to use to measure these conditions.
+An absolute answer to these questions is likely unrealistic due to variations across subpopulations and geographical settings.\
+However, we advise researchers to pay more attention to the local context and the lived experience of the population they seek to study when selecting syndemic conditions to investigate.
+Focus groups or Delphi studies interrogating peer navigators of grassroots organisation serving MSM may help to select more pertinent variables.
+Indeed, by drawing on their own experiences and knowledge of the public they work with on a daily basis, peer navigators may help researchers ground their research more effectively.\
+Additionally, exploratory qualitative studies may also serve as a first step in describing a syndemic arrangement before selecting syndemic conditions for a quantitative study.
+As Singer et al.
+stated in their 2020 paper:'[t]he syndemic relationship first needs to be observed then measured, not theorised and used to predict diseases outcomes [...]' [@Singer2020].
 
@@
 
-Taken together, `r percent(.HIV_number/nrow(summary_quantitative))` of the quantitative studies in our sample had an HIV-related outcome, whether in the form of sexual risk behaviors, HIV diagnosis, HIV screening, adherence to antiretroviral therapy, PrEP use, viral load or engagement in HIV care.
+Taken together, `r percent(.HIV_number/nrow(summary_quantitative))` of the quantitative studies in our sample had an HIV-related outcome, whether in the form of sexual risk behaviours, HIV diagnosis, HIV screening, adherence to antiretroviral therapy, PrEP use, viral load or engagement in HIV care.
 
 This omnipresence of HIV in syndemic literature applied to MSM is understandable.
-The first description of a syndemic, the SAVA syndemic, incorporated AIDS as part of a syndemic [@singer1996].
+The first description of a syndemic, the SAVA syndemic, included AIDS as part of a syndemic [@singer1996].
 Then, a few years later, the first paper on syndemic in the MSM population had HIV-related outcomes, in the form of HIV serostatus and CAS [@Stall2003].
-Furthermore MSM were the first and most severely affected population when the AIDS epidemic started [@decock2012].
+Furthermore, MSM were the first and most severely affected population when the AIDS epidemic started [@decock2012].
 Nowadays, male-to-male sexual contact still represents nearly 70% of the new HIV cases in the USA [@centerfordiseasecontrolandprevention2020].
-While we can't deny the importance of the HIV pandemic, notably for MSM, we would argue that HIV is not the only issue in need of attention.
+While we can't deny the importance of the HIV pandemic, notably for MSM, and especially in the Global South, where more research on syndemics and HIV is needed, we would argue that HIV is not the only issue in need of attention.
 
-Indeed, MSM are also disproportionately affected by, amongst others, suicide, anxiety, depression and substance use[@ross2018; @luo2017; @Medley2016].
+Indeed, MSM are also disproportionately affected by, among others, suicide, anxiety, depression and substance use [@ross2018; @luo2017; @Medley2016].
 Moreover, with the advances in antiretroviral therapy and the subsequent decline in HIV-related mortality, a Canadian study showed that gay men were more likely to die from suicide than from HIV in 2011 [@hottes2015].
-Even if the estimates Hottes' paper overestimated the mortality due to suicide among MSM, suicide would still be a leading cause of death in this population while being studied as an outcome in only `r sum(!is.na(.outcomes$outcome_suicide))` papers in our sample.
+Even if the estimates presented in Hottes' paper overestimate the mortality due to suicide among MSM, suicide would still be a leading cause of death in this population while being studied as an outcome in only `r sum(!is.na(.outcomes$outcome_suicide))` papers in our sample.
 
-Furthermore, when studying HIV as an outcome, we would argue that using condomless anal sex as a proxy should be reviewed and better proxies sought.
-Indeed, condomless anal sex was one of the criteria in `r .CAS_number` studies out of the `r sum(!is.na(.outcomes$outcome_sexual_risk))` with sexual risk behaviors as an outcome and `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CAS))` studies considered all form of condomless anal sex as a risk behavior.
+Furthermore, when studying HIV as an outcome, we would argue that using condomless anal sex as a proxy should be reviewed, and better proxies sought.
+Indeed, condomless anal sex was one of the criteria in `r .CAS_number` studies out of the `r sum(!is.na(.outcomes$outcome_sexual_risk))` with sexual risk behaviours as an outcome and `r sum(!is.na(.outcomes_sex_risk_measurement$outcome_CAS))` studies considered all forms of condomless anal sex as a risk behaviour.
 However, without refinement, this outcome fails to capture the changes in HIV prevention strategies such as PrEP or Treatment as Prevention (TasP).
-Only `r english(sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS)))` studies in our sample took PrEP use and an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.
+Only `r english(sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_VL_CAS))+sum(!is.na(.outcomes_sex_risk_measurement$outcome_PrEP_CAS)))` studies in our sample took PrEP use and/or an undetectable viral load into account when considering condomless anal sex as a risk factor for HIV acquisition.
+Moreover, of these papers the oldest was published in 2019 [@Batchelder2019] although the FDA has approved PrEP for HIV prevention in 2012.\
 When the first paper on syndemic theory applied to MSM was published, engaging in condomless anal sex would have led to a high risk of acquiring HIV.
-Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV [@calabrese2017] and our methodologies in syndemic research should reflect this evolution.
-In addition, qualitative research gives an insight into risk behaviors and offers a more nuanced view on this topic than a binary variable of consistent condom use for anal intercourse.
+Nowadays, people could be on PrEP, forego the use of a condom and still be at a very low risk of acquiring HIV [@calabrese2017].
+Our methodologies in syndemic research should reflect this evolution.
+In addition, qualitative research gives an insight into risk behaviours and offers a more nuanced view on this topic than a binary variable of consistent condom use for anal intercourse.
 One such paper published in 2017 showed that risk practices fell into different subjectivities such as active and consistent pursuit of condomless sex, lack of assertiveness to a partner's initiative of condomless anal sex and combination of episodic risk practices and reduction strategies [@Adam2017].
 Besides, some studies showed that participants with a greater number of syndemic conditions would engage more frequently in condomless anal sex while not being more likely to test positive for HIV [@Mustanski2017; @Pitpitan2016].
-On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated to self-reported HIV but not to condomless anal sex [@chuang2018].
-Taken together, we thus postulate that condomless anal sex should at least be replaced by "condomless anal sex without consistent PrEP use or with a detectable viral load" when an investigator seek to use sexual risk behaviors as an outcome.
-
-In summary, we recommend that future research should focus on other aspects of MSM's health than HIV infection and, when studying HIV as an outcome to prefer laboratory-based outcomes or more refined sexual risk variables than condomless anal sex.
+On the other hand, a paper from 2018 found that having a greater number of syndemic conditions was associated with self-reported HIV but not to condomless anal sex [@chuang2018].
+Taken together, we thus postulate that condomless anal sex should at least be replaced by "condomless anal sex without consistent PrEP use or with a detectable viral load" when an investigator seeks to use sexual risk behaviours as an outcome.
 
@@
 Two issues arise from this statistical approach.
-First, summation score are additive by essence, thus unsuitable to demonstrate an interaction [@tsai2015].
-Second, two psychometric assumptions are made by such a model : (1) the unidimensionality of the construct and (2) equal factor weighting [@Halkitis2013a].
-Put simply, using a summation score would imply that (1) every condition forms a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having an history of childhood sexual abuse would contribute equally to a syndemic).
+First, summation scores are additive by essence, thus unsuitable to demonstrate an interaction [@tsai2015].
+Second, two psychometric assumptions are made by such a model: (1) the unidimensionality of the construct and (2) equal factor weighting [@Halkitis2013a].
+Put simply, using a summation score would imply that (1) every condition forms a single construct and that (2) every condition contributes equally to said construct (which would mean for example that feeling depressed during the past 14 days and having a history of childhood sexual abuse would contribute equally to a syndemic).
 The unidimensionality aspect of the construct has received some empirical support by Mustanski et al.
 as well as by Starks et al.
-using respectively Structural Equation Modeling and Latent Class Analysis [@Mustanski2014; @Starks2014].
+using respectively Structural Equation Modelling and Latent Class Analysis [@Mustanski2014; @Starks2014].
 On the contrary, Leblanc et al.
 failed to construct a single latent syndemic variable in their analysis [@leblanc2021].
-Moreover constraining factor loadings to be equal resulted in worse fit in the studies by Mustanski and Starks.
+Moreover, constraining factor loadings to be equal resulted in worse fit in the studies by Mustanski and Starks.
 
 In short, the result of our review suggests that as much as `r percent(.score_data/nrow(summary_quantitative))` of the quantitative literature on syndemic theory applied to MSM doesn't empirically support the presence of a syndemic and employs questionable statistical assumptions.
-Those studies are more an exploration of psychosocial risk factors associated to HIV acquisition or progression than the holistic framework syndemic is supposed to be.
+Those studies are more an exploration of psychosocial risk factors associated with HIV acquisition or progression than the holistic framework syndemic is supposed to be.
 
-As mentioned in the results, two statistically distinct models may be envisioned apart from synergistically interacting epidemics : mutually causal epidemics and serially causal epidemics [@Tsai2018a].
-As such, mediation analysis, path analysis or structural equation modeling may prove useful to assess an interaction.
+As mentioned in the results, two statistically distinct models may be envisioned apart from synergistically interacting epidemics: mutually causal epidemics and serially causal epidemics [@Tsai2018a].
+As such, mediation analysis, path analysis or structural equation modelling may prove useful to assess an interaction.
 
-More recently, a new statistical approach inspired from research in psychopathology has been used to model syndemics : network analysis [@Lee; @lee2020].
+More recently, a new statistical approach inspired from research in psychopathology has been used to model syndemics: network analysis [@Lee; @lee2020].
 The core principle of this approach is that mental disorders arise from causal interactions between symptoms in a network [@borsboom2017].
 Applied to syndemic theory, a syndemic would then be the network and the various conditions would then be the nodes of the network.
-Furthermore, one of the benefits of this approach resides in the theoretical possibility to identify influential nodes in a network : nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network [@robinaugh2016].
-In short, in addition to being statistically sound and coherent with the model of mutually causal epidemics, network analysis could offer actionable data to improve the health of MSM by identifying which conditions should be prioritized for interventions [@Tsai2018a].
+Furthermore, one of the benefits of this approach resides in the theoretical possibility to identify influential nodes in a network: nodes that play a significant part in the activation of the network and that could be the prime target of an intervention in order to deactivate the network [@robinaugh2016].
+In short, in addition to being statistically sound and coherent with the model of mutually causal epidemics, network analysis could offer actionable data to improve the health of MSM by identifying which conditions should be prioritised for interventions [@Tsai2018a].
 
 We recommend that future research should abandon the summation score approach and attempt to clarify which model of interaction receives the most empirical support in order to implement effective public health interventions.
-Indeed as reminded by Chakrapani et al.
-the three models have different programmatic implications [@Chakrapani2019].
+Indeed, as reminded by Chakrapani et al., the three models have different programmatic implications [@Chakrapani2019].
 In the case of synergistically interacting epidemics, a single intervention may yield greater health improvement than if no interaction was present.
@@
 Social support was shown to moderate the effect of syndemic conditions on viral load, providing a significant protective effect [@friedman2016].
-Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic conditions on substance use showed that Black MSM with more social support were more likely to stay in the low-risk class or transitioning from the high risk class to the low-risk class [@turpin2020].
+Moreover, a paper using Latent Transition Analysis to evaluate the impact of syndemic conditions on substance use showed that Black MSM with more social support were more likely to stay in the low-risk class or transitioning from the high-risk class to the low-risk class [@turpin2020].
 However, Chakrapani et al.
@@
 
-On the topic of resilience resources, Zhang et al did not find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
+On the topic of resilience resources, Zhang et al.
+did not find evidence of a moderating effect of resilience on the relationship between syndemic conditions and physical activity [@Zhang2019].
 O'Leary et al.
-did not find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviors, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
-On the other hand, Kurtz et al found that, among MSM living with HIV, serosorting was positively associated with higher levels of two resilience factors : coping self-efficacy and positive coping skills [@Kurtz2012].
+did not find a buffering effect of resilience factors on the relationship between syndemic conditions and sexual risk behaviours, though optimism and education buffered the relationship between syndemic conditions and self-reported HIV status [@OLeary2014a].
+On the other hand, Kurtz et al.
+found that, among MSM living with HIV, serosorting was positively associated with higher levels of two resilience factors: coping self-efficacy and positive coping skills [@Kurtz2012].
 Similarly, Hart et al.
@@
 found a protective effect of most resilience resources identified against HIV [@woodward2017].
+Additionally, as pointed out by Namer and Razum, focusing on risk rather than resilience and survivorship poses the threat of alienating minority groups rather than prioritising them [@namer2021].
 
-We recommend that future work continues to explore the impact of resilience in partially counteracting syndemics to develop public health interventions that aim to foster resilience resources among MSM.
-Moreover, as pointed out by Namer and Razum, focusing on risk rather than resilience and survivorship poses the threat of alienating minority groups rather than prioritizing them [@namer2021].
+Minority stress represents another important framework as it explains how social stigma can get under the skin of minorised populations [@Meyer2003].
+Indeed, minority stress is fully integrated into theories of syndemic production among MSM [@stall2007; @singer2017].
+In these theories, the minority stress experienced by MSM leads to maladaptive coping strategies such as substance abuse, development of psychopathological conditions such as anxiety disorders and depression, hereby increasing sexual risk behaviours.
+Therefore, minority stress theory offers a mechanistic explanation of the second tenet of syndemic theory: the formation and clustering of diseases due to adverse social conditions.\
+As we recommend that future research better incorporate mental health issues, we believe that minority stress theory could be more often integrated into future analysis.\
+Additionally, another advantage of minority stress theory is that it avoids pathologising MSM by placing the focus on the social roots of mental health issues.
 
-Minority stress represents another interesting framework as it allows to explain how social stigma can get under the skin of minorized populations [@Meyer2003].
-
-Finally, although intersectionality was only used by two studies [@ferlatte2018; @Quinn] we believe the field would benefit from this framework.
-Indeed as shown in our results, there is some discrepancy in the results for MSM's subpopulation, especially for MSMW/bisexual men, Black MSM and Latino MSM.
+Finally, although intersectionality was only used by two studies [@ferlatte2018; @Quinn], we believe the field would benefit from this framework.
+Indeed, as shown in our results, there is some discrepancy in the results for subpopulations of MSM, especially for MSMW/bisexual men, Black MSM and Latino MSM.
 We believe that the inattention to systemic inequalities and structural disadvantage in the field may partly explain these discrepancies.
 In fact, only `r percent((summary_quantitative %>% filter(!is.na(unstable_housing) | !is.na(discrimination) | !is.na(incarceration) | !is.na(poverty)| !is.na (unemployment) | !is.na(healthcare_access)) %>% nrow())/nrow(summary_quantitative))` of the quantitative studies examine a structural condition such as discrimination, poverty or access to healthcare.
+However, as Bulled et al.
+reminds us, one of the goals of the syndemic framework is to "identify the role of power and structural injustices in creating pathology and recognising how pathology can intensify inequalities and multiple forms of oppression" [@bulled2022].
 
-Some scholars are skeptical on the usefulness of syndemic theory to intersectionality and question the possibility of a conversation between the two fields [@sangaramoorthy2021].
-As pertinent as the authors commentary is, we do believe in the possibility of making the two field converse.
+Some scholars are sceptical of the usefulness of syndemic theory to intersectionality and question the possibility of a conversation between the two fields [@sangaramoorthy2021].
+As pertinent as the authors' commentary is, we do believe in the possibility of bringing the two fields together.
 As Quinn pointed out in her response, incorporating an intersectional framework into syndemic research may address issues of power, oppression and structural violence, neglected thus far in the field [@quinn2021].
-Doing so, we may attend to some gap in the literature and disentangle the complex web of stigma and structural violence faced by sexual minority men, especially MSM situated at the intersection of multiple form of systemic discrimination such as racism, homophobia, biphobia, transphobia, classism, ableism or stigma against sex workers or people living with HIV.
+Doing so, we may address some gaps in the literature and disentangle the complex web of stigma and structural violence faced by sexual minority men, especially MSM situated at the intersection of multiple form of systemic discrimination such as racism, homophobia, biphobia, transphobia, classism, ableism or stigma against sex workers or people living with HIV.
+Furthermore, we agree with Bulled et al.
+when they argue that we need a syndemic analysis to understand clustering of diseases in marginalised populations [@bulled2022] .
+Moreover, given the results of this review, we share the opinion that most of the criticism from Sangaramoorthy and Benton stems from flaws in the way research in the field was conducted rather than flaws in the framework itself.
+
+## Recommendations
+
+In light of these results, we propose the following suggestions to improve the quality of research on syndemic theory applied to MSM:
+
+1.
+The local context should be taken into consideration more effectively by scholars.
+Analysis of the physical space through spatial epidemiology should be encouraged while merging data from different states and countries should be avoided as it blurs our understanding of the socioeconomic and cultural contexts in which MSM evolve.
+
+2.  More research should be conducted in the Global South, taking into account the difficulties involved when transposing some measures to different sociocultural contexts.
+
+3.
+Researchers should carefully select syndemic conditions to avoid unnecessary dispersion and to select the most relevant variables to MSM in a given place at a given time.
+Exploratory qualitative research, focus groups or Delphi survey should be used before trying to quantify a syndemic.
+
+4.  More attention should be paid to the selection of scales or sets of criteria when attempting to measure a syndemic condition to improve the reproducibility of the results.
+
+5.
+A better understanding of how diseases interact is urgently needed.
+First, future research should abandon the summation score approach and aim to determine the model of interaction with the most empirical support.
+Second, future research should elucidate the mechanisms of bio-social and bio-bio interactions.
+Qualitative and mixed method studies should be employed more often to achieve this.
+
+6.
+More attention should be given to structural disadvantage and systemic inequalities such as racism, biphobia, and transphobia in order to gain a better insight into racial disparities in syndemic production.
+Furthermore, the impact of monosexism and cissexism on the health of MSM should become a topic of investigation.
+
+7.
+Transgender men should be included in the population of MSM in future studies, rather than conflating sex and gender by excluding them while often including transgender women alongside MSM.
+Moreover, whenever possible, data from MSMW should be disaggregated to allow in-depth analysis.
+
+8.
+Researchers should seek to study other aspects of MSM's health than HIV infection.
+Mental health should no longer be neglected anymore.
+Moreover, when studying HIV infection, the outcome condomless anal sex should be replaced or refined.
+
+9.  Future work should continue to explore the impact of resilience in partially counteracting syndemics to develop public health interventions that aim to foster resilience resources among MSM.

### 2022-04-22 _bookdown_files/06-conclusion.Rmd
Reviews [1st round]

--- 2022-01-13 _bookdown_files/06-conclusion.Rmd
@@
-# Strengths and limitations
+# Strengths and Limitations
 
-This review is the first Scoping Review to map the current knowledge in Syndemic Theory applied to MSM.
-We charted and presented detailed data regarding the way research has been done.
-As such, we offer a precious insight and actionable recommendations for the future of the field.
+This review is the first scoping review to map the current knowledge in syndemic theory applied to MSM.
+We charted and presented detailed data regarding the existing literature.
+As such, we offer insight and actionable recommendations for the future of the field.
 Our search strategy of electronic databases was comprehensive and developed with the help of the director of health sciences library of our institution.
-We combined this database search with a secondary hand-search of references lists of the included studies.
+We combined this database search with a subsequent hand search of reference lists of the included studies.
 Moreover, we conducted a fully transparent and reproducible review.
-Other researchers may freely reuse our data and scripts to conduct their own work or use our database to identify papers pertinent for their research projects.
+Other researchers may freely reuse our data and scripts to conduct their own work or use our online visualisations to identify papers pertinent to their research projects.
 
-Nevertheless, even though we took several steps to ensure the comprehensiveness of our search strategy, we may still have missed some relevant literature.
+Nevertheless, though we took several steps to ensure the comprehensiveness of our search strategy, we may still have missed some relevant literature.
 Furthermore, one of our inclusion criteria was the centrality of syndemic theory to the screened paper.
-Although two reviewers screened a part of the studies independently, this criteria may be somewhat arbitrary and other researchers may have chosen to include papers we rejected or the contrary.
+Although two reviewers screened a part of the studies independently, this criterion may be somewhat arbitrary and other researchers may have chosen to include papers we rejected or the contrary.
 Finally, the usual limitations of a scoping review apply such as the lack of risk of bias and strength of evidence assessment.
 
-# Conclusion and recommendations
+# Conclusion
 
-Our review of syndemic research applied to MSM revealed some important limitations that must be addressed in future work.
-The field of syndemic research would benefit from studying more MSM subpopulations, in more diverse geographical settings, especially in the Global South.
-Furthermore, promising methods such as spatial epidemiology or network analysis may help to advance the field while methods such as summary count should be abandoned.
-More qualitative and mixed design may enhance our understanding of the complex interactions of a syndemic on the lived experiences of marginalized people.
-Outcomes should be less focused on sexual health and start to explore other potential impacts of a syndemic on health.
-Finally, conditions that constitute a syndemic should be more precisely defined and the measurement of those conditions should be more standardized while taking into account the difficulties of transposing some measures in different sociocultural contexts.
-
-Despite our critical stance on the current literature, we remained convinced that syndemic is a useful framework to study the health of marginalized populations in a holistic way and the current research still offered valuable insights on the health of MSM.
-It is vital that research continues to evolve in order to deepen our understanding and, by consequence, improve the health of marginalized populations worldwide.
+Despite our critical stance on the current literature, we remain convinced that syndemic theory is a useful framework to study the health of marginalised populations in a holistic way and the current research still offers valuable insights on the health of MSM.
+It is vital that research continue to evolve in order to deepen our understanding and, by consequence, improve the health of marginalised populations worldwide.
 

### 2022-04-22 _bookdown_files/index.Rmd
Reviews [1st round]

@@
 ---
-title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
+title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men: a Scoping Review"
 author: 
@@
 - "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
-- "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
+- "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-5653-615X"
 - "^3^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
@@
 link-citations: true
-csl: ["./_bookdown_files/social-science-and-medicine.csl"]
+csl: ["./_bookdown_files/apa.csl"]
 bibliography: ["./_bookdown_files/references.bib"]

### 2022-04-22 _bookdown_files/03-methodology.Rmd
Revisions

@@
 
-The complete protocol of this scoping review was published in 2020 [Author (2020 of publication) Details omitted for double-blind review.].
+The complete protocol of this scoping review was published in 2020 (Author, 2020. Details omitted for double-blind review).
 
@@
 Scripts, statistics, charts, tables and the present paper was generated using R [@rcoreteam2020], RStudio [@rstudioteam2020] and the appropriate packages.
-To ensure the complete transparency and reproducibility of this article, the lead author (M.O.) uploaded all data used to generate this article on Open Science Framework ([[DOI:[masked](DOI:%5Bmasked](DOI:%5Bmasked%5D(DOI:%5Bmasked)%7B.uri%7D){.uri} for the anonymity of the review])
+To ensure the complete transparency and reproducibility of this article, the lead author uploaded all data used to generate this article on Open Science Framework ([DOI: masked for the anonymity of the review])
 
